---
title: "CIDI Lifetime GAD: Diagnostic Algorithm (GLAD Study data)"
author: "Molly Davies and Alicia Peel"
date: "21/05/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Set up

Clear workspace
```{r clear workspace}
#rm(list = ls())
```

```{r load packages}
library(knitr)
library(tidyverse)
library(car)
library(psych)
library(lubridate)
library(broom)
library(ggfortify)
library(summarytools)
library(ggformula)
library(data.table)
```

```{r source path for reading/saving data}
#Source raw data directory (raw_path) & clean data export directory (cleaned_path)
source("../GLAD_data_path.R")
```

```{r read in cleaned CIDIA data}
CIDIA_file <- paste(raw_path, "CIDIA.rds", sep = "")

CIDIA.cc <- read_rds(CIDIA_file)
```

```{r visualise CIDIA data}
head(CIDIA.cc)
```

```{r create dataset of GAD diagnostic variables}
CIDIA.items <- CIDIA.cc %>%
  select(ID,
        cidia.felt_worried,
        cidia.felt_worried_more,
        cidia.longest_period_worry_years,
        cidia.longest_period_worry_months,
        cidia.longest_period_worry_categorical,
        cidia.worry_stronger_than_others,
        cidia.most_days,
        cidia.more_than_one_thing,
        cidia.difficult_to_stop,
        cidia.different_worries,
        cidia.couldnt_stop,
        cidia.difficult_to_control,
        cidia.restless,
        cidia.on_edge,
        cidia.tired,
        cidia.difficulty_concentrating,
        cidia.irritable,
        cidia.tense_muscles,
        cidia.trouble_sleeping,
        cidia.functioning,
        cidia.felt_worried_numeric,
        cidia.felt_worried_more_numeric,
        cidia.worry_stronger_than_others_numeric,
        cidia.most_days_numeric,
        cidia.more_than_one_thing_numeric,
        cidia.difficult_to_stop_numeric,
        cidia.different_worries_numeric,
        cidia.couldnt_stop_numeric,
        cidia.difficult_to_control_numeric,
        cidia.restless_numeric,
        cidia.on_edge_numeric,
        cidia.tired_numeric,
        cidia.difficulty_concentrating_numeric,
        cidia.irritable_numeric,
        cidia.tense_muscles_numeric,
        cidia.trouble_sleeping_numeric,
        cidia.functioning_numeric)
```

```{r recode as NAs}
#Change all prefer not to answers and don't knows to NA
CIDIA.items[CIDIA.items == "Don't know"] <- NA
CIDIA.items[CIDIA.items == "Prefer not to answer"] <- NA
CIDIA.items[CIDIA.items == "Seen but not answered"] <- NA
CIDIA.items[CIDIA.items == -88] <- NA
CIDIA.items[CIDIA.items == -99] <- NA
CIDIA.items[CIDIA.items == -77] <- NA
```

# Cleaning variables

## Longest period of worry
This variable was changed during GLAD data collection from categorical to continuous response.
New variable cidia.longest_period_worry_categorical_combined created which recodes all continuous responses as 
categorical, and allows for easy analysis of all participants together.

### Longest period of worry - continuous (combined)
The continuous variable consisted of months and years, which need to be added together.
```{r longest_period_worry combine years and months}
#Visualise data
summary(CIDIA.items$cidia.longest_period_worry_years)
summary(CIDIA.items$cidia.longest_period_worry_months)
#Convert months to years
CIDIA.items$cidia.longest_period_worry_months.years <- CIDIA.items$cidia.longest_period_worry_months/12
#Combine month & year values for total time of longest period of worry
CIDIA.items$cidia.longest_period_worry_combined.unc <- rowSums(cbind(CIDIA.items$cidia.longest_period_worry_months.years, CIDIA.items$cidia.longest_period_worry_years))
#Round the new variable
CIDIA.items$cidia.longest_period_worry_combined <- round(CIDIA.items$cidia.longest_period_worry_combined.unc, digits = 2)
summary(CIDIA.items$cidia.longest_period_worry_combined)
```

### Longest period of worry categorical + continuous (all)
Combine categorical and continuous variables into a single categorical variable.
```{r create longest_period_worry_categorical.combined}
#Create column
CIDIA.items$cidia.longest_period_worry_categorical_combined.unc <- NA
#Combine columns into single categorical variable
CIDIA.items$cidia.longest_period_worry_categorical_combined.unc <- with(CIDIA.items,
                                                                     ifelse(is.na(cidia.longest_period_worry_categorical) 
                                                                            & !is.na(cidia.longest_period_worry_combined),
                                                                       (cut(cidia.longest_period_worry_combined,
                                                                           breaks = c(0, 5.9, 12, 60, Inf),
                                                                           labels = c(1, 2, 3, 5))),
                                                                       cidia.longest_period_worry_categorical))

```

```{r recode longest_period_worry_categorical.combined}
#Recode factor
CIDIA.items$cidia.longest_period_worry_categorical_combined <-
  recode_factor(CIDIA.items$cidia.longest_period_worry_categorical_combined.unc,
                             "1" = "Less than 6 months",
                             "2" = "Between 6 and 12 months",
                             "3" = "Between 1 and 5 years", 
                             "4" = "More than 5 years", 
                             "5" = "All of my life/as long as I can remember", 
                             "6" = "Prefer not to answer")
```

```{r longest_period_worry_categorical summary, results='asis'}
summarytools::freq(CIDIA.items$cidia.longest_period_worry_categorical_combined,
                   style = "rmarkdown")
```

```{r compare total NA in combined variable to originals}
#There should be fewer NAs in the categorical_combined variable than in the categorical and continuous variables alone
sum(is.na(CIDIA.items$cidia.longest_period_worry_categorical)) #Categorical
sum(is.na(CIDIA.items$cidia.longest_period_worry_combined)) #Continuous
sum(is.na(CIDIA.items$cidia.longest_period_worry_categorical_combined)) #Combined

```

# DSM-5 GAD Diagnostic Algorithm

A.   Excessive  anxiety  and  worry  (apprehensive  expectation),  occurring  more  days  than not for at least 6 months, about a number of events or activities (such as work or school performance).

B.  The  individual finds it difficult to control the worry.

C.  The  anxiety and  worry are  associated  with  three  (or more)  of the following  six symptoms (with at least some symptoms having been present for more days than not for thepast 6 months)
  1.   Restlessness or feeling  keyed up or on edge.
  2.   Being easily fatigued.
  3.   Difficulty concentrating or mind going  blank.
  4.   Irritability.
  5.   Muscle tension.
  6.   Sleep  disturbance  (difficulty  falling  or  staying  asleep,  or  restless,  unsatisfyingsleep).

D.  The anxiety, worry, or physical symptoms cause clinically significant distress*** or impairment in social,  occupational,  or other important areas of functioning.

E.  The disturbance  is  not attributable to the  physiological  effects  of a substance  (e.g.,  adrug of abuse,  a medication) or another medical condition  (e.g.,  hyperthyroidism).***

F.   The  disturbance  is  not  better  explained  by  another  mental  disorder***

*The CIDIA does not measure these items

# Screening variables
The GAD screening questions include:
1) Anxiety or worry (criterion A)
2) Duration of 6 months or more


*How the screening works*
If the participant responds No (0) to both anxiety and worry variables they are scored 0 for diagnosis and skip the remaining questions.

If the participant reports either anxiety or worry but doesn't report symptoms lasting 6 months or longer, then:
    i) If they signed up before April 2020, they skipped the remaining questions
    ii) If they signed up during or after April 2020, they are asked follow-up questions about duration in months. If they report symptoms lasting at least 1 month, they continue to the remaining questions to assess subthreshold GAD. They have the option to select 6 months in this question, so researchers conducting analyses on datasets post April 2020 should take this into account.


Create variable for worry and duration screen
```{r variable for worry and duration screener}
CIDIA.items <- CIDIA.items %>% 
  mutate(cidia.screener_numeric = 
           case_when(
             cidia.felt_worried == "No" & cidia.felt_worried_more == "No" 
             ~ 0,
             (cidia.felt_worried == "Yes" | cidia.felt_worried_more == "Yes") & 
               cidia.longest_period_worry_categorical_combined == "Less than 6 months"
             ~ 0,
             (cidia.felt_worried == "Yes" | cidia.felt_worried_more == "Yes") &
               (cidia.longest_period_worry_categorical_combined == "Between 6 and 12 months" |
                  cidia.longest_period_worry_categorical_combined == "Between 1 and 5 years" |
                  cidia.longest_period_worry_categorical_combined == "More than 5 years" |
                  cidia.longest_period_worry_categorical_combined == "All of my life/as long as I can remember") ~ 1
           ))

summary(as.factor(CIDIA.items$cidia.screener_numeric))

```

## Criterion variables
In each case where more than 1 response fulfills a diagnostic criterion, a new variable is created.

Note: These criterion variables will have a large number of NAs if the screening criteria aren't met, as the question is not displayed in these cases. This is accounted for in the algorithm.

A. Excessive  anxiety  and  worry  (apprehensive  expectation), occurring  more  days  than not for at least 6 months, about a number of events or activities (such as work or school performance).
```{r variable for criterion A}
CIDIA.items <- CIDIA.items %>% 
  mutate(cidia.criterion_A_numeric =
           case_when(
             cidia.felt_worried == "No" & cidia.felt_worried_more == "No" & cidia.worry_stronger_than_others == "No" ~ 0,
             cidia.most_days == "No" ~ 0,
             (cidia.more_than_one_thing == "No" & cidia.different_worries == "No") ~ 0,
             #A. Excessive  anxiety  and  worry
             (cidia.felt_worried == "Yes" | cidia.felt_worried_more == "Yes" | cidia.worry_stronger_than_others == "Yes") &
               #A. occurring  more  days  than not (frequency)
               cidia.most_days == "Yes" &
               #A. about a number of events or activities
               (cidia.more_than_one_thing == "Yes" | cidia.different_worries == "Yes") ~ 1
         ))

freq(CIDIA.items$cidia.criterion_A_numeric)
```

```{r variable for criterion B}

```

```{r}
 #A. Excessive anxiety/worry
                                             (cidia.felt_worried == "Yes" | cidia.felt_worried_more == "Yes" | cidia.worry_stronger_than_others == "Yes") &
                                               #A. at least 6 months (duration)
                                               (cidia.longest_period_worry_categorical_combined == "Between 6 and 12 months" |
                                                  cidia.longest_period_worry_categorical_combined == "Between 1 and 5 years" |
                                                  cidia.longest_period_worry_categorical_combined == "More than 5 years" |
                                                  cidia.longest_period_worry_categorical_combined == "All of my life/as long as I can remember") &
                                               #A. occurring  more  days  than not (frequency)
                                               (cidia.most_days == "Yes") &
                                               #A. about a number of events or activities (such as work or school performance)
                                               (cidia.more_than_one_thing == "Yes" | cidia.different_worries == "Yes") & 
                                               #B. The  individual finds it difficult to control the worry.
                                               (cidia.difficult_to_stop == "Yes" | cidia.couldnt_stop == "Yes" | cidia.difficult_to_control == "Yes") &
                                               #D. The anxiety, worry, or physical symptoms cause impairment in functioning.
                                               (cidia.functioning == "A lot" | cidia.functioning == "Some"), #A lot (3) or some (2)
                                             1, 0
```


## Missingness

```{r variable for symptom missingness}
#Missing responses/no information on any of the core symptoms of anxiety
#(Later, if no.info > 1 overall, then lifetime GAD will be coded as NA)

CIDIA.items$no.info<-0
#+1 to missingness score if all 3 questions assessing criterion A excessive anxiety/worry are left unanswered
CIDIA.items$no.info<-with(CIDIA.items,
                             ifelse(is.na(cidia.felt_worried) & is.na(cidia.felt_worried_more) 
                                    & is.na(cidia.worry_stronger_than_others), 1, 0
                                    )
                             )
#+1 to missingness score if duration (criterion A), frequency (criterion A), or functioning (criterion D) are unanswered
CIDIA.items$no.info <- with(CIDIA.items,
                               ifelse(is.na(cidia.most_days) |
                                        is.na(cidia.longest_period_worry_categorical_combined) |
                                        is.na(cidia.functioning),
                                      no.info + 1, 0
                                                )
                                      )
#+1 to missingness score if both questions assessing number of worries (criterion A) are missed
CIDIA.items$no.info <- with(CIDIA.items,
                               ifelse(is.na(cidia.more_than_one_thing) &
                                        is.na(cidia.different_worries),
                                      no.info + 1, 0
                                                )
                                      )
#+1 to missingness score if all 3 questions assessing difficulty in controlling worry (criterion B) are missed
CIDIA.items$no.info <- with(CIDIA.items,
                               ifelse(is.na(cidia.difficult_to_stop) &
                                        is.na(cidia.couldnt_stop) &
                                        is.na(cidia.difficult_to_control),
                                      no.info + 1, 0
                                                )
                                      )

summary(as.factor(CIDIA.items$no.info))
```

```{r variable for core GAD criteria}
#Create variable for meeting all core DSM GAD criteria
CIDIA.items$cidia.anxiety_screen.calc <- with(CIDIA.items,
                                           ifelse(
                                             #A. Excessive anxiety/worry
                                             (cidia.felt_worried == "Yes" | cidia.felt_worried_more == "Yes" | cidia.worry_stronger_than_others == "Yes") &
                                               #A. at least 6 months (duration)
                                               (cidia.longest_period_worry_categorical_combined == "Between 6 and 12 months" |
                                                  cidia.longest_period_worry_categorical_combined == "Between 1 and 5 years" |
                                                  cidia.longest_period_worry_categorical_combined == "More than 5 years" |
                                                  cidia.longest_period_worry_categorical_combined == "All of my life/as long as I can remember") &
                                               #A. occurring  more  days  than not (frequency)
                                               (cidia.most_days == "Yes") &
                                               #A. about a number of events or activities (such as work or school performance)
                                               (cidia.more_than_one_thing == "Yes" | cidia.different_worries == "Yes") & 
                                               #B. The  individual finds it difficult to control the worry.
                                               (cidia.difficult_to_stop == "Yes" | cidia.couldnt_stop == "Yes" | cidia.difficult_to_control == "Yes") &
                                               #D. The anxiety, worry, or physical symptoms cause impairment in functioning.
                                               (cidia.functioning == "A lot" | cidia.functioning == "Some"), #A lot (3) or some (2)
                                             1, 0
                                           )
                                          )

summary(as.factor(CIDIA.items$cidia.anxiety_screen.calc))

```



```{r variable for restless & keyed up/on edge}
#Create variable for restlessness or keyed up/on edge (which is a single symptom criterion in the DSM for GAD)
CIDIA.items$cidia.restless_on_edge <- NA
CIDIA.items$cidia.restless_on_edge <- with(CIDIA.items,
                                                    ifelse(
                                                      (!is.na(cidia.restless) 
                                                       & cidia.restless == "Yes") |
                                                        (!is.na(cidia.on_edge) 
                                                         & cidia.on_edge == "Yes"),
                                                      1, 0
                                                    ))

CIDIA.items$cidia.restless_on_edge <- with(CIDIA.items,
                                                    ifelse(is.na(cidia.restless) 
                                                           & is.na(cidia.on_edge), 
                                                    NA, cidia.restless_on_edge)
                                                    )

summary(as.factor(CIDIA.items$cidia.restless_on_edge))

```

Calculate anxiety symptoms 'score' (the number of criterion C symptoms endorsed)

C.  The  anxiety and  worry are  associated  with  three  (or more)  of the following  six symptoms (with at least some symptoms having been present for more days than not for thepast 6 months)
  1.   Restlessness or feeling  keyed up or on edge.
  2.   Being easily fatigued.
  3.   Difficulty concentrating or mind going  blank*.
  4.   Irritability.
  5.   Muscle tension.
  6.   Sleep  disturbance  (difficulty  falling  or  staying  asleep,  or  restless,  unsatisfyingsleep).
  
*CIDIA doesn't measure mind going blank

```{r anxiety symptom score}
#Create score for anxiety symptoms 
#Do NOT use 'is.na' for these as then you cannot +1 to it. Use the no.info item for NA. 
CIDIA.items$cidia.lifetime_anxiety_total.calc<-0
#Criterion C.1 - Restlessness or feeling keyed up or on edge
CIDIA.items$cidia.lifetime_anxiety_total.calc<-with(CIDIA.items, 
                                    ifelse(!is.na(cidia.restless_on_edge) 
                                           & cidia.restless_on_edge > 0, 
                                           cidia.lifetime_anxiety_total.calc + 1, cidia.lifetime_anxiety_total.calc))
#Criterion C.2 - Being easily fatigued
CIDIA.items$cidia.lifetime_anxiety_total.calc<-with(CIDIA.items,
                                    ifelse(!is.na(cidia.tired) 
                                           & cidia.tired =="Yes",
                                           cidia.lifetime_anxiety_total.calc + 1, cidia.lifetime_anxiety_total.calc))
#Criterion C.3 - Difficulty concentrating
CIDIA.items$cidia.lifetime_anxiety_total.calc<-with(CIDIA.items,
                                    ifelse(!is.na(cidia.difficulty_concentrating) 
                                           & cidia.difficulty_concentrating == "Yes",
                                           cidia.lifetime_anxiety_total.calc + 1, cidia.lifetime_anxiety_total.calc))
#Criterion C.4 - Irritability
CIDIA.items$cidia.lifetime_anxiety_total.calc<-with(CIDIA.items, 
                                    ifelse(!is.na(cidia.irritable) &
                                             cidia.irritable == "Yes", 
                                           cidia.lifetime_anxiety_total.calc + 1, cidia.lifetime_anxiety_total.calc))
#Criterion C.5 - Muscle tension
CIDIA.items$cidia.lifetime_anxiety_total.calc<-with(CIDIA.items, 
                                    ifelse(!is.na(cidia.tense_muscles) & cidia.tense_muscles == "Yes", 
                                           cidia.lifetime_anxiety_total.calc + 1, cidia.lifetime_anxiety_total.calc))
#Criterion C.6 - Sleep disturbance
CIDIA.items$cidia.lifetime_anxiety_total.calc<-with(CIDIA.items, 
                                    ifelse(!is.na(cidia.trouble_sleeping) 
                                           & cidia.trouble_sleeping == "Yes", 
                                           cidia.lifetime_anxiety_total.calc + 1, cidia.lifetime_anxiety_total.calc))

summary(as.factor(CIDIA.items$cidia.lifetime_anxiety_total.calc))

```

```{r anxiety symptom NA count score}
#Create score to calculate how many missing values are in the anxiety symptom scores

CIDIA.items$cidia.lifetime_anxiety_total.calc.NA<-0

CIDIA.items$cidia.lifetime_anxiety_total.calc.NA<-with(CIDIA.items, 
                                    ifelse(is.na(cidia.restless_on_edge), 
                                           cidia.lifetime_anxiety_total.calc.NA + 1, cidia.lifetime_anxiety_total.calc.NA))

CIDIA.items$cidia.lifetime_anxiety_total.calc.NA<-with(CIDIA.items,
                                    ifelse(is.na(cidia.tired),
                                           cidia.lifetime_anxiety_total.calc.NA + 1, cidia.lifetime_anxiety_total.calc.NA))

CIDIA.items$cidia.lifetime_anxiety_total.calc.NA<-with(CIDIA.items,
                                    ifelse(is.na(cidia.difficulty_concentrating),
                                           cidia.lifetime_anxiety_total.calc.NA + 1, cidia.lifetime_anxiety_total.calc.NA))

CIDIA.items$cidia.lifetime_anxiety_total.calc.NA<-with(CIDIA.items, 
                                    ifelse(is.na(cidia.irritable), 
                                           cidia.lifetime_anxiety_total.calc.NA + 1, cidia.lifetime_anxiety_total.calc.NA))

CIDIA.items$cidia.lifetime_anxiety_total.calc.NA<-with(CIDIA.items, 
                                    ifelse(is.na(cidia.tense_muscles), 
                                           cidia.lifetime_anxiety_total.calc.NA + 1, cidia.lifetime_anxiety_total.calc.NA))

CIDIA.items$cidia.lifetime_anxiety_total.calc.NA<-with(CIDIA.items, 
                                    ifelse(is.na(cidia.trouble_sleeping), 
                                           cidia.lifetime_anxiety_total.calc.NA + 1, cidia.lifetime_anxiety_total.calc.NA))

summary(as.factor(CIDIA.items$cidia.lifetime_anxiety_total.calc.NA))

```

```{r lifetime GAD variable}
CIDIA.items$cidia.lifetime_anxiety.calc <- with(CIDIA.items,
                                                      ifelse(
                                                        no.info > 0, NA,
                                                        ifelse((!is.na(cidia.lifetime_anxiety_total.calc) & cidia.lifetime_anxiety_total.calc > 2)
                                                               & (!is.na(cidia.anxiety_screen.calc) & 
                                                                    cidia.anxiety_screen.calc == 1), 1, 0
                                                               )
                                                        )
                                                      )

summary(as.factor(CIDIA.items$cidia.lifetime_anxiety.calc))
```

```{r recode as NA missingness in anxiety score}
#Ppts are coded NA if they didn't respond to the number of questions that could have met diagnostic criteria 
#(diagnostic criteria = 3 or more symptoms)
#e.g. if the ppt endorsed 2 symptoms, but didn't respond to minimum 1 other question, then they are coded as NA

CIDIA.items$cidia.lifetime_anxiety.calc <- with(CIDIA.items,
                                                      ifelse(cidia.lifetime_anxiety_total.calc == 2 & cidia.lifetime_anxiety_total.calc.NA > 0,
                                                             NA, cidia.lifetime_anxiety.calc))

CIDIA.items$cidia.lifetime_anxiety.calc <- with(CIDIA.items,
                                                      ifelse(cidia.lifetime_anxiety_total.calc == 1 & cidia.lifetime_anxiety_total.calc.NA > 1,
                                                             NA, cidia.lifetime_anxiety.calc))

CIDIA.items$cidia.lifetime_anxiety.calc <- with(CIDIA.items,
                                                      ifelse(cidia.lifetime_anxiety_total.calc == 0 & cidia.lifetime_anxiety_total.calc.NA > 2,
                                                             NA, cidia.lifetime_anxiety.calc))

summary(as.factor(CIDIA.items$cidia.lifetime_anxiety.calc))

```

```{r recode as 0 if responded no to screeners}

#If both screening Qs are 0, lifetime anxiety is coded as 0 (not NA)
CIDIA.items$cidia.lifetime_anxiety.calc <- with(CIDIA.items,
                                                      ifelse(
                                                        is.na(cidia.lifetime_anxiety.calc), 
                                                        ifelse(
                                                        cidia.screener_numeric == 0, 
                                                        0, cidia.lifetime_anxiety.calc), 
                                                        cidia.lifetime_anxiety.calc
                                                               )
                                                        )

summary(as.factor(CIDIA.items$cidia.lifetime_anxiety.calc))

```

```{r merge lifetime anxiety variable into dataset}

CIDIA <- CIDIA.items[,c("ID", "cidia.anxiety_screen.calc", "cidia.restless_on_edge", "cidia.lifetime_anxiety_total.calc", "cidia.lifetime_anxiety_total.calc.NA", "cidia.lifetime_anxiety.calc")]

CIDIA.cc <- left_join(CIDIA.cc, CIDIA, by = "ID")
```

##Recode calculated lifetime_anxiety variables

```{r lifetime_anxiety_screen recode}
summary(CIDIA.cc$cidia.anxiety_screen.calc)

#Store old variable as unc
CIDIA.cc$cidia.anxiety_screen.calc.unc <- NA
CIDIA.cc$cidia.anxiety_screen.calc.unc <- CIDIA.cc$cidia.anxiety_screen.calc

CIDIA.cc$cidia.anxiety_screen.calc <- recode_factor(CIDIA.cc$cidia.anxiety_screen.calc.unc,
                             "0" = "No",
                             "1" = "Yes")
```

```{r lifetime_anxiety_screen summary, results='asis'}
summarytools::freq(CIDIA.cc$cidia.anxiety_screen.calc,
                   style = "rmarkdown")
```

```{r lifetime_anxiety recode}
summary(as.factor(CIDIA.cc$cidia.lifetime_anxiety.calc))

#Rename variable and recode
CIDIA.cc$cidia.diagnosis <- recode_factor(CIDIA.cc$cidia.lifetime_anxiety.calc,
                             "0" = "No GAD diagnosis",
                             "1" = "GAD diagnosis")
#Create numeric diagnosis variable
CIDIA.cc$cidia.diagnosis_numeric <- CIDIA.cc$cidia.lifetime_anxiety.calc
```

```{r lifetime_anxiety_screen summary, results='asis'}
summarytools::freq(CIDIA.cc$cidia.diagnosis,
                   style = "rmarkdown")
```

## Clean CIDIA dataset

```{r clean CIDIA dataframe}

CIDIA.clean <- CIDIA.cc %>%
  select(ID,
        cidia.felt_worried,
        cidia.felt_worried_more,
        cidia.longest_period_worry_years,
        cidia.longest_period_worry_months,
        cidia.longest_period_worry_categorical,
        cidia.worry_stronger_than_others,
        cidia.most_days,
        cidia.more_than_one_thing,
        cidia.difficult_to_stop,
        cidia.different_worries,
        cidia.couldnt_stop,
        cidia.difficult_to_control,
        cidia.restless,
        cidia.on_edge,
        cidia.tired,
        cidia.difficulty_concentrating,
        cidia.irritable,
        cidia.tense_muscles,
        cidia.trouble_sleeping,
        cidia.functioning,
        cidia.anxiety_screen.calc, 
        cidia.restless_on_edge, 
        cidia.lifetime_anxiety_total.calc,
        cidia.lifetime_anxiety_total.calc.NA,
        cidia.diagnosis,
        cidia.diagnosis_numeric)

#Export into a rds file:
saveRDS(object = CIDIA.clean, file = paste0(cleaned_path, "CIDIA_cleaned.rds"))

# Saves the R data including the recoding
#save.image(file = paste0(cleaned_path, "GLAD_CIDIA_clean.RData")
```
