---
title: "CIDI Lifetime GAD: Diagnostic algorithm (GLAD Study data)"
author: "Molly R. Davies and Alicia J. Peel"
date: "21/05/2020"
output: html_document
---

This script runs an algorithm adapted from the Composite International Diagnostic Interview - Short form (CIDI-SF), based on DSM-5 diagnostic criteria, to ascertain likely lifetime diagnosis of generalised anxiety disorder (GAD)using the GLAD Study and COPING NIHR BioResource (NBR) data..

Algorithm developed for the paper "Comparison of algorithm-based versus single-item phenotyping measures of depression and anxiety disorders in the GLAD Study cohort" - Davies et al (in prep).

Full description of the algorithms and scripts written for the paper can be accessed at:
https://github.com/mollyrdavies/GLAD-Diagnostic-algorithms.git

Script written by M. R. Davies and Alicia J. Peel.
Email:  molly.davies@kcl.ac.uk

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Set up

Clear workspace
```{r clear workspace}
rm(list = ls())
```

Select which cohorts to run the algorithms on by changing the value to TRUE (include) or FALSE (exclude). If multiple cohorts selected, data will be combined into a single dataset.

*Note: Currently only GLAD and COPING_NBR cohorts included in algorithms.
```{r select cohorts}
GLAD = TRUE
COPING_NBR = TRUE
```

```{r load packages}
library(tidyverse)
library(psych)
library(summarytools)
```

```{r source path for reading/saving data}
#Source raw data directory (raw_path) & clean data export directory (cleaned_path)
source("../../../DF1.0_data_path.R")
```


# CIDIA pre-processing

```{r read in CIDIA data}
if (GLAD == TRUE) {
#Read GLAD data
glad_cidia_file <- paste(glad_raw_path, "cidia_glad.rds", sep = "")
glad_cidia <- read_rds(glad_cidia_file)
}

if (COPING_NBR == TRUE) {
#Read COPING NBR data
coping_nbr_cidia_file <- paste(coping_nbr_raw_path, "cidia_coping_nbr.rds", sep = "")
coping_nbr_cidia <- read_rds(coping_nbr_cidia_file)
}
```

```{r CIDIA add sample column}
if (GLAD == TRUE) {
glad_cidia$sample <- "GLAD"
}
if (COPING_NBR == TRUE) {
coping_nbr_cidia$sample <- "NBR"
}
```

```{r GLAD CIDIA renaming}
if (GLAD == TRUE) {
glad_cidia_renamed <- glad_cidia %>% 
  drop_na(externalDataReference) %>% 
  distinct(externalDataReference, .keep_all = TRUE) %>% 
  rename("ID" = "externalDataReference")
}
```

```{r visualise renamed GLAD CIDIA data}
if (GLAD == TRUE) {
skimr::skim(glad_cidia_renamed)
}
```

```{r COPING CIDIA renaming}
if (COPING_NBR == TRUE) {
coping_nbr_cidia_renamed <- coping_nbr_cidia %>% 
  drop_na(subjectid) %>% 
  distinct(subjectid, .keep_all = TRUE) %>% 
  rename("ID" = "subjectid",
         #"COPING_ID" = "externalDataReference", #not extracted, add if needed
         "cidia.longest_period_continued_kind.3" = "cidia.longest_period_continued_kind.3.1", #Different from GLAD
         "cidia.longest_period_continued_kind.4" = "cidia.longest_period_continued_kind.3" #Different from GLAD
         )
}
```

```{r visualise renamed COPING CIDIA data}
if (COPING_NBR == TRUE) {
  skimr::skim(coping_nbr_cidia_renamed)
}
```

```{r rename GLAD CIDIA dataset (if GLAD only)}
if (GLAD == TRUE & COPING_NBR == FALSE) {
  CIDIA_renamed.combined <- glad_cidia_renamed
}
```

```{r rename COPING NBR CIDIA dataset (if COPING NBR only)}
if (GLAD == FALSE & COPING_NBR == TRUE) {
  CIDIA_renamed.combined <- coping_nbr_cidia_renamed
}
```

```{r merge GLAD & COPING NBR CIDIA datasets}
if (GLAD == TRUE & COPING_NBR == TRUE) {
  CIDIA_renamed.combined <- bind_rows(
    glad_cidia_renamed,
    coping_nbr_cidia_renamed
    )
}
```

```{r skim combined CIDIA dataset}
skimr::skim(CIDIA_renamed.combined)
```

```{r clean dataset}
CIDIA <- CIDIA_renamed.combined %>%
  select(-externalDataReference) %>% 
  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
  mutate_if(is.numeric, ~na_if(., -99)) %>%
  mutate_if(is.numeric, ~na_if(., -77)) %>%
  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to answer"))
```

# Cleaning variables

## Longest period of worry
This variable was changed during GLAD data collection from categorical to continuous response.
New variable cidia.longest_period_continued_kind.2_combined created which recodes all continuous responses as 
categorical, and allows for easy analysis of all participants together.

### Longest period of worry - continuous (combined)
The continuous variable consisted of months and years, which need to be added together.
```{r GLAD longest_period_worry combine years and months}
if (GLAD == TRUE) {
#Visualise data
summary(CIDIA$cidia.longest_period_continued_kind)
summary(CIDIA$cidia.longest_period_continued_kind.1)

#Convert months to numeric
CIDIA$cidia.longest_period_continued_kind.1 <- as.numeric(CIDIA$cidia.longest_period_continued_kind.1)

#Convert months to years
CIDIA$cidia.longest_period_continued_kind.1.years <- CIDIA$cidia.longest_period_continued_kind.1/12

#Set value for 'months as years' variable to zero if the other contains a value
CIDIA.months.years<-data.frame(cbind(CIDIA$cidia.longest_period_continued_kind.1.years, CIDIA$cidia.longest_period_continued_kind))
names(CIDIA.months.years)<-c("cidia.longest_period_continued_kind.1.years", "cidia.longest_period_continued_kind")

#Recode 'months as years' variable to 0 if years variable has a value 
CIDIA.months.years<-CIDIA.months.years %>%
  mutate(cidia.longest_period_continued_kind.1.years =
           case_when(
             is.na(cidia.longest_period_continued_kind.1.years) & is.na(cidia.longest_period_continued_kind) ~ NA_real_,
             is.na(cidia.longest_period_continued_kind.1.years) & !is.na(cidia.longest_period_continued_kind) ~ 0,
             !is.na(cidia.longest_period_continued_kind.1.years) ~ cidia.longest_period_continued_kind.1.years
           ),
         cidia.longest_period_continued_kind = 
           case_when(
             is.na(cidia.longest_period_continued_kind) & is.na(cidia.longest_period_continued_kind.1.years) ~ NA_real_,
             is.na(cidia.longest_period_continued_kind) & !is.na(cidia.longest_period_continued_kind.1.years) ~ 0, 
             !is.na(cidia.longest_period_continued_kind) ~ cidia.longest_period_continued_kind))
         
#Combine month & year values for total time of longest period of worry
CIDIA$cidia.longest_period_worry_combined.unc <- rowSums(cbind(CIDIA.months.years$cidia.longest_period_continued_kind.1.years, CIDIA.months.years$cidia.longest_period_continued_kind))

#Round the new variable
CIDIA$cidia.longest_period_worry_combined <- round(CIDIA$cidia.longest_period_worry_combined.unc, digits = 2)

#Summarise new variable
summary(CIDIA$cidia.longest_period_worry_combined)

sum(with(CIDIA,
         ifelse(!is.na(cidia.longest_period_worry_combined) & cidia.longest_period_worry_combined > 50, 1, 0)
         )
)
}

#If COPING only, add variable to COPING_NBR data so below script works
if (GLAD == FALSE & COPING_NBR == TRUE) {
  CIDIA$cidia.longest_period_worry_combined <- NA
}
```

### Longest period of worry categorical - combined (COPING cohorts only)
The COPING baseline includes a follow-up question asking participants who selected "less than 6 months" how long (in months) was their longest period of worry. There was an option to select 6 months, which would qualify for a diagnosis.
```{r COPING combine longest period of worry categorical variables}
if (COPING_NBR == TRUE) {
CIDIA <- CIDIA %>% 
  mutate(cidia.longest_period_continued_kind.2_combined =
           case_when(
             cidia.longest_period_continued_kind.2 > 1 ~ cidia.longest_period_continued_kind.2,
             cidia.longest_period_continued_kind.2 == 1 & cidia.longest_period_continued_kind.3 == 6 ~ 2,
             cidia.longest_period_continued_kind.2 == 1 & cidia.longest_period_continued_kind.3 < 6 ~ cidia.longest_period_continued_kind.2,
             cidia.longest_period_continued_kind.2 == 1 & is.na(cidia.longest_period_continued_kind.3) ~ cidia.longest_period_continued_kind.2
           ))
summary(as.factor(CIDIA$cidia.longest_period_continued_kind.2))
summary(as.factor(CIDIA$cidia.longest_period_continued_kind.2_combined))
}

#IF GLAD only, transfer GLAD kind.2 variable so below script works
if (GLAD == TRUE & COPING_NBR == FALSE) {
  CIDIA$cidia.longest_period_continued_kind.2_combined <- CIDIA$cidia.longest_period_continued_kind.2
}
```


### Longest period of worry categorical + continuous (all)
Combine categorical and continuous variables into a single categorical variable.
```{r create longest_period_worry_categorical.combined}
#Create column
CIDIA$cidia.longest_period_continued_kind.2_combined.unc <- NA
#Combine columns into single categorical variable
CIDIA$cidia.longest_period_continued_kind.2_combined.unc <- with(
  CIDIA,
  ifelse(is.na(cidia.longest_period_continued_kind.2_combined) 
         & !is.na(cidia.longest_period_worry_combined),
         (cut(cidia.longest_period_worry_combined,
              breaks = c(0, 0.49, 1, 5, Inf),
              labels = c(1, 2, 3, 5))),
         cidia.longest_period_continued_kind.2_combined))

```

```{r recode longest_period_worry_categorical.combined}
#Recode factor
CIDIA$cidia.longest_period_worry_combined_cleaned <-
  recode_factor(CIDIA$cidia.longest_period_continued_kind.2_combined.unc,
                             "1" = "Less than 6 months",
                             "2" = "Between 6 and 12 months",
                             "3" = "Between 1 and 5 years", 
                             "4" = "More than 5 years", 
                             "5" = "All of my life/as long as I can remember", 
                             "6" = "Prefer not to answer")
```

```{r longest_period_worry_categorical summary, results='asis'}
summarytools::freq(CIDIA$cidia.longest_period_worry_combined_cleaned,
                   style = "rmarkdown")
```

```{r compare total NA in combined variable to originals}
#There should be fewer NAs in the categorical_combined variable than in the categorical and continuous variables alone
sum(is.na(CIDIA$cidia.longest_period_continued_kind.2_combined)) #Categorical
sum(is.na(CIDIA$cidia.longest_period_worry_combined)) #Continuous
sum(is.na(CIDIA$cidia.longest_period_worry_combined_cleaned)) #Combined

```

# DSM-5 GAD diagnostic criteria

A.   Excessive  anxiety  and  worry  (apprehensive  expectation),  occurring  more  days  than not for at least 6 months, about a number of events or activities (such as work or school performance).

B.  The  individual finds it difficult to control the worry.

C.  The  anxiety and  worry are  associated  with  three  (or more)  of the following  six symptoms (with at least some symptoms having been present for more days than not for thepast 6 months)
  1.   Restlessness or feeling  keyed up or on edge.
  2.   Being easily fatigued.
  3.   Difficulty concentrating or mind going  blank.
  4.   Irritability.
  5.   Muscle tension.
  6.   Sleep  disturbance  (difficulty  falling  or  staying  asleep,  or  restless,  unsatisfying sleep).

D.  The anxiety, worry, or physical symptoms cause clinically significant distress*** or impairment in social,  occupational,  or other important areas of functioning.

E.  The disturbance  is  not attributable to the  physiological  effects  of a substance  (e.g.,  adrug of abuse,  a medication) or another medical condition  (e.g.,  hyperthyroidism).***

F.   The  disturbance  is  not  better  explained  by  another  mental  disorder***

*The CIDIA does not measure these items

# Screening variables
The GAD screening questions include:
1) Anxiety or worry (criterion A)
2) Duration of 6 months or more


*How the screening works*
If the participant responds No (0) to both anxiety and worry variables they are scored 0 for diagnosis and skip the remaining questions.

If the participant reports either anxiety or worry but doesn't report symptoms lasting 6 months or longer, then:
    i) If they signed up before April 2020, they skipped the remaining questions
    ii) If they signed up during or after April 2020, they are asked follow-up questions about duration in months. If they report symptoms lasting at least 1 month, they continue to the remaining questions to assess subthreshold GAD. They have the option to select 6 months in this question, so researchers conducting analyses on datasets post April 2020 should take this into account.


Create variable for worry and duration screen
```{r variable for worry and duration screener}
CIDIA <- CIDIA %>% 
  mutate(cidia.screener_numeric = 
           case_when(
             cidia.tense_anxious_felt_worried == 0 & cidia.lot_people_things_situation == 0 
             ~ 0,
             (cidia.tense_anxious_felt_worried == 1 | cidia.lot_people_things_situation == 1) & 
               cidia.longest_period_worry_combined_cleaned == "Less than 6 months"
             ~ 0,
             (cidia.tense_anxious_felt_worried == 1 | cidia.lot_people_things_situation == 1) &
               (cidia.longest_period_worry_combined_cleaned == "Between 6 and 12 months" |
                  cidia.longest_period_worry_combined_cleaned == "Between 1 and 5 years" |
                  cidia.longest_period_worry_combined_cleaned == "More than 5 years" |
                  cidia.longest_period_worry_combined_cleaned == "All of my life/as long as I can remember") 
             ~ 1
           ))
summary(as.factor(CIDIA$cidia.screener_numeric))

#Duration criteria variable created for curiosity, to check N participants that didn't meet this criterion
CIDIA <- CIDIA %>% 
  mutate(cidia.duration_numeric = 
           case_when(
             cidia.tense_anxious_felt_worried == 0 & cidia.lot_people_things_situation == 0 
             ~ -99,
             cidia.longest_period_worry_combined_cleaned == "Less than 6 months"
             ~ 0,
             (cidia.longest_period_worry_combined_cleaned == "Between 6 and 12 months" |
                  cidia.longest_period_worry_combined_cleaned == "Between 1 and 5 years" |
                  cidia.longest_period_worry_combined_cleaned == "More than 5 years" |
                  cidia.longest_period_worry_combined_cleaned == "All of my life/as long as I can remember") ~ 1
           ))

summary(as.factor(CIDIA$cidia.duration_numeric))

```

# Criterion variables
In each case where more than 1 response fulfills a diagnostic criterion, a new variable is created.

Note: These criterion variables will have a large number of NAs if the screening criteria aren't met, as the question is not displayed in these cases. This is accounted for in the algorithm.

A. Excessive  anxiety  and  worry  (apprehensive  expectation), occurring more days than not for at least 6 months, about a number of events or activities.
Note: Worry and duration are not included here, as the screener variable accounts for those responses.
```{r variable for criterion A}
CIDIA <- CIDIA %>% 
  mutate(cidia.criterion_A_numeric =
           case_when(
             cidia.did_you_worry_most_days == 0 ~ 0,
             (cidia.job_security_failing_health == 0 & cidia.mind_worries_time == 0) ~ 0,
               #A. occurring  more  days  than not (frequency)
               cidia.did_you_worry_most_days == 1 &
               #A. about a number of events or activities
               (cidia.job_security_failing_health == 1 | cidia.mind_worries_time == 1) ~ 1
         ))

freq(CIDIA$cidia.criterion_A_numeric)
```

B.  The  individual finds it difficult to control the worry.
```{r variable for criterion B}
CIDIA <- CIDIA %>% 
  mutate(cidia.criterion_B_numeric = 
           case_when(
             cidia.stop_worrying_difficult_find == 0 & 
               (cidia.matter_hard_strong_put == 0 | cidia.matter_hard_strong_put == 1 | cidia.matter_hard_strong_put == 2) & 
               (cidia.control_difficult_find_worry == 0 | cidia.control_difficult_find_worry == 1 | cidia.control_difficult_find_worry == 2) ~ 0,
             cidia.stop_worrying_difficult_find == 1 | cidia.matter_hard_strong_put == 3 | cidia.control_difficult_find_worry == 3 ~ 1
           ))

freq(CIDIA$cidia.criterion_B_numeric)
```

Create variable for restlessness or keyed up/on edge (which is a single symptom criterion in the DSM for GAD)
```{r variable for restless & keyed up/on edge (criterion C)}
CIDIA <- CIDIA %>% 
  mutate(cidia.restless_on_edge_numeric =
           case_when(
             cidia.restless == 0 & cidia.keyed_up_or_on_edge == 0 ~ 0,
             cidia.restless == 1 | cidia.keyed_up_or_on_edge == 1 ~ 1
           ))

summary(as.factor(CIDIA$cidia.restless_on_edge_numeric))

```


Calculate anxiety symptoms 'score' (the number of criterion C symptoms endorsed)

C.  The  anxiety and  worry are  associated  with  three  (or more)  of the following  six symptoms (with at least some symptoms having been present for more days than not for thepast 6 months)
  1.   Restlessness or feeling  keyed up or on edge.
  2.   Being easily fatigued.
  3.   Difficulty concentrating or mind going  blank*.
  4.   Irritability.
  5.   Muscle tension.
  6.   Sleep  disturbance  (difficulty  falling  or  staying  asleep,  or  restless,  unsatisfyingsleep).
  
*CIDIA doesn't measure mind going blank
```{r anxiety symptom score (criterion C)}
#Create score for anxiety symptoms 
#Do NOT use 'is.na' for these as then you cannot +1 to it. Use the no.info item for NA. 
CIDIA$cidia.criterion_C_score_numeric<-0
#Criterion C.1 - Restlessness or feeling keyed up or on edge
CIDIA$cidia.criterion_C_score_numeric<-with(CIDIA, 
                                    ifelse(!is.na(cidia.restless_on_edge_numeric) 
                                           & cidia.restless_on_edge_numeric > 0, 
                                           cidia.criterion_C_score_numeric + 1, cidia.criterion_C_score_numeric))
#Criterion C.2 - Being easily fatigued
CIDIA$cidia.criterion_C_score_numeric<-with(CIDIA,
                                    ifelse(!is.na(cidia.easily_tired) 
                                           & cidia.easily_tired ==1,
                                           cidia.criterion_C_score_numeric + 1, cidia.criterion_C_score_numeric))
#Criterion C.3 - Difficulty concentrating
CIDIA$cidia.criterion_C_score_numeric<-with(CIDIA,
                                    ifelse(!is.na(cidia.mind_difficulty_keeping) 
                                           & cidia.mind_difficulty_keeping == 1,
                                           cidia.criterion_C_score_numeric + 1, cidia.criterion_C_score_numeric))
#Criterion C.4 - Irritability
CIDIA$cidia.criterion_C_score_numeric<-with(CIDIA, 
                                    ifelse(!is.na(cidia.more_irritable_than_usual) &
                                             cidia.more_irritable_than_usual == 1, 
                                           cidia.criterion_C_score_numeric + 1, cidia.criterion_C_score_numeric))
#Criterion C.5 - Muscle tension
CIDIA$cidia.criterion_C_score_numeric<-with(CIDIA, 
                                    ifelse(!is.na(cidia.having_tense_sore_or_aching_muscles) & cidia.having_tense_sore_or_aching_muscles == 1, 
                                           cidia.criterion_C_score_numeric + 1, cidia.criterion_C_score_numeric))
#Criterion C.6 - Sleep disturbance
CIDIA$cidia.criterion_C_score_numeric<-with(CIDIA, 
                                    ifelse(!is.na(cidia.often_having_trouble_falling_or_staying_asleep) 
                                           & cidia.often_having_trouble_falling_or_staying_asleep == 1, 
                                           cidia.criterion_C_score_numeric + 1, cidia.criterion_C_score_numeric))

summary(as.factor(CIDIA$cidia.criterion_C_score_numeric))

```

D. The anxiety, worry, or physical symptoms cause impairment in functioning.
```{r variable for criterion D}
CIDIA <- CIDIA %>% 
  mutate(cidia.criterion_D_numeric =
           case_when(
             cidia.including_study_problems_interfere == 0 | cidia.including_study_problems_interfere == 1 ~ 0,
             cidia.including_study_problems_interfere == 2 | cidia.including_study_problems_interfere == 3 ~ 1
           ))
freq(CIDIA$cidia.criterion_D_numeric)
```

# Missingness

```{r variable for missingness}
#Missing responses/no information on any of the core symptoms of anxiety
#(Later, if no.info > 1 overall, then lifetime GAD will be coded as NA)

CIDIA$no.info<-0
#+1 to missingness score if criterion A variable is NA
CIDIA$no.info<-with(CIDIA,
                             ifelse(is.na(cidia.criterion_A_numeric), 
                                    no.info + 1, no.info)
                             )
#+1 to missingness score if difficulty controlling worry (criterion B) variable is NA
CIDIA$no.info<-with(CIDIA,
                             ifelse(is.na(cidia.criterion_B_numeric), 
                                    no.info + 1, no.info)
                             )
#+1 to missingness score if functioning (criterion D) is unanswered
CIDIA$no.info <- with(CIDIA,
                               ifelse(is.na(cidia.criterion_D_numeric),
                                      no.info + 1, no.info)
                                      )

summary(as.factor(CIDIA$no.info))
```


```{r anxiety symptom NA count score}
#Create score to calculate how many missing values are in the anxiety symptom scores

CIDIA$cidia.criterion_C_score_numeric.NA<-0

CIDIA$cidia.criterion_C_score_numeric.NA<-with(CIDIA, 
                                    ifelse(is.na(cidia.restless_on_edge_numeric), 
                                           cidia.criterion_C_score_numeric.NA + 1, cidia.criterion_C_score_numeric.NA))

CIDIA$cidia.criterion_C_score_numeric.NA<-with(CIDIA,
                                    ifelse(is.na(cidia.easily_tired),
                                           cidia.criterion_C_score_numeric.NA + 1, cidia.criterion_C_score_numeric.NA))

CIDIA$cidia.criterion_C_score_numeric.NA<-with(CIDIA,
                                    ifelse(is.na(cidia.mind_difficulty_keeping),
                                           cidia.criterion_C_score_numeric.NA + 1, cidia.criterion_C_score_numeric.NA))

CIDIA$cidia.criterion_C_score_numeric.NA<-with(CIDIA, 
                                    ifelse(is.na(cidia.more_irritable_than_usual), 
                                           cidia.criterion_C_score_numeric.NA + 1, cidia.criterion_C_score_numeric.NA))

CIDIA$cidia.criterion_C_score_numeric.NA<-with(CIDIA, 
                                    ifelse(is.na(cidia.having_tense_sore_or_aching_muscles), 
                                           cidia.criterion_C_score_numeric.NA + 1, cidia.criterion_C_score_numeric.NA))

CIDIA$cidia.criterion_C_score_numeric.NA<-with(CIDIA, 
                                    ifelse(is.na(cidia.often_having_trouble_falling_or_staying_asleep), 
                                           cidia.criterion_C_score_numeric.NA + 1, cidia.criterion_C_score_numeric.NA))

summary(as.factor(CIDIA$cidia.criterion_C_score_numeric.NA))

```

# DSM-5 GAD diagnostic algorithm

```{r lifetime GAD diagnosis variable}
CIDIA <- CIDIA %>% 
  mutate(cidia.diagnosis_numeric =
           case_when(
             #Ppts are coded NA if they didn't respond to any of the screening questions
             is.na(cidia.screener_numeric) ~ NA_real_,
             #Ppts are coded 0 if they didn't meet screening criteria
             cidia.screener_numeric == 0 ~ 0,
             #Ppts are coded NA if they didn't respond to symptom questions that may have met diagnostic criteria
             cidia.criterion_C_score_numeric == 2 & cidia.criterion_C_score_numeric.NA > 0 ~ NA_real_,
             cidia.criterion_C_score_numeric == 1 & cidia.criterion_C_score_numeric.NA > 1 ~ NA_real_,
             cidia.screener_numeric == 1 & (cidia.criterion_C_score_numeric == 0 & cidia.criterion_C_score_numeric.NA > 2) ~ NA_real_,
             #Ppts are coded NA if they met screening criteria but didn't respond to at least one of the other criteria
             cidia.screener_numeric == 1 & no.info > 0 ~ NA_real_,
             #Ppts are coded 0 if they don't meet one of the core criteria
             cidia.criterion_A_numeric == 0 |
               cidia.criterion_B_numeric == 0 |
               cidia.criterion_C_score_numeric < 3 |
               cidia.criterion_D_numeric == 0 ~ 0,
             #Ppts are coded 1 if they meet all DSM-5 GAD criteria
             cidia.screener_numeric == 1 &
               cidia.criterion_A_numeric == 1 &
               cidia.criterion_B_numeric == 1 &
               cidia.criterion_C_score_numeric >= 3 &
               cidia.criterion_D_numeric == 1 ~ 1
           ))

freq(CIDIA$cidia.diagnosis_numeric)

```

```{r cidia.diagnosis recode}
#Rename variable and recode
CIDIA$cidia.diagnosis <- recode_factor(CIDIA$cidia.diagnosis_numeric,
                             "0" = "No GAD diagnosis",
                             "1" = "GAD diagnosis")
freq(CIDIA$cidia.diagnosis)
```

```{r lifetime_anxiety_screen summary, results='asis'}
summarytools::freq(CIDIA$cidia.diagnosis,
                   style = "rmarkdown")
```

# Clean CIDIA dataset

```{r clean CIDIA dataframe}

#Export into a rds file:
saveRDS(object = CIDIA, file = paste0(cleaned_path, "CIDIA_cleaned.rds"))

# Saves the R data including the recoding
#save.image(file = paste0(cleaned_path, "GLAD_CIDIA_clean.RData")
```
