---
title: "Lifetime DSM-5 panic disorder: Diagnostic algorithm (GLAD Study data)"
author: "Molly R. Davies"
date: "24/10/2020"
output: html_document
---

This script runs an algorithm based on DSM-5 diagnostic criteria, to ascertain likely lifetime diagnosis of panic disorder using the GLAD Study data.

Algorithm developed for the paper "Comparison of algorithm-based versus single-item phenotyping measures of depression and anxiety disorders in the GLAD Study cohort" - Davies et al (in prep).

Full description of the algorithms and scripts written for the paper can be accessed at:
https://github.com/mollyrdavies/GLAD-Diagnostic-algorithms.git

Script written by M. R. Davies.
Email:  molly.davies@kcl.ac.uk

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Set up

Clear workspace
```{r clear workspace}
rm(list = ls())
```

```{r load packages}
library(psych)
library(tidyverse)
library(summarytools)
```

```{r source path for reading/saving data}
#Source raw data directory (raw_path) & clean data export directory (cleaned_path)
source("../ANXCMBD_data_path.R")
```

```{r read in cleaned PAD data}
PAD_file <- paste(renamed_path, "PAD.rds", sep = "")

PAD.cc <- read_rds(PAD_file)
```

```{r visualise PAD data}
head(PAD.cc)
```

```{r create dataset of PAD diagnostic variables}

#Create dataset of all variables needed for PAD diagnosis
PAD.items <- PAD.cc %>%
    mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
    mutate_if(is.numeric, ~na_if(., -99)) %>%
    mutate_if(is.numeric, ~na_if(., -77)) %>%
    mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
    mutate_if(is.factor, ~na_if(., "Don't know")) %>%
    mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
    mutate_if(is.factor, ~na_if(., "Prefer not to answer"))
```

# DSM-5 panic disorder diagnostic criteria

A.   Recurrent unexpected panic attacks. A panic attack is an abrupt surge of intense fear or intense discomfort that reaches a peak within minutes, and during which time four (or more) of the following symptoms occur; Note: The abrupt surge can occur from a calm state or an anxious state.
1.	Palpitations, pounding heart, or accelerated heart rate.
2.	Sweating.
3.	Trembling or shaking.
4.	Sensations of shortness of breath or smothering.
5.	Feelings of choking.
6.	Chest pain or discomfort.
7.	Nausea or abdominal distress.
8.	Feeling dizzy, unsteady, light-headed, or faint.
9.	Chills or heat sensations.
10.	Paresthesias (numbness or tingling sensations).
11.	Derealization (feelings of unreality) or depersonalization (being detached from one¬self).
12.	Fear of losing control or “going crazy.”
13.	Fear of dying. 
Note: Culture-specific symptoms (e.g., tinnitus, neck soreness, headache, uncontrol¬lable screaming or crying) may be seen. Such symptoms should not count as one of the four required symptoms.*

B.  At least one of the attacks has been followed by 1 month (or more) of one or both of the following:
1.	Persistent concern or worry about additional panic attacks or their consequences (e.g., losing control, having a heart attack, “going crazy”).
2.	A significant maladaptive change in behavior related to the attacks (e.g., behaviors designed to avoid having panic attacks, such as avoidance of exercise or unfamiliar situations).

C.  The disturbance is not attributable to the physiological effects of a substance (e.g., a drug of abuse, a medication) or another medical condition (e.g., hyperthyroidism, car¬diopulmonary disorders).

D.  The disturbance is not better explained by another mental disorder (e.g., the panic at¬tacks do not occur only in response to feared social situations, as in social anxiety dis¬order: in response to circumscribed phobic objects or situations, as in specific phobia: in  response to obsessions, as in  obsessive-compulsive  disorder: in response to re¬minders of traumatic events, as in posttraumatic stress disorder: or in response to separation from attachment figures, as in separation anxiety disorder)*


*The questionnaire does not adequately or fully measure these criteria

## Screening variables
The panic disorder screening questions include:
1) 4 or more panic symptoms (criterion A) must be endorsed

*How the screening questions work*
If participants endorse fewer than 4 panic symptoms, then they are given a 0 for diagnosis 


Calculate PAD symptoms 'score' (the number of criterion A symptoms endorsed)
```{r PAD symptom score}
#Create score for PAD symptoms
#Do NOT use 'is.na' for these as then you cannot +1 to it. Use the no.info item for NA (below). 
PAD.items$pad.panic_symptoms_numeric<-0

#Criterion A.1 - Heart was pounding or racing
PAD.items$pad.panic_symptoms_numeric<-with(PAD.items, 
                                    ifelse(!is.na(pad.heart_poundingracing) 
                                           & pad.heart_poundingracing == 1, 
                                           pad.panic_symptoms_numeric + 1, pad.panic_symptoms_numeric))
#Criterion A.2 - Sweating
PAD.items$pad.panic_symptoms_numeric<-with(PAD.items,
                                    ifelse(!is.na(pad.sweating) 
                                           & pad.sweating == 1,
                                           pad.panic_symptoms_numeric + 1, pad.panic_symptoms_numeric))
#Criterion A.3 - Trembling or shaking
PAD.items$pad.panic_symptoms_numeric<-with(PAD.items,
                                    ifelse(!is.na(pad.short_of_breathsmothered) 
                                           & pad.short_of_breathsmothered == 1,
                                           pad.panic_symptoms_numeric + 1, pad.panic_symptoms_numeric))
#Criterion A.4 - Short of breath
PAD.items$pad.panic_symptoms_numeric<-with(PAD.items, 
                                    ifelse(!is.na(pad.short_of_breathsmothered) &
                                             pad.short_of_breathsmothered == 1, 
                                           pad.panic_symptoms_numeric + 1, pad.panic_symptoms_numeric))
#Criterion A.5 - Felt like you were choking
PAD.items$pad.panic_symptoms_numeric<-with(PAD.items, 
                                    ifelse(!is.na(pad.choking) &
                                             pad.choking == 1, 
                                           pad.panic_symptoms_numeric + 1, pad.panic_symptoms_numeric))
#Criterion A.6 - Had pain or discomfort in chest
PAD.items$pad.panic_symptoms_numeric<-with(PAD.items, 
                                    ifelse(!is.na(pad.paindiscomfort_in_your_chest) & pad.paindiscomfort_in_your_chest == 1, 
                                           pad.panic_symptoms_numeric + 1, pad.panic_symptoms_numeric))
#Criterion A.7 - Nauseous or felt sick in the stomach
PAD.items$pad.panic_symptoms_numeric<-with(PAD.items, 
                                    ifelse(!is.na(pad.nauseousfelt_sick_in_the_stomach) 
                                           & pad.nauseousfelt_sick_in_the_stomach == 1, 
                                           pad.panic_symptoms_numeric + 1, pad.panic_symptoms_numeric))
#Criterion A.8 - Dizzy, unsteady, light-headed or faint
PAD.items$pad.panic_symptoms_numeric<-with(PAD.items,
                                    ifelse(!is.na(pad.dizzy_unsteady_lightheaded_or_faint) 
                                           & pad.dizzy_unsteady_lightheaded_or_faint == 1,
                                           pad.panic_symptoms_numeric + 1, pad.panic_symptoms_numeric))
#Criterion A.9 - Felt hot or cold
PAD.items$pad.panic_symptoms_numeric<-with(PAD.items, 
                                    ifelse(!is.na(pad.hot_or_cold) 
                                           & pad.hot_or_cold == 1, 
                                           pad.panic_symptoms_numeric + 1, pad.panic_symptoms_numeric))
#Criterion A.10 - Felt numbness or tingling sensations
PAD.items$pad.panic_symptoms_numeric<-with(PAD.items, 
                                    ifelse(!is.na(pad.numbnesstingling_sensations) 
                                           & pad.numbnesstingling_sensations == 1, 
                                           pad.panic_symptoms_numeric + 1, pad.panic_symptoms_numeric))
#Criterion A.11 - Felt like things weren't real, or felt detached from self
PAD.items$pad.panic_symptoms_numeric<-with(PAD.items, 
                                    ifelse(!is.na(pad.detached_real_felt_things) 
                                           & pad.detached_real_felt_things == 1, 
                                           pad.panic_symptoms_numeric + 1, pad.panic_symptoms_numeric))
#Criterion A.12 - Afraid going to lose control or go crazy
PAD.items$pad.panic_symptoms_numeric<-with(PAD.items, 
                                    ifelse(!is.na(pad.lose_control_crazy_afraid) 
                                           & pad.lose_control_crazy_afraid == 1, 
                                           pad.panic_symptoms_numeric + 1, pad.panic_symptoms_numeric))
#Criterion A.13 - Afraid going to die
PAD.items$pad.panic_symptoms_numeric<-with(PAD.items, 
                                    ifelse(!is.na(pad.afraid_you_were_going_to_die) 
                                           & pad.afraid_you_were_going_to_die == 1, 
                                           pad.panic_symptoms_numeric + 1, pad.panic_symptoms_numeric))
#Check distribution of scores
summary(as.factor(PAD.items$pad.panic_symptoms_numeric))

```

## Combining criterion variables
Criterion B for panic disorder includes both persistent worry about panic attacks and also a duration of 1 month or longer.

In the questionnaire, the duration question is not displayed if the participant indicates 'no' to all the worry symptoms. (Rationale: if the participant doesn't have these worries, then it doesn't make sense to ask how long they've had the worries for)
```{r panic disorder criterion B}
PAD.items <- PAD.items %>% 
  mutate(pad.criterion_B_numeric =
    case_when(pad.nervous_feel_anxious_panic == 0 & 
                pad.losing_control_heart_attack == 0 & 
                pad.avoid_situations_panic_attacks == 0 ~ 0,
              pad.panic_attacks_avoid_situations == 1 ~ 0,
              pad.nervous_feel_anxious_panic == 1 & pad.panic_attacks_avoid_situations > 1 ~ 1, 
              pad.losing_control_heart_attack == 1 & pad.panic_attacks_avoid_situations > 1 ~ 1, 
              pad.avoid_situations_panic_attacks == 1 & pad.panic_attacks_avoid_situations > 1 ~ 1,
              is.na(pad.nervous_feel_anxious_panic) ~ NA_real_,
              is.na(pad.losing_control_heart_attack) ~ NA_real_,
              is.na(pad.avoid_situations_panic_attacks) ~ NA_real_,
              (pad.nervous_feel_anxious_panic == 1 | pad.losing_control_heart_attack == 1 | pad.losing_control_heart_attack == 1) & is.na(pad.panic_attacks_avoid_situations) ~ NA_real_
              )
  )

freq(PAD.items$pad.criterion_B_numeric)
```

# Missingness

*Screening missingness variable:*
If participants do not respond to the screening questions, then they are not shown the remaining questions and should autmatically have "NA" as their score.

Note: The way that the questionnaire is designed in Qualtrics (the GLAD survey software), it's impossible for participants to have NA in one criterion A item and not another. They either have all NAs, or none. As a result, the 'pad.panic_symptoms.NA' variable created in the chunk below will only have 0 and 13 as values.
```{r panic attack symptoms NA count score}
#Create score to calculate how many missing values are in the PAD symptom scores
PAD.items$pad.panic_symptoms.NA<-0

#Criterion A.1 - Heart was pounding or racing
PAD.items$pad.panic_symptoms.NA<-with(PAD.items, 
                                    ifelse(is.na(pad.heart_poundingracing), 
                                           pad.panic_symptoms.NA + 1, pad.panic_symptoms.NA))
#Criterion A.2 - Sweating
PAD.items$pad.panic_symptoms.NA<-with(PAD.items,
                                    ifelse(is.na(pad.sweating),
                                           pad.panic_symptoms.NA + 1, pad.panic_symptoms.NA))
#Criterion A.3 - Trembling or shaking
PAD.items$pad.panic_symptoms.NA<-with(PAD.items,
                                    ifelse(is.na(pad.short_of_breathsmothered),
                                           pad.panic_symptoms.NA + 1, pad.panic_symptoms.NA))
#Criterion A.4 - Short of breath
PAD.items$pad.panic_symptoms.NA<-with(PAD.items, 
                                    ifelse(is.na(pad.short_of_breathsmothered), 
                                           pad.panic_symptoms.NA + 1, pad.panic_symptoms.NA))
#Criterion A.5 - Felt like you were choking
PAD.items$pad.panic_symptoms.NA<-with(PAD.items, 
                                    ifelse(is.na(pad.choking), 
                                           pad.panic_symptoms.NA + 1, pad.panic_symptoms.NA))
#Criterion A.6 - Had pain or discomfort in chest
PAD.items$pad.panic_symptoms.NA<-with(PAD.items, 
                                    ifelse(is.na(pad.paindiscomfort_in_your_chest), 
                                           pad.panic_symptoms.NA + 1, pad.panic_symptoms.NA))
#Criterion A.7 - Nauseous or felt sick in the stomach
PAD.items$pad.panic_symptoms.NA<-with(PAD.items, 
                                    ifelse(is.na(pad.nauseousfelt_sick_in_the_stomach), 
                                           pad.panic_symptoms.NA + 1, pad.panic_symptoms.NA))
#Criterion A.8 - Dizzy, unsteady, light-headed or faint
PAD.items$pad.panic_symptoms.NA<-with(PAD.items,
                                    ifelse(is.na(pad.dizzy_unsteady_lightheaded_or_faint),
                                           pad.panic_symptoms.NA + 1, pad.panic_symptoms.NA))
#Criterion A.9 - Felt hot or cold
PAD.items$pad.panic_symptoms.NA<-with(PAD.items, 
                                    ifelse(is.na(pad.hot_or_cold), 
                                           pad.panic_symptoms.NA + 1, pad.panic_symptoms.NA))
#Criterion A.10 - Felt numbness or tingling sensations
PAD.items$pad.panic_symptoms.NA<-with(PAD.items, 
                                    ifelse(is.na(pad.numbnesstingling_sensations), 
                                           pad.panic_symptoms.NA + 1, pad.panic_symptoms.NA))
#Criterion A.11 - Felt like things weren't real, or felt detached from self
PAD.items$pad.panic_symptoms.NA<-with(PAD.items, 
                                    ifelse(is.na(pad.detached_real_felt_things), 
                                           pad.panic_symptoms.NA + 1, pad.panic_symptoms.NA))
#Criterion A.12 - Afraid going to lose control or go crazy
PAD.items$pad.panic_symptoms.NA<-with(PAD.items, 
                                    ifelse(is.na(pad.lose_control_crazy_afraid), 
                                           pad.panic_symptoms.NA + 1, pad.panic_symptoms.NA))
#Criterion A.13 - Afraid going to die
PAD.items$pad.panic_symptoms.NA<-with(PAD.items, 
                                    ifelse(is.na(pad.afraid_you_were_going_to_die), 
                                           pad.panic_symptoms.NA + 1, pad.panic_symptoms.NA))

summary(as.factor(PAD.items$pad.panic_symptoms.NA))

```

*Symptom missingness*
Similarly, once participants pass the screeners, if any of the other core symptoms are NA then the participant might have received a diagnosis of panic disorder, but we won't know. 

Future considerations: If a participant has an NA in this score but was far from meeting diagnostic criteria, then we may still want to keep them as a '0' for diagnosis.
```{r variable for PAD criteria missingness}
#Missing responses/no information on core symptoms
PAD.items$no.info<-0
#+1 to missingness score if criterion B is missing
PAD.items$no.info <- with(PAD.items,
                               ifelse(is.na(pad.criterion_B_numeric),
                                      no.info + 1, no.info
                                                )
                                      )
#+1 to missingness if criterion C item is missing
PAD.items$no.info <- with(PAD.items,
                               ifelse(is.na(pad.medical_condition_drugs_sudden),
                                      no.info + 1, no.info
                                                )
                                      )
#+1 to missingness if criterion D items are missing
PAD.items$no.info <- with(PAD.items,
                               ifelse(is.na(pad.sudden_anxiety_attacks_strong) & is.na(pad.strong_fears_attack_situation),
                                      no.info + 1, no.info
                                                )
                                      )

summary(as.factor(PAD.items$no.info))
```

# DSM-5 panic disorder algorithm

```{r lifetime PAD diagnosis variable}
#Code lifetime PAD as NA if any core symptoms were missed
PAD.items <- PAD.items %>% 
  mutate(pad.diagnosis_numeric =
           case_when(
        #Diagnosis is NA if screener is skipped
               pad.panic_symptoms.NA > 0 ~ NA_real_,
        #Diagnosis is NA if ppt met screening criteria and are missing one of the other core symptoms
             (pad.panic_symptoms_numeric > 3 & no.info > 0) ~ NA_real_,
        #Diagnosis is 0 if ppt didn't meet criteria
             #Criterion A. Less than 4 symptoms of panic attacks endorsed
             (
               (pad.panic_symptoms_numeric < 4) |
               #Criterion B. Duration of less than 1 month or no concern/worry
               pad.criterion_B_numeric == 0 |
               #Criterion C. Always the result of medical condition or drug use
               (pad.medical_condition_drugs_sudden == 2) |
               #Criterion D. Occurs only in phobic situations
               (pad.sudden_anxiety_attacks_strong == 1 & pad.strong_fears_attack_situation == 0)) ~ 0,
        #Diagnosis is 1 if ppt met criteria
             #Criterion A. At least 4 symptoms of panic attacks endorsed
             (
               (pad.panic_symptoms_numeric > 3) &
               #Criterion B. Duration of at least 1 month and persistent concern/worry
               pad.criterion_B_numeric == 1 &
               #Criterion C. Not the result of medical condition or drug use
               (pad.medical_condition_drugs_sudden == 0 | pad.medical_condition_drugs_sudden == 1) &
               #Criterion D. Doesn't occur only in phobic situations
               (pad.sudden_anxiety_attacks_strong == 0 | pad.strong_fears_attack_situation == 1)) ~ 1
             )
             )
  
summary(as.factor(PAD.items$pad.diagnosis_numeric))

```

# Recode calculated lifetime PAD diagnosis variable

```{r pad.diagnosis factor}

PAD.items$pad.diagnosis <- recode_factor(PAD.items$pad.diagnosis_numeric,
                             "0" = "No panic disorder",
                             "1" = "Panic disorder")
#Summary of recoded variable
freq(PAD.items$pad.diagnosis)
```

# Clean PAD dataset

```{r clean PAD dataframe}

#Export into a rds file:
saveRDS(object = PAD.items, file = paste0(cleaned_path, "PAD_cleaned.rds"))

# Saves the R data including the recoding
#save.image(file = paste0(cleaned_path, "GLAD_PAD_clean.RData"))
```