---
title: "Lifetime DSM-5 specific phobia: Diagnostic algorithm (GLAD and COPING NBR data)"
author: "Molly R. Davies"
date: "16/04/2021"
output: html_document
---

This script runs an algorithm based on DSM-5 diagnostic criteria, to ascertain likely lifetime diagnosis of specific phobia using the GLAD Study and COPING NIHR BioResource (NBR) data.

Algorithm developed for the paper "Comparison of algorithm-based versus single-item phenotyping measures of depression and anxiety disorders in the GLAD Study cohort" - Davies et al (in prep).

Full description of the algorithms and scripts written for the paper can be accessed at:
https://github.com/mollyrdavies/GLAD-Diagnostic-algorithms.git

Script written by M. R. Davies.
Email:  molly.davies@kcl.ac.uk

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Set up

Clear workspace
```{r clear workspace}
rm(list = ls())
```

Select which cohorts to run the algorithms on by changing the value to TRUE (include) or FALSE (exclude). If multiple cohorts selected, data will be combined into a single dataset.

*Note: Currently only GLAD and COPING_NBR cohorts included in algorithms.
```{r select cohorts}
GLAD = TRUE
COPING_NBR = TRUE
```

```{r load packages}
library(tidyverse)
library(psych)
library(summarytools)
```

```{r source path for reading/saving data}
#Source raw data directory (raw_path) & clean data export directory (cleaned_path)
source("../../../DF1.0_data_path.R")
```

# SPEC pre-processing

```{r read in SPEC data}
if (GLAD == TRUE) {
#Read GLAD data
glad_spec_file <- paste(glad_raw_path, "spec_glad.rds", sep = "")
glad_spec <- read_rds(glad_spec_file)
}

if (COPING_NBR == TRUE) {
#Read COPING data
coping_nbr_spec_file <- paste(coping_nbr_optional_raw_path, "spec_coping_nbr_optional.rds", sep = "")
coping_nbr_spec <- read_rds(coping_nbr_spec_file)
}

```

```{r SPEC add sample column}
if (GLAD == TRUE) {
glad_spec$sample <- "GLAD"
}

if (COPING_NBR == TRUE) {
coping_nbr_spec$sample <- "NBR"
}
```

```{r GLAD SPEC renaming}
if (GLAD == TRUE) {
glad_spec_renamed <- glad_spec %>% 
  drop_na(externalDataReference) %>%
  distinct(externalDataReference, .keep_all = TRUE) %>% 
  rename("ID" = "externalDataReference")
}
```

```{r visualise renamed GLAD SPEC data}
if (GLAD == TRUE) {
skimr::skim(glad_spec_renamed)
}
```

```{r COPING SPEC renaming}
if (COPING_NBR == TRUE) {
coping_nbr_spec_renamed <- coping_nbr_spec %>% 
  drop_na(recipientFirstName) %>% 
  distinct(recipientFirstName, .keep_all = TRUE) %>% 
  rename("ID" = "recipientFirstName",
         "COPING_ID" = "externalDataReference",
         "spec.interfered_activities_fears_life" = "spec.activities_interfered_life_fears" #different from GLAD
         )
}
```

```{r visualise renamed COPING SPEC data}
if (COPING_NBR == TRUE) {
  skimr::skim(coping_nbr_spec_renamed)
}
```


```{r rename GLAD SPEC dataset (if GLAD only)}
if (GLAD == TRUE & COPING_NBR == FALSE) {
  SPEC_renamed.combined <- glad_spec_renamed
}
```

```{r rename COPING NBR SPEC dataset (if COPING NBR only)}
if (GLAD == FALSE & COPING_NBR == TRUE) {
  SPEC_renamed.combined <- coping_nbr_spec_renamed
}
```

```{r merge GLAD & COPING NBR SPEC datasets}
if (GLAD == TRUE & COPING_NBR == TRUE) {
  SPEC_renamed.combined <- bind_rows(
    glad_spec_renamed,
    coping_nbr_spec_renamed
)
}
```

```{r create dataset of SPEC diagnostic variables}
SPEC <- SPEC_renamed.combined %>%
    mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
    mutate_if(is.numeric, ~na_if(., -99)) %>%
    mutate_if(is.numeric, ~na_if(., -77)) #%>%
    #mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
    #mutate_if(is.factor, ~na_if(., "Don't know")) %>%
    #mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
    #mutate_if(is.factor, ~na_if(., "Prefer not to answer"))
```

# DSM-5 Specific phobia diagnostic criteria

A.  Marked fear or anxiety about a specific object or situation (e.g., flying, heights, animals, receiving an injection, seeing blood). 

B.  The phobic object or situation almost always provokes immediate fear or anxiety.

C.  The phobic object or situation is actively avoided or endured with intense fear or anxiety.

D.  The fear or anxiety is out of proportion to the actual danger posed by the specific objector situation and to the sociocultural context.

E.  The fear, anxiety, or avoidance is persistent, typically lasting for 6 months or more.

F.   The fear, anxiety, or avoidance causes clinically significant distress* or impairment in social, occupational, or other important areas of functioning.

G.  The  disturbance is not better explained by the symptoms of another mental disorder, including fear, anxiety, and avoidance of situations associated with panic-like symptoms or other  incapacitating  symptoms (as in agoraphobia): objects or situations related to obsessions (as in obsessive-compulsive disorder); reminders of traumatic events (as in posttraumatic stress disorder); separation from home or attachment figures (as in sep¬aration anxiety disorder); or social situations (as in social anxiety disorder).*


*The questionnaire doesn't adequately measure significant distress or criterion G.

## Screening variables
The specific phobia section screening questions include:
1) At least one phobia (criterion A) must be endorsed
2) Frequency of these fears (criterion B) are almost always or always present when exposed to the phobia


*How the screening questions work*
If participants answer 'No' to all phobias in criterion A, then they are given a 0 for diagnosis and skip the remaining questions.

If participants answer 'Yes' to any phobia in criterion A but report frequency of these fears as "Never", "Only one or two times ever", or "Some of the time", then they are given a 0 for diagnosis and skip the remaining questions.


Criterion A. Calculate specific phobias count 'score' (the number of phobias endorsed)
```{r phobias count score screener}
#Create score for number of phobias endorsed
#Do NOT use 'is.na' for these as then you cannot +1 to it. Use the no.info item for NA (below).
SPEC$spec.phobias_count_numeric <- 0

#Environmental phobia
SPEC$spec.phobias_count_numeric<-with(SPEC,
                                                    ifelse(
                                                      spec.environment == 1, 
                                                      spec.phobias_count_numeric + 1, spec.phobias_count_numeric))
#Situation phobia
SPEC$spec.phobias_count_numeric<-with(SPEC,
                                                    ifelse(
                                                      spec.situations == 1, 
                                                      spec.phobias_count_numeric + 1, spec.phobias_count_numeric))
#Animal phobia
SPEC$spec.phobias_count_numeric<-with(SPEC,
                                                    ifelse(
                                                      spec.animals == 1, 
                                                      spec.phobias_count_numeric + 1, spec.phobias_count_numeric))
#Blood or injection phobia
SPEC$spec.phobias_count_numeric<-with(SPEC,
                                                    ifelse(
                                                      spec.blood_injections_or_injury == 1, 
                                                      spec.phobias_count_numeric + 1, spec.phobias_count_numeric))
#Other phobia
SPEC$spec.phobias_count_numeric<-with(SPEC,
                                                    ifelse(
                                                      spec.other == 1, 
                                                      spec.phobias_count_numeric + 1, spec.phobias_count_numeric))

freq(SPEC$spec.phobias_count_numeric)
```

Criterion A and B screener variable.
```{r specific phobia screener}
#Criterion A screening variable
SPEC <- SPEC %>% 
  mutate(specific_phobia_screener_numeric = 
           case_when(
             spec.phobias_count_numeric == 0 ~ 0,
             spec.phobias_count_numeric > 0 & (spec.situations_anxiety_fear == 0 | spec.situations_anxiety_fear == 1 | spec.situations_anxiety_fear == 2) ~ 0,
             spec.phobias_count_numeric > 0 & (spec.situations_anxiety_fear == 3 | spec.situations_anxiety_fear == 4) ~ 1,
             is.na(spec.environment) & is.na(spec.situations) & is.na(spec.animals) & is.na(spec.blood_injections_or_injury) & is.na(spec.other) ~ NA_real_,
             spec.phobias_count_numeric > 0 & is.na(spec.situations_anxiety_fear) ~ NA_real_
           ))

summary(as.factor(SPEC$specific_phobia_screener_numeric))
```

## Missingness

*Screening missingness variable:*
If participants do not respond to one of the screening questions, then they are not shown the remaining questions and should autmatically have "NA" as their score.

For criterion B, NA is only counted if criterion A is 1 (since otherwise the question was not displayed).


Criterion A missingness variable
```{r phobias NA count score}
#Missing responses/no information on phobias
SPEC$spec.phobias_NA_count_numeric <- 0

#Environmental phobia NA
SPEC$spec.phobias_NA_count_numeric<-with(SPEC,
                                                    ifelse(
                                                      is.na(spec.environment), 
                                                      spec.phobias_NA_count_numeric + 1, spec.phobias_NA_count_numeric))
#Situation phobia
SPEC$spec.phobias_NA_count_numeric<-with(SPEC,
                                                    ifelse(
                                                      is.na(spec.situations), 
                                                      spec.phobias_NA_count_numeric + 1, spec.phobias_NA_count_numeric))
#Animal phobia
SPEC$spec.phobias_NA_count_numeric<-with(SPEC,
                                                    ifelse(
                                                      is.na(spec.animals), 
                                                      spec.phobias_NA_count_numeric + 1, spec.phobias_NA_count_numeric))
#Blood or injection phobia
SPEC$spec.phobias_NA_count_numeric<-with(SPEC,
                                                    ifelse(
                                                      is.na(spec.blood_injections_or_injury), 
                                                      spec.phobias_NA_count_numeric + 1, spec.phobias_NA_count_numeric))
#Other phobia
SPEC$spec.phobias_NA_count_numeric<-with(SPEC,
                                                    ifelse(
                                                      is.na(spec.other), 
                                                      spec.phobias_NA_count_numeric + 1, spec.phobias_NA_count_numeric))

freq(SPEC$spec.phobias_NA_count_numeric)
```


```{r specific phobia screeners NA count score}
SPEC$spec.specific_phobia_screen.calc.NA<-0
#+1 if criterion A (number of phobias) is 0 and has more than one NA
SPEC$spec.specific_phobia_screen.calc.NA<-with(SPEC, 
                                    ifelse(
                                      (spec.phobias_count_numeric == 0 & spec.phobias_NA_count_numeric > 0), 
                                           spec.specific_phobia_screen.calc.NA + 1, spec.specific_phobia_screen.calc.NA))
#If criterian B (almost always provoking fear) is NA, but criterion A was met
SPEC$spec.specific_phobia_screen.calc.NA<-with(SPEC,
                                    ifelse(spec.phobias_count_numeric > 0 & is.na(spec.situations_anxiety_fear),
                                           spec.specific_phobia_screen.calc.NA + 1, spec.specific_phobia_screen.calc.NA))

summary(as.factor(SPEC$spec.specific_phobia_screen.calc.NA))
```

*Symptom missingness variable:*
Similarly, once participants pass the screeners, if any of the other core symptoms are NA then the participant might have received a diagnosis of specific phobia, but we won't know. 

Future considerations: If a participant has an NA in this score but was far from meeting diagnostic criteria, then we may still want to keep them as a '0' for diagnosis.
```{r specific phobia NA symptom count score}

SPEC$spec.specific_phobia_symptoms.calc.NA<-0
#If criterion D is NA
SPEC$spec.specific_phobia_symptoms.calc.NA<-with(SPEC, 
                                    ifelse(specific_phobia_screener_numeric %in% 1 & is.na(spec.actual_danger_involved_proportion), 
                                           spec.specific_phobia_symptoms.calc.NA + 1, spec.specific_phobia_symptoms.calc.NA))

#If criterion F (functional impairment) is NA
SPEC$spec.specific_phobia_symptoms.calc.NA<-with(SPEC,
                                    ifelse(specific_phobia_screener_numeric %in% 1 & is.na(spec.interfered_activities_fears_life),
                                           spec.specific_phobia_symptoms.calc.NA + 1, spec.specific_phobia_symptoms.calc.NA))
#If both items for criterion C (avoid or endure) are NA
SPEC$spec.specific_phobia_symptoms.calc.NA<-with(SPEC, 
                                    ifelse(specific_phobia_screener_numeric %in% 1 & is.na(spec.avoid_these_situations) & is.na(spec.endure_them_with_intense_anxiety), 
                                           spec.specific_phobia_symptoms.calc.NA + 1, spec.specific_phobia_symptoms.calc.NA))

summary(as.factor(SPEC$spec.specific_phobia_symptoms.calc.NA))

```

# DSM-5 specific phobia algorithm
Applying the diagnostic algorithm to questionnaire responses
```{r diagnostic algorithm for specific phobia}
SPEC <- SPEC %>% 
  mutate(spec.diagnosis_numeric =
           case_when(
#Ppts are coded NA if they didn't respond to the screening questions, or had "No" in one screening question and NA in the other
             spec.specific_phobia_screen.calc.NA > 0 ~ NA_real_,
#Ppts are coded NA if they didn't respond to symptom questions that may have met diagnostic criteria
             specific_phobia_screener_numeric > 0 & spec.specific_phobia_symptoms.calc.NA > 0 ~ NA_real_,
#No phobia
        #Criterion A (not met)
             spec.phobias_count_numeric == 0 |
        #Criterion E. Frequency (not met)
             (spec.situations_anxiety_fear == 0 | spec.situations_anxiety_fear == 1 | spec.situations_anxiety_fear == 2) |
        #Criterion D. Out of proportion (not met)
             spec.actual_danger_involved_proportion == 0 | 
        #Criterion E. Duration (not met)
             (spec.longest_time_fears_lasted == 1) | 
        #Criterion F. Functional impairment (not met)
             (spec.interfered_activities_fears_life == 0 | spec.interfered_activities_fears_life == 1) | 
        #Criterion C. Avoid or endure (not met)
             (spec.avoid_these_situations == 0 & spec.endure_them_with_intense_anxiety == 0) ~ 0,
#Any phobia
        #Criterion A
             spec.phobias_count_numeric > 0 &
        #Criterion E. Frequency
             (spec.situations_anxiety_fear == 3 | spec.situations_anxiety_fear == 4) & 
        #Criterion D. Out of proportion
             spec.actual_danger_involved_proportion == 1 &
        #Criterion E. Duration
            (spec.longest_time_fears_lasted == 2 | spec.longest_time_fears_lasted == 3 | 
               spec.longest_time_fears_lasted == 4 | spec.longest_time_fears_lasted == 5) & 
        #Criterion F. Functional impairment
            (spec.interfered_activities_fears_life == 2 | spec.interfered_activities_fears_life == 3) &
        #Criterion C. Avoid or endure
            (spec.avoid_these_situations == 1 | spec.endure_them_with_intense_anxiety == 1) ~ 1)) #Criterion C. Avoid or endure

#Get frequencies
freq(SPEC$spec.diagnosis_numeric)
```

```{r recode any phobia as a factor}
#Recode any phobia variable and change variable name
SPEC$spec.diagnosis <- recode_factor(SPEC$spec.diagnosis_numeric      ,
                             "0" = "No phobia",
                             "1" = "Any specific phobia"
                             )
freq(SPEC$spec.diagnosis)
```

# Create individual specific phobia variables

```{r individual specific phobia variables}
#Environmental phobia
SPEC <- SPEC %>% 
  mutate(spec.environment_phobia_diagnosis_numeric = 
           case_when(
             spec.environment == 1 & spec.diagnosis_numeric == 1 ~ 0,
             spec.environment == 0 & spec.diagnosis_numeric == 1 ~ 0,
             spec.diagnosis_numeric == 0 ~ 0,
             is.na(spec.diagnosis_numeric) ~ NA_real_,
             is.na(spec.environment) ~ NA_real_
           ))
## Recode factor
SPEC <- SPEC %>% 
  mutate(spec.environment_phobia_diagnosis =
           recode_factor(spec.environment_phobia_diagnosis_numeric,
                         "0" = "No environment phobia",
                         "1" = "Environment phobia"))
#Situational phobia
SPEC <- SPEC %>% 
  mutate(spec.situation_phobia_diagnosis_numeric = 
           case_when(
             spec.situations == 1 & spec.diagnosis_numeric == 1 ~ 0,
             spec.situations == 0 & spec.diagnosis_numeric == 1 ~ 0,
             spec.diagnosis_numeric == 0 ~ 0,
             is.na(spec.diagnosis_numeric) ~ NA_real_,
             is.na(spec.situations) ~ NA_real_
           ))
## Recode factor
SPEC <- SPEC %>% 
  mutate(spec.situation_phobia_diagnosis =
           recode_factor(spec.situation_phobia_diagnosis_numeric,
                         "0" = "No situation phobia",
                         "1" = "Situation phobia"))
#Animal phobia
SPEC <- SPEC %>% 
  mutate(spec.animal_phobia_diagnosis_numeric = 
           case_when(
             spec.animals == 1 & spec.diagnosis_numeric == 1 ~ 0,
             spec.animals == 0 & spec.diagnosis_numeric == 1 ~ 0,
             spec.diagnosis_numeric == 0 ~ 0,
             is.na(spec.diagnosis_numeric) ~ NA_real_,
             is.na(spec.animals) ~ NA_real_
           ))
## Recode factor
SPEC <- SPEC %>% 
  mutate(spec.animal_phobia_diagnosis =
           recode_factor(spec.animal_phobia_diagnosis_numeric,
                         "0" = "No animal phobia",
                         "1" = "Animal phobia"))
#Blood injection phobia
SPEC <- SPEC %>% 
  mutate(spec.blood_injection_phobia_diagnosis_numeric = 
           case_when(
             spec.blood_injections_or_injury == 1 & spec.diagnosis_numeric == 1 ~ 0,
             spec.blood_injections_or_injury == 0 & spec.diagnosis_numeric == 1 ~ 0,
             spec.diagnosis_numeric == 0 ~ 0,
             is.na(spec.diagnosis_numeric) ~ NA_real_,
             is.na(spec.blood_injections_or_injury) ~ NA_real_
           ))
## Recode factor
SPEC <- SPEC %>% 
  mutate(spec.blood_injection_phobia_diagnosis =
           recode_factor(spec.blood_injection_phobia_diagnosis_numeric,
                         "0" = "No blood or injection phobia",
                         "1" = "Blood or injection phobia"))
#Other phobia
SPEC <- SPEC %>% 
  mutate(spec.other_phobia_diagnosis_numeric = 
           case_when(
             spec.other == 1 & spec.diagnosis_numeric == 1 ~ 0,
             spec.other == 0 & spec.diagnosis_numeric == 1 ~ 0,
             spec.diagnosis_numeric == 0 ~ 0,
             is.na(spec.diagnosis_numeric) ~ NA_real_,
             is.na(spec.other) ~ NA_real_
           ))
## Recode factor
SPEC <- SPEC %>% 
  mutate(spec.other_phobia_diagnosis =
           recode_factor(spec.other_phobia_diagnosis_numeric,
                         "0" = "No other phobia",
                         "1" = "Other phobia"))
```

# Clean SPEC dataset
```{r clean SPEC dataframe}

#Export data
saveRDS(object = SPEC, file = paste0(cleaned_path, "SPEC_cleaned.rds"))

# Save the R data including the recoding
#save.image(file = paste0(cleaned_path, "GLAD_SPEC_clean.RData"))
```