---
title: "DIAGCOMP_descriptives_frequencies"
author: "Molly R. Davies"
date: 30/10/2020
output:  
  html_document:
    df_print: paged
    toc: yes
    toc_depth: 2
    toc_float:
      collapsed: false
    number_sections: false
    highlight: monochrome
    theme: cerulean
code_folding: show

html_notebook:
  theme: cerulean
toc: yes
---

This is the script to run demographic descriptives and frequencies of the single-item/algorithm-based diagnoses of the GLAD Study sample. Results are reported in the paper titled "Comparison of algorithm-based versus single-item phenotyping measures of depression and anxiety disorders in the GLAD Study cohort" - Davies et al (in prep).

Script written by M. R. Davies.
Email:  molly.davies@kcl.ac.uk

All scripts for the paper can be accessed at:
https://github.com/mollyrdavies/GLAD-Diagnostic-algorithms.git

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Set up
```{r install packages}
#install.packages("summarytools")
#install.packages("tidyverse")
#install.packages("descr")
```

```{r import packages}
library(descr)
library(summarytools)
library(tidyverse)
```

```{r source file paths}
source("../../GLAD_data_path.R")
```

```{r read data}
dat.cc <- read_rds(paste0(cleaned_path, "combined_cleaned_new_variables.rds"))
```

```{r visualise dataset}
dim(dat.cc)
head(dat.cc)
```

# Demographics of GLAD sample

## Mean age

```{r mean age}                        
mean(dat.cc$age, na.rm = T)
```

## Sex frequencies

```{r sex freq}                        
freq(dat.cc$sex)
```

## Ethnicity frequencies

```{r ethnicity freq}
freq(dat.cc$Ethnicity)
```

## Highest Education frequencies

```{r higher education freq}
freq(dat.cc$Highest.Education)
```

# Diagnosis: Frequencies and proportions
Frequencies of diagnoses calculated for participants with values in BOTH single-item and algorithm-based diagnosis per disorder.
Participants with NAs for one measure were excluded for that diagnosis.

# Get frequencies for each diagnosis, excluding NAs per disorder

```{r MDD frequencies}
#Algorithm-based MDD frequencies
dat.cc %>% 
  filter(!is.na(mhd.MDD) & !is.na(cidid.diagnosis)) %>%
  summarytools::freq(cidid.diagnosis, report.NAs = T) 

#Single-item MDD frequencies
dat.cc %>% 
  filter(!is.na(mhd.MDD) & !is.na(cidid.diagnosis)) %>%
  summarytools::freq(mhd.MDD)

```

```{r Any Anxiety frequencies}
#Algorithm-based any anxiety frequencies
dat.cc %>% 
  filter(!is.na(LifetimeAnyAnx) & !is.na(ClinicianAnyAnx)) %>%
  summarytools::freq(LifetimeAnyAnx)

#Single-item any anxiety frequencies
dat.cc %>% 
  filter(!is.na(LifetimeAnyAnx) & !is.na(ClinicianAnyAnx)) %>%
  summarytools::freq(ClinicianAnyAnx)

```

```{r GAD frequencies}
#Algorithm-based GAD frequencies
dat.cc %>% 
  filter(!is.na(mhd.GAD) & !is.na(cidia.diagnosis)) %>%
  summarytools::freq(cidia.diagnosis)

#Single-item GAD frequencies
dat.cc %>% 
  filter(!is.na(mhd.GAD) & !is.na(cidia.diagnosis)) %>%
  summarytools::freq(mhd.GAD)

```

```{r Specific phobia frequencies}
#Algorithm-based specific phobia frequencies
dat.cc %>% 
  filter(!is.na(mhd.specific_phobia) & !is.na(spec.diagnosis)) %>%
  summarytools::freq(spec.diagnosis)

#Single-item specific phobia frequencies
dat.cc %>% 
  filter(!is.na(mhd.specific_phobia) & !is.na(spec.diagnosis)) %>%
  summarytools::freq(mhd.specific_phobia)
```

```{r Social anxiety disorder frequencies}
#Algorithm-based social anxiety frequencies
dat.cc %>% 
  filter(!is.na(mhd.social_anxiety) & !is.na(socp.diagnosis)) %>%
  summarytools::freq(socp.diagnosis)

#Single-item social anxiety frequencies
dat.cc %>% 
  filter(!is.na(mhd.social_anxiety) & !is.na(socp.diagnosis)) %>%
  summarytools::freq(mhd.social_anxiety)

```

```{r Panic disorder frequencies}
#Algorithm-based panic disorder frequencies
dat.cc %>% 
  filter(!is.na(mhd.panic_disorder) & !is.na(pad.diagnosis)) %>%
  summarytools::freq(pad.diagnosis)

#Single-item panic disorder frequencies
dat.cc %>% 
  filter(!is.na(mhd.panic_disorder) & !is.na(pad.diagnosis)) %>%
  summarytools::freq(mhd.panic_disorder)

```

```{r Panic Attacks vs Lifetime Panic disorder frequencies}
#Single-item panic attacks frequencies
dat.cc %>% 
  filter(!is.na(mhd.panic_attacks) & !is.na(mhd.panic_disorder) & !is.na(pad.diagnosis)) %>%
  summarytools::freq(mhd.panic_attacks)

```

```{r Agoraphobia frequencies}
#Algorithm-based agoraphobia frequencies
dat.cc %>% 
  filter(!is.na(mhd.agoraphobia) & !is.na(agp.diagnosis)) %>%
  summarytools::freq(agp.diagnosis)

#Single-item agoraphobia frequencies
dat.cc %>% 
  filter(!is.na(mhd.agoraphobia) & !is.na(agp.diagnosis)) %>%
  summarytools::freq(mhd.agoraphobia)
```


# Number of diagnoses/comorbidities in sample
Check the number of diagnoses in the sample to see:
- N ppts with 0 diagnoses
- N ppts with 1 diagnosis
- N ppts with 2+ diagnoses

## Single-item diagnoses
Note: Single-item panic disorder was added partway through data collection. The single-item count variable is therefore not coded as NA for panic disorder missingness to avoid excessive data loss.
```{r create variable of N single-item diagnoses}
#Sum all clinical diagnoses and remove NAs (except panic disorder, as this variable was included partway through data collection)
dat.cc$selfreport_noPanic <- rowSums(dat.cc[,c("mhd.MDD_numeric", 
                                           "mhd.GAD_numeric", 
                                           "mhd.specific_phobia_numeric", 
                                           "mhd.social_anxiety_numeric", 
                                           "mhd.agoraphobia_numeric")], na.rm=FALSE)

#Add panic only for particpants without NA in above variable
dat.cc$selfreport.n <- with(dat.cc,
                          ifelse(
                            is.na(selfreport_noPanic), 
                            NA, 
                            rowSums(dat.cc[,c("selfreport_noPanic", 
                                            "mhd.panic_disorder_numeric")], na.rm = TRUE)
                                 )
                          )
freq(dat.cc$selfreport_noPanic)
freq(dat.cc$selfreport.n)
```

```{r get N with 1+ or 2+ single-item diagnosis}
#N with 1+ SR diagnosis
table(dat.cc[,c("selfreport.n")]>0)

#N with 2+ SR diagnoses
table(dat.cc[,c("selfreport.n")]>1)

```

```{r get mean single-item diagnoses}

mean(dat.cc$selfreport.n, na.rm = T)

```

## Algorithm-based diagnoses

```{r create variable of N algorithm-based diagnoses}
#Sum all algorithm-based diagnoses and include NAs (coded as 0)
dat.cc$algorithm_based_count_numeric <- rowSums(dat.cc[,c("cidid.diagnosis_numeric", 
                                                          "cidia.diagnosis_numeric", 
                                                          "spec.diagnosis_numeric", 
                                                          "socp.diagnosis_numeric", 
                                                          "pad.diagnosis_numeric", 
                                                          "agp.diagnosis_numeric")], 
                                                na.rm=TRUE)

#Check what it would be if the NAs were excluded
dat.cc$algorithm_based_noNA.n <- rowSums(dat.cc[,c("cidid.diagnosis_numeric", 
                                                   "cidia.diagnosis_numeric", 
                                                   "spec.diagnosis_numeric", 
                                                   "socp.diagnosis_numeric", 
                                                   "pad.diagnosis_numeric", 
                                                   "agp.diagnosis_numeric")], 
                                         na.rm=FALSE)

#Summarise
summary(as.factor(dat.cc$algorithm_based_count_numeric))
summary(as.factor(dat.cc$algorithm_based_noNA.n))

```

```{r NAs in algorithm-based outcomes}

#Do NOT use 'is.na' for these as then you cannot +1 to it. Use the no.info item for NA (below). 
dat.cc$algorithm_based_NA.n<-0

#MDD
dat.cc$algorithm_based_NA.n<-with(dat.cc, 
                         ifelse(is.na(cidid.diagnosis_numeric),
                                algorithm_based_NA.n + 1, algorithm_based_NA.n))
#GAD
dat.cc$algorithm_based_NA.n<-with(dat.cc, 
                         ifelse(is.na(cidia.diagnosis_numeric),
                                algorithm_based_NA.n + 1, algorithm_based_NA.n))
#Specific phobia
dat.cc$algorithm_based_NA.n<-with(dat.cc, 
                         ifelse(is.na(spec.diagnosis_numeric),
                                algorithm_based_NA.n + 1, algorithm_based_NA.n))
#Social phobia
dat.cc$algorithm_based_NA.n<-with(dat.cc, 
                         ifelse(is.na(socp.diagnosis_numeric),
                                algorithm_based_NA.n + 1, algorithm_based_NA.n))
#Panic disorder
dat.cc$algorithm_based_NA.n<-with(dat.cc, 
                         ifelse(is.na(pad.diagnosis_numeric),
                                algorithm_based_NA.n + 1, algorithm_based_NA.n))
#Agoraphobia
dat.cc$algorithm_based_NA.n<-with(dat.cc, 
                         ifelse(is.na(agp.diagnosis_numeric),
                                algorithm_based_NA.n + 1, algorithm_based_NA.n))
#Check distribution of scores
summary(as.factor(dat.cc$algorithm_based_NA.n))


```

```{r get N with 1+ or 2+ algorithm-based diagnosis}

#N with 1+ algorithm-based diagnosis
table(dat.cc[,c("algorithm_based_count_numeric")]>0)

#N with 2+ algorithm-based diagnoses
table(dat.cc[,c("algorithm_based_count_numeric")]>1)

```

```{r get mean algorithm-based diagnoses}

mean(dat.cc$algorithm_based_count_numeric, na.rm = T)

```

## Look at N algorithm-based diagnoses in participants with >=1 single-item diagnoses

```{r subset participants with 1+ single-item diagnosis}
#Subset
selfreport_n1 <- subset(dat.cc, selfreport.n > 0)
#Check correct number of participants
nrow(selfreport_n1)


```

```{r get subset N with 0, 1 or 2+ algorithm-based diagnosis}

#N with no algorithm-based diagnosis
table(selfreport_n1[,c("algorithm_based_noNA.n")]==0)

#N with 1 algorithm-based diagnosis
table(selfreport_n1[,c("algorithm_based_count_numeric")]==1)

#N with 2+ algorithm-based diagnoses
table(selfreport_n1[,c("algorithm_based_count_numeric")]>1)

```

```{r get mean subset algorithm-based diagnoses}

mean(selfreport_n1$algorithm_based_count_numeric, na.rm = T)

```

## Look at N single-item diagnoses in participants with >=1 algorithm-based diagnoses

```{r subset participants with 1+ algorithm-based diagnosis}
#Subset
algorithm_based_n1 <- subset(dat.cc, algorithm_based_count_numeric > 0)
#Check correct number of participants
nrow(algorithm_based_n1)

```

```{r get subset N with 0, 1 or 2+ single-item diagnosis}

#N with no algorithm-based diagnosis
table(algorithm_based_n1[,c("selfreport.n")]==0)

#N with 1 algorithm-based diagnosis
table(algorithm_based_n1[,c("selfreport.n")]==1)

#N with 2+ algorithm-based diagnoses
table(algorithm_based_n1[,c("selfreport.n")]>1)

```

```{r get mean subset single-item diagnoses}

mean(algorithm_based_n1$selfreport.n, na.rm = T)

```