---
title: "DIAGCOMP_variable_creation"
author: "Molly R. Davies"
date: "30/10/2020"
output: html_document
---

This recodes/creates new variables utilised in analyses for the paper "Comparison of algorithm-based versus single-item phenotyping measures of depression and anxiety disorders in the GLAD Study cohort" - Davies et al (in prep).

Script written by M. R. Davies.
Email:  molly.davies@kcl.ac.uk

All scripts for the paper can be accessed at:
https://github.com/mollyrdavies/GLAD-Diagnostic-algorithms.git

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Set up

Clear workspace
```{r clear workspace}
rm(list = ls())
```

```{r create GLAD color palette}
# GLAD color palette:

GLADpalette = c("#efc00b",   # Yellow
                "#b7dee8",   # Light blue (logo)
                "#009fb7",   # Turquoise (dropdown menu)
                "#215968")   # Dark blue (website text)
```

```{r install packages}
#install.packages("tidyverse")
```

```{r import packages}
library(tidyverse)
```

# Get data

```{r source file paths}
source("../GLAD_data_path.R")
```

```{r read data}
dat.cc <- read_rds(paste0(cleaned_path, "combined_cleaned.rds"))
```

# Rename and recode diagnostic variables

```{r lifetime MDD as factor}

dat.cc$LifetimeDepression <- recode_factor(dat.cc$cidid.diagnosis_numeric,
                                            "0" = "Never had MDD",
                                            "1" = "Lifetime MDD",
                                           .missing = NULL)

summary(dat.cc$LifetimeDepression)

```

```{r lifetime GAD as factor}

dat.cc$LifetimeGAD <- recode_factor(dat.cc$cidia.diagnosis_numeric,
                                            "0" = "Never had GAD",
                                            "1" = "Lifetime GAD",
                                            .missing = NULL)


summary(dat.cc$LifetimeGAD)

```

```{r lifetime specific phobia as factor}

dat.cc$SpecificPhobia <- recode_factor(dat.cc$spec.diagnosis_numeric,
                                            "0" = "Never had specific phobia",
                                            "1" = "Lifetime specific phobia")

summary(dat.cc$SpecificPhobia)

```

```{r lifetime social phobia as factor}

dat.cc$SocialPhobia <- recode_factor(dat.cc$socp.diagnosis_numeric,
                                            "0" = "Never had social phobia",
                                            "1" = "Lifetime social phobia")

summary(dat.cc$SocialPhobia)

```

```{r lifetime panic disorder as factor}

dat.cc$PanicDisorder <- recode_factor(dat.cc$pad.diagnosis_numeric,
                                            "0" = "Never had panic disorder",
                                            "1" = "Lifetime panic disorder")

summary(dat.cc$PanicDisorder)

```

```{r lifetime agoraphobia as factor}

dat.cc$Agoraphobia <- recode_factor(dat.cc$agp.diagnosis_numeric,
                                            "0" = "Never had agoraphobia",
                                            "1" = "Lifetime agoraphobia")

summary(dat.cc$Agoraphobia)

```

```{r clinician diagnosis MDD as factor}

dat.cc$ClinicianMDD <- recode_factor(dat.cc$mhd.MDD_numeric,
                                            "0" = "No MDD diagnosis",
                                            "1" = "MDD diagnosis",
                                            "-77" = NULL,
                                            "-88" = NULL,
                                            "-99" = NULL,
                                            .missing = NULL)

summary(dat.cc$ClinicianMDD)

```

```{r clinician diagnosis GAD as factor}
##Recode in dat.cc dataset
dat.cc$ClinicianGAD <- recode_factor(dat.cc$mhd.GAD_numeric,
                                            "0" = "No GAD diagnosis",
                                            "1" = "GAD diagnosis",
                                            "-77" = NULL,
                                            "-88" = NULL,
                                            "-99" = NULL,
                                            .missing = NULL)

summary(dat.cc$ClinicianGAD)

```

```{r clinician diagnosis specific phobia as factor}

dat.cc$ClinicianSpecPhob <- recode_factor(dat.cc$mhd.specific_phobia_numeric,
                                          "0" = "No specific phobia diagnosis",
                                          "1" = "Specific phobia diagnosis",
                                          "-77" = NULL,
                                          "-88" = NULL,
                                          "-99" = NULL,
                                          .missing = NULL)

summary(dat.cc$ClinicianSpecPhob)

```

```{r clinician diagnosis social phobia as factor}

dat.cc$ClinicianSocialPhob <- recode_factor(dat.cc$mhd.social_anxiety_numeric,
                                            "0" = "No social phobia diagnosis",
                                            "1" = "Social phobia diagnosis",
                                            "-77" = NULL,
                                            "-99" = NULL,
                                            .missing = NULL)

summary(dat.cc$ClinicianSocialPhob)

```

```{r clinician diagnosis panic disorder as factor}

dat.cc$ClinicianPanicDis <- recode_factor(dat.cc$mhd.panic_disorder_numeric,
                                            "0" = "No panic disorder diagnosis",
                                            "1" = "Panic disorder diagnosis",
                                            "-77" = NULL,
                                            "-88" = NULL,
                                            "-99" = NULL,
                                            .missing = NULL)

summary(dat.cc$ClinicianPanicDis)

```

```{r clinician diagnosis panic attacks as factor}

dat.cc$ClinicianPanicAttacks <- recode_factor(dat.cc$mhd.panic_attacks_numeric,
                                            "0" = "No panic attacks diagnosis",
                                            "1" = "Panic attacks diagnosis",
                                            "-77" = NULL,
                                            "-88" = NULL,
                                            "-99" = NULL,
                                            .missing = NULL)

summary(dat.cc$ClinicianPanicAttacks)

```

```{r clinician diagnosis agoraphobia as factor}

dat.cc$ClinicianAgoraphobia <- recode_factor(dat.cc$mhd.agoraphobia_numeric,
                                            "0" = "No agoraphobia diagnosis",
                                            "1" = "Agoraphobia diagnosis",
                                            "-77" = NULL,
                                            "-88" = NULL,
                                            "-99" = NULL,
                                            .missing = NULL)

summary(dat.cc$ClinicianAgoraphobia)

```

## Create any anxiety variables (clinician and lifetime)

```{r create any anxiety variables}
#Create clinician and lifetime any anxiety variables
dat.cc <- dat.cc %>% 
  mutate(ClinicianAnyAnx.n =
           case_when(
             mhd.GAD_numeric == 0 & 
               mhd.specific_phobia_numeric == 0 & mhd.social_anxiety_numeric == 0 &
               mhd.panic_disorder_numeric == 0 & mhd.agoraphobia_numeric == 0 ~ 0,
             mhd.GAD_numeric == 1 | mhd.specific_phobia_numeric == 1 | 
               mhd.social_anxiety_numeric == 1 |
               mhd.panic_disorder_numeric == 1 | mhd.agoraphobia_numeric == 1 ~ 1
           ),
         LifetimeAnyAnx.n = 
           case_when(
             cidia.diagnosis_numeric == 0 & spec.diagnosis_numeric == 0 & 
               socp.diagnosis_numeric == 0 &
               pad.diagnosis_numeric == 0 & agp.diagnosis_numeric == 0 ~ 0,
             cidia.diagnosis_numeric == 1 | spec.diagnosis_numeric == 1 |
               socp.diagnosis_numeric == 1 |
               pad.diagnosis_numeric == 1 | agp.diagnosis_numeric == 1 ~ 1
           ))

#Recode as factors
dat.cc$ClinicianAnyAnx <- recode_factor(dat.cc$ClinicianAnyAnx.n,
                                        "0" = "No anxiety diagnosis",
                                        "1" = "Any anxiety diagnosis",
                                        .missing = NULL)

dat.cc$LifetimeAnyAnx <- recode_factor(dat.cc$LifetimeAnyAnx.n,
                                        "0" = "Never had anxiety",
                                        "1" = "Lifetime any anxiety")

#Get frequencies
freq(dat.cc$ClinicianAnyAnx)
freq(dat.cc$LifetimeAnyAnx)
```

```{r Save combined dataset as rds file}
saveRDS(object = dat.cc, file = paste0(cleaned_path, "combined_cleaned_new_variables.rds"))
```

