---
title: "DIAGCOMP_sensitivity_specificity: Data freeze 1.0"
author: "Molly R. Davies"
date: 18/04/2021
output:  
  html_document:
    df_print: paged
    toc: yes
    toc_depth: 2
    toc_float:
      collapsed: false
    number_sections: false
    highlight: monochrome
    theme: cerulean
code_folding: show

html_notebook:
  theme: cerulean
toc: yes
---

This script runs sensitivity and specificity analyses for single-item and algorithm-based major depression and anxiety disorder diagnoses variables on the GLAD Study and COPING NIHR BioResource (NBR) data. 

Results are reported in the paper "Comparison of algorithm-based versus single-item phenotyping measures of depression and anxiety disorders in the GLAD Study cohort" - Davies et al (in prep).

Script written by M. R. Davies.
Email:  molly.davies@kcl.ac.uk

All scripts for the paper can be accessed at:
https://github.com/mollyrdavies/GLAD-Diagnostic-algorithms.git

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Set up
```{r install packages}

#install.packages("reshape2")
#install.packages("tidyverse")
#install.packages("knitr")
#install.packages("kableExtra")
#install.packages("descr")
#install.packages("caret")
#install.packages("irr")
#install.packages("hablar")
#install.packages("patchwork")
#install.packages("car")
#install.packages("ggpubr")
#install.packages("epiR")

```

```{r import packages}
library(caret)
library(irr)
library(ggpubr)
library(descr)
library(kableExtra)
library(epiR)
library(tidyverse)
```

```{r source file paths}
source("../../DF1.0_data_path.R")
```

```{r read data}
dat <- read_rds(paste0(cleaned_path, "DIAGCOMP_final_dataset.rds"))
```

# Variables
Create new dataset with only crosstab variables of interest
```{r select variables}
cidi <- dat %>%
  select("ID",
         "sample",
         "mhd.mdd",
         "mhd.gad",
         "mhd.specific_phobia",
         "mhd.social_anxiety",
         "mhd.panic_attacks",
         "mhd.panic_disorder",
         "mhd.agoraphobia",
         "ClinicianAnyAnx.n",
         "cidid.diagnosis_numeric",
         "cidia.diagnosis_numeric",
         "spec.diagnosis_numeric",
         "socp.diagnosis_numeric",
         "pad.diagnosis_numeric",
         "agp.diagnosis_numeric",
         "LifetimeAnyAnx.n"
         )
```

Ensure that all factor levels are the same for the variables, which is required to conduct the sensitivity/specificity analyses.
```{r create new factor version of variables}

cidi <- cidi %>% 
  mutate(ClinicianMDD.f =
           as.factor(case_when(
             mhd.mdd == 0 ~ "No diagnosis",
             mhd.mdd == 1 ~ "Diagnosis"
           )),
         ClinicianGAD.f =
           as.factor(case_when(
             mhd.gad == 0 ~ "No diagnosis",
             mhd.gad == 1 ~ "Diagnosis"
         )),
         ClinicianSpecPhob.f = 
           as.factor(case_when(
             mhd.specific_phobia == 0 ~ "No diagnosis",
             mhd.specific_phobia == 1 ~ "Diagnosis"
           )),
         ClinicianSocialPhob.f = 
           as.factor(case_when(
             mhd.social_anxiety == 0 ~ "No diagnosis",
             mhd.social_anxiety == 1 ~ "Diagnosis"
           )),
         ClinicianPanicDis.f = 
           as.factor(case_when(
             mhd.panic_disorder == 0 ~ "No diagnosis",
             mhd.panic_disorder == 1 ~ "Diagnosis"
           )),
         ClinicianPanicAttacks.f =
           as.factor(case_when(
             mhd.panic_attacks == 0 ~ "No diagnosis",
             mhd.panic_attacks == 1 ~ "Diagnosis"
           )),
         ClinicianAgoraphobia.f = 
           as.factor(case_when(
             mhd.agoraphobia == 0 ~ "No diagnosis",
             mhd.agoraphobia == 1 ~ "Diagnosis"
           )),
         ClinicianAnyAnx.f = 
           as.factor(case_when(
             ClinicianAnyAnx.n == 0 ~ "No diagnosis",
             ClinicianAnyAnx.n == 1 ~ "Diagnosis"
           )),
         LifetimeMDD.f =
           as.factor(case_when(
             cidid.diagnosis_numeric == 0 ~ "No diagnosis",
             cidid.diagnosis_numeric == 1 ~ "Diagnosis"
           )),
         LifetimeGAD.f =
           as.factor(case_when(
             cidia.diagnosis_numeric == 0 ~ "No diagnosis",
             cidia.diagnosis_numeric == 1 ~ "Diagnosis"
         )),
         LifetimeSpecPhob.f = 
           as.factor(case_when(
             spec.diagnosis_numeric == 0 ~ "No diagnosis",
             spec.diagnosis_numeric == 1 ~ "Diagnosis"
           )),
         LifetimeSocialPhob.f = 
           as.factor(case_when(
             socp.diagnosis_numeric == 0 ~ "No diagnosis",
             socp.diagnosis_numeric == 1 ~ "Diagnosis"
           )),
         LifetimePanicDis.f = 
           as.factor(case_when(
             pad.diagnosis_numeric == 0 ~ "No diagnosis",
             pad.diagnosis_numeric == 1 ~ "Diagnosis"
           )),
         LifetimeAgoraphobia.f = 
           as.factor(case_when(
             agp.diagnosis_numeric == 0 ~ "No diagnosis",
             agp.diagnosis_numeric == 1 ~ "Diagnosis"
           )),
         LifetimeAnyAnx.f = 
           as.factor(case_when(
             LifetimeAnyAnx.n == 0 ~ "No diagnosis",
             LifetimeAnyAnx.n == 1 ~ "Diagnosis"
           ))
         )
      
```


Since single-item panic disorder was added midway through data collection, we want to ensure all comparisons with panic attacks are made with the same participants
```{r recode SI panic attacks as NA when panic disorder NA}
#Create variable
cidi <- cidi %>% 
  mutate(ClinicianPanicAttacks.n.cc =
           case_when(is.na(ClinicianPanicDis.f) ~ NA_real_,
                     !is.na(ClinicianPanicDis.f) ~ mhd.panic_attacks)
         )
#Recode as factor
cidi <- cidi %>% 
  mutate(ClinicianPanicAttacks.f.cc = 
           as.factor(case_when(
             ClinicianPanicAttacks.n.cc == 0 ~ "No diagnosis",
             ClinicianPanicAttacks.n.cc == 1 ~ "Diagnosis")
             )
         )
```


# Cross Tabulations and Agreement
Run agreement (accuracy), sensitivity, specificity, Cohen's kappa, and McNemar's Test analyses

```{r set unused agreement statistics}
#These will be removed from the agreements table
unused_agreement <- c("AccuracyNull", "AccuracyPValue", "Balanced Accuracy",
                      "Detection Prevalence", "Detection Rate", "F1",
                      "Neg Pred Value", "Pos Pred Value", "Precision", "Prevalence", "Recall",
                      "Sensitivity", "Specificity")
```


## Full sample

### Algorithm-based diagnosis as reference point

Major depressive disorder
```{r Full sample MDD SI-AB crosstabs and agreement}
si_ab_mdd.cM <- confusionMatrix(cidi$ClinicianMDD.f,
                            cidi$LifetimeMDD.f,
                            positive = "Diagnosis",
                            dnn = c("Single-item", "Algorithm-based"))

#Create dataframe of agreements
si_ab_mdd.classes <- as.matrix(si_ab_mdd.cM, what = "classes")
si_ab_mdd.overall <- as.matrix(si_ab_mdd.cM, what = "overall")
si_ab_mdd.raw <- as.data.frame(rbind(si_ab_mdd.classes,
                                     si_ab_mdd.overall))
colnames(si_ab_mdd.raw) <- "MDD"

#Fromat dataframe
si_ab_mdd.incomplete <- si_ab_mdd.raw %>%  
  rownames_to_column() %>% 
  mutate(rowname = rownames(si_ab_mdd.raw)) %>% 
  gather(Diagnosis, value, -rowname) %>% 
  spread(rowname, value) %>% 
  select(-unused_agreement)

#Calculate sensitivity and specificity with 95% CI
si_ab_mdd.95ci <- summary(epiR::epi.tests(as.table(as.matrix(si_ab_mdd.cM)), conf.level = 0.95)) %>%
  round(., 2) %>% 
  rownames_to_column() %>% 
  filter(rowname == "se" | rowname == "sp") %>% 
  mutate(combined =
           sprintf("%.2f (%.2f, %.2f)", 
                   est,
                   lower,
                   upper),
         Diagnosis = "MDD") %>% 
  select(-c(est, lower, upper)) %>% 
  pivot_wider(names_from = rowname, values_from = combined) %>% 
  rename("Sensitivity" = "se",
         "Specificity" = "sp")

#Combine dataframe with sensitivity/specificity
si_ab_mdd.df <- merge(si_ab_mdd.incomplete,
                      si_ab_mdd.95ci)

#Create dataframe of crosstab
si_ab_mdd.xtabs <- as.data.frame(as.matrix(si_ab_mdd.cM))
si_ab_mdd.xtabs.df <- si_ab_mdd.xtabs %>% 
  rownames_to_column() %>% 
  rename("AB Yes" =
           "Diagnosis",
         "AB No" = "No diagnosis",
        "Crosstab"  = "rowname") %>% 
  mutate(Diagnosis = "MDD",
         Crosstab = recode_factor(Crosstab,
                                 "Diagnosis" = "SI Yes",
                                 "No diagnosis" = "SI No")
         ) 

si_ab_mdd.df
si_ab_mdd.xtabs.df
si_ab_mdd.95ci
```

Generalised anxiety disorder
```{r Full sample GAD SI-AB crosstabs and agreement}
si_ab_gad.cM <- confusionMatrix(cidi$ClinicianGAD.f,
                                cidi$LifetimeGAD.f,
                                positive = "Diagnosis",
                                dnn = c("Single-item", "Algorithm-based"))

#Create dataframe of agreements
si_ab_gad.classes<- as.matrix(si_ab_gad.cM, what = "classes")
si_ab_gad.overall <- as.matrix(si_ab_gad.cM, what = "overall")
si_ab_gad.raw <- as.data.frame(rbind(si_ab_gad.classes,
                                     si_ab_gad.overall))
colnames(si_ab_gad.raw) <- "GAD"

#Fromat dataframe
si_ab_gad.incomplete <- si_ab_gad.raw %>% 
  rownames_to_column() %>% 
  mutate(rowname = rownames(si_ab_gad.raw)) %>% 
  gather(Diagnosis, value, -rowname) %>% 
  spread(rowname, value) %>% 
  select(-unused_agreement)

#Calculate sensitivity and specificity with 95% CI
si_ab_gad.95ci <- summary(epiR::epi.tests(as.table(as.matrix(si_ab_gad.cM)), conf.level = 0.95)) %>%
  round(., 2) %>% 
  rownames_to_column() %>% 
  filter(rowname == "se" | rowname == "sp") %>% 
  mutate(combined =
           sprintf("%.2f (%.2f, %.2f)", 
                   est,
                   lower,
                   upper),
         Diagnosis = "GAD") %>% 
  select(-c(est, lower, upper)) %>% 
  pivot_wider(names_from = rowname, values_from = combined) %>% 
  rename("Sensitivity" = "se",
         "Specificity" = "sp")

#Combine dataframe with sensitivity/specificity
si_ab_gad.df <- merge(si_ab_gad.incomplete,
                      si_ab_gad.95ci)

#Create dataframe of crosstab
si_ab_gad.xtabs <- as.data.frame(as.matrix(si_ab_gad.cM))
si_ab_gad.xtabs.df <- si_ab_gad.xtabs %>% 
  rownames_to_column() %>% 
  rename("AB Yes" =
           "Diagnosis",
         "AB No" = "No diagnosis",
        "Crosstab"  = "rowname") %>% 
  mutate(Diagnosis = "GAD",
         Crosstab = recode_factor(Crosstab,
                                 "Diagnosis" = "SI Yes",
                                 "No diagnosis" = "SI No")
         )

si_ab_gad.df
si_ab_gad.xtabs.df
```

Specific phobia
```{r Full sample Specific phobia SI-AB crosstabs and agreement}
si_ab_spec.cM <- confusionMatrix(cidi$ClinicianSpecPhob.f,
                                 cidi$LifetimeSpecPhob.f,
                                 positive = "Diagnosis",
                                 dnn = c("Single-item", "Algorithm-based"))

#Create dataframe of agreements
si_ab_spec.classes<- as.matrix(si_ab_spec.cM, what = "classes")
si_ab_spec.overall <- as.matrix(si_ab_spec.cM, what = "overall")
si_ab_spec.raw <- as.data.frame(rbind(si_ab_spec.classes,
                                     si_ab_spec.overall))
colnames(si_ab_spec.raw) <- "SPEC"

#Fromat dataframe
si_ab_spec.incomplete <- si_ab_spec.raw %>% 
  rownames_to_column() %>% 
  mutate(rowname = rownames(si_ab_spec.raw)) %>% 
  gather(Diagnosis, value, -rowname) %>% 
  spread(rowname, value) %>% 
  select(-unused_agreement)

#Calculate sensitivity and specificity with 95% CI
si_ab_spec.95ci <- summary(epiR::epi.tests(as.table(as.matrix(si_ab_spec.cM)), conf.level = 0.95)) %>%
  round(., 2) %>% 
  rownames_to_column() %>% 
  filter(rowname == "se" | rowname == "sp") %>% 
  mutate(combined =
           sprintf("%.2f (%.2f, %.2f)", 
                   est,
                   lower,
                   upper),
         Diagnosis = "SPEC") %>% 
  select(-c(est, lower, upper)) %>% 
  pivot_wider(names_from = rowname, values_from = combined) %>% 
  rename("Sensitivity" = "se",
         "Specificity" = "sp")

#Combine dataframe with sensitivity/specificity
si_ab_spec.df <- merge(si_ab_spec.incomplete,
                      si_ab_spec.95ci)

#Create dataframe of crosstab
si_ab_spec.xtabs <- as.data.frame(as.matrix(si_ab_spec.cM))
si_ab_spec.xtabs.df <- si_ab_spec.xtabs %>% 
  rownames_to_column() %>% 
  rename("AB Yes" =
           "Diagnosis",
         "AB No" = "No diagnosis",
        "Crosstab"  = "rowname") %>% 
  mutate(Diagnosis = "SPEC",
         Crosstab = recode_factor(Crosstab,
                                 "Diagnosis" = "SI Yes",
                                 "No diagnosis" = "SI No")
         )

si_ab_spec.df
si_ab_spec.xtabs.df
```

Social anxiety disorder
```{r Full sample Social anxiety disorder SI-AB crosstabs and agreement}
si_ab_socp.cM <- confusionMatrix(cidi$ClinicianSocialPhob.f,
                                  cidi$LifetimeSocialPhob.f,
                                  positive = "Diagnosis",
                                  dnn = c("Single-item", "Algorithm-based"))

#Create dataframe of agreements
si_ab_socp.classes<- as.matrix(si_ab_socp.cM, what = "classes")
si_ab_socp.overall <- as.matrix(si_ab_socp.cM, what = "overall")
si_ab_socp.raw <- as.data.frame(rbind(si_ab_socp.classes,
                                     si_ab_socp.overall))
colnames(si_ab_socp.raw) <- "SOCP"

#Fromat dataframe
si_ab_socp.incomplete <- si_ab_socp.raw %>% 
  rownames_to_column() %>% 
  mutate(rowname = rownames(si_ab_socp.raw)) %>% 
  gather(Diagnosis, value, -rowname) %>% 
  spread(rowname, value) %>% 
  select(-unused_agreement)

#Calculate sensitivity and specificity with 95% CI
si_ab_socp.95ci <- summary(epiR::epi.tests(as.table(as.matrix(si_ab_socp.cM)), conf.level = 0.95)) %>%
  round(., 2) %>% 
  rownames_to_column() %>% 
  filter(rowname == "se" | rowname == "sp") %>% 
  mutate(combined =
           sprintf("%.2f (%.2f, %.2f)", 
                   est,
                   lower,
                   upper),
         Diagnosis = "SOCP") %>% 
  select(-c(est, lower, upper)) %>% 
  pivot_wider(names_from = rowname, values_from = combined) %>% 
  rename("Sensitivity" = "se",
         "Specificity" = "sp")

#Combine dataframe with sensitivity/specificity
si_ab_socp.df <- merge(si_ab_socp.incomplete,
                      si_ab_socp.95ci)

#Create dataframe of crosstab
si_ab_socp.xtabs <- as.data.frame(as.matrix(si_ab_socp.cM))
si_ab_socp.xtabs.df <- si_ab_socp.xtabs %>% 
  rownames_to_column() %>% 
  rename("AB Yes" =
           "Diagnosis",
         "AB No" = "No diagnosis",
        "Crosstab"  = "rowname") %>% 
  mutate(Diagnosis = "SOCP",
         Crosstab = recode_factor(Crosstab,
                                 "Diagnosis" = "SI Yes",
                                 "No diagnosis" = "SI No")
         )

si_ab_socp.df
si_ab_socp.xtabs.df
```

Panic disorder
```{r Full sample Panic disorder SI-AB crosstabs and agreement}
si_ab_pad.cM <- confusionMatrix(cidi$ClinicianPanicDis.f,
                                cidi$LifetimePanicDis.f,
                                positive = "Diagnosis",
                                dnn = c("Single-item", "Algorithm-based"))

#Create dataframe of agreements
si_ab_pad.classes<- as.matrix(si_ab_pad.cM, what = "classes")
si_ab_pad.overall <- as.matrix(si_ab_pad.cM, what = "overall")
si_ab_pad.raw <- as.data.frame(rbind(si_ab_pad.classes,
                                     si_ab_pad.overall))
colnames(si_ab_pad.raw) <- "PAD"

#Fromat dataframe
si_ab_pad.incomplete <- si_ab_pad.raw %>% 
  rownames_to_column() %>% 
  mutate(rowname = rownames(si_ab_pad.raw)) %>% 
  gather(Diagnosis, value, -rowname) %>% 
  spread(rowname, value) %>% 
  select(-unused_agreement)

#Calculate sensitivity and specificity with 95% CI
si_ab_pad.95ci <- summary(epiR::epi.tests(as.table(as.matrix(si_ab_pad.cM)), conf.level = 0.95)) %>%
  round(., 2) %>% 
  rownames_to_column() %>% 
  filter(rowname == "se" | rowname == "sp") %>% 
  mutate(combined =
           sprintf("%.2f (%.2f, %.2f)", 
                   est,
                   lower,
                   upper),
         Diagnosis = "PAD") %>% 
  select(-c(est, lower, upper)) %>% 
  pivot_wider(names_from = rowname, values_from = combined) %>% 
  rename("Sensitivity" = "se",
         "Specificity" = "sp")

#Combine dataframe with sensitivity/specificity
si_ab_pad.df <- merge(si_ab_pad.incomplete,
                      si_ab_pad.95ci)

#Create dataframe of crosstab
si_ab_pad.xtabs <- as.data.frame(as.matrix(si_ab_pad.cM))
si_ab_pad.xtabs.df <- si_ab_pad.xtabs %>% 
  rownames_to_column() %>% 
  rename("AB Yes" =
           "Diagnosis",
         "AB No" = "No diagnosis",
        "Crosstab"  = "rowname") %>% 
  mutate(Diagnosis = "PAD",
         Crosstab = recode_factor(Crosstab,
                                 "Diagnosis" = "SI Yes",
                                 "No diagnosis" = "SI No")
         )

si_ab_pad.df
si_ab_pad.xtabs.df
```

Panic attacks
The single-item panic attack variable here is being compared to lifetime panic disorder.
```{r Full sample Panic Attacks SI-AB crosstabs and agreement for Panic Disorder}
si_ab_pattacks.cM <- confusionMatrix(cidi$ClinicianPanicAttacks.f.cc,
                                cidi$LifetimePanicDis.f, 
                                positive = "Diagnosis",
                                dnn = c("Single-item", "Algorithm-based"))

#Create dataframe of agreements
si_ab_pattacks.classes<- as.matrix(si_ab_pattacks.cM, what = "classes")
si_ab_pattacks.overall <- as.matrix(si_ab_pattacks.cM, what = "overall")
si_ab_pattacks.raw <- as.data.frame(rbind(si_ab_pattacks.classes,
                                     si_ab_pattacks.overall))
colnames(si_ab_pattacks.raw) <- "PanicAttacks"

#Fromat dataframe
si_ab_pattacks.incomplete <- si_ab_pattacks.raw %>% 
  rownames_to_column() %>% 
  mutate(rowname = rownames(si_ab_pattacks.raw)) %>% 
  gather(Diagnosis, value, -rowname) %>% 
  spread(rowname, value) %>% 
  select(-unused_agreement)

#Calculate sensitivity and specificity with 95% CI
si_ab_pattacks.95ci <- summary(epiR::epi.tests(as.table(as.matrix(si_ab_pattacks.cM)), conf.level = 0.95)) %>%
  round(., 2) %>% 
  rownames_to_column() %>% 
  filter(rowname == "se" | rowname == "sp") %>% 
  mutate(combined =
           sprintf("%.2f (%.2f, %.2f)", 
                   est,
                   lower,
                   upper),
         Diagnosis = "PanicAttacks") %>% 
  select(-c(est, lower, upper)) %>% 
  pivot_wider(names_from = rowname, values_from = combined) %>% 
  rename("Sensitivity" = "se",
         "Specificity" = "sp")

#Combine dataframe with sensitivity/specificity
si_ab_pattacks.df <- merge(si_ab_pattacks.incomplete,
                      si_ab_pattacks.95ci)

#Create dataframe of crosstab
si_ab_pattacks.xtabs <- as.data.frame(as.matrix(si_ab_pattacks.cM))
si_ab_pattacks.xtabs.df <- si_ab_pattacks.xtabs %>% 
  rownames_to_column() %>% 
  rename("AB Yes" =
           "Diagnosis",
         "AB No" = "No diagnosis",
        "Crosstab"  = "rowname") %>% 
  mutate(Diagnosis = "PanicAttacks",
         Crosstab = recode_factor(Crosstab,
                                 "Diagnosis" = "SI Yes",
                                 "No diagnosis" = "SI No")
         )

si_ab_pattacks.df
si_ab_pattacks.xtabs.df
```

Agoraphobia
```{r Full sample Agoraphobia SI-AB crosstabs and agreement}
si_ab_agp.cM <- confusionMatrix(cidi$ClinicianAgoraphobia.f,
                                cidi$LifetimeAgoraphobia.f,
                                positive = "Diagnosis",
                                dnn = c("Single-item", "Algorithm-based"))

#Create dataframe of agreements
si_ab_agp.classes<- as.matrix(si_ab_agp.cM, what = "classes")
si_ab_agp.overall <- as.matrix(si_ab_agp.cM, what = "overall")
si_ab_agp.raw <- as.data.frame(rbind(si_ab_agp.classes,
                                     si_ab_agp.overall))
colnames(si_ab_agp.raw) <- "AGP"

#Fromat dataframe
si_ab_agp.incomplete <- si_ab_agp.raw %>% 
  rownames_to_column() %>% 
  mutate(rowname = rownames(si_ab_agp.raw)) %>% 
  gather(Diagnosis, value, -rowname) %>% 
  spread(rowname, value) %>% 
  select(-unused_agreement)

#Calculate sensitivity and specificity with 95% CI
si_ab_agp.95ci <- summary(epiR::epi.tests(as.table(as.matrix(si_ab_agp.cM)), conf.level = 0.95)) %>%
  round(., 2) %>% 
  rownames_to_column() %>% 
  filter(rowname == "se" | rowname == "sp") %>% 
  mutate(combined =
           sprintf("%.2f (%.2f, %.2f)", 
                   est,
                   lower,
                   upper),
         Diagnosis = "AGP") %>% 
  select(-c(est, lower, upper)) %>% 
  pivot_wider(names_from = rowname, values_from = combined) %>% 
  rename("Sensitivity" = "se",
         "Specificity" = "sp")

#Combine dataframe with sensitivity/specificity
si_ab_agp.df <- merge(si_ab_agp.incomplete,
                      si_ab_agp.95ci)

#Create dataframe of crosstab
si_ab_agp.xtabs <- as.data.frame(as.matrix(si_ab_agp.cM))
si_ab_agp.xtabs.df <- si_ab_agp.xtabs %>% 
  rownames_to_column() %>% 
  rename("AB Yes" =
           "Diagnosis",
         "AB No" = "No diagnosis",
        "Crosstab"  = "rowname") %>% 
  mutate(Diagnosis = "AGP",
         Crosstab = recode_factor(Crosstab,
                                 "Diagnosis" = "SI Yes",
                                 "No diagnosis" = "SI No")
         )

si_ab_agp.df
si_ab_agp.xtabs.df
```

Any anxiety
```{r Full sample Any Anxiety SI-AB crosstabs and agreement}
si_ab_anyanx.cM <- confusionMatrix(cidi$ClinicianAnyAnx.f, 
                                cidi$LifetimeAnyAnx.f,
                                positive = "Diagnosis",
                                dnn = c("Single-item", "Algorithm-based"))

#Create dataframe of agreements
si_ab_anyanx.classes<- as.matrix(si_ab_anyanx.cM, what = "classes")
si_ab_anyanx.overall <- as.matrix(si_ab_anyanx.cM, what = "overall")
si_ab_anyanx.raw <- as.data.frame(rbind(si_ab_anyanx.classes,
                                     si_ab_anyanx.overall))
colnames(si_ab_anyanx.raw) <- "AnyAnxiety"

#Fromat dataframe
si_ab_anyanx.incomplete <- si_ab_anyanx.raw %>% 
  rownames_to_column() %>% 
  mutate(rowname = rownames(si_ab_anyanx.raw)) %>% 
  gather(Diagnosis, value, -rowname) %>% 
  spread(rowname, value) %>% 
  select(-unused_agreement)

#Calculate sensitivity and specificity with 95% CI
si_ab_anyanx.95ci <- summary(epiR::epi.tests(as.table(as.matrix(si_ab_anyanx.cM)), conf.level = 0.95)) %>%
  round(., 2) %>% 
  rownames_to_column() %>% 
  filter(rowname == "se" | rowname == "sp") %>% 
  mutate(combined =
           sprintf("%.2f (%.2f, %.2f)", 
                   est,
                   lower,
                   upper),
         Diagnosis = "AnyAnxiety") %>% 
  select(-c(est, lower, upper)) %>% 
  pivot_wider(names_from = rowname, values_from = combined) %>% 
  rename("Sensitivity" = "se",
         "Specificity" = "sp")

#Combine dataframe with sensitivity/specificity
si_ab_anyanx.df <- merge(si_ab_anyanx.incomplete,
                      si_ab_anyanx.95ci)

#Create dataframe of crosstab
si_ab_anyanx.xtabs <- as.data.frame(as.matrix(si_ab_anyanx.cM))
si_ab_anyanx.xtabs.df <- si_ab_anyanx.xtabs %>% 
  rownames_to_column() %>% 
  rename("AB Yes" =
           "Diagnosis",
         "AB No" = "No diagnosis",
        "Crosstab"  = "rowname") %>% 
  mutate(Diagnosis = "AnyAnxiety",
         Crosstab = recode_factor(Crosstab,
                                 "Diagnosis" = "SI Yes",
                                 "No diagnosis" = "SI No")
         )

si_ab_anyanx.df
si_ab_anyanx.xtabs.df
```

```{r Full sample combine SI-AB agreement tables}
si_ab_all.raw <- bind_rows(si_ab_mdd.df,
                           si_ab_anyanx.df,
                           si_ab_gad.df,
                           si_ab_spec.df,
                           si_ab_socp.df,
                           si_ab_pad.df,
                           si_ab_pattacks.df,
                           si_ab_agp.df)

si_ab_all <- si_ab_all.raw %>% 
  rename("Sensitivity SI-AB" = "Sensitivity",
         "Specificity SI-AB" = "Specificity") %>% 
  relocate(Kappa, .after = last_col())

si_ab_all
```

```{r Full sample combine all xtabs tables}
all_xtabs.raw <- bind_rows(si_ab_mdd.xtabs.df,
                           si_ab_anyanx.xtabs.df,
                           si_ab_gad.xtabs.df,
                           si_ab_spec.xtabs.df,
                           si_ab_socp.xtabs.df,
                           si_ab_pad.xtabs.df,
                           si_ab_pattacks.xtabs.df,
                           si_ab_agp.xtabs.df)

all_xtabs <- all_xtabs.raw %>%  
  relocate(Diagnosis)

all_xtabs
```

### Single-item diagnosis as reference point

Major depressive disorder
```{r Full sample MDD AB-SI crosstabs and agreement}
ab_si_mdd.cM <- confusionMatrix(cidi$LifetimeMDD.f,
                                cidi$ClinicianMDD.f, 
                                positive = "Diagnosis",
                                dnn = c("Algorithm-based", "Single-item"))

#Create dataframe of agreements
ab_si_mdd.classes<- as.matrix(ab_si_mdd.cM, what = "classes")
ab_si_mdd.overall <- as.matrix(ab_si_mdd.cM, what = "overall")
ab_si_mdd.raw <- as.data.frame(rbind(ab_si_mdd.classes,
                                     ab_si_mdd.overall))
colnames(ab_si_mdd.raw) <- "MDD"

#Fromat dataframe
ab_si_mdd.incomplete <- ab_si_mdd.raw %>% 
  rownames_to_column() %>% 
  mutate(rowname = rownames(ab_si_mdd.raw)) %>% 
  gather(Diagnosis, value, -rowname) %>% 
  spread(rowname, value) %>% 
  select(-unused_agreement)

#Calculate sensitivity and specificity with 95% CI
ab_si_mdd.95ci <- summary(epiR::epi.tests(as.table(as.matrix(ab_si_mdd.cM)), conf.level = 0.95)) %>%
  round(., 2) %>% 
  rownames_to_column() %>% 
  filter(rowname == "se" | rowname == "sp") %>% 
  mutate(combined =
           sprintf("%.2f (%.2f, %.2f)", 
                   est,
                   lower,
                   upper),
         Diagnosis = "MDD") %>% 
  select(-c(est, lower, upper)) %>% 
  pivot_wider(names_from = rowname, values_from = combined) %>% 
  rename("Sensitivity" = "se",
         "Specificity" = "sp")

#Combine dataframe with sensitivity/specificity
ab_si_mdd.df <- merge(ab_si_mdd.incomplete,
                      ab_si_mdd.95ci)

ab_si_mdd.df
```

Generalised anxiety disorder
```{r Full sample GAD AB-SI crosstabs and agreement}
ab_si_gad.cM <- confusionMatrix(cidi$LifetimeGAD.f,
                                cidi$ClinicianGAD.f, 
                                positive = "Diagnosis",
                                dnn = c("Algorithm-based", "Single-item"))

#Create dataframe of agreements
ab_si_gad.classes<- as.matrix(ab_si_gad.cM, what = "classes")
ab_si_gad.overall <- as.matrix(ab_si_gad.cM, what = "overall")
ab_si_gad.raw <- as.data.frame(rbind(ab_si_gad.classes,
                                     ab_si_gad.overall))
colnames(ab_si_gad.raw) <- "GAD"

#Fromat dataframe
ab_si_gad.incomplete <- ab_si_gad.raw %>% 
  rownames_to_column() %>% 
  mutate(rowname = rownames(ab_si_gad.raw)) %>% 
  gather(Diagnosis, value, -rowname) %>% 
  spread(rowname, value) %>% 
  select(-unused_agreement)

#Calculate sensitivity and specificity with 95% CI
ab_si_gad.95ci <- summary(epiR::epi.tests(as.table(as.matrix(ab_si_gad.cM)), conf.level = 0.95)) %>%
  round(., 2) %>% 
  rownames_to_column() %>% 
  filter(rowname == "se" | rowname == "sp") %>% 
  mutate(combined =
           sprintf("%.2f (%.2f, %.2f)", 
                   est,
                   lower,
                   upper),
         Diagnosis = "GAD") %>% 
  select(-c(est, lower, upper)) %>% 
  pivot_wider(names_from = rowname, values_from = combined) %>% 
  rename("Sensitivity" = "se",
         "Specificity" = "sp")

#Combine dataframe with sensitivity/specificity
ab_si_gad.df <- merge(ab_si_gad.incomplete,
                      ab_si_gad.95ci)

ab_si_gad.df
```

Specific phobia
```{r Full sample Specific phobia AB-SI crosstabs and agreement}
ab_si_spec.cM <- confusionMatrix(cidi$LifetimeSpecPhob.f,
                                 cidi$ClinicianSpecPhob.f, 
                                 positive = "Diagnosis",
                                 dnn = c("Algorithm-based", "Single-item"))

#Create dataframe of agreements
ab_si_spec.classes<- as.matrix(ab_si_spec.cM, what = "classes")
ab_si_spec.overall <- as.matrix(ab_si_spec.cM, what = "overall")
ab_si_spec.raw <- as.data.frame(rbind(ab_si_spec.classes,
                                     ab_si_spec.overall))
colnames(ab_si_spec.raw) <- "SPEC"

#Fromat dataframe
ab_si_spec.incomplete <- ab_si_spec.raw %>% 
  rownames_to_column() %>% 
  mutate(rowname = rownames(ab_si_spec.raw)) %>% 
  gather(Diagnosis, value, -rowname) %>% 
  spread(rowname, value) %>% 
  select(-unused_agreement)

#Calculate sensitivity and specificity with 95% CI
ab_si_spec.95ci <- summary(epiR::epi.tests(as.table(as.matrix(ab_si_spec.cM)), conf.level = 0.95)) %>%
  round(., 2) %>% 
  rownames_to_column() %>% 
  filter(rowname == "se" | rowname == "sp") %>% 
  mutate(combined =
           sprintf("%.2f (%.2f, %.2f)", 
                   est,
                   lower,
                   upper),
         Diagnosis = "SPEC") %>% 
  select(-c(est, lower, upper)) %>% 
  pivot_wider(names_from = rowname, values_from = combined) %>% 
  rename("Sensitivity" = "se",
         "Specificity" = "sp")

#Combine dataframe with sensitivity/specificity
ab_si_spec.df <- merge(ab_si_spec.incomplete,
                      ab_si_spec.95ci)

ab_si_spec.df
```

Social anxiety disorder
```{r Full sample Social anxiety disorder AB-SI crosstabs and agreement}
ab_si_socp.cM <- confusionMatrix(cidi$LifetimeSocialPhob.f,
                                 cidi$ClinicianSocialPhob.f, 
                                 positive = "Diagnosis",
                                 dnn = c("Algorithm-based", "Single-item"))

#Create dataframe of agreements
ab_si_socp.classes<- as.matrix(ab_si_socp.cM, what = "classes")
ab_si_socp.overall <- as.matrix(ab_si_socp.cM, what = "overall")
ab_si_socp.raw <- as.data.frame(rbind(ab_si_socp.classes,
                                     ab_si_socp.overall))
colnames(ab_si_socp.raw) <- "SOCP"

#Fromat dataframe
ab_si_socp.incomplete <- ab_si_socp.raw %>% 
  rownames_to_column() %>% 
  mutate(rowname = rownames(ab_si_socp.raw)) %>% 
  gather(Diagnosis, value, -rowname) %>% 
  spread(rowname, value) %>% 
  select(-unused_agreement)

#Calculate sensitivity and specificity with 95% CI
ab_si_socp.95ci <- summary(epiR::epi.tests(as.table(as.matrix(ab_si_socp.cM)), conf.level = 0.95)) %>%
  round(., 2) %>% 
  rownames_to_column() %>% 
  filter(rowname == "se" | rowname == "sp") %>% 
  mutate(combined =
           sprintf("%.2f (%.2f, %.2f)", 
                   est,
                   lower,
                   upper),
         Diagnosis = "SOCP") %>% 
  select(-c(est, lower, upper)) %>% 
  pivot_wider(names_from = rowname, values_from = combined) %>% 
  rename("Sensitivity" = "se",
         "Specificity" = "sp")

#Combine dataframe with sensitivity/specificity
ab_si_socp.df <- merge(ab_si_socp.incomplete,
                      ab_si_socp.95ci)

ab_si_socp.df
```

Panic disorder
```{r Full sample Panic disorder AB-SI crosstabs and agreement}
ab_si_pad.cM <- confusionMatrix(cidi$LifetimePanicDis.f,
                                cidi$ClinicianPanicDis.f, 
                                positive = "Diagnosis",
                                dnn = c("Algorithm-based", "Single-item"))

#Create dataframe of agreements
ab_si_pad.classes<- as.matrix(ab_si_pad.cM, what = "classes")
ab_si_pad.overall <- as.matrix(ab_si_pad.cM, what = "overall")
ab_si_pad.raw <- as.data.frame(rbind(ab_si_pad.classes,
                                     ab_si_pad.overall))
colnames(ab_si_pad.raw) <- "PAD"

#Fromat dataframe
ab_si_pad.incomplete <- ab_si_pad.raw %>% 
  rownames_to_column() %>% 
  mutate(rowname = rownames(ab_si_pad.raw)) %>% 
  gather(Diagnosis, value, -rowname) %>% 
  spread(rowname, value) %>% 
  select(-unused_agreement)

#Calculate sensitivity and specificity with 95% CI
ab_si_pad.95ci <- summary(epiR::epi.tests(as.table(as.matrix(ab_si_pad.cM)), conf.level = 0.95)) %>%
  round(., 2) %>% 
  rownames_to_column() %>% 
  filter(rowname == "se" | rowname == "sp") %>% 
  mutate(combined =
           sprintf("%.2f (%.2f, %.2f)", 
                   est,
                   lower,
                   upper),
         Diagnosis = "PAD") %>% 
  select(-c(est, lower, upper)) %>% 
  pivot_wider(names_from = rowname, values_from = combined) %>% 
  rename("Sensitivity" = "se",
         "Specificity" = "sp")

#Combine dataframe with sensitivity/specificity
ab_si_pad.df <- merge(ab_si_pad.incomplete,
                      ab_si_pad.95ci)

ab_si_pad.df
```

Panic attacks
Algorithm-based panic disorder is being compared with single-item panic attacks.
```{r Full sample Panic Attacks AB-SI crosstabs and agreement with Panic Disorder, echo=FALSE}
ab_si_pattacks.cM <- confusionMatrix(cidi$LifetimePanicDis.f, 
                                     cidi$ClinicianPanicAttacks.f.cc, 
                                     positive = "Diagnosis",
                                     dnn = c("Algorithm-based", "Single-item"))

#Create dataframe of agreements
ab_si_pattacks.classes<- as.matrix(ab_si_pattacks.cM, what = "classes")
ab_si_pattacks.overall <- as.matrix(ab_si_pattacks.cM, what = "overall")
ab_si_pattacks.raw <- as.data.frame(rbind(ab_si_pattacks.classes,
                                     ab_si_pattacks.overall))
colnames(ab_si_pattacks.raw) <- "PanicAttacks"

#Fromat dataframe
ab_si_pattacks.incomplete <- ab_si_pattacks.raw %>% 
  rownames_to_column() %>% 
  mutate(rowname = rownames(ab_si_pattacks.raw)) %>% 
  gather(Diagnosis, value, -rowname) %>% 
  spread(rowname, value) %>% 
  select(-unused_agreement)

#Calculate sensitivity and specificity with 95% CI
ab_si_pattacks.95ci <- summary(epiR::epi.tests(as.table(as.matrix(ab_si_pattacks.cM)), conf.level = 0.95)) %>%
  round(., 2) %>% 
  rownames_to_column() %>% 
  filter(rowname == "se" | rowname == "sp") %>% 
  mutate(combined =
           sprintf("%.2f (%.2f, %.2f)", 
                   est,
                   lower,
                   upper),
         Diagnosis = "PanicAttacks") %>% 
  select(-c(est, lower, upper)) %>% 
  pivot_wider(names_from = rowname, values_from = combined) %>% 
  rename("Sensitivity" = "se",
         "Specificity" = "sp")

#Combine dataframe with sensitivity/specificity
ab_si_pattacks.df <- merge(ab_si_pattacks.incomplete,
                      ab_si_pattacks.95ci)

ab_si_pattacks.df
```

Agoraphobia
```{r Full sample Agoraphobia AB-SI crosstabs and agreement}
ab_si_agp.cM <- confusionMatrix(cidi$LifetimeAgoraphobia.f, 
                                cidi$ClinicianAgoraphobia.f, 
                                positive = "Diagnosis",
                                dnn = c("Algorithm-based", "Single-item"))

#Create dataframe of agreements
ab_si_agp.classes<- as.matrix(ab_si_agp.cM, what = "classes")
ab_si_agp.overall <- as.matrix(ab_si_agp.cM, what = "overall")
ab_si_agp.raw <- as.data.frame(rbind(ab_si_agp.classes,
                                     ab_si_agp.overall))
colnames(ab_si_agp.raw) <- "AGP"

#Fromat dataframe
ab_si_agp.incomplete <- ab_si_agp.raw %>% 
  rownames_to_column() %>% 
  mutate(rowname = rownames(ab_si_agp.raw)) %>% 
  gather(Diagnosis, value, -rowname) %>% 
  spread(rowname, value) %>% 
  select(-unused_agreement)

#Calculate sensitivity and specificity with 95% CI
ab_si_agp.95ci <- summary(epiR::epi.tests(as.table(as.matrix(ab_si_agp.cM)), conf.level = 0.95)) %>%
  round(., 2) %>% 
  rownames_to_column() %>% 
  filter(rowname == "se" | rowname == "sp") %>% 
  mutate(combined =
           sprintf("%.2f (%.2f, %.2f)", 
                   est,
                   lower,
                   upper),
         Diagnosis = "AGP") %>% 
  select(-c(est, lower, upper)) %>% 
  pivot_wider(names_from = rowname, values_from = combined) %>% 
  rename("Sensitivity" = "se",
         "Specificity" = "sp")

#Combine dataframe with sensitivity/specificity
ab_si_agp.df <- merge(ab_si_agp.incomplete,
                      ab_si_agp.95ci)

ab_si_agp.df
```

Any anxiety
```{r Full sample Any Anxiety AB-SI crosstabs and agreement}
ab_si_anyanx.cM <- confusionMatrix(cidi$LifetimeAnyAnx.f,
                                   cidi$ClinicianAnyAnx.f, 
                                   positive = "Diagnosis",
                                   dnn = c("Algorithm-based", "Single-item"))

#Create dataframe of agreements
ab_si_anyanx.classes<- as.matrix(ab_si_anyanx.cM, what = "classes")
ab_si_anyanx.overall <- as.matrix(ab_si_anyanx.cM, what = "overall")
ab_si_anyanx.raw <- as.data.frame(rbind(ab_si_anyanx.classes,
                                     ab_si_anyanx.overall))
colnames(ab_si_anyanx.raw) <- "AnyAnxiety"

#Fromat dataframe
ab_si_anyanx.incomplete <- ab_si_anyanx.raw %>% 
  rownames_to_column() %>% 
  mutate(rowname = rownames(ab_si_anyanx.raw)) %>% 
  gather(Diagnosis, value, -rowname) %>% 
  spread(rowname, value) %>% 
  select(-unused_agreement)

#Calculate sensitivity and specificity with 95% CI
ab_si_anyanx.95ci <- summary(epiR::epi.tests(as.table(as.matrix(ab_si_anyanx.cM)), conf.level = 0.95)) %>%
  round(., 2) %>% 
  rownames_to_column() %>% 
  filter(rowname == "se" | rowname == "sp") %>% 
  mutate(combined =
           sprintf("%.2f (%.2f, %.2f)", 
                   est,
                   lower,
                   upper),
         Diagnosis = "AnyAnxiety") %>% 
  select(-c(est, lower, upper)) %>% 
  pivot_wider(names_from = rowname, values_from = combined) %>% 
  rename("Sensitivity" = "se",
         "Specificity" = "sp")

#Combine dataframe with sensitivity/specificity
ab_si_anyanx.df <- merge(ab_si_anyanx.incomplete,
                      ab_si_anyanx.95ci)

ab_si_anyanx.df
```

```{r Full sample combine AB-SI agreement tables}
ab_si_all.raw <- bind_rows(ab_si_mdd.df,
                           ab_si_anyanx.df,
                           ab_si_gad.df,
                           ab_si_spec.df,
                           ab_si_socp.df,
                           ab_si_pad.df,
                           ab_si_pattacks.df,
                           ab_si_agp.df)

ab_si_all <- ab_si_all.raw %>% 
  select(Diagnosis,
         "Sensitivity AB-SI" = "Sensitivity",
         "Specificity AB-SI" = "Specificity") 

ab_si_all
```

### Agreement table for all statistics

```{r Full sample combine all agreement tables}
full_sample_all_agreement <- merge(si_ab_all,
                       ab_si_all) %>%
  relocate(Kappa, .after = last_col()) %>% 
  mutate(Diagnosis = 
           factor(Diagnosis,
                  levels = c("MDD", "AnyAnxiety", "GAD", "SPEC", "SOCP", "PanicAttacks", "PAD", "AGP"))
         ) %>% 
  arrange(., Diagnosis)

full_sample_all_agreement
```

```{r Full sample combine agreements and xtabs tables}
full_sample_all_agreement_xtabs <- merge(all_xtabs,
                                         full_sample_all_agreement) %>%
  mutate(Diagnosis = 
           factor(Diagnosis,
                  levels = c("MDD", "AnyAnxiety", "GAD", "SPEC", "SOCP", "PanicAttacks", "PAD", "AGP")),
         Sample = "Full sample"
         ) %>% 
  arrange(., Diagnosis) %>% 
  relocate(Sample)

full_sample_all_agreement_xtabs
```


## By sample

```{r create sample datasets}
cidi.glad <- cidi %>% 
  filter(sample == "GLAD")

cidi.nbr <- cidi %>% 
  filter(sample == "NBR")
```


### GLAD

#### Algorithm-based diagnosis as reference point

Major depressive disorder
```{r GLAD MDD SI-AB crosstabs and agreement}
glad_si_ab_mdd.cM <- confusionMatrix(cidi.glad$ClinicianMDD.f,
                            cidi.glad$LifetimeMDD.f,
                            positive = "Diagnosis",
                            dnn = c("Single-item", "Algorithm-based"))

#Create dataframe of agreements
glad_si_ab_mdd.classes <- as.matrix(glad_si_ab_mdd.cM, what = "classes")
glad_si_ab_mdd.overall <- as.matrix(glad_si_ab_mdd.cM, what = "overall")
glad_si_ab_mdd.raw <- as.data.frame(rbind(glad_si_ab_mdd.classes,
                                     glad_si_ab_mdd.overall))
colnames(glad_si_ab_mdd.raw) <- "MDD"

#Fromat dataframe
glad_si_ab_mdd.incomplete <- glad_si_ab_mdd.raw %>% 
  rownames_to_column() %>% 
  mutate(rowname = rownames(glad_si_ab_mdd.raw)) %>% 
  gather(Diagnosis, value, -rowname) %>% 
  spread(rowname, value) %>% 
  select(-unused_agreement)

#Calculate sensitivity and specificity with 95% CI
glad_si_ab_mdd.95ci <- summary(epiR::epi.tests(as.table(as.matrix(glad_si_ab_mdd.cM)), conf.level = 0.95)) %>%
  round(., 2) %>% 
  rownames_to_column() %>% 
  filter(rowname == "se" | rowname == "sp") %>% 
  mutate(combined =
           sprintf("%.2f (%.2f, %.2f)", 
                   est,
                   lower,
                   upper),
         Diagnosis = "MDD") %>% 
  select(-c(est, lower, upper)) %>% 
  pivot_wider(names_from = rowname, values_from = combined) %>% 
  rename("Sensitivity" = "se",
         "Specificity" = "sp")

#Combine dataframe with sensitivity/specificity
glad_si_ab_mdd.df <- merge(glad_si_ab_mdd.incomplete,
                      glad_si_ab_mdd.95ci)

#Create dataframe of crosstab
glad_si_ab_mdd.xtabs <- as.data.frame(as.matrix(glad_si_ab_mdd.cM))
glad_si_ab_mdd.xtabs.df <- glad_si_ab_mdd.xtabs %>% 
  rownames_to_column() %>% 
  rename("AB Yes" =
           "Diagnosis",
         "AB No" = "No diagnosis",
        "Crosstab"  = "rowname") %>% 
  mutate(Diagnosis = "MDD",
         Crosstab = recode_factor(Crosstab,
                                 "Diagnosis" = "SI Yes",
                                 "No diagnosis" = "SI No")
         )

glad_si_ab_mdd.df
glad_si_ab_mdd.xtabs.df
```

Generalised anxiety disorder
```{r GLAD GAD SI-AB crosstabs and agreement}
glad_si_ab_gad.cM <- confusionMatrix(cidi.glad$ClinicianGAD.f,
                                cidi.glad$LifetimeGAD.f,
                                positive = "Diagnosis",
                                dnn = c("Single-item", "Algorithm-based"))

#Create dataframe of agreements
glad_si_ab_gad.classes<- as.matrix(glad_si_ab_gad.cM, what = "classes")
glad_si_ab_gad.overall <- as.matrix(glad_si_ab_gad.cM, what = "overall")
glad_si_ab_gad.raw <- as.data.frame(rbind(glad_si_ab_gad.classes,
                                     glad_si_ab_gad.overall))
colnames(glad_si_ab_gad.raw) <- "GAD"

#Fromat dataframe
glad_si_ab_gad.incomplete <- glad_si_ab_gad.raw %>% 
  rownames_to_column() %>% 
  mutate(rowname = rownames(glad_si_ab_gad.raw)) %>% 
  gather(Diagnosis, value, -rowname) %>% 
  spread(rowname, value) %>% 
  select(-unused_agreement)

#Calculate sensitivity and specificity with 95% CI
glad_si_ab_gad.95ci <- summary(epiR::epi.tests(as.table(as.matrix(glad_si_ab_gad.cM)), conf.level = 0.95)) %>%
  round(., 2) %>% 
  rownames_to_column() %>% 
  filter(rowname == "se" | rowname == "sp") %>% 
  mutate(combined =
           sprintf("%.2f (%.2f, %.2f)", 
                   est,
                   lower,
                   upper),
         Diagnosis = "GAD") %>% 
  select(-c(est, lower, upper)) %>% 
  pivot_wider(names_from = rowname, values_from = combined) %>% 
  rename("Sensitivity" = "se",
         "Specificity" = "sp")

#Combine dataframe with sensitivity/specificity
glad_si_ab_gad.df <- merge(glad_si_ab_gad.incomplete,
                      glad_si_ab_gad.95ci)

#Create dataframe of crosstab
glad_si_ab_gad.xtabs <- as.data.frame(as.matrix(glad_si_ab_gad.cM))
glad_si_ab_gad.xtabs.df <- glad_si_ab_gad.xtabs %>% 
  rownames_to_column() %>% 
  rename("AB Yes" =
           "Diagnosis",
         "AB No" = "No diagnosis",
        "Crosstab"  = "rowname") %>% 
  mutate(Diagnosis = "GAD",
         Crosstab = recode_factor(Crosstab,
                                 "Diagnosis" = "SI Yes",
                                 "No diagnosis" = "SI No")
         )

glad_si_ab_gad.df
glad_si_ab_gad.xtabs.df
```

Specific phobia
```{r GLAD Specific phobia SI-AB crosstabs and agreement}
glad_si_ab_spec.cM <- confusionMatrix(cidi.glad$ClinicianSpecPhob.f,
                                 cidi.glad$LifetimeSpecPhob.f,
                                 positive = "Diagnosis",
                                 dnn = c("Single-item", "Algorithm-based"))

#Create dataframe of agreements
glad_si_ab_spec.classes<- as.matrix(glad_si_ab_spec.cM, what = "classes")
glad_si_ab_spec.overall <- as.matrix(glad_si_ab_spec.cM, what = "overall")
glad_si_ab_spec.raw <- as.data.frame(rbind(glad_si_ab_spec.classes,
                                     glad_si_ab_spec.overall))
colnames(glad_si_ab_spec.raw) <- "SPEC"

#Fromat dataframe
glad_si_ab_spec.incomplete <- glad_si_ab_spec.raw %>% 
  rownames_to_column() %>% 
  mutate(rowname = rownames(glad_si_ab_spec.raw)) %>% 
  gather(Diagnosis, value, -rowname) %>% 
  spread(rowname, value) %>% 
  select(-unused_agreement)

#Calculate sensitivity and specificity with 95% CI
glad_si_ab_spec.95ci <- summary(epiR::epi.tests(as.table(as.matrix(glad_si_ab_spec.cM)), conf.level = 0.95)) %>%
  round(., 2) %>% 
  rownames_to_column() %>% 
  filter(rowname == "se" | rowname == "sp") %>% 
  mutate(combined =
           sprintf("%.2f (%.2f, %.2f)", 
                   est,
                   lower,
                   upper),
         Diagnosis = "SPEC") %>% 
  select(-c(est, lower, upper)) %>% 
  pivot_wider(names_from = rowname, values_from = combined) %>% 
  rename("Sensitivity" = "se",
         "Specificity" = "sp")

#Combine dataframe with sensitivity/specificity
glad_si_ab_spec.df <- merge(glad_si_ab_spec.incomplete,
                      glad_si_ab_spec.95ci)

#Create dataframe of crosstab
glad_si_ab_spec.xtabs <- as.data.frame(as.matrix(glad_si_ab_spec.cM))
glad_si_ab_spec.xtabs.df <- glad_si_ab_spec.xtabs %>% 
  rownames_to_column() %>% 
  rename("AB Yes" =
           "Diagnosis",
         "AB No" = "No diagnosis",
        "Crosstab"  = "rowname") %>% 
  mutate(Diagnosis = "SPEC",
         Crosstab = recode_factor(Crosstab,
                                 "Diagnosis" = "SI Yes",
                                 "No diagnosis" = "SI No")
         )

glad_si_ab_spec.df
glad_si_ab_spec.xtabs.df
```

Social anxiety disorder
```{r GLAD Social anxiety disorder SI-AB crosstabs and agreement}
glad_si_ab_socp.cM <- confusionMatrix(cidi.glad$ClinicianSocialPhob.f,
                                  cidi.glad$LifetimeSocialPhob.f,
                                  positive = "Diagnosis",
                                  dnn = c("Single-item", "Algorithm-based"))

#Create dataframe of agreements
glad_si_ab_socp.classes<- as.matrix(glad_si_ab_socp.cM, what = "classes")
glad_si_ab_socp.overall <- as.matrix(glad_si_ab_socp.cM, what = "overall")
glad_si_ab_socp.raw <- as.data.frame(rbind(glad_si_ab_socp.classes,
                                     glad_si_ab_socp.overall))
colnames(glad_si_ab_socp.raw) <- "SOCP"

#Fromat dataframe
glad_si_ab_socp.incomplete <- glad_si_ab_socp.raw %>% 
  rownames_to_column() %>% 
  mutate(rowname = rownames(glad_si_ab_socp.raw)) %>% 
  gather(Diagnosis, value, -rowname) %>% 
  spread(rowname, value) %>% 
  select(-unused_agreement)

#Calculate sensitivity and specificity with 95% CI
glad_si_ab_socp.95ci <- summary(epiR::epi.tests(as.table(as.matrix(glad_si_ab_socp.cM)), conf.level = 0.95)) %>%
  round(., 2) %>% 
  rownames_to_column() %>% 
  filter(rowname == "se" | rowname == "sp") %>% 
  mutate(combined =
           sprintf("%.2f (%.2f, %.2f)", 
                   est,
                   lower,
                   upper),
         Diagnosis = "SOCP") %>% 
  select(-c(est, lower, upper)) %>% 
  pivot_wider(names_from = rowname, values_from = combined) %>% 
  rename("Sensitivity" = "se",
         "Specificity" = "sp")

#Combine dataframe with sensitivity/specificity
glad_si_ab_socp.df <- merge(glad_si_ab_socp.incomplete,
                      glad_si_ab_socp.95ci)

#Create dataframe of crosstab
glad_si_ab_socp.xtabs <- as.data.frame(as.matrix(glad_si_ab_socp.cM))
glad_si_ab_socp.xtabs.df <- glad_si_ab_socp.xtabs %>% 
  rownames_to_column() %>% 
  rename("AB Yes" =
           "Diagnosis",
         "AB No" = "No diagnosis",
        "Crosstab"  = "rowname") %>% 
  mutate(Diagnosis = "SOCP",
         Crosstab = recode_factor(Crosstab,
                                 "Diagnosis" = "SI Yes",
                                 "No diagnosis" = "SI No")
         )

glad_si_ab_socp.df
glad_si_ab_socp.xtabs.df
```

Panic disorder
```{r GLAD Panic disorder SI-AB crosstabs and agreement}
glad_si_ab_pad.cM <- confusionMatrix(cidi.glad$ClinicianPanicDis.f,
                                cidi.glad$LifetimePanicDis.f,
                                positive = "Diagnosis",
                                dnn = c("Single-item", "Algorithm-based"))

#Create dataframe of agreements
glad_si_ab_pad.classes<- as.matrix(glad_si_ab_pad.cM, what = "classes")
glad_si_ab_pad.overall <- as.matrix(glad_si_ab_pad.cM, what = "overall")
glad_si_ab_pad.raw <- as.data.frame(rbind(glad_si_ab_pad.classes,
                                     glad_si_ab_pad.overall))
colnames(glad_si_ab_pad.raw) <- "PAD"

#Fromat dataframe
glad_si_ab_pad.incomplete <- glad_si_ab_pad.raw %>% 
  rownames_to_column() %>% 
  mutate(rowname = rownames(glad_si_ab_pad.raw)) %>% 
  gather(Diagnosis, value, -rowname) %>% 
  spread(rowname, value) %>% 
  select(-unused_agreement)

#Calculate sensitivity and specificity with 95% CI
glad_si_ab_pad.95ci <- summary(epiR::epi.tests(as.table(as.matrix(glad_si_ab_pad.cM)), conf.level = 0.95)) %>%
  round(., 2) %>% 
  rownames_to_column() %>% 
  filter(rowname == "se" | rowname == "sp") %>% 
  mutate(combined =
           sprintf("%.2f (%.2f, %.2f)", 
                   est,
                   lower,
                   upper),
         Diagnosis = "PAD") %>% 
  select(-c(est, lower, upper)) %>% 
  pivot_wider(names_from = rowname, values_from = combined) %>% 
  rename("Sensitivity" = "se",
         "Specificity" = "sp")

#Combine dataframe with sensitivity/specificity
glad_si_ab_pad.df <- merge(glad_si_ab_pad.incomplete,
                      glad_si_ab_pad.95ci)

#Create dataframe of crosstab
glad_si_ab_pad.xtabs <- as.data.frame(as.matrix(glad_si_ab_pad.cM))
glad_si_ab_pad.xtabs.df <- glad_si_ab_pad.xtabs %>% 
  rownames_to_column() %>% 
  rename("AB Yes" =
           "Diagnosis",
         "AB No" = "No diagnosis",
        "Crosstab"  = "rowname") %>% 
  mutate(Diagnosis = "PAD",
         Crosstab = recode_factor(Crosstab,
                                 "Diagnosis" = "SI Yes",
                                 "No diagnosis" = "SI No")
         )

glad_si_ab_pad.df
glad_si_ab_pad.xtabs.df
```

Panic attacks
The single-item panic attack variable here is being compared to lifetime panic disorder.
```{r GLAD Panic Attacks SI-AB crosstabs and agreement for Panic Disorder}
glad_si_ab_pattacks.cM <- confusionMatrix(cidi.glad$ClinicianPanicAttacks.f.cc,
                                cidi.glad$LifetimePanicDis.f, 
                                positive = "Diagnosis",
                                dnn = c("Single-item", "Algorithm-based"))

#Create dataframe of agreements
glad_si_ab_pattacks.classes<- as.matrix(glad_si_ab_pattacks.cM, what = "classes")
glad_si_ab_pattacks.overall <- as.matrix(glad_si_ab_pattacks.cM, what = "overall")
glad_si_ab_pattacks.raw <- as.data.frame(rbind(glad_si_ab_pattacks.classes,
                                     glad_si_ab_pattacks.overall))
colnames(glad_si_ab_pattacks.raw) <- "PanicAttacks"

#Fromat dataframe
glad_si_ab_pattacks.incomplete <- glad_si_ab_pattacks.raw %>% 
  rownames_to_column() %>% 
  mutate(rowname = rownames(glad_si_ab_pattacks.raw)) %>% 
  gather(Diagnosis, value, -rowname) %>% 
  spread(rowname, value) %>% 
  select(-unused_agreement)

#Calculate sensitivity and specificity with 95% CI
glad_si_ab_pattacks.95ci <- summary(epiR::epi.tests(as.table(as.matrix(glad_si_ab_pattacks.cM)), conf.level = 0.95)) %>%
  round(., 2) %>% 
  rownames_to_column() %>% 
  filter(rowname == "se" | rowname == "sp") %>% 
  mutate(combined =
           sprintf("%.2f (%.2f, %.2f)", 
                   est,
                   lower,
                   upper),
         Diagnosis = "PanicAttacks") %>% 
  select(-c(est, lower, upper)) %>% 
  pivot_wider(names_from = rowname, values_from = combined) %>% 
  rename("Sensitivity" = "se",
         "Specificity" = "sp")

#Combine dataframe with sensitivity/specificity
glad_si_ab_pattacks.df <- merge(glad_si_ab_pattacks.incomplete,
                      glad_si_ab_pattacks.95ci)

#Create dataframe of crosstab
glad_si_ab_pattacks.xtabs <- as.data.frame(as.matrix(glad_si_ab_pattacks.cM))
glad_si_ab_pattacks.xtabs.df <- glad_si_ab_pattacks.xtabs %>% 
  rownames_to_column() %>% 
  rename("AB Yes" =
           "Diagnosis",
         "AB No" = "No diagnosis",
        "Crosstab"  = "rowname") %>% 
  mutate(Diagnosis = "PanicAttacks",
         Crosstab = recode_factor(Crosstab,
                                 "Diagnosis" = "SI Yes",
                                 "No diagnosis" = "SI No")
         )

glad_si_ab_pattacks.df
glad_si_ab_pattacks.xtabs.df
```

Agoraphobia
```{r GLAD Agoraphobia SI-AB crosstabs and agreement}
glad_si_ab_agp.cM <- confusionMatrix(cidi.glad$ClinicianAgoraphobia.f,
                                cidi.glad$LifetimeAgoraphobia.f,
                                positive = "Diagnosis",
                                dnn = c("Single-item", "Algorithm-based"))

#Create dataframe of agreements
glad_si_ab_agp.classes<- as.matrix(glad_si_ab_agp.cM, what = "classes")
glad_si_ab_agp.overall <- as.matrix(glad_si_ab_agp.cM, what = "overall")
glad_si_ab_agp.raw <- as.data.frame(rbind(glad_si_ab_agp.classes,
                                     glad_si_ab_agp.overall))
colnames(glad_si_ab_agp.raw) <- "AGP"

#Fromat dataframe
glad_si_ab_agp.incomplete <- glad_si_ab_agp.raw %>% 
  rownames_to_column() %>% 
  mutate(rowname = rownames(glad_si_ab_agp.raw)) %>% 
  gather(Diagnosis, value, -rowname) %>% 
  spread(rowname, value) %>% 
  select(-unused_agreement)

#Calculate sensitivity and specificity with 95% CI
glad_si_ab_agp.95ci <- summary(epiR::epi.tests(as.table(as.matrix(glad_si_ab_agp.cM)), conf.level = 0.95)) %>%
  round(., 2) %>% 
  rownames_to_column() %>% 
  filter(rowname == "se" | rowname == "sp") %>% 
  mutate(combined =
           sprintf("%.2f (%.2f, %.2f)", 
                   est,
                   lower,
                   upper),
         Diagnosis = "AGP") %>% 
  select(-c(est, lower, upper)) %>% 
  pivot_wider(names_from = rowname, values_from = combined) %>% 
  rename("Sensitivity" = "se",
         "Specificity" = "sp")

#Combine dataframe with sensitivity/specificity
glad_si_ab_agp.df <- merge(glad_si_ab_agp.incomplete,
                      glad_si_ab_agp.95ci)

#Create dataframe of crosstab
glad_si_ab_agp.xtabs <- as.data.frame(as.matrix(glad_si_ab_agp.cM))
glad_si_ab_agp.xtabs.df <- glad_si_ab_agp.xtabs %>% 
  rownames_to_column() %>% 
  rename("AB Yes" =
           "Diagnosis",
         "AB No" = "No diagnosis",
        "Crosstab"  = "rowname") %>% 
  mutate(Diagnosis = "AGP",
         Crosstab = recode_factor(Crosstab,
                                 "Diagnosis" = "SI Yes",
                                 "No diagnosis" = "SI No")
         )

glad_si_ab_agp.df
glad_si_ab_agp.xtabs.df
```

Any anxiety
```{r GLAD Any Anxiety SI-AB crosstabs and agreement}
glad_si_ab_anyanx.cM <- confusionMatrix(cidi.glad$ClinicianAnyAnx.f, 
                                cidi.glad$LifetimeAnyAnx.f,
                                positive = "Diagnosis",
                                dnn = c("Single-item", "Algorithm-based"))

#Create dataframe of agreements
glad_si_ab_anyanx.classes<- as.matrix(glad_si_ab_anyanx.cM, what = "classes")
glad_si_ab_anyanx.overall <- as.matrix(glad_si_ab_anyanx.cM, what = "overall")
glad_si_ab_anyanx.raw <- as.data.frame(rbind(glad_si_ab_anyanx.classes,
                                     glad_si_ab_anyanx.overall))
colnames(glad_si_ab_anyanx.raw) <- "AnyAnxiety"

#Fromat dataframe
glad_si_ab_anyanx.incomplete <- glad_si_ab_anyanx.raw %>% 
  rownames_to_column() %>% 
  mutate(rowname = rownames(glad_si_ab_anyanx.raw)) %>% 
  gather(Diagnosis, value, -rowname) %>% 
  spread(rowname, value) %>% 
  select(-unused_agreement)

#Calculate sensitivity and specificity with 95% CI
glad_si_ab_anyanx.95ci <- summary(epiR::epi.tests(as.table(as.matrix(glad_si_ab_anyanx.cM)), conf.level = 0.95)) %>%
  round(., 2) %>% 
  rownames_to_column() %>% 
  filter(rowname == "se" | rowname == "sp") %>% 
  mutate(combined =
           sprintf("%.2f (%.2f, %.2f)", 
                   est,
                   lower,
                   upper),
         Diagnosis = "AnyAnxiety") %>% 
  select(-c(est, lower, upper)) %>% 
  pivot_wider(names_from = rowname, values_from = combined) %>% 
  rename("Sensitivity" = "se",
         "Specificity" = "sp")

#Combine dataframe with sensitivity/specificity
glad_si_ab_anyanx.df <- merge(glad_si_ab_anyanx.incomplete,
                      glad_si_ab_anyanx.95ci)

#Create dataframe of crosstab
glad_si_ab_anyanx.xtabs <- as.data.frame(as.matrix(glad_si_ab_anyanx.cM))
glad_si_ab_anyanx.xtabs.df <- glad_si_ab_anyanx.xtabs %>% 
  rownames_to_column() %>% 
  rename("AB Yes" =
           "Diagnosis",
         "AB No" = "No diagnosis",
        "Crosstab"  = "rowname") %>% 
  mutate(Diagnosis = "AnyAnxiety",
         Crosstab = recode_factor(Crosstab,
                                 "Diagnosis" = "SI Yes",
                                 "No diagnosis" = "SI No")
         )

glad_si_ab_anyanx.df
glad_si_ab_anyanx.xtabs.df
```

```{r GLAD combine SI-AB agreement tables}
glad_si_ab_all.raw <- bind_rows(glad_si_ab_mdd.df,
                           glad_si_ab_anyanx.df,
                           glad_si_ab_gad.df,
                           glad_si_ab_spec.df,
                           glad_si_ab_socp.df,
                           glad_si_ab_pad.df,
                           glad_si_ab_pattacks.df,
                           glad_si_ab_agp.df)

glad_si_ab_all <- glad_si_ab_all.raw %>% 
  rename("Sensitivity SI-AB" = "Sensitivity",
         "Specificity SI-AB" = "Specificity") %>% 
  relocate(Kappa, .after = last_col())

glad_si_ab_all
```

```{r GLAD combine all xtabs tables}
glad_all_xtabs.raw <- bind_rows(glad_si_ab_mdd.xtabs.df,
                           glad_si_ab_anyanx.xtabs.df,
                           glad_si_ab_gad.xtabs.df,
                           glad_si_ab_spec.xtabs.df,
                           glad_si_ab_socp.xtabs.df,
                           glad_si_ab_pad.xtabs.df,
                           glad_si_ab_pattacks.xtabs.df,
                           glad_si_ab_agp.xtabs.df)

glad_all_xtabs <- glad_all_xtabs.raw %>%  
  relocate(Diagnosis)

glad_all_xtabs
```

####Single-item diagnosis as reference point

Major depressive disorder
```{r GLAD MDD AB-SI crosstabs and agreement}
glad_ab_si_mdd.cM <- confusionMatrix(cidi.glad$LifetimeMDD.f,
                                cidi.glad$ClinicianMDD.f, 
                                positive = "Diagnosis",
                                dnn = c("Algorithm-based", "Single-item"))

#Create dataframe of agreements
glad_ab_si_mdd.classes<- as.matrix(glad_ab_si_mdd.cM, what = "classes")
glad_ab_si_mdd.overall <- as.matrix(glad_ab_si_mdd.cM, what = "overall")
glad_ab_si_mdd.raw <- as.data.frame(rbind(glad_ab_si_mdd.classes,
                                     glad_ab_si_mdd.overall))
colnames(glad_ab_si_mdd.raw) <- "MDD"

#Fromat dataframe
glad_ab_si_mdd.incomplete <- glad_ab_si_mdd.raw %>% 
  rownames_to_column() %>% 
  mutate(rowname = rownames(glad_ab_si_mdd.raw)) %>% 
  gather(Diagnosis, value, -rowname) %>% 
  spread(rowname, value) %>% 
  select(-unused_agreement)

#Calculate sensitivity and specificity with 95% CI
glad_ab_si_mdd.95ci <- summary(epiR::epi.tests(as.table(as.matrix(glad_ab_si_mdd.cM)), conf.level = 0.95)) %>%
  round(., 2) %>% 
  rownames_to_column() %>% 
  filter(rowname == "se" | rowname == "sp") %>% 
  mutate(combined =
           sprintf("%.2f (%.2f, %.2f)", 
                   est,
                   lower,
                   upper),
         Diagnosis = "MDD") %>% 
  select(-c(est, lower, upper)) %>% 
  pivot_wider(names_from = rowname, values_from = combined) %>% 
  rename("Sensitivity" = "se",
         "Specificity" = "sp")

#Combine dataframe with sensitivity/specificity
glad_ab_si_mdd.df <- merge(glad_ab_si_mdd.incomplete,
                      glad_ab_si_mdd.95ci)

glad_ab_si_mdd.df
```

Generalised anxiety disorder
```{r GLAD GAD AB-SI crosstabs and agreement}
glad_ab_si_gad.cM <- confusionMatrix(cidi.glad$LifetimeGAD.f,
                                cidi.glad$ClinicianGAD.f, 
                                positive = "Diagnosis",
                                dnn = c("Algorithm-based", "Single-item"))

#Create dataframe of agreements
glad_ab_si_gad.classes<- as.matrix(glad_ab_si_gad.cM, what = "classes")
glad_ab_si_gad.overall <- as.matrix(glad_ab_si_gad.cM, what = "overall")
glad_ab_si_gad.raw <- as.data.frame(rbind(glad_ab_si_gad.classes,
                                     glad_ab_si_gad.overall))
colnames(glad_ab_si_gad.raw) <- "GAD"

#Fromat dataframe
glad_ab_si_gad.incomplete <- glad_ab_si_gad.raw %>% 
  rownames_to_column() %>% 
  mutate(rowname = rownames(glad_ab_si_gad.raw)) %>% 
  gather(Diagnosis, value, -rowname) %>% 
  spread(rowname, value) %>% 
  select(-unused_agreement)

#Calculate sensitivity and specificity with 95% CI
glad_ab_si_gad.95ci <- summary(epiR::epi.tests(as.table(as.matrix(glad_ab_si_gad.cM)), conf.level = 0.95)) %>%
  round(., 2) %>% 
  rownames_to_column() %>% 
  filter(rowname == "se" | rowname == "sp") %>% 
  mutate(combined =
           sprintf("%.2f (%.2f, %.2f)", 
                   est,
                   lower,
                   upper),
         Diagnosis = "GAD") %>% 
  select(-c(est, lower, upper)) %>% 
  pivot_wider(names_from = rowname, values_from = combined) %>% 
  rename("Sensitivity" = "se",
         "Specificity" = "sp")

#Combine dataframe with sensitivity/specificity
glad_ab_si_gad.df <- merge(glad_ab_si_gad.incomplete,
                      glad_ab_si_gad.95ci)

glad_ab_si_gad.df
```

Specific phobia
```{r GLAD Specific phobia AB-SI crosstabs and agreement}
glad_ab_si_spec.cM <- confusionMatrix(cidi.glad$LifetimeSpecPhob.f,
                                 cidi.glad$ClinicianSpecPhob.f, 
                                 positive = "Diagnosis",
                                 dnn = c("Algorithm-based", "Single-item"))

#Create dataframe of agreements
glad_ab_si_spec.classes<- as.matrix(glad_ab_si_spec.cM, what = "classes")
glad_ab_si_spec.overall <- as.matrix(glad_ab_si_spec.cM, what = "overall")
glad_ab_si_spec.raw <- as.data.frame(rbind(glad_ab_si_spec.classes,
                                     glad_ab_si_spec.overall))
colnames(glad_ab_si_spec.raw) <- "SPEC"

#Fromat dataframe
glad_ab_si_spec.incomplete <- glad_ab_si_spec.raw %>%  
  rownames_to_column() %>% 
  mutate(rowname = rownames(glad_ab_si_spec.raw)) %>% 
  gather(Diagnosis, value, -rowname) %>% 
  spread(rowname, value) %>% 
  select(-unused_agreement)

#Calculate sensitivity and specificity with 95% CI
glad_ab_si_spec.95ci <- summary(epiR::epi.tests(as.table(as.matrix(glad_ab_si_spec.cM)), conf.level = 0.95)) %>%
  round(., 2) %>% 
  rownames_to_column() %>% 
  filter(rowname == "se" | rowname == "sp") %>% 
  mutate(combined =
           sprintf("%.2f (%.2f, %.2f)", 
                   est,
                   lower,
                   upper),
         Diagnosis = "SPEC") %>% 
  select(-c(est, lower, upper)) %>% 
  pivot_wider(names_from = rowname, values_from = combined) %>% 
  rename("Sensitivity" = "se",
         "Specificity" = "sp")

#Combine dataframe with sensitivity/specificity
glad_ab_si_spec.df <- merge(glad_ab_si_spec.incomplete,
                      glad_ab_si_spec.95ci)

glad_ab_si_spec.df
```

Social anxiety disorder
```{r GLAD Social anxiety disorder AB-SI crosstabs and agreement}
glad_ab_si_socp.cM <- confusionMatrix(cidi.glad$LifetimeSocialPhob.f,
                                 cidi.glad$ClinicianSocialPhob.f, 
                                 positive = "Diagnosis",
                                 dnn = c("Algorithm-based", "Single-item"))

#Create dataframe of agreements
glad_ab_si_socp.classes<- as.matrix(glad_ab_si_socp.cM, what = "classes")
glad_ab_si_socp.overall <- as.matrix(glad_ab_si_socp.cM, what = "overall")
glad_ab_si_socp.raw <- as.data.frame(rbind(glad_ab_si_socp.classes,
                                     glad_ab_si_socp.overall))
colnames(glad_ab_si_socp.raw) <- "SOCP"

#Fromat dataframe
glad_ab_si_socp.incomplete <- glad_ab_si_socp.raw %>% 
  rownames_to_column() %>% 
  mutate(rowname = rownames(glad_ab_si_socp.raw)) %>% 
  gather(Diagnosis, value, -rowname) %>% 
  spread(rowname, value) %>% 
  select(-unused_agreement)

#Calculate sensitivity and specificity with 95% CI
glad_ab_si_socp.95ci <- summary(epiR::epi.tests(as.table(as.matrix(glad_ab_si_socp.cM)), conf.level = 0.95)) %>%
  round(., 2) %>% 
  rownames_to_column() %>% 
  filter(rowname == "se" | rowname == "sp") %>% 
  mutate(combined =
           sprintf("%.2f (%.2f, %.2f)", 
                   est,
                   lower,
                   upper),
         Diagnosis = "SOCP") %>% 
  select(-c(est, lower, upper)) %>% 
  pivot_wider(names_from = rowname, values_from = combined) %>% 
  rename("Sensitivity" = "se",
         "Specificity" = "sp")

#Combine dataframe with sensitivity/specificity
glad_ab_si_socp.df <- merge(glad_ab_si_socp.incomplete,
                      glad_ab_si_socp.95ci)

glad_ab_si_socp.df
```

Panic disorder
```{r GLAD Panic disorder AB-SI crosstabs and agreement}
glad_ab_si_pad.cM <- confusionMatrix(cidi.glad$LifetimePanicDis.f,
                                cidi.glad$ClinicianPanicDis.f, 
                                positive = "Diagnosis",
                                dnn = c("Algorithm-based", "Single-item"))

#Create dataframe of agreements
glad_ab_si_pad.classes<- as.matrix(glad_ab_si_pad.cM, what = "classes")
glad_ab_si_pad.overall <- as.matrix(glad_ab_si_pad.cM, what = "overall")
glad_ab_si_pad.raw <- as.data.frame(rbind(glad_ab_si_pad.classes,
                                     glad_ab_si_pad.overall))
colnames(glad_ab_si_pad.raw) <- "PAD"

#Fromat dataframe
glad_ab_si_pad.incomplete <- glad_ab_si_pad.raw %>% 
  rownames_to_column() %>% 
  mutate(rowname = rownames(glad_ab_si_pad.raw)) %>% 
  gather(Diagnosis, value, -rowname) %>% 
  spread(rowname, value) %>% 
  select(-unused_agreement)

#Calculate sensitivity and specificity with 95% CI
glad_ab_si_pad.95ci <- summary(epiR::epi.tests(as.table(as.matrix(glad_ab_si_pad.cM)), conf.level = 0.95)) %>%
  round(., 2) %>% 
  rownames_to_column() %>% 
  filter(rowname == "se" | rowname == "sp") %>% 
  mutate(combined =
           sprintf("%.2f (%.2f, %.2f)", 
                   est,
                   lower,
                   upper),
         Diagnosis = "PAD") %>% 
  select(-c(est, lower, upper)) %>% 
  pivot_wider(names_from = rowname, values_from = combined) %>% 
  rename("Sensitivity" = "se",
         "Specificity" = "sp")

#Combine dataframe with sensitivity/specificity
glad_ab_si_pad.df <- merge(glad_ab_si_pad.incomplete,
                      glad_ab_si_pad.95ci)

glad_ab_si_pad.df
```

Panic attacks
Algorithm-based panic disorder is being compared with single-item panic attacks.
```{r GLAD Panic Attacks AB-SI crosstabs and agreement with Panic Disorder, echo=FALSE}
glad_ab_si_pattacks.cM <- confusionMatrix(cidi.glad$LifetimePanicDis.f, 
                                     cidi.glad$ClinicianPanicAttacks.f.cc, 
                                     positive = "Diagnosis",
                                     dnn = c("Algorithm-based", "Single-item"))

#Create dataframe of agreements
glad_ab_si_pattacks.classes<- as.matrix(glad_ab_si_pattacks.cM, what = "classes")
glad_ab_si_pattacks.overall <- as.matrix(glad_ab_si_pattacks.cM, what = "overall")
glad_ab_si_pattacks.raw <- as.data.frame(rbind(glad_ab_si_pattacks.classes,
                                     glad_ab_si_pattacks.overall))
colnames(glad_ab_si_pattacks.raw) <- "PanicAttacks"

#Fromat dataframe
glad_ab_si_pattacks.incomplete <- glad_ab_si_pattacks.raw %>% 
  rownames_to_column() %>% 
  mutate(rowname = rownames(glad_ab_si_pattacks.raw)) %>% 
  gather(Diagnosis, value, -rowname) %>% 
  spread(rowname, value) %>% 
  select(-unused_agreement)

#Calculate sensitivity and specificity with 95% CI
glad_ab_si_pattacks.95ci <- summary(epiR::epi.tests(as.table(as.matrix(glad_ab_si_pattacks.cM)), conf.level = 0.95)) %>%
  round(., 2) %>% 
  rownames_to_column() %>% 
  filter(rowname == "se" | rowname == "sp") %>% 
  mutate(combined =
           sprintf("%.2f (%.2f, %.2f)", 
                   est,
                   lower,
                   upper),
         Diagnosis = "PanicAttacks") %>% 
  select(-c(est, lower, upper)) %>% 
  pivot_wider(names_from = rowname, values_from = combined) %>% 
  rename("Sensitivity" = "se",
         "Specificity" = "sp")

#Combine dataframe with sensitivity/specificity
glad_ab_si_pattacks.df <- merge(glad_ab_si_pattacks.incomplete,
                      glad_ab_si_pattacks.95ci)

glad_ab_si_pattacks.df
```

Agoraphobia
```{r GLAD Agoraphobia AB-SI crosstabs and agreement}
glad_ab_si_agp.cM <- confusionMatrix(cidi.glad$LifetimeAgoraphobia.f, 
                                cidi.glad$ClinicianAgoraphobia.f, 
                                positive = "Diagnosis",
                                dnn = c("Algorithm-based", "Single-item"))

#Create dataframe of agreements
glad_ab_si_agp.classes<- as.matrix(glad_ab_si_agp.cM, what = "classes")
glad_ab_si_agp.overall <- as.matrix(glad_ab_si_agp.cM, what = "overall")
glad_ab_si_agp.raw <- as.data.frame(rbind(glad_ab_si_agp.classes,
                                     glad_ab_si_agp.overall))
colnames(glad_ab_si_agp.raw) <- "AGP"

#Fromat dataframe
glad_ab_si_agp.incomplete <- glad_ab_si_agp.raw %>% 
  rownames_to_column() %>% 
  mutate(rowname = rownames(glad_ab_si_agp.raw)) %>% 
  gather(Diagnosis, value, -rowname) %>% 
  spread(rowname, value) %>% 
  select(-unused_agreement)

#Calculate sensitivity and specificity with 95% CI
glad_ab_si_agp.95ci <- summary(epiR::epi.tests(as.table(as.matrix(glad_ab_si_agp.cM)), conf.level = 0.95)) %>%
  round(., 2) %>% 
  rownames_to_column() %>% 
  filter(rowname == "se" | rowname == "sp") %>% 
  mutate(combined =
           sprintf("%.2f (%.2f, %.2f)", 
                   est,
                   lower,
                   upper),
         Diagnosis = "AGP") %>% 
  select(-c(est, lower, upper)) %>% 
  pivot_wider(names_from = rowname, values_from = combined) %>% 
  rename("Sensitivity" = "se",
         "Specificity" = "sp")

#Combine dataframe with sensitivity/specificity
glad_ab_si_agp.df <- merge(glad_ab_si_agp.incomplete,
                      glad_ab_si_agp.95ci)

glad_ab_si_agp.df
```

Any anxiety
```{r GLAD Any Anxiety AB-SI crosstabs and agreement}
glad_ab_si_anyanx.cM <- confusionMatrix(cidi.glad$LifetimeAnyAnx.f,
                                   cidi.glad$ClinicianAnyAnx.f, 
                                   positive = "Diagnosis",
                                   dnn = c("Algorithm-based", "Single-item"))

#Create dataframe of agreements
glad_ab_si_anyanx.classes<- as.matrix(glad_ab_si_anyanx.cM, what = "classes")
glad_ab_si_anyanx.overall <- as.matrix(glad_ab_si_anyanx.cM, what = "overall")
glad_ab_si_anyanx.raw <- as.data.frame(rbind(glad_ab_si_anyanx.classes,
                                     glad_ab_si_anyanx.overall))
colnames(glad_ab_si_anyanx.raw) <- "AnyAnxiety"

#Fromat dataframe
glad_ab_si_anyanx.incomplete <- glad_ab_si_anyanx.raw %>% 
  rownames_to_column() %>% 
  mutate(rowname = rownames(glad_ab_si_anyanx.raw)) %>% 
  gather(Diagnosis, value, -rowname) %>% 
  spread(rowname, value) %>% 
  select(-unused_agreement)

#Calculate sensitivity and specificity with 95% CI
glad_ab_si_anyanx.95ci <- summary(epiR::epi.tests(as.table(as.matrix(glad_ab_si_anyanx.cM)), conf.level = 0.95)) %>%
  round(., 2) %>% 
  rownames_to_column() %>% 
  filter(rowname == "se" | rowname == "sp") %>% 
  mutate(combined =
           sprintf("%.2f (%.2f, %.2f)", 
                   est,
                   lower,
                   upper),
         Diagnosis = "AnyAnxiety") %>% 
  select(-c(est, lower, upper)) %>% 
  pivot_wider(names_from = rowname, values_from = combined) %>% 
  rename("Sensitivity" = "se",
         "Specificity" = "sp")

#Combine dataframe with sensitivity/specificity
glad_ab_si_anyanx.df <- merge(glad_ab_si_anyanx.incomplete,
                      glad_ab_si_anyanx.95ci)

glad_ab_si_anyanx.df
```

```{r GLAD combine AB-SI agreement tables}
glad_ab_si_all.raw <- bind_rows(glad_ab_si_mdd.df,
                           glad_ab_si_anyanx.df,
                           glad_ab_si_gad.df,
                           glad_ab_si_spec.df,
                           glad_ab_si_socp.df,
                           glad_ab_si_pad.df,
                           glad_ab_si_pattacks.df,
                           glad_ab_si_agp.df)

glad_ab_si_all <- glad_ab_si_all.raw %>% 
  select(Diagnosis,
         "Sensitivity AB-SI" = "Sensitivity",
         "Specificity AB-SI" = "Specificity") 

glad_ab_si_all
```

#### Agreement table for all statistics

```{r GLAD combine all agreement tables}
glad_all_agreement <- merge(glad_si_ab_all,
                       glad_ab_si_all) %>%
  relocate(Kappa, .after = last_col()) %>% 
  mutate(Diagnosis = 
           factor(Diagnosis,
                  levels = c("MDD", "AnyAnxiety", "GAD", "SPEC", "SOCP", "PanicAttacks", "PAD", "AGP"))
         ) %>% 
  arrange(., Diagnosis)

glad_all_agreement
```

```{r GLAD combine agreements and xtabs tables}
glad_all_agreement_xtabs <- merge(glad_all_xtabs,
                             glad_all_agreement) %>%
  mutate(Diagnosis = 
           factor(Diagnosis,
                  levels = c("MDD", "AnyAnxiety", "GAD", "SPEC", "SOCP", "PanicAttacks", "PAD", "AGP")),
         Sample = "GLAD"
         ) %>% 
  arrange(., Diagnosis) %>% 
  relocate(Sample)

glad_all_agreement_xtabs
```

### COPING NBR

#### Algorithm-based diagnosis as reference point

Major depressive disorder
```{r COPING NBR MDD SI-AB crosstabs and agreement}
nbr_si_ab_mdd.cM <- confusionMatrix(cidi.nbr$ClinicianMDD.f,
                            cidi.nbr$LifetimeMDD.f,
                            positive = "Diagnosis",
                            dnn = c("Single-item", "Algorithm-based"))

#Create dataframe of agreements
nbr_si_ab_mdd.classes <- as.matrix(nbr_si_ab_mdd.cM, what = "classes")
nbr_si_ab_mdd.overall <- as.matrix(nbr_si_ab_mdd.cM, what = "overall")
nbr_si_ab_mdd.raw <- as.data.frame(rbind(nbr_si_ab_mdd.classes,
                                     nbr_si_ab_mdd.overall))
colnames(nbr_si_ab_mdd.raw) <- "MDD"

#Fromat dataframe
nbr_si_ab_mdd.incomplete <- nbr_si_ab_mdd.raw %>% 
  rownames_to_column() %>% 
  mutate(rowname = rownames(nbr_si_ab_mdd.raw)) %>% 
  gather(Diagnosis, value, -rowname) %>% 
  spread(rowname, value) %>% 
  select(-unused_agreement)

#Calculate sensitivity and specificity with 95% CI
nbr_si_ab_mdd.95ci <- summary(epiR::epi.tests(as.table(as.matrix(nbr_si_ab_mdd.cM)), conf.level = 0.95)) %>%
  round(., 2) %>% 
  rownames_to_column() %>% 
  filter(rowname == "se" | rowname == "sp") %>% 
  mutate(combined =
           sprintf("%.2f (%.2f, %.2f)", 
                   est,
                   lower,
                   upper),
         Diagnosis = "MDD") %>% 
  select(-c(est, lower, upper)) %>% 
  pivot_wider(names_from = rowname, values_from = combined) %>% 
  rename("Sensitivity" = "se",
         "Specificity" = "sp")

#Combine dataframe with sensitivity/specificity
nbr_si_ab_mdd.df <- merge(nbr_si_ab_mdd.incomplete,
                      nbr_si_ab_mdd.95ci)

#Create dataframe of crosstab
nbr_si_ab_mdd.xtabs <- as.data.frame(as.matrix(nbr_si_ab_mdd.cM))
nbr_si_ab_mdd.xtabs.df <- nbr_si_ab_mdd.xtabs %>% 
  rownames_to_column() %>% 
  rename("AB Yes" =
           "Diagnosis",
         "AB No" = "No diagnosis",
        "Crosstab"  = "rowname") %>% 
  mutate(Diagnosis = "MDD",
         Crosstab = recode_factor(Crosstab,
                                 "Diagnosis" = "SI Yes",
                                 "No diagnosis" = "SI No")
         )

nbr_si_ab_mdd.df
nbr_si_ab_mdd.xtabs.df
```

Generalised anxiety disorder
```{r COPING NBR GAD SI-AB crosstabs and agreement}
nbr_si_ab_gad.cM <- confusionMatrix(cidi.nbr$ClinicianGAD.f,
                                cidi.nbr$LifetimeGAD.f,
                                positive = "Diagnosis",
                                dnn = c("Single-item", "Algorithm-based"))

#Create dataframe of agreements
nbr_si_ab_gad.classes<- as.matrix(nbr_si_ab_gad.cM, what = "classes")
nbr_si_ab_gad.overall <- as.matrix(nbr_si_ab_gad.cM, what = "overall")
nbr_si_ab_gad.raw <- as.data.frame(rbind(nbr_si_ab_gad.classes,
                                     nbr_si_ab_gad.overall))
colnames(nbr_si_ab_gad.raw) <- "GAD"

#Fromat dataframe
nbr_si_ab_gad.incomplete <- nbr_si_ab_gad.raw %>% 
  rownames_to_column() %>% 
  mutate(rowname = rownames(nbr_si_ab_gad.raw)) %>% 
  gather(Diagnosis, value, -rowname) %>% 
  spread(rowname, value) %>% 
  select(-unused_agreement)

#Calculate sensitivity and specificity with 95% CI
nbr_si_ab_gad.95ci <- summary(epiR::epi.tests(as.table(as.matrix(nbr_si_ab_gad.cM)), conf.level = 0.95)) %>%
  round(., 2) %>% 
  rownames_to_column() %>% 
  filter(rowname == "se" | rowname == "sp") %>% 
  mutate(combined =
           sprintf("%.2f (%.2f, %.2f)", 
                   est,
                   lower,
                   upper),
         Diagnosis = "GAD") %>% 
  select(-c(est, lower, upper)) %>% 
  pivot_wider(names_from = rowname, values_from = combined) %>% 
  rename("Sensitivity" = "se",
         "Specificity" = "sp")

#Combine dataframe with sensitivity/specificity
nbr_si_ab_gad.df <- merge(nbr_si_ab_gad.incomplete,
                      nbr_si_ab_gad.95ci)

#Create dataframe of crosstab
nbr_si_ab_gad.xtabs <- as.data.frame(as.matrix(nbr_si_ab_gad.cM))
nbr_si_ab_gad.xtabs.df <- nbr_si_ab_gad.xtabs %>% 
  rownames_to_column() %>% 
  rename("AB Yes" =
           "Diagnosis",
         "AB No" = "No diagnosis",
        "Crosstab"  = "rowname") %>% 
  mutate(Diagnosis = "GAD",
         Crosstab = recode_factor(Crosstab,
                                 "Diagnosis" = "SI Yes",
                                 "No diagnosis" = "SI No")
         )

nbr_si_ab_gad.df
nbr_si_ab_gad.xtabs.df
```

Specific phobia
```{r COPING NBR Specific phobia SI-AB crosstabs and agreement}
nbr_si_ab_spec.cM <- confusionMatrix(cidi.nbr$ClinicianSpecPhob.f,
                                 cidi.nbr$LifetimeSpecPhob.f,
                                 positive = "Diagnosis",
                                 dnn = c("Single-item", "Algorithm-based"))

#Create dataframe of agreements
nbr_si_ab_spec.classes<- as.matrix(nbr_si_ab_spec.cM, what = "classes")
nbr_si_ab_spec.overall <- as.matrix(nbr_si_ab_spec.cM, what = "overall")
nbr_si_ab_spec.raw <- as.data.frame(rbind(nbr_si_ab_spec.classes,
                                     nbr_si_ab_spec.overall))
colnames(nbr_si_ab_spec.raw) <- "SPEC"

#Fromat dataframe
nbr_si_ab_spec.incomplete <- nbr_si_ab_spec.raw %>% 
  rownames_to_column() %>% 
  mutate(rowname = rownames(nbr_si_ab_spec.raw)) %>% 
  gather(Diagnosis, value, -rowname) %>% 
  spread(rowname, value) %>% 
  select(-unused_agreement)

#Calculate sensitivity and specificity with 95% CI
nbr_si_ab_spec.95ci <- summary(epiR::epi.tests(as.table(as.matrix(nbr_si_ab_spec.cM)), conf.level = 0.95)) %>%
  round(., 2) %>% 
  rownames_to_column() %>% 
  filter(rowname == "se" | rowname == "sp") %>% 
  mutate(combined =
           sprintf("%.2f (%.2f, %.2f)", 
                   est,
                   lower,
                   upper),
         Diagnosis = "SPEC") %>% 
  select(-c(est, lower, upper)) %>% 
  pivot_wider(names_from = rowname, values_from = combined) %>% 
  rename("Sensitivity" = "se",
         "Specificity" = "sp")

#Combine dataframe with sensitivity/specificity
nbr_si_ab_spec.df <- merge(nbr_si_ab_spec.incomplete,
                      nbr_si_ab_spec.95ci)

#Create dataframe of crosstab
nbr_si_ab_spec.xtabs <- as.data.frame(as.matrix(nbr_si_ab_spec.cM))
nbr_si_ab_spec.xtabs.df <- nbr_si_ab_spec.xtabs %>% 
  rownames_to_column() %>% 
  rename("AB Yes" =
           "Diagnosis",
         "AB No" = "No diagnosis",
        "Crosstab"  = "rowname") %>% 
  mutate(Diagnosis = "SPEC",
         Crosstab = recode_factor(Crosstab,
                                 "Diagnosis" = "SI Yes",
                                 "No diagnosis" = "SI No")
         )

nbr_si_ab_spec.df
nbr_si_ab_spec.xtabs.df
```

Social anxiety disorder
```{r COPING NBR Social anxiety disorder SI-AB crosstabs and agreement}
nbr_si_ab_socp.cM <- confusionMatrix(cidi.nbr$ClinicianSocialPhob.f,
                                  cidi.nbr$LifetimeSocialPhob.f,
                                  positive = "Diagnosis",
                                  dnn = c("Single-item", "Algorithm-based"))

#Create dataframe of agreements
nbr_si_ab_socp.classes<- as.matrix(nbr_si_ab_socp.cM, what = "classes")
nbr_si_ab_socp.overall <- as.matrix(nbr_si_ab_socp.cM, what = "overall")
nbr_si_ab_socp.raw <- as.data.frame(rbind(nbr_si_ab_socp.classes,
                                     nbr_si_ab_socp.overall))
colnames(nbr_si_ab_socp.raw) <- "SOCP"

#Fromat dataframe
nbr_si_ab_socp.incomplete <- nbr_si_ab_socp.raw %>% 
  rownames_to_column() %>% 
  mutate(rowname = rownames(nbr_si_ab_socp.raw)) %>% 
  gather(Diagnosis, value, -rowname) %>% 
  spread(rowname, value) %>% 
  select(-unused_agreement)

#Calculate sensitivity and specificity with 95% CI
nbr_si_ab_socp.95ci <- summary(epiR::epi.tests(as.table(as.matrix(nbr_si_ab_socp.cM)), conf.level = 0.95)) %>%
  round(., 2) %>% 
  rownames_to_column() %>% 
  filter(rowname == "se" | rowname == "sp") %>% 
  mutate(combined =
           sprintf("%.2f (%.2f, %.2f)", 
                   est,
                   lower,
                   upper),
         Diagnosis = "SOCP") %>% 
  select(-c(est, lower, upper)) %>% 
  pivot_wider(names_from = rowname, values_from = combined) %>% 
  rename("Sensitivity" = "se",
         "Specificity" = "sp")

#Combine dataframe with sensitivity/specificity
nbr_si_ab_socp.df <- merge(nbr_si_ab_socp.incomplete,
                      nbr_si_ab_socp.95ci)

#Create dataframe of crosstab
nbr_si_ab_socp.xtabs <- as.data.frame(as.matrix(nbr_si_ab_socp.cM))
nbr_si_ab_socp.xtabs.df <- nbr_si_ab_socp.xtabs %>% 
  rownames_to_column() %>% 
  rename("AB Yes" =
           "Diagnosis",
         "AB No" = "No diagnosis",
        "Crosstab"  = "rowname") %>% 
  mutate(Diagnosis = "SOCP",
         Crosstab = recode_factor(Crosstab,
                                 "Diagnosis" = "SI Yes",
                                 "No diagnosis" = "SI No")
         )

nbr_si_ab_socp.df
nbr_si_ab_socp.xtabs.df
```

Panic disorder
```{r COPING NBR Panic disorder SI-AB crosstabs and agreement}
nbr_si_ab_pad.cM <- confusionMatrix(cidi.nbr$ClinicianPanicDis.f,
                                cidi.nbr$LifetimePanicDis.f,
                                positive = "Diagnosis",
                                dnn = c("Single-item", "Algorithm-based"))

#Create dataframe of agreements
nbr_si_ab_pad.classes<- as.matrix(nbr_si_ab_pad.cM, what = "classes")
nbr_si_ab_pad.overall <- as.matrix(nbr_si_ab_pad.cM, what = "overall")
nbr_si_ab_pad.raw <- as.data.frame(rbind(nbr_si_ab_pad.classes,
                                     nbr_si_ab_pad.overall))
colnames(nbr_si_ab_pad.raw) <- "PAD"

#Fromat dataframe
nbr_si_ab_pad.incomplete <- nbr_si_ab_pad.raw %>% 
  rownames_to_column() %>% 
  mutate(rowname = rownames(nbr_si_ab_pad.raw)) %>% 
  gather(Diagnosis, value, -rowname) %>% 
  spread(rowname, value) %>% 
  select(-unused_agreement)

#Calculate sensitivity and specificity with 95% CI
nbr_si_ab_pad.95ci <- summary(epiR::epi.tests(as.table(as.matrix(nbr_si_ab_pad.cM)), conf.level = 0.95)) %>%
  round(., 2) %>% 
  rownames_to_column() %>% 
  filter(rowname == "se" | rowname == "sp") %>% 
  mutate(combined =
           sprintf("%.2f (%.2f, %.2f)", 
                   est,
                   lower,
                   upper),
         Diagnosis = "PAD") %>% 
  select(-c(est, lower, upper)) %>% 
  pivot_wider(names_from = rowname, values_from = combined) %>% 
  rename("Sensitivity" = "se",
         "Specificity" = "sp")

#Combine dataframe with sensitivity/specificity
nbr_si_ab_pad.df <- merge(nbr_si_ab_pad.incomplete,
                      nbr_si_ab_pad.95ci)

#Create dataframe of crosstab
nbr_si_ab_pad.xtabs <- as.data.frame(as.matrix(nbr_si_ab_pad.cM))
nbr_si_ab_pad.xtabs.df <- nbr_si_ab_pad.xtabs %>% 
  rownames_to_column() %>% 
  rename("AB Yes" =
           "Diagnosis",
         "AB No" = "No diagnosis",
        "Crosstab"  = "rowname") %>% 
  mutate(Diagnosis = "PAD",
         Crosstab = recode_factor(Crosstab,
                                 "Diagnosis" = "SI Yes",
                                 "No diagnosis" = "SI No")
         )

nbr_si_ab_pad.df
nbr_si_ab_pad.xtabs.df
```

Panic attacks
The single-item panic attack variable here is being compared to lifetime panic disorder.
```{r COPING NBR Panic Attacks SI-AB crosstabs and agreement for Panic Disorder}
nbr_si_ab_pattacks.cM <- confusionMatrix(cidi.nbr$ClinicianPanicAttacks.f.cc,
                                cidi.nbr$LifetimePanicDis.f, 
                                positive = "Diagnosis",
                                dnn = c("Single-item", "Algorithm-based"))

#Create dataframe of agreements
nbr_si_ab_pattacks.classes<- as.matrix(nbr_si_ab_pattacks.cM, what = "classes")
nbr_si_ab_pattacks.overall <- as.matrix(nbr_si_ab_pattacks.cM, what = "overall")
nbr_si_ab_pattacks.raw <- as.data.frame(rbind(nbr_si_ab_pattacks.classes,
                                     nbr_si_ab_pattacks.overall))
colnames(nbr_si_ab_pattacks.raw) <- "PanicAttacks"

#Fromat dataframe
nbr_si_ab_pattacks.incomplete <- nbr_si_ab_pattacks.raw %>% 
  rownames_to_column() %>% 
  mutate(rowname = rownames(nbr_si_ab_pattacks.raw)) %>% 
  gather(Diagnosis, value, -rowname) %>% 
  spread(rowname, value) %>% 
  select(-unused_agreement)

#Calculate sensitivity and specificity with 95% CI
nbr_si_ab_pattacks.95ci <- summary(epiR::epi.tests(as.table(as.matrix(nbr_si_ab_pattacks.cM)), conf.level = 0.95)) %>%
  round(., 2) %>% 
  rownames_to_column() %>% 
  filter(rowname == "se" | rowname == "sp") %>% 
  mutate(combined =
           sprintf("%.2f (%.2f, %.2f)", 
                   est,
                   lower,
                   upper),
         Diagnosis = "PanicAttacks") %>% 
  select(-c(est, lower, upper)) %>% 
  pivot_wider(names_from = rowname, values_from = combined) %>% 
  rename("Sensitivity" = "se",
         "Specificity" = "sp")

#Combine dataframe with sensitivity/specificity
nbr_si_ab_pattacks.df <- merge(nbr_si_ab_pattacks.incomplete,
                      nbr_si_ab_pattacks.95ci)

#Create dataframe of crosstab
nbr_si_ab_pattacks.xtabs <- as.data.frame(as.matrix(nbr_si_ab_pattacks.cM))
nbr_si_ab_pattacks.xtabs.df <- nbr_si_ab_pattacks.xtabs %>% 
  rownames_to_column() %>% 
  rename("AB Yes" =
           "Diagnosis",
         "AB No" = "No diagnosis",
        "Crosstab"  = "rowname") %>% 
  mutate(Diagnosis = "PanicAttacks",
         Crosstab = recode_factor(Crosstab,
                                 "Diagnosis" = "SI Yes",
                                 "No diagnosis" = "SI No")
         )

nbr_si_ab_pattacks.df
nbr_si_ab_pattacks.xtabs.df
```

Agoraphobia
```{r COPING NBR Agoraphobia SI-AB crosstabs and agreement}
nbr_si_ab_agp.cM <- confusionMatrix(cidi.nbr$ClinicianAgoraphobia.f,
                                cidi.nbr$LifetimeAgoraphobia.f,
                                positive = "Diagnosis",
                                dnn = c("Single-item", "Algorithm-based"))

#Create dataframe of agreements
nbr_si_ab_agp.classes<- as.matrix(nbr_si_ab_agp.cM, what = "classes")
nbr_si_ab_agp.overall <- as.matrix(nbr_si_ab_agp.cM, what = "overall")
nbr_si_ab_agp.raw <- as.data.frame(rbind(nbr_si_ab_agp.classes,
                                     nbr_si_ab_agp.overall))
colnames(nbr_si_ab_agp.raw) <- "AGP"

#Fromat dataframe
nbr_si_ab_agp.incomplete <- nbr_si_ab_agp.raw %>% 
  rownames_to_column() %>% 
  mutate(rowname = rownames(nbr_si_ab_agp.raw)) %>% 
  gather(Diagnosis, value, -rowname) %>% 
  spread(rowname, value) %>% 
  select(-unused_agreement)

#Calculate sensitivity and specificity with 95% CI
nbr_si_ab_agp.95ci <- summary(epiR::epi.tests(as.table(as.matrix(nbr_si_ab_agp.cM)), conf.level = 0.95)) %>%
  round(., 2) %>% 
  rownames_to_column() %>% 
  filter(rowname == "se" | rowname == "sp") %>% 
  mutate(combined =
           sprintf("%.2f (%.2f, %.2f)", 
                   est,
                   lower,
                   upper),
         Diagnosis = "AGP") %>% 
  select(-c(est, lower, upper)) %>% 
  pivot_wider(names_from = rowname, values_from = combined) %>% 
  rename("Sensitivity" = "se",
         "Specificity" = "sp")

#Combine dataframe with sensitivity/specificity
nbr_si_ab_agp.df <- merge(nbr_si_ab_agp.incomplete,
                      nbr_si_ab_agp.95ci)

#Create dataframe of crosstab
nbr_si_ab_agp.xtabs <- as.data.frame(as.matrix(nbr_si_ab_agp.cM))
nbr_si_ab_agp.xtabs.df <- nbr_si_ab_agp.xtabs %>% 
  rownames_to_column() %>% 
  rename("AB Yes" =
           "Diagnosis",
         "AB No" = "No diagnosis",
        "Crosstab"  = "rowname") %>% 
  mutate(Diagnosis = "AGP",
         Crosstab = recode_factor(Crosstab,
                                 "Diagnosis" = "SI Yes",
                                 "No diagnosis" = "SI No")
         )

nbr_si_ab_agp.df
nbr_si_ab_agp.xtabs.df
```

Any anxiety
```{r COPING NBR Any Anxiety SI-AB crosstabs and agreement}
nbr_si_ab_anyanx.cM <- confusionMatrix(cidi.nbr$ClinicianAnyAnx.f, 
                                cidi.nbr$LifetimeAnyAnx.f,
                                positive = "Diagnosis",
                                dnn = c("Single-item", "Algorithm-based"))

#Create dataframe of agreements
nbr_si_ab_anyanx.classes<- as.matrix(nbr_si_ab_anyanx.cM, what = "classes")
nbr_si_ab_anyanx.overall <- as.matrix(nbr_si_ab_anyanx.cM, what = "overall")
nbr_si_ab_anyanx.raw <- as.data.frame(rbind(nbr_si_ab_anyanx.classes,
                                     nbr_si_ab_anyanx.overall))
colnames(nbr_si_ab_anyanx.raw) <- "AnyAnxiety"

#Fromat dataframe
nbr_si_ab_anyanx.incomplete <- nbr_si_ab_anyanx.raw %>% 
  rownames_to_column() %>% 
  mutate(rowname = rownames(nbr_si_ab_anyanx.raw)) %>% 
  gather(Diagnosis, value, -rowname) %>% 
  spread(rowname, value) %>% 
  select(-unused_agreement)

#Calculate sensitivity and specificity with 95% CI
nbr_si_ab_anyanx.95ci <- summary(epiR::epi.tests(as.table(as.matrix(nbr_si_ab_anyanx.cM)), conf.level = 0.95)) %>%
  round(., 2) %>% 
  rownames_to_column() %>% 
  filter(rowname == "se" | rowname == "sp") %>% 
  mutate(combined =
           sprintf("%.2f (%.2f, %.2f)", 
                   est,
                   lower,
                   upper),
         Diagnosis = "AnyAnxiety") %>% 
  select(-c(est, lower, upper)) %>% 
  pivot_wider(names_from = rowname, values_from = combined) %>% 
  rename("Sensitivity" = "se",
         "Specificity" = "sp")

#Combine dataframe with sensitivity/specificity
nbr_si_ab_anyanx.df <- merge(nbr_si_ab_anyanx.incomplete,
                      nbr_si_ab_anyanx.95ci)

#Create dataframe of crosstab
nbr_si_ab_anyanx.xtabs <- as.data.frame(as.matrix(nbr_si_ab_anyanx.cM))
nbr_si_ab_anyanx.xtabs.df <- nbr_si_ab_anyanx.xtabs %>% 
  rownames_to_column() %>% 
  rename("AB Yes" =
           "Diagnosis",
         "AB No" = "No diagnosis",
        "Crosstab"  = "rowname") %>% 
  mutate(Diagnosis = "AnyAnxiety",
         Crosstab = recode_factor(Crosstab,
                                 "Diagnosis" = "SI Yes",
                                 "No diagnosis" = "SI No")
         )

nbr_si_ab_anyanx.df
nbr_si_ab_anyanx.xtabs.df
```

```{r COPING NBR combine SI-AB agreement tables}
nbr_si_ab_all.raw <- bind_rows(nbr_si_ab_mdd.df,
                           nbr_si_ab_anyanx.df,
                           nbr_si_ab_gad.df,
                           nbr_si_ab_spec.df,
                           nbr_si_ab_socp.df,
                           nbr_si_ab_pad.df,
                           nbr_si_ab_pattacks.df,
                           nbr_si_ab_agp.df)

nbr_si_ab_all <- nbr_si_ab_all.raw %>% 
  rename("Sensitivity SI-AB" = "Sensitivity",
         "Specificity SI-AB" = "Specificity") %>% 
  relocate(Kappa, .after = last_col())

nbr_si_ab_all
```

```{r COPING NBR combine all xtabs tables}
nbr_all_xtabs.raw <- bind_rows(nbr_si_ab_mdd.xtabs.df,
                           nbr_si_ab_anyanx.xtabs.df,
                           nbr_si_ab_gad.xtabs.df,
                           nbr_si_ab_spec.xtabs.df,
                           nbr_si_ab_socp.xtabs.df,
                           nbr_si_ab_pad.xtabs.df,
                           nbr_si_ab_pattacks.xtabs.df,
                           nbr_si_ab_agp.xtabs.df)

nbr_all_xtabs <- nbr_all_xtabs.raw %>%  
  relocate(Diagnosis)

nbr_all_xtabs
```

#### Single-item diagnosis as reference point

Major depressive disorder
```{r COPING NBR MDD AB-SI crosstabs and agreement}
nbr_ab_si_mdd.cM <- confusionMatrix(cidi.nbr$LifetimeMDD.f,
                                cidi.nbr$ClinicianMDD.f, 
                                positive = "Diagnosis",
                                dnn = c("Algorithm-based", "Single-item"))

#Create dataframe of agreements
nbr_ab_si_mdd.classes<- as.matrix(nbr_ab_si_mdd.cM, what = "classes")
nbr_ab_si_mdd.overall <- as.matrix(nbr_ab_si_mdd.cM, what = "overall")
nbr_ab_si_mdd.raw <- as.data.frame(rbind(nbr_ab_si_mdd.classes,
                                     nbr_ab_si_mdd.overall))
colnames(nbr_ab_si_mdd.raw) <- "MDD"

#Fromat dataframe
nbr_ab_si_mdd.incomplete <- nbr_ab_si_mdd.raw %>% 
  rownames_to_column() %>% 
  mutate(rowname = rownames(nbr_ab_si_mdd.raw)) %>% 
  gather(Diagnosis, value, -rowname) %>% 
  spread(rowname, value) %>% 
  select(-unused_agreement)

#Calculate sensitivity and specificity with 95% CI
nbr_ab_si_mdd.95ci <- summary(epiR::epi.tests(as.table(as.matrix(nbr_ab_si_mdd.cM)), conf.level = 0.95)) %>%
  round(., 2) %>% 
  rownames_to_column() %>% 
  filter(rowname == "se" | rowname == "sp") %>% 
  mutate(combined =
           sprintf("%.2f (%.2f, %.2f)", 
                   est,
                   lower,
                   upper),
         Diagnosis = "MDD") %>% 
  select(-c(est, lower, upper)) %>% 
  pivot_wider(names_from = rowname, values_from = combined) %>% 
  rename("Sensitivity" = "se",
         "Specificity" = "sp")

#Combine dataframe with sensitivity/specificity
nbr_ab_si_mdd.df <- merge(nbr_ab_si_mdd.incomplete,
                      nbr_ab_si_mdd.95ci)

nbr_ab_si_mdd.df
```

Generalised anxiety disorder
```{r COPING NBR GAD AB-SI crosstabs and agreement}
nbr_ab_si_gad.cM <- confusionMatrix(cidi.nbr$LifetimeGAD.f,
                                cidi.nbr$ClinicianGAD.f, 
                                positive = "Diagnosis",
                                dnn = c("Algorithm-based", "Single-item"))

#Create dataframe of agreements
nbr_ab_si_gad.classes<- as.matrix(nbr_ab_si_gad.cM, what = "classes")
nbr_ab_si_gad.overall <- as.matrix(nbr_ab_si_gad.cM, what = "overall")
nbr_ab_si_gad.raw <- as.data.frame(rbind(nbr_ab_si_gad.classes,
                                     nbr_ab_si_gad.overall))
colnames(nbr_ab_si_gad.raw) <- "GAD"

#Fromat dataframe
nbr_ab_si_gad.incomplete <- nbr_ab_si_gad.raw %>% 
  rownames_to_column() %>% 
  mutate(rowname = rownames(nbr_ab_si_gad.raw)) %>% 
  gather(Diagnosis, value, -rowname) %>% 
  spread(rowname, value) %>% 
  select(-unused_agreement)

#Calculate sensitivity and specificity with 95% CI
nbr_ab_si_gad.95ci <- summary(epiR::epi.tests(as.table(as.matrix(nbr_ab_si_gad.cM)), conf.level = 0.95)) %>%
  round(., 2) %>% 
  rownames_to_column() %>% 
  filter(rowname == "se" | rowname == "sp") %>% 
  mutate(combined =
           sprintf("%.2f (%.2f, %.2f)", 
                   est,
                   lower,
                   upper),
         Diagnosis = "GAD") %>% 
  select(-c(est, lower, upper)) %>% 
  pivot_wider(names_from = rowname, values_from = combined) %>% 
  rename("Sensitivity" = "se",
         "Specificity" = "sp")

#Combine dataframe with sensitivity/specificity
nbr_ab_si_gad.df <- merge(nbr_ab_si_gad.incomplete,
                      nbr_ab_si_gad.95ci)

nbr_ab_si_gad.df
```

Specific phobia
```{r COPING NBR Specific phobia AB-SI crosstabs and agreement}
nbr_ab_si_spec.cM <- confusionMatrix(cidi.nbr$LifetimeSpecPhob.f,
                                 cidi.nbr$ClinicianSpecPhob.f, 
                                 positive = "Diagnosis",
                                 dnn = c("Algorithm-based", "Single-item"))

#Create dataframe of agreements
nbr_ab_si_spec.classes<- as.matrix(nbr_ab_si_spec.cM, what = "classes")
nbr_ab_si_spec.overall <- as.matrix(nbr_ab_si_spec.cM, what = "overall")
nbr_ab_si_spec.raw <- as.data.frame(rbind(nbr_ab_si_spec.classes,
                                     nbr_ab_si_spec.overall))
colnames(nbr_ab_si_spec.raw) <- "SPEC"

#Fromat dataframe
nbr_ab_si_spec.incomplete <- nbr_ab_si_spec.raw %>% 
  rownames_to_column() %>% 
  mutate(rowname = rownames(nbr_ab_si_spec.raw)) %>% 
  gather(Diagnosis, value, -rowname) %>% 
  spread(rowname, value) %>% 
  select(-unused_agreement)

#Calculate sensitivity and specificity with 95% CI
nbr_ab_si_spec.95ci <- summary(epiR::epi.tests(as.table(as.matrix(nbr_ab_si_spec.cM)), conf.level = 0.95)) %>%
  round(., 2) %>% 
  rownames_to_column() %>% 
  filter(rowname == "se" | rowname == "sp") %>% 
  mutate(combined =
           sprintf("%.2f (%.2f, %.2f)", 
                   est,
                   lower,
                   upper),
         Diagnosis = "SPEC") %>% 
  select(-c(est, lower, upper)) %>% 
  pivot_wider(names_from = rowname, values_from = combined) %>% 
  rename("Sensitivity" = "se",
         "Specificity" = "sp")

#Combine dataframe with sensitivity/specificity
nbr_ab_si_spec.df <- merge(nbr_ab_si_spec.incomplete,
                      nbr_ab_si_spec.95ci)

nbr_ab_si_spec.df
```

Social anxiety disorder
```{r COPING NBR Social anxiety disorder AB-SI crosstabs and agreement}
nbr_ab_si_socp.cM <- confusionMatrix(cidi.nbr$LifetimeSocialPhob.f,
                                 cidi.nbr$ClinicianSocialPhob.f, 
                                 positive = "Diagnosis",
                                 dnn = c("Algorithm-based", "Single-item"))

#Create dataframe of agreements
nbr_ab_si_socp.classes<- as.matrix(nbr_ab_si_socp.cM, what = "classes")
nbr_ab_si_socp.overall <- as.matrix(nbr_ab_si_socp.cM, what = "overall")
nbr_ab_si_socp.raw <- as.data.frame(rbind(nbr_ab_si_socp.classes,
                                     nbr_ab_si_socp.overall))
colnames(nbr_ab_si_socp.raw) <- "SOCP"

#Fromat dataframe
nbr_ab_si_socp.incomplete <- nbr_ab_si_socp.raw %>% 
  rownames_to_column() %>% 
  mutate(rowname = rownames(nbr_ab_si_socp.raw)) %>% 
  gather(Diagnosis, value, -rowname) %>% 
  spread(rowname, value) %>% 
  select(-unused_agreement)

#Calculate sensitivity and specificity with 95% CI
nbr_ab_si_socp.95ci <- summary(epiR::epi.tests(as.table(as.matrix(nbr_ab_si_socp.cM)), conf.level = 0.95)) %>%
  round(., 2) %>% 
  rownames_to_column() %>% 
  filter(rowname == "se" | rowname == "sp") %>% 
  mutate(combined =
           sprintf("%.2f (%.2f, %.2f)", 
                   est,
                   lower,
                   upper),
         Diagnosis = "SOCP") %>% 
  select(-c(est, lower, upper)) %>% 
  pivot_wider(names_from = rowname, values_from = combined) %>% 
  rename("Sensitivity" = "se",
         "Specificity" = "sp")

#Combine dataframe with sensitivity/specificity
nbr_ab_si_socp.df <- merge(nbr_ab_si_socp.incomplete,
                      nbr_ab_si_socp.95ci)

nbr_ab_si_socp.df
```

Panic disorder
```{r COPING NBR Panic disorder AB-SI crosstabs and agreement}
nbr_ab_si_pad.cM <- confusionMatrix(cidi.nbr$LifetimePanicDis.f,
                                cidi.nbr$ClinicianPanicDis.f, 
                                positive = "Diagnosis",
                                dnn = c("Algorithm-based", "Single-item"))

#Create dataframe of agreements
nbr_ab_si_pad.classes<- as.matrix(nbr_ab_si_pad.cM, what = "classes")
nbr_ab_si_pad.overall <- as.matrix(nbr_ab_si_pad.cM, what = "overall")
nbr_ab_si_pad.raw <- as.data.frame(rbind(nbr_ab_si_pad.classes,
                                     nbr_ab_si_pad.overall))
colnames(nbr_ab_si_pad.raw) <- "PAD"

#Fromat dataframe
nbr_ab_si_pad.incomplete <- nbr_ab_si_pad.raw %>% 
  rownames_to_column() %>% 
  mutate(rowname = rownames(nbr_ab_si_pad.raw)) %>% 
  gather(Diagnosis, value, -rowname) %>% 
  spread(rowname, value) %>% 
  select(-unused_agreement)

#Calculate sensitivity and specificity with 95% CI
nbr_ab_si_pad.95ci <- summary(epiR::epi.tests(as.table(as.matrix(nbr_ab_si_pad.cM)), conf.level = 0.95)) %>%
  round(., 2) %>% 
  rownames_to_column() %>% 
  filter(rowname == "se" | rowname == "sp") %>% 
  mutate(combined =
           sprintf("%.2f (%.2f, %.2f)", 
                   est,
                   lower,
                   upper),
         Diagnosis = "PAD") %>% 
  select(-c(est, lower, upper)) %>% 
  pivot_wider(names_from = rowname, values_from = combined) %>% 
  rename("Sensitivity" = "se",
         "Specificity" = "sp")

#Combine dataframe with sensitivity/specificity
nbr_ab_si_pad.df <- merge(nbr_ab_si_pad.incomplete,
                      nbr_ab_si_pad.95ci)

nbr_ab_si_pad.df
```

Panic attacks
Algorithm-based panic disorder is being compared with single-item panic attacks.
```{r COPING NBR Panic Attacks AB-SI crosstabs and agreement with Panic Disorder, echo=FALSE}
nbr_ab_si_pattacks.cM <- confusionMatrix(cidi.nbr$LifetimePanicDis.f, 
                                     cidi.nbr$ClinicianPanicAttacks.f.cc, 
                                     positive = "Diagnosis",
                                     dnn = c("Algorithm-based", "Single-item"))

#Create dataframe of agreements
nbr_ab_si_pattacks.classes<- as.matrix(nbr_ab_si_pattacks.cM, what = "classes")
nbr_ab_si_pattacks.overall <- as.matrix(nbr_ab_si_pattacks.cM, what = "overall")
nbr_ab_si_pattacks.raw <- as.data.frame(rbind(nbr_ab_si_pattacks.classes,
                                     nbr_ab_si_pattacks.overall))
colnames(nbr_ab_si_pattacks.raw) <- "PanicAttacks"

#Fromat dataframe
nbr_ab_si_pattacks.incomplete <- nbr_ab_si_pattacks.raw %>% 
  rownames_to_column() %>% 
  mutate(rowname = rownames(nbr_ab_si_pattacks.raw)) %>% 
  gather(Diagnosis, value, -rowname) %>% 
  spread(rowname, value) %>% 
  select(-unused_agreement)

#Calculate sensitivity and specificity with 95% CI
nbr_ab_si_pattacks.95ci <- summary(epiR::epi.tests(as.table(as.matrix(nbr_ab_si_pattacks.cM)), conf.level = 0.95)) %>%
  round(., 2) %>% 
  rownames_to_column() %>% 
  filter(rowname == "se" | rowname == "sp") %>% 
  mutate(combined =
           sprintf("%.2f (%.2f, %.2f)", 
                   est,
                   lower,
                   upper),
         Diagnosis = "PanicAttacks") %>% 
  select(-c(est, lower, upper)) %>% 
  pivot_wider(names_from = rowname, values_from = combined) %>% 
  rename("Sensitivity" = "se",
         "Specificity" = "sp")

#Combine dataframe with sensitivity/specificity
nbr_ab_si_pattacks.df <- merge(nbr_ab_si_pattacks.incomplete,
                      nbr_ab_si_pattacks.95ci)

nbr_ab_si_pattacks.df
```

Agoraphobia
```{r COPING NBR Agoraphobia AB-SI crosstabs and agreement}
nbr_ab_si_agp.cM <- confusionMatrix(cidi.nbr$LifetimeAgoraphobia.f, 
                                cidi.nbr$ClinicianAgoraphobia.f, 
                                positive = "Diagnosis",
                                dnn = c("Algorithm-based", "Single-item"))

#Create dataframe of agreements
nbr_ab_si_agp.classes<- as.matrix(nbr_ab_si_agp.cM, what = "classes")
nbr_ab_si_agp.overall <- as.matrix(nbr_ab_si_agp.cM, what = "overall")
nbr_ab_si_agp.raw <- as.data.frame(rbind(nbr_ab_si_agp.classes,
                                     nbr_ab_si_agp.overall))
colnames(nbr_ab_si_agp.raw) <- "AGP"

#Fromat dataframe
nbr_ab_si_agp.incomplete <- nbr_ab_si_agp.raw %>% 
  rownames_to_column() %>% 
  mutate(rowname = rownames(nbr_ab_si_agp.raw)) %>% 
  gather(Diagnosis, value, -rowname) %>% 
  spread(rowname, value) %>% 
  select(-unused_agreement)

#Calculate sensitivity and specificity with 95% CI
nbr_ab_si_agp.95ci <- summary(epiR::epi.tests(as.table(as.matrix(nbr_ab_si_agp.cM)), conf.level = 0.95)) %>%
  round(., 2) %>% 
  rownames_to_column() %>% 
  filter(rowname == "se" | rowname == "sp") %>% 
  mutate(combined =
           sprintf("%.2f (%.2f, %.2f)", 
                   est,
                   lower,
                   upper),
         Diagnosis = "AGP") %>% 
  select(-c(est, lower, upper)) %>% 
  pivot_wider(names_from = rowname, values_from = combined) %>% 
  rename("Sensitivity" = "se",
         "Specificity" = "sp")

#Combine dataframe with sensitivity/specificity
nbr_ab_si_agp.df <- merge(nbr_ab_si_agp.incomplete,
                      nbr_ab_si_agp.95ci)

nbr_ab_si_agp.df
```

Any anxiety
```{r COPING NBR Any Anxiety AB-SI crosstabs and agreement}
nbr_ab_si_anyanx.cM <- confusionMatrix(cidi.nbr$LifetimeAnyAnx.f,
                                   cidi.nbr$ClinicianAnyAnx.f, 
                                   positive = "Diagnosis",
                                   dnn = c("Algorithm-based", "Single-item"))

#Create dataframe of agreements
nbr_ab_si_anyanx.classes<- as.matrix(nbr_ab_si_anyanx.cM, what = "classes")
nbr_ab_si_anyanx.overall <- as.matrix(nbr_ab_si_anyanx.cM, what = "overall")
nbr_ab_si_anyanx.raw <- as.data.frame(rbind(nbr_ab_si_anyanx.classes,
                                     nbr_ab_si_anyanx.overall))
colnames(nbr_ab_si_anyanx.raw) <- "AnyAnxiety"

#Fromat dataframe
nbr_ab_si_anyanx.incomplete <- nbr_ab_si_anyanx.raw %>% 
  rownames_to_column() %>% 
  mutate(rowname = rownames(nbr_ab_si_anyanx.raw)) %>% 
  gather(Diagnosis, value, -rowname) %>% 
  spread(rowname, value) %>% 
  select(-unused_agreement)

#Calculate sensitivity and specificity with 95% CI
nbr_ab_si_anyanx.95ci <- summary(epiR::epi.tests(as.table(as.matrix(nbr_ab_si_anyanx.cM)), conf.level = 0.95)) %>%
  round(., 2) %>% 
  rownames_to_column() %>% 
  filter(rowname == "se" | rowname == "sp") %>% 
  mutate(combined =
           sprintf("%.2f (%.2f, %.2f)", 
                   est,
                   lower,
                   upper),
         Diagnosis = "AnyAnxiety") %>% 
  select(-c(est, lower, upper)) %>% 
  pivot_wider(names_from = rowname, values_from = combined) %>% 
  rename("Sensitivity" = "se",
         "Specificity" = "sp")

#Combine dataframe with sensitivity/specificity
nbr_ab_si_anyanx.df <- merge(nbr_ab_si_anyanx.incomplete,
                      nbr_ab_si_anyanx.95ci)

nbr_ab_si_anyanx.df
```

```{r COPING NBR combine AB-SI agreement tables}
nbr_ab_si_all.raw <- bind_rows(nbr_ab_si_mdd.df,
                           nbr_ab_si_anyanx.df,
                           nbr_ab_si_gad.df,
                           nbr_ab_si_spec.df,
                           nbr_ab_si_socp.df,
                           nbr_ab_si_pad.df,
                           nbr_ab_si_pattacks.df,
                           nbr_ab_si_agp.df)

nbr_ab_si_all <- nbr_ab_si_all.raw %>% 
  select(Diagnosis,
         "Sensitivity AB-SI" = "Sensitivity",
         "Specificity AB-SI" = "Specificity") 

nbr_ab_si_all
```

#### Agreement table for all statistics

```{r COPING NBR combine all agreement tables}
nbr_all_agreement <- merge(nbr_si_ab_all,
                       nbr_ab_si_all) %>%
  relocate(Kappa, .after = last_col()) %>% 
  mutate(Diagnosis = 
           factor(Diagnosis,
                  levels = c("MDD", "AnyAnxiety", "GAD", "SPEC", "SOCP", "PanicAttacks", "PAD", "AGP"))
         ) %>% 
  arrange(., Diagnosis)

nbr_all_agreement
```

```{r COPING NBR combine agreements and xtabs tables}
nbr_all_agreement_xtabs <- merge(nbr_all_xtabs,
                             nbr_all_agreement) %>%
  mutate(Diagnosis = 
           factor(Diagnosis,
                  levels = c("MDD", "AnyAnxiety", "GAD", "SPEC", "SOCP", "PanicAttacks", "PAD", "AGP")),
         Sample = "COPING NBR"
         ) %>% 
  arrange(., Diagnosis) %>% 
  relocate(Sample)

nbr_all_agreement_xtabs
```

## Full sample and by sample combined table

```{r combine all agreement tables}
all_agreement_xtabs <- rbind(full_sample_all_agreement_xtabs,
                             glad_all_agreement_xtabs,
                             nbr_all_agreement_xtabs) %>% 
  mutate(Accuracy = 
           sprintf("%.2f (%.2f, %.2f)",
                   Accuracy*100,
                   AccuracyLower*100,
                   AccuracyUpper*100)) %>% 
  select(-c(AccuracyLower, AccuracyUpper)) %>%
  arrange(., Diagnosis) %>% 
  mutate(Diagnosis = 
           case_when(
             Diagnosis == "MDD" ~ "MDD",
             Diagnosis == "GAD" ~ "GAD",
             Diagnosis == "AnyAnxiety" ~ "Any anxiety",
             Diagnosis == "SPEC" ~ "Specific phobia",
             Diagnosis == "SOCP" ~ "Social anxiety disorder",
             Diagnosis == "PAD" ~ "Panic disorder",
             Diagnosis == "PanicAttacks" ~ "Panic attacks",
             Diagnosis == "AGP" ~ "Agoraphobia"
           ),
         Diagnosis = 
           case_when(
             Crosstab == "SI Yes" ~ Diagnosis,
             Crosstab == "SI No" ~ ""
           ),
         Sample = 
           case_when(
             Crosstab == "SI Yes" ~ Sample,
             Crosstab == "SI No" ~ ""
           ),
         SI = 
           case_when(
             Crosstab == "SI Yes" ~ "Single-item (SI)",
             Crosstab == "SI No" ~ ""
           ),
         Accuracy = 
           case_when(
             Crosstab == "SI Yes" ~ Accuracy,
             Crosstab == "SI No" ~ ""
           ),
         `Sensitivity SI-AB` = 
           case_when(
             Crosstab == "SI Yes" ~ `Sensitivity SI-AB`,
             Crosstab == "SI No" ~ ""
           ),
         `Specificity SI-AB` = 
           case_when(
             Crosstab == "SI Yes" ~ `Specificity SI-AB`,
             Crosstab == "SI No" ~ ""
           ),
         `Sensitivity AB-SI` = 
           case_when(
             Crosstab == "SI Yes" ~ `Sensitivity AB-SI`,
             Crosstab == "SI No" ~ ""
           ),
         `Specificity AB-SI` = 
           case_when(
             Crosstab == "SI Yes" ~ `Specificity AB-SI`,
             Crosstab == "SI No" ~ ""
           ),
         Kappa = 
           case_when(
             Crosstab == "SI Yes" ~ as.character(round(Kappa, 2)),
             Crosstab == "SI No" ~ ""
           ),
         McnemarPValue = 
           case_when(
             Crosstab == "SI Yes" & 
               McnemarPValue < 0.001 ~ "p < 0.001",
             Crosstab == "SI Yes" & 
               McnemarPValue > 0.001 & McnemarPValue < 0.01 ~ "p < 0.01",
             Crosstab == "SI Yes" & 
               McnemarPValue > 0.01 & McnemarPValue < 0.05 ~ "p < 0.05",
             Crosstab == "SI Yes" & 
               McnemarPValue > 0.05 ~ paste0("p ~ ", round(McnemarPValue, 2)),
             Crosstab == "SI No" ~ ""
           ),
         Crosstab = 
           case_when(
             Crosstab == "SI Yes" ~ "Yes",
             Crosstab == "SI No" ~ "No"
           )
           ) %>% 
  rename("Accuracy (%)" = "Accuracy",
         "Cohort" = "Sample",
         "Disorder" = "Diagnosis",
         "Mcnemar's test" = "McnemarPValue") %>%
  relocate(c(Disorder, Cohort, SI)) %>% 
  relocate(`Mcnemar's test`, .after = last_col())

kable(all_agreement_xtabs)
```


# Analyses of difference

## GLAD vs COPING sample characteristics
    Cohort as grouping variable with the different characteristics
    Chi-square if dichotomous; independent t-test for continuous variables

Indendent samples t-test to assess differences in age between GLAD vs COPING cohorts
```{r t-test age}

```


Chi-square tests to assess differences between GLAD vs COPING cohorts in:
- Sex
- Ethnicity
- Highest education

```{r chi-square sex}

```

```{r chi-square ethnicity}

```

```{r chi-square highest education}

```

## Male vs female diagnostic agreements
    Chi-square test (Female: Yes/No)

```{r}

```

