---
title: "DIAGCOMP_descriptives_frequencies"
author: "Molly R. Davies"
date: 30/10/2020
output:  
  html_document:
    df_print: paged
    toc: yes
    toc_depth: 2
    toc_float:
      collapsed: false
    number_sections: false
    highlight: monochrome
    theme: cerulean
code_folding: show

html_notebook:
  theme: cerulean
toc: yes
---

This is the script to run demographic descriptives and frequencies of the single-item/algorithm-based diagnoses of the GLAD Study sample. Results are reported in the paper titled "Comparison of algorithm-based versus single-item phenotyping measures of depression and anxiety disorders in the GLAD Study cohort" - Davies et al (in prep).

Script written by M. R. Davies.
Email:  molly.davies@kcl.ac.uk

All scripts for the paper can be accessed at:
https://github.com/mollyrdavies/GLAD-Diagnostic-algorithms.git

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Set up
```{r install packages}
#install.packages("summarytools")
#install.packages("tidyverse")
#install.packages("descr")
```

```{r import packages}
library(descr)
library(summarytools)
library(tidyverse)
```

```{r source file paths}
source("../../DF1.0_data_path.R")
```

```{r read data}
dat.cc <- read_rds(paste0(cleaned_path, "combined_cleaned_new_variables.rds"))
```

```{r visualise dataset}
dim(dat.cc)
head(dat.cc)
```

# Demographics of GLAD sample

## Mean age

```{r mean age}                        
mean(dat.cc$age, na.rm = T)
```

## Sex frequencies

```{r sex freq}                        
freq(dat.cc$sex)
```

## Ethnicity frequencies

```{r ethnicity freq}
freq(dat.cc$Ethnicity)
```

## Highest Education frequencies

```{r higher education freq}
freq(dat.cc$Highest.Education)
```

# Diagnosis: Frequencies and proportions
Frequencies of diagnoses calculated for participants with values in BOTH single-item and algorithm-based diagnosis per disorder.
Participants with NAs for one measure were excluded for that diagnosis.

# Get frequencies for each diagnosis, excluding NAs per disorder

```{r MDD frequencies}
#Algorithm-based MDD frequencies
dat.cc %>% 
  filter(!is.na(mhd.mdd) & !is.na(cidid.diagnosis)) %>%
  summarytools::freq(cidid.diagnosis, report.NAs = T) 

#Single-item MDD frequencies
dat.cc %>% 
  filter(!is.na(mhd.mdd) & !is.na(cidid.diagnosis)) %>%
  summarytools::freq(mhd.mdd)

```

```{r Any Anxiety frequencies}
#Algorithm-based any anxiety frequencies
dat.cc %>% 
  filter(!is.na(LifetimeAnyAnx) & !is.na(ClinicianAnyAnx)) %>%
  summarytools::freq(LifetimeAnyAnx)

#Single-item any anxiety frequencies
dat.cc %>% 
  filter(!is.na(LifetimeAnyAnx) & !is.na(ClinicianAnyAnx)) %>%
  summarytools::freq(ClinicianAnyAnx)

```

```{r GAD frequencies}
#Algorithm-based GAD frequencies
dat.cc %>% 
  filter(!is.na(mhd.gad) & !is.na(cidia.diagnosis)) %>%
  summarytools::freq(cidia.diagnosis)

#Single-item GAD frequencies
dat.cc %>% 
  filter(!is.na(mhd.gad) & !is.na(cidia.diagnosis)) %>%
  summarytools::freq(mhd.gad)

```

```{r Specific phobia frequencies}
#Algorithm-based specific phobia frequencies
dat.cc %>% 
  filter(!is.na(mhd.specific_phobia) & !is.na(spec.diagnosis)) %>%
  summarytools::freq(spec.diagnosis)

#Single-item specific phobia frequencies
dat.cc %>% 
  filter(!is.na(mhd.specific_phobia) & !is.na(spec.diagnosis)) %>%
  summarytools::freq(mhd.specific_phobia)
```

```{r Social anxiety disorder frequencies}
#Algorithm-based social anxiety frequencies
dat.cc %>% 
  filter(!is.na(mhd.social_anxiety) & !is.na(socp.diagnosis)) %>%
  summarytools::freq(socp.diagnosis)

#Single-item social anxiety frequencies
dat.cc %>% 
  filter(!is.na(mhd.social_anxiety) & !is.na(socp.diagnosis)) %>%
  summarytools::freq(mhd.social_anxiety)

```

```{r Panic disorder frequencies}
#Algorithm-based panic disorder frequencies
dat.cc %>% 
  filter(!is.na(mhd.panic_disorder) & !is.na(pad.diagnosis)) %>%
  summarytools::freq(pad.diagnosis)

#Single-item panic disorder frequencies
dat.cc %>% 
  filter(!is.na(mhd.panic_disorder) & !is.na(pad.diagnosis)) %>%
  summarytools::freq(mhd.panic_disorder)

```

```{r Panic Attacks vs Lifetime Panic disorder frequencies}
#Single-item panic attacks frequencies
dat.cc %>% 
  filter(!is.na(mhd.panic_attacks) & !is.na(mhd.panic_disorder) & !is.na(pad.diagnosis)) %>%
  summarytools::freq(mhd.panic_attacks)

```

```{r Agoraphobia frequencies}
#Algorithm-based agoraphobia frequencies
dat.cc %>% 
  filter(!is.na(mhd.agoraphobia) & !is.na(agp.diagnosis)) %>%
  summarytools::freq(agp.diagnosis)

#Single-item agoraphobia frequencies
dat.cc %>% 
  filter(!is.na(mhd.agoraphobia) & !is.na(agp.diagnosis)) %>%
  summarytools::freq(mhd.agoraphobia)
```


# Number of diagnoses/comorbidities in sample
Check the number of diagnoses in the sample to see:
- N ppts with 0 diagnoses
- N ppts with 1 diagnosis
- N ppts with 2+ diagnoses

## Single-item diagnoses
Note: Single-item panic disorder was added partway through data collection. The single-item count variable is therefore not coded as NA for panic disorder missingness to avoid excessive data loss.
```{r create variable of N single-item diagnoses}
#Sum all clinical diagnoses and remove NAs (except panic disorder, as this variable was included partway through data collection)
dat.cc$selfreport_noPanic <- rowSums(dat.cc[,c("mhd.mdd", 
                                           "mhd.gad", 
                                           "mhd.specific_phobia", 
                                           "mhd.social_anxiety", 
                                           "mhd.agoraphobia")], na.rm=FALSE)

#Add panic only for particpants without NA in above variable
dat.cc$selfreport.n <- with(dat.cc,
                          ifelse(
                            is.na(selfreport_noPanic), 
                            NA, 
                            rowSums(dat.cc[,c("selfreport_noPanic", 
                                            "mhd.panic_disorder")], na.rm = TRUE)
                                 )
                          )
freq(dat.cc$selfreport_noPanic)
freq(dat.cc$selfreport.n)
```

```{r get N with 1+ or 2+ single-item diagnosis}
#N with 1+ SR diagnosis
table(dat.cc[,c("selfreport.n")]>0)

#N with 2+ SR diagnoses
table(dat.cc[,c("selfreport.n")]>1)

```

```{r get mean single-item diagnoses}

mean(dat.cc$selfreport.n, na.rm = T)

```

## Algorithm-based diagnoses

```{r create variable of N algorithm-based diagnoses}
#Sum all algorithm-based diagnoses and include NAs (coded as 0)
dat.cc$algorithm_based_count_numeric <- rowSums(dat.cc[,c("cidid.diagnosis_numeric", 
                                                          "cidia.diagnosis_numeric", 
                                                          "spec.diagnosis_numeric", 
                                                          "socp.diagnosis_numeric", 
                                                          "pad.diagnosis_numeric", 
                                                          "agp.diagnosis_numeric")], 
                                                na.rm=TRUE)

#Check what it would be if the NAs were excluded
dat.cc$algorithm_based_noNA.n <- rowSums(dat.cc[,c("cidid.diagnosis_numeric", 
                                                   "cidia.diagnosis_numeric", 
                                                   "spec.diagnosis_numeric", 
                                                   "socp.diagnosis_numeric", 
                                                   "pad.diagnosis_numeric", 
                                                   "agp.diagnosis_numeric")], 
                                         na.rm=FALSE)

#Summarise
summary(as.factor(dat.cc$algorithm_based_count_numeric))
summary(as.factor(dat.cc$algorithm_based_noNA.n))

```

```{r NAs in algorithm-based outcomes}

#Do NOT use 'is.na' for these as then you cannot +1 to it. Use the no.info item for NA (below). 
dat.cc$algorithm_based_NA.n<-0

#MDD
dat.cc$algorithm_based_NA.n<-with(dat.cc, 
                         ifelse(is.na(cidid.diagnosis_numeric),
                                algorithm_based_NA.n + 1, algorithm_based_NA.n))
#GAD
dat.cc$algorithm_based_NA.n<-with(dat.cc, 
                         ifelse(is.na(cidia.diagnosis_numeric),
                                algorithm_based_NA.n + 1, algorithm_based_NA.n))
#Specific phobia
dat.cc$algorithm_based_NA.n<-with(dat.cc, 
                         ifelse(is.na(spec.diagnosis_numeric),
                                algorithm_based_NA.n + 1, algorithm_based_NA.n))
#Social phobia
dat.cc$algorithm_based_NA.n<-with(dat.cc, 
                         ifelse(is.na(socp.diagnosis_numeric),
                                algorithm_based_NA.n + 1, algorithm_based_NA.n))
#Panic disorder
dat.cc$algorithm_based_NA.n<-with(dat.cc, 
                         ifelse(is.na(pad.diagnosis_numeric),
                                algorithm_based_NA.n + 1, algorithm_based_NA.n))
#Agoraphobia
dat.cc$algorithm_based_NA.n<-with(dat.cc, 
                         ifelse(is.na(agp.diagnosis_numeric),
                                algorithm_based_NA.n + 1, algorithm_based_NA.n))
#Check distribution of scores
summary(as.factor(dat.cc$algorithm_based_NA.n))


```

```{r get N with 1+ or 2+ algorithm-based diagnosis}

#N with 1+ algorithm-based diagnosis
table(dat.cc[,c("algorithm_based_count_numeric")]>0)

#N with 2+ algorithm-based diagnoses
table(dat.cc[,c("algorithm_based_count_numeric")]>1)

```

```{r get mean algorithm-based diagnoses}

mean(dat.cc$algorithm_based_count_numeric, na.rm = T)

```

## Look at N algorithm-based diagnoses in participants with >=1 single-item diagnoses

```{r subset participants with 1+ single-item diagnosis}
#Subset
selfreport_n1 <- subset(dat.cc, selfreport.n > 0)
#Check correct number of participants
nrow(selfreport_n1)

```

```{r get subset N with 0, 1 or 2+ algorithm-based diagnosis}

#N with no algorithm-based diagnosis
table(selfreport_n1[,c("algorithm_based_noNA.n")]==0)

#N with 1 algorithm-based diagnosis
table(selfreport_n1[,c("algorithm_based_count_numeric")]==1)

#N with 2+ algorithm-based diagnoses
table(selfreport_n1[,c("algorithm_based_count_numeric")]>1)

```

```{r get mean subset algorithm-based diagnoses}
mean(selfreport_n1$algorithm_based_count_numeric, na.rm = T)
```

## Look at N single-item diagnoses in participants with >=1 algorithm-based diagnoses

```{r subset participants with 1+ algorithm-based diagnosis}
#Subset
algorithm_based_n1 <- subset(dat.cc, algorithm_based_count_numeric > 0)
#Check correct number of participants
nrow(algorithm_based_n1)

```

```{r get subset N with 0, 1 or 2+ single-item diagnosis}

#N with no algorithm-based diagnosis
table(algorithm_based_n1[,c("selfreport.n")]==0)

#N with 1 algorithm-based diagnosis
table(algorithm_based_n1[,c("selfreport.n")]==1)

#N with 2+ algorithm-based diagnoses
table(algorithm_based_n1[,c("selfreport.n")]>1)

```

```{r get mean subset single-item diagnoses}
mean(algorithm_based_n1$selfreport.n, na.rm = T)
```

# Agreement frequencies
## Create function to run concordance

```{r create function to take the sum of ifelse statement: yes is 1 no is 0}

sum_ifelse <- function(x, y) {
  sum(ifelse(x & y, 1, 0), na.rm=T)
}

```

## Create table of AB/SI agreements/disagreements for each disorder

```{r create dataframe with agree/disagree results}

## COLUMN ORDER: ##
#Agreement: No diagnosis (AB NO, SI NO)",
#Disagreement: AB no, SI yes",
#Disagreement: AB Yes, SI No",
#Agreement: diagnosis (AB Yes, SI Yes)"

##Create a blank matrix
table0.m <- matrix(c(
                   #Fill in MDD row
                   sum_ifelse(dat.cc$cidid.diagnosis_numeric == 0, dat.cc$mhd.mdd == 0),  
                   sum_ifelse(dat.cc$cidid.diagnosis_numeric == 0, dat.cc$mhd.mdd == 1),
                   sum_ifelse(dat.cc$cidid.diagnosis_numeric == 1, dat.cc$mhd.mdd == 0),
                   sum_ifelse(dat.cc$cidid.diagnosis_numeric == 1, dat.cc$mhd.mdd == 1),
                   sum_ifelse(!is.na(dat.cc$cidid.diagnosis_numeric), !is.na(dat.cc$mhd.mdd)),
                   #Fill in any anxiety row
                   sum_ifelse(dat.cc$LifetimeAnyAnx.n == 0, dat.cc$ClinicianAnyAnx.n == 0),  
                   sum_ifelse(dat.cc$LifetimeAnyAnx.n == 0, dat.cc$ClinicianAnyAnx.n == 1),
                   sum_ifelse(dat.cc$LifetimeAnyAnx.n == 1, dat.cc$ClinicianAnyAnx.n == 0),
                   sum_ifelse(dat.cc$LifetimeAnyAnx.n == 1, dat.cc$ClinicianAnyAnx.n == 1),
                   sum_ifelse(!is.na(dat.cc$LifetimeAnyAnx), !is.na(dat.cc$ClinicianAnyAnx)),
                   #Fill in GAD row
                   sum_ifelse(dat.cc$cidia.diagnosis_numeric == 0, dat.cc$mhd.gad == 0),               
                   sum_ifelse(dat.cc$cidia.diagnosis_numeric == 0, dat.cc$mhd.gad == 1),       
                   sum_ifelse(dat.cc$cidia.diagnosis_numeric == 1, dat.cc$mhd.gad == 0),
                   sum_ifelse(dat.cc$cidia.diagnosis_numeric == 1, dat.cc$mhd.gad == 1),
                   sum_ifelse(!is.na(dat.cc$cidia.diagnosis_numeric), !is.na(dat.cc$mhd.gad)),
                   #Fill in SpecPhob row
                   sum_ifelse(dat.cc$spec.diagnosis_numeric == 0, dat.cc$mhd.specific_phobia == 0), 
                   sum_ifelse(dat.cc$spec.diagnosis_numeric == 0, dat.cc$mhd.specific_phobia == 1), 
                   sum_ifelse(dat.cc$spec.diagnosis_numeric == 1, dat.cc$mhd.specific_phobia == 0),
                   sum_ifelse(dat.cc$spec.diagnosis_numeric == 1, dat.cc$mhd.specific_phobia == 1), 
                   sum_ifelse(!is.na(dat.cc$spec.diagnosis_numeric), !is.na(dat.cc$mhd.specific_phobia)),
                   #Fill in SocialPhob row 
                   sum_ifelse(dat.cc$socp.diagnosis_numeric == 0, dat.cc$mhd.social_anxiety == 0), 
                   sum_ifelse(dat.cc$socp.diagnosis_numeric == 0, dat.cc$mhd.social_anxiety == 1), 
                   sum_ifelse(dat.cc$socp.diagnosis_numeric == 1, dat.cc$mhd.social_anxiety == 0),
                   sum_ifelse(dat.cc$socp.diagnosis_numeric == 1, dat.cc$mhd.social_anxiety == 1),
                   sum_ifelse(!is.na(dat.cc$socp.diagnosis_numeric), !is.na(dat.cc$mhd.social_anxiety)),
                   #Fill in Panic attacks row
                   sum(ifelse(dat.cc$pad.diagnosis_numeric == 0 & dat.cc$mhd.panic_attacks == 0 & !is.na(dat.cc$mhd.panic_disorder), 1, 0), na.rm=T), 
                   sum(ifelse(dat.cc$pad.diagnosis_numeric == 0 & dat.cc$mhd.panic_attacks == 1 & !is.na(dat.cc$mhd.panic_disorder), 1, 0), na.rm=T),
                   sum(ifelse(dat.cc$pad.diagnosis_numeric == 1 & dat.cc$mhd.panic_attacks == 0 & !is.na(dat.cc$mhd.panic_disorder), 1, 0), na.rm=T),
                   sum(ifelse(dat.cc$pad.diagnosis_numeric == 1 & dat.cc$mhd.panic_attacks == 1 & !is.na(dat.cc$mhd.panic_disorder), 1, 0), na.rm=T), 
                   sum(ifelse(!is.na(dat.cc$pad.diagnosis_numeric) & !is.na(dat.cc$mhd.panic_attacks) & !is.na(dat.cc$mhd.panic_disorder), 1, 0), na.rm=T),
                   #Fill in Panic disorder row
                   sum_ifelse(dat.cc$pad.diagnosis_numeric == 0, dat.cc$mhd.panic_disorder == 0), 
                   sum_ifelse(dat.cc$pad.diagnosis_numeric == 0, dat.cc$mhd.panic_disorder == 1),
                   sum_ifelse(dat.cc$pad.diagnosis_numeric == 1, dat.cc$mhd.panic_disorder == 0),
                   sum_ifelse(dat.cc$pad.diagnosis_numeric == 1, dat.cc$mhd.panic_disorder == 1), 
                   sum_ifelse(!is.na(dat.cc$pad.diagnosis_numeric), !is.na(dat.cc$mhd.panic_disorder)),
                   #Fill in Agoraphobia row
                   sum_ifelse(dat.cc$agp.diagnosis_numeric == 0, dat.cc$mhd.agoraphobia == 0),
                   sum_ifelse(dat.cc$agp.diagnosis_numeric == 0, dat.cc$mhd.agoraphobia == 1),
                   sum_ifelse(dat.cc$agp.diagnosis_numeric == 1, dat.cc$mhd.agoraphobia == 0),
                   sum_ifelse(dat.cc$agp.diagnosis_numeric == 1, dat.cc$mhd.agoraphobia == 1),
                   sum_ifelse(!is.na(dat.cc$agp.diagnosis_numeric), !is.na(dat.cc$mhd.agoraphobia))
                   ),
                   nrow = 8,
                   ncol = 5,
                   byrow = T)

##Convert it to a dataframe 
table0 <- data.frame(table0.m)

##Add column names (clinician diagnoses)
colnames(table0) <- c("Agreement: No diagnosis (AB NO, SI NO)",
                      "Disagreement: screened negative, diagnosis (AB no, SI yes)",
                      "Disagreement: screened positive, no diagnosis (AB Yes, SI No)",
                      "Agreement: diagnosis (AB Yes, SI Yes)",
                      "Total (N)")

##Add row names (lifetime diagnoses) - eventually add script to add N per diagnosis to row names
rownames(table0) <- c("Major depressive disorder", 
                      "Any anxiety",
                      "Generalised anxiety disorder", 
                      "Specific phobia", 
                      "Social anxiety disorder",
                      "Panic attacks",
                      "Panic disorder",
                      "Agoraphobia")

##Visualise
table0
```

# Agreements by sex

## Male-only dataset

```{r dataset by sex}

dat.male <- dat.cc %>% 
  filter(sex == 0)

```


## Male-only table of AB/SI agreements/disagreements for each disorder

```{r create male-only dataframe with agree/disagree results}

## COLUMN ORDER: ##
#Agreement: No diagnosis (AB NO, SI NO)",
#Disagreement: AB no, SI yes",
#Disagreement: AB Yes, SI No",
#Agreement: diagnosis (AB Yes, SI Yes)"

##Create a blank matrix
table1.m <- matrix(c(
                   #Fill in MDD row
                   sum_ifelse(dat.male$cidid.diagnosis_numeric == 0, dat.male$mhd.mdd == 0),  
                   sum_ifelse(dat.male$cidid.diagnosis_numeric == 0, dat.male$mhd.mdd == 1),
                   sum_ifelse(dat.male$cidid.diagnosis_numeric == 1, dat.male$mhd.mdd == 0),
                   sum_ifelse(dat.male$cidid.diagnosis_numeric == 1, dat.male$mhd.mdd == 1),
                   sum_ifelse(!is.na(dat.male$cidid.diagnosis_numeric), !is.na(dat.male$mhd.mdd)),
                   #Fill in any anxiety row
                   sum_ifelse(dat.male$LifetimeAnyAnx.n == 0, dat.male$ClinicianAnyAnx.n == 0),  
                   sum_ifelse(dat.male$LifetimeAnyAnx.n == 0, dat.male$ClinicianAnyAnx.n == 1),
                   sum_ifelse(dat.male$LifetimeAnyAnx.n == 1, dat.male$ClinicianAnyAnx.n == 0),
                   sum_ifelse(dat.male$LifetimeAnyAnx.n == 1, dat.male$ClinicianAnyAnx.n == 1),
                   sum_ifelse(!is.na(dat.male$LifetimeAnyAnx), !is.na(dat.male$ClinicianAnyAnx)),
                   #Fill in GAD row
                   sum_ifelse(dat.male$cidia.diagnosis_numeric == 0, dat.male$mhd.gad == 0),               
                   sum_ifelse(dat.male$cidia.diagnosis_numeric == 0, dat.male$mhd.gad == 1),       
                   sum_ifelse(dat.male$cidia.diagnosis_numeric == 1, dat.male$mhd.gad == 0),
                   sum_ifelse(dat.male$cidia.diagnosis_numeric == 1, dat.male$mhd.gad == 1),
                   sum_ifelse(!is.na(dat.male$cidia.diagnosis_numeric), !is.na(dat.male$mhd.gad)),
                   #Fill in SpecPhob row
                   sum_ifelse(dat.male$spec.diagnosis_numeric == 0, dat.male$mhd.specific_phobia == 0), 
                   sum_ifelse(dat.male$spec.diagnosis_numeric == 0, dat.male$mhd.specific_phobia == 1), 
                   sum_ifelse(dat.male$spec.diagnosis_numeric == 1, dat.male$mhd.specific_phobia == 0),
                   sum_ifelse(dat.male$spec.diagnosis_numeric == 1, dat.male$mhd.specific_phobia == 1), 
                   sum_ifelse(!is.na(dat.male$spec.diagnosis_numeric), !is.na(dat.male$mhd.specific_phobia)),
                   #Fill in SocialPhob row 
                   sum_ifelse(dat.male$socp.diagnosis_numeric == 0, dat.male$mhd.social_anxiety == 0), 
                   sum_ifelse(dat.male$socp.diagnosis_numeric == 0, dat.male$mhd.social_anxiety == 1), 
                   sum_ifelse(dat.male$socp.diagnosis_numeric == 1, dat.male$mhd.social_anxiety == 0),
                   sum_ifelse(dat.male$socp.diagnosis_numeric == 1, dat.male$mhd.social_anxiety == 1),
                   sum_ifelse(!is.na(dat.male$socp.diagnosis_numeric), !is.na(dat.male$mhd.social_anxiety)),
                   #Fill in Panic attacks row
                   sum(ifelse(dat.male$pad.diagnosis_numeric == 0 & dat.male$mhd.panic_attacks == 0 & !is.na(dat.male$mhd.panic_disorder), 1, 0), na.rm=T), 
                   sum(ifelse(dat.male$pad.diagnosis_numeric == 0 & dat.male$mhd.panic_attacks == 1 & !is.na(dat.male$mhd.panic_disorder), 1, 0), na.rm=T),
                   sum(ifelse(dat.male$pad.diagnosis_numeric == 1 & dat.male$mhd.panic_attacks == 0 & !is.na(dat.male$mhd.panic_disorder), 1, 0), na.rm=T),
                   sum(ifelse(dat.male$pad.diagnosis_numeric == 1 & dat.male$mhd.panic_attacks == 1 & !is.na(dat.male$mhd.panic_disorder), 1, 0), na.rm=T), 
                   sum(ifelse(!is.na(dat.male$pad.diagnosis_numeric) & !is.na(dat.male$mhd.panic_attacks) & !is.na(dat.male$mhd.panic_disorder), 1, 0), na.rm=T),
                   #Fill in Panic disorder row
                   sum_ifelse(dat.male$pad.diagnosis_numeric == 0, dat.male$mhd.panic_disorder == 0), 
                   sum_ifelse(dat.male$pad.diagnosis_numeric == 0, dat.male$mhd.panic_disorder == 1),
                   sum_ifelse(dat.male$pad.diagnosis_numeric == 1, dat.male$mhd.panic_disorder == 0),
                   sum_ifelse(dat.male$pad.diagnosis_numeric == 1, dat.male$mhd.panic_disorder == 1), 
                   sum_ifelse(!is.na(dat.male$pad.diagnosis_numeric), !is.na(dat.male$mhd.panic_disorder)),
                   #Fill in Agoraphobia row
                   sum_ifelse(dat.male$agp.diagnosis_numeric == 0, dat.male$mhd.agoraphobia == 0),
                   sum_ifelse(dat.male$agp.diagnosis_numeric == 0, dat.male$mhd.agoraphobia == 1),
                   sum_ifelse(dat.male$agp.diagnosis_numeric == 1, dat.male$mhd.agoraphobia == 0),
                   sum_ifelse(dat.male$agp.diagnosis_numeric == 1, dat.male$mhd.agoraphobia == 1),
                   sum_ifelse(!is.na(dat.male$agp.diagnosis_numeric), !is.na(dat.male$mhd.agoraphobia))
                   ),
                   nrow = 8,
                   ncol = 5,
                   byrow = T)

##Convert it to a dataframe 
table1 <- data.frame(table1.m)

##Add column names (clinician diagnoses)
colnames(table1) <- c("Agreement: No diagnosis (AB NO, SI NO)",
                      "Disagreement: screened negative, diagnosis (AB no, SI yes)",
                      "Disagreement: screened positive, no diagnosis (AB Yes, SI No)",
                      "Agreement: diagnosis (AB Yes, SI Yes)",
                      "Total (N)")

##Add row names (lifetime diagnoses) - eventually add script to add N per diagnosis to row names
rownames(table1) <- c("Major depressive disorder", 
                      "Any anxiety",
                      "Generalised anxiety disorder", 
                      "Specific phobia", 
                      "Social anxiety disorder",
                      "Panic attacks",
                      "Panic disorder",
                      "Agoraphobia")

##Visualise
table1
```

## Female-only dataset

```{r dataset by sex}

dat.female <- dat.cc %>% 
  filter(sex == 1)

```


## Female-only table of AB/SI agreements/disagreements for each disorder

```{r create female-only dataframe with agree/disagree results}

## COLUMN ORDER: ##
#Agreement: No diagnosis (AB NO, SI NO)",
#Disagreement: AB no, SI yes",
#Disagreement: AB Yes, SI No",
#Agreement: diagnosis (AB Yes, SI Yes)"

##Create a blank matrix
table2.m <- matrix(c(
                   #Fill in MDD row
                   sum_ifelse(dat.female$cidid.diagnosis_numeric == 0, dat.female$mhd.mdd == 0),  
                   sum_ifelse(dat.female$cidid.diagnosis_numeric == 0, dat.female$mhd.mdd == 1),
                   sum_ifelse(dat.female$cidid.diagnosis_numeric == 1, dat.female$mhd.mdd == 0),
                   sum_ifelse(dat.female$cidid.diagnosis_numeric == 1, dat.female$mhd.mdd == 1),
                   sum_ifelse(!is.na(dat.female$cidid.diagnosis_numeric), !is.na(dat.female$mhd.mdd)),
                   #Fill in any anxiety row
                   sum_ifelse(dat.female$LifetimeAnyAnx.n == 0, dat.female$ClinicianAnyAnx.n == 0),  
                   sum_ifelse(dat.female$LifetimeAnyAnx.n == 0, dat.female$ClinicianAnyAnx.n == 1),
                   sum_ifelse(dat.female$LifetimeAnyAnx.n == 1, dat.female$ClinicianAnyAnx.n == 0),
                   sum_ifelse(dat.female$LifetimeAnyAnx.n == 1, dat.female$ClinicianAnyAnx.n == 1),
                   sum_ifelse(!is.na(dat.female$LifetimeAnyAnx), !is.na(dat.female$ClinicianAnyAnx)),
                   #Fill in GAD row
                   sum_ifelse(dat.female$cidia.diagnosis_numeric == 0, dat.female$mhd.gad == 0),               
                   sum_ifelse(dat.female$cidia.diagnosis_numeric == 0, dat.female$mhd.gad == 1),       
                   sum_ifelse(dat.female$cidia.diagnosis_numeric == 1, dat.female$mhd.gad == 0),
                   sum_ifelse(dat.female$cidia.diagnosis_numeric == 1, dat.female$mhd.gad == 1),
                   sum_ifelse(!is.na(dat.female$cidia.diagnosis_numeric), !is.na(dat.female$mhd.gad)),
                   #Fill in SpecPhob row
                   sum_ifelse(dat.female$spec.diagnosis_numeric == 0, dat.female$mhd.specific_phobia == 0), 
                   sum_ifelse(dat.female$spec.diagnosis_numeric == 0, dat.female$mhd.specific_phobia == 1), 
                   sum_ifelse(dat.female$spec.diagnosis_numeric == 1, dat.female$mhd.specific_phobia == 0),
                   sum_ifelse(dat.female$spec.diagnosis_numeric == 1, dat.female$mhd.specific_phobia == 1), 
                   sum_ifelse(!is.na(dat.female$spec.diagnosis_numeric), !is.na(dat.female$mhd.specific_phobia)),
                   #Fill in SocialPhob row 
                   sum_ifelse(dat.female$socp.diagnosis_numeric == 0, dat.female$mhd.social_anxiety == 0), 
                   sum_ifelse(dat.female$socp.diagnosis_numeric == 0, dat.female$mhd.social_anxiety == 1), 
                   sum_ifelse(dat.female$socp.diagnosis_numeric == 1, dat.female$mhd.social_anxiety == 0),
                   sum_ifelse(dat.female$socp.diagnosis_numeric == 1, dat.female$mhd.social_anxiety == 1),
                   sum_ifelse(!is.na(dat.female$socp.diagnosis_numeric), !is.na(dat.female$mhd.social_anxiety)),
                   #Fill in Panic attacks row
                   sum(ifelse(dat.female$pad.diagnosis_numeric == 0 & dat.female$mhd.panic_attacks == 0 & !is.na(dat.female$mhd.panic_disorder), 1, 0), na.rm=T), 
                   sum(ifelse(dat.female$pad.diagnosis_numeric == 0 & dat.female$mhd.panic_attacks == 1 & !is.na(dat.female$mhd.panic_disorder), 1, 0), na.rm=T),
                   sum(ifelse(dat.female$pad.diagnosis_numeric == 1 & dat.female$mhd.panic_attacks == 0 & !is.na(dat.female$mhd.panic_disorder), 1, 0), na.rm=T),
                   sum(ifelse(dat.female$pad.diagnosis_numeric == 1 & dat.female$mhd.panic_attacks == 1 & !is.na(dat.female$mhd.panic_disorder), 1, 0), na.rm=T), 
                   sum(ifelse(!is.na(dat.female$pad.diagnosis_numeric) & !is.na(dat.female$mhd.panic_attacks) & !is.na(dat.female$mhd.panic_disorder), 1, 0), na.rm=T),
                   #Fill in Panic disorder row
                   sum_ifelse(dat.female$pad.diagnosis_numeric == 0, dat.female$mhd.panic_disorder == 0), 
                   sum_ifelse(dat.female$pad.diagnosis_numeric == 0, dat.female$mhd.panic_disorder == 1),
                   sum_ifelse(dat.female$pad.diagnosis_numeric == 1, dat.female$mhd.panic_disorder == 0),
                   sum_ifelse(dat.female$pad.diagnosis_numeric == 1, dat.female$mhd.panic_disorder == 1), 
                   sum_ifelse(!is.na(dat.female$pad.diagnosis_numeric), !is.na(dat.female$mhd.panic_disorder)),
                   #Fill in Agoraphobia row
                   sum_ifelse(dat.female$agp.diagnosis_numeric == 0, dat.female$mhd.agoraphobia == 0),
                   sum_ifelse(dat.female$agp.diagnosis_numeric == 0, dat.female$mhd.agoraphobia == 1),
                   sum_ifelse(dat.female$agp.diagnosis_numeric == 1, dat.female$mhd.agoraphobia == 0),
                   sum_ifelse(dat.female$agp.diagnosis_numeric == 1, dat.female$mhd.agoraphobia == 1),
                   sum_ifelse(!is.na(dat.female$agp.diagnosis_numeric), !is.na(dat.female$mhd.agoraphobia))
                   ),
                   nrow = 8,
                   ncol = 5,
                   byrow = T)

##Convert it to a dataframe 
table2 <- data.frame(table2.m)

##Add column names (clinician diagnoses)
colnames(table2) <- c("Agreement: No diagnosis (AB NO, SI NO)",
                      "Disagreement: screened negative, diagnosis (AB no, SI yes)",
                      "Disagreement: screened positive, no diagnosis (AB Yes, SI No)",
                      "Agreement: diagnosis (AB Yes, SI Yes)",
                      "Total (N)")

##Add row names (lifetime diagnoses) - eventually add script to add N per diagnosis to row names
rownames(table2) <- c("Major depressive disorder", 
                      "Any anxiety",
                      "Generalised anxiety disorder", 
                      "Specific phobia", 
                      "Social anxiety disorder",
                      "Panic attacks",
                      "Panic disorder",
                      "Agoraphobia")

##Visualise
table2
```