---
title: "DIAGCOMP_MHD_cleaning: Data freeze 1.0 (GLAD and COPING NBR data)"
author: "Molly R. Davies"
date: "16/04/2021"
output: html_document
---

This is the script to clean the mental health diagnoses (MHD) variables of the GLAD Study and COPING NIHR BioResource (NBR) data for the paper "Comparison of algorithm-based versus single-item phenotyping measures of depression and anxiety disorders in the GLAD Study cohort" - Davies et al (in prep).

The MHD dataset includes all single-item diagnoses.

Script written by M. R. Davies.
Email:  molly.davies@kcl.ac.uk

All scripts for the paper can be accessed at:
https://github.com/mollyrdavies/GLAD-Diagnostic-algorithms.git

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Set up

Clear workspace
```{r clear workspace}
#rm(list = ls())
```

Select which cohorts to run the cleaning script on by changing the value to TRUE (include) or FALSE (exclude). If multiple cohorts selected, data will be combined into a single dataset.

*Note: Currently only GLAD and COPING_NBR cohorts included.
```{r select cohorts}
GLAD = TRUE
COPING_NBR = TRUE
```

```{r load packages}
library(tidyverse)
library(psych)
library(summarytools)
```

```{r source path for reading/saving data}
#Source raw data directory (raw_path) & clean data export directory (cleaned_path)
source("../../DF1.0_data_path.R")
```


# MHD pre-processing

```{r read in MHD data}
if (GLAD == TRUE) {
#Read GLAD data
glad_mhd_file <- paste(glad_raw_path, "mhd_glad.rds", sep = "")
glad_mhd <- read_rds(glad_mhd_file)
}

if (COPING_NBR == TRUE) {
#Read COPING NBR data
coping_nbr_mhd_file <- paste(coping_nbr_raw_path, "mhd_coping_nbr.rds", sep = "")
coping_nbr_mhd <- read_rds(coping_nbr_mhd_file)
}
```

Add information on cohort/sample.
```{r MHD add sample column}
if (GLAD == TRUE) {
glad_mhd$sample <- "GLAD"
}

if (COPING_NBR == TRUE) {
coping_nbr_mhd$sample <- "NBR"
}
```

##GLAD
```{r clean GLAD MHD variables}
if (GLAD == TRUE) {
glad_mhd_renamed <- glad_mhd %>% 
  drop_na(externalDataReference) %>% 
  distinct(externalDataReference, .keep_all = TRUE) %>% 
  rename("ID" = "externalDataReference") %>%
  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
  mutate_if(is.numeric, ~na_if(., -99)) %>%
  mutate_if(is.numeric, ~na_if(., -77)) %>%
  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))
}
```

##COPING/NBR
```{r clean COPING MHD variables}
if (COPING_NBR == TRUE) {
coping_nbr_mhd_renamed <- coping_nbr_mhd %>%
  drop_na(subjectid) %>% 
  distinct(subjectid, .keep_all = TRUE) %>% 
  rename("ID" = "subjectid",
         #"COPING_ID" = "LoginID", #not exported
         "mhd.mdd" = "mhd.depression",
         "mhd.gad" = "mhd.anxiety_nerves_or_generalised_anxiety_disorder",
         "mhd.bipolar" = "mhd.mania_hypomania_bipolar_or_manicdepression",
         "mhd.social_anxiety" = "mhd.social_anxiety_or_social_phobia"
         ) %>% 
  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
  mutate_if(is.numeric, ~na_if(., -99)) %>%
  mutate_if(is.numeric, ~na_if(., -77)) %>%
  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))
}
```

```{r rename GLAD MHD dataset (if GLAD only)}
if (GLAD == TRUE & COPING_NBR == FALSE) {
  MHD_renamed.combined <- glad_mhd_renamed
}
```

```{r rename COPING NBR MHD dataset (if COPING NBR only)}
if (GLAD == FALSE & COPING_NBR == TRUE) {
  MHD_renamed.combined <- coping_nbr_mhd_renamed
}
```

```{r merge GLAD & COPING NBR MHD datasets}
if (GLAD == TRUE & COPING_NBR == TRUE) {
MHD_renamed.combined <- bind_rows(
  glad_mhd_renamed,
  coping_nbr_mhd_renamed
)
}
```

# Export clean dataset

```{r select MHD variables}
#Select variables
#MHD.clean <- MHD_renamed.combined %>%
#  select(ID,
#        mhd.mdd,
#        mhd.pmdd,
#        mhd.bipolar_disorder,
#        mhd.gad,
#        mhd.specific_phobia,
#        mhd.social_anxiety,
#        mhd.panic_attacks,
#        mhd.panic_disorder,
#        mhd.agoraphobia
#        )

#Export into a rds file:
saveRDS(object = MHD_renamed.combined, file = paste0(cleaned_path, "MHD_cleaned.rds"))

# Saves the R data including the recoding
#save.image(file = paste0(cleaned_path, "GLAD_MHD_clean.RData")
```