---
title: "DIAGCOMP_DEM_cleaning: Data freeze 1.0 (GLAD and COPING NBR data)"
author: "Molly R. Davies"
date: "16/04/2021"
output: html_document
---

This is the cleaning script for the demographic (DEM) variables of the GLAD Study and COPING NIHR BioResource (NBR) samples for the paper titled "Comparison of algorithm-based versus single-item phenotyping measures of depression and anxiety disorders in the GLAD Study cohort" - Davies et al (in prep).

Script written by M. R. Davies.
Email:  molly.davies@kcl.ac.uk

All scripts for the paper can be accessed at:
https://github.com/mollyrdavies/GLAD-Diagnostic-algorithms.git

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Set up
# Set up

Clear workspace
```{r clear workspace}
rm(list = ls())
```

Select which cohorts to run the cleaning script on by changing the value to TRUE (include) or FALSE (exclude). If multiple cohorts selected, data will be combined into a single dataset.

*Note: Currently only GLAD and COPING_NBR cohorts included.
```{r select cohorts}
GLAD = TRUE
COPING_NBR = TRUE
```

```{r load packages}
library(tidyverse)
library(psych)
library(summarytools)
```

```{r source path for reading/saving data}
#Source raw data directory (raw_path) & clean data export directory (cleaned_path)
source("../../DF1.0_data_path.R")
```

# DEM pre-processing

# DEM renaming

```{r read in DEM data}
if (GLAD == TRUE) {
#Read in GLAD data
glad_dem <- read_rds(paste(glad_raw_path, "dem_glad.rds", sep = ""))
}

if (COPING_NBR == TRUE) {
#Read in COPING data
coping_nbr_employ <- read_rds(paste(coping_nbr_raw_path, "employ_coping_nbr.rds", sep = ""))
coping_nbr_dem <- read_rds(paste(coping_nbr_raw_path, "demographics_coping_nbr.rds", sep = ""))
nbr_ethnicity_raw <- read_csv(nbr_ethnicity_file)
}
```

```{r DEM add sample column}
if (GLAD == TRUE) {
  glad_dem$sample <- "GLAD"
}

if (COPING_NBR == TRUE) {
coping_nbr_dem$sample <- "NBR"
coping_nbr_employ$sample <- "NBR"
nbr_ethnicity_raw$sample <- "NBR"
}

```

##GLAD
```{r select GLAD DEM variables}
if (GLAD == TRUE) {
glad_dem_renamed <- glad_dem %>% 
  drop_na(externalDataReference) %>% 
  distinct(externalDataReference, .keep_all = TRUE) %>% 
  rename("ID" = "externalDataReference",
         "age" = "dem.how_old_are_you_now.txt",
         "sex" = "dem.select_questionnaire_items_medical",
         "gender" = "dem.which_gender_do_you_identify_with",
         "dem.university_numeric" = "dem.college_or_university_degree",
         "dem.alevels_numeric" = "dem.a_levelsas_levels_or_equivalent",
         "dem.gcse_numeric" = "dem.o_levelsgcses_or_equivalent",
         "dem.cse_numeric" = "dem.cses_or_equivalent",
         "dem.NVQ_numeric" = "dem.nvq_or_hnd_or_hnc_or_equivalent",
         "dem.education_other_numeric" = "dem.other_professional_qualifications",
         "dem.ethnicity_numeric" = "dem.questions_based_ethnic_origin",
         "dem.employment_numeric" = "dem.what_is_your_current_employment_status"
         ) %>%
  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
  mutate_if(is.numeric, ~na_if(., -99)) %>%
  mutate_if(is.numeric, ~na_if(., -77))
}
```

```{r GLAD DEM ethnicity factor}
if (GLAD == TRUE) {
glad_dem_renamed$dem.ethnicity <- recode_factor(glad_dem_renamed$dem.ethnicity_numeric,
                                                "1"	= "White, white European or Caucasian",
                                                "2"	= "Mixed or multiple ethnic origins",
                                                "3"	= "Asian or Asian British (including Chinese)",
                                                "4"	= "Black or Black British",
                                                "5"	= "Arab",
                                                "6"	= "Other",
                                                "-77" = NULL,
                                                "-88" = NULL,
                                                "-99" = NULL)
}
```

##COPING/NBR
```{r rename COPING DEM variables}
if (COPING_NBR == TRUE) {
coping_nbr_dem_renamed <- coping_nbr_dem %>%
  drop_na(subjectid) %>% 
  distinct(subjectid, .keep_all = TRUE) %>% 
  rename("ID" = "subjectid",
         #"COPING_ID" = "LoginID", #not exported
         "sex" = "demographics.select_questionnaire_items_medical",
         "gender" = "demographics.which_gender_do_you_identify_with",
         "Birthday_numeric" = "demographics.day",
         "Birthmonth_numeric" = "demographics.month",
         "Birthyear_numeric" = "demographics.year"
         ) %>% 
  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
  mutate_if(is.numeric, ~na_if(., -99)) %>%
  mutate_if(is.numeric, ~na_if(., -77))
}
```

```{r rename COPING employ variables}
if (COPING_NBR == TRUE) {
coping_nbr_employ_renamed <- coping_nbr_employ %>%
  drop_na(subjectid) %>% 
  distinct(subjectid, .keep_all = TRUE) %>% 
  rename("ID" = "subjectid",
         "COPING_ID" = "externalDataReference",
         "dem.alevels_numeric" = "employ.a_levelsas_levels_or_equivalent",
         "dem.gcse_numeric" = "employ.o_levelsgcses_or_equivalent",
         "dem.cse_numeric" = "employ.cses_or_equivalent",
         "dem.NVQ_numeric" = "employ.nvq_or_hnd_or_hnc_or_equivalent",
         "dem.education_other_numeric" = "employ.other_professional_qualifications_e.g._nursing_teaching",
          "dem.employment_numeric" = "employ.fulltime_employed" 
         ) %>% 
  mutate(employ.college_or_university_degree =
           case_when(
             employ.phd == 1 |
               employ.masters_degree_or_equivalent == 1 | 
               employ.postgraduate_degree_or_equivalent == 1 |
               employ.bachelors_degree_or_equivalent == 1 ~ 1,
             employ.phd == 0 &
               employ.masters_degree_or_equivalent == 0 & 
               employ.postgraduate_degree_or_equivalent == 0 &
               employ.bachelors_degree_or_equivalent == 0 ~ 0
           )) %>%
  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
  mutate_if(is.numeric, ~na_if(., -99)) %>%
  mutate_if(is.numeric, ~na_if(., -77)) %>%
  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))
}
```

```{r nbr sample cleaning}
if (COPING_NBR == TRUE) {
nbr_ethnicity <- nbr_ethnicity_raw %>%
  drop_na(`NBR ID`) %>% # Drop NAs
  distinct(`NBR ID`, .keep_all = TRUE) %>% # Remove duplicates based on ID
  select(
         ID = "NBR ID", #ID
         sample, # Sample
         cohort = cohort, #Cohort
         dem.ethnicity.unc = ethnicity # Ethnicity
         ) %>%
  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
  mutate_if(is.numeric, ~na_if(., -99)) %>%
  mutate_if(is.numeric, ~na_if(., -77)) %>%
  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))

# Inspect dimensions
dim(nbr_ethnicity)
# Inspect colnames
colnames(nbr_ethnicity)
#Differences
dim(nbr_ethnicity_raw)[1]-dim(nbr_ethnicity)[1]
}
```

```{r nbr sample recode ethnicity}
if (COPING_NBR == TRUE) {
#Recode details ethnicity info
nbr_ethnicity$dem.nbr_ethnicity_full <- recode_factor(nbr_ethnicity$dem.ethnicity.unc,
                                             "A" = "White - British",
                                             "B" = "White - Irish",
                                             "C" = "White - Other",
                                             "D" = "Mixed - White & Black Caribbean",
                                             "E" = "Mixed - White & Black African",
                                             "F" = "Mixed - White & Asian",
                                             "G" = "Mixed - Other",
                                             "H" = "Asian - Indian",
                                             "J" = "Asian - Pakistani",
                                             "K" = "Asian - Bangladeshi",
                                             "L" = "Asian - Other",
                                             "M" = "Black - Caribbean",
                                             "N" = "Black - African",
                                             "P" = "Black - Other",
                                             "R" = "Chinese - Chinese",
                                             "S" = "Chinese - Other",
                                             "W" = "White - not disclosed", ## Asking NBR what this level means
                                             "Z" = NULL,
                                             "99" = NULL)

#Match GLAD/EDGI/RAMP categories
nbr_ethnicity$dem.ethnicity <- recode_factor(nbr_ethnicity$dem.ethnicity.unc,
                                             "A" = "White, white European or Caucasian",
                                             "B" = "White, white European or Caucasian",
                                             "C" = "White, white European or Caucasian",
                                             "D" = "Mixed or multiple ethnic origins",
                                             "E" = "Mixed or multiple ethnic origins",
                                             "F" = "Mixed or multiple ethnic origins",
                                             "G" = "Mixed or multiple ethnic origins",
                                             "H" = "Asian or Asian British (including Chinese)",
                                             "J" = "Asian or Asian British (including Chinese)",
                                             "K" = "Asian or Asian British (including Chinese)",
                                             "L" = "Asian or Asian British (including Chinese)",
                                             "M" = "Black or Black British",
                                             "N" = "Black or Black British",
                                             "P" = "Black or Black British",
                                             "R" = "Asian or Asian British (including Chinese)",
                                             "S" = "Asian or Asian British (including Chinese)",
                                             "W" = "White, white European or Caucasian", 
                                             "Z" = NULL,
                                             "99" = NULL)

#Create numeric version
nbr_ethnicity$dem.ethnicity_numeric <- as.numeric(nbr_ethnicity$dem.ethnicity)
}
```

```{r merge COPING NBR DEM datasets by ID}
if (COPING_NBR == TRUE) {
coping_nbr_dem_employ <- left_join(coping_nbr_dem_renamed,
                               coping_nbr_employ_renamed,
                           by = c("ID", "sample", "startDate", "endDate"))

coping_nbr_dem_all <- left_join(coping_nbr_dem_employ,
                               nbr_ethnicity,
                           by = c("ID", "sample"))

}
```

```{r rename GLAD DEM dataset (if GLAD only)}
if (GLAD == TRUE & COPING_NBR == FALSE) {
  DEM_renamed.combined <- glad_dem_renamed
}
```

```{r rename COPING NBR DEM dataset (if COPING NBR only)}
if (GLAD == FALSE & COPING_NBR == TRUE) {
  DEM_renamed.combined <- coping_nbr_dem_all
}
```

```{r merge DEM datasets}
if (GLAD == TRUE & COPING_NBR == TRUE) {
DEM_renamed.combined <- bind_rows(
  glad_dem_renamed,
  coping_nbr_dem_all
)
}
```


```{r select variables}
DEM <- DEM_renamed.combined %>% 
  select(ID,
         age,
         sex,
         dem.university_numeric,
         dem.alevels_numeric,
         dem.gcse_numeric,
         dem.cse_numeric,
         dem.NVQ_numeric,
         dem.education_other_numeric,
         dem.ethnicity_numeric,
         dem.employment_numeric
         ) 
```

```{r add unc to column names}
colnames(DEM) <- paste(colnames(DEM), "unc", sep = ".")
```

```{r visualise demographics data}
head(DEM)
```

# Age

## Average age (in text, Sample Descriptors section)

```{r checking outliers: density plot Age}
##Get summary to see range
summary(DEM$age.unc)

## Create a variable for the mean to add the mean line in the graph
age.clean <- DEM$age.unc
m <- mean(age.clean, na.rm = TRUE)

## Create version of dataset with only unique column names (to fix an error with ggplot)
DEM.plot <- DEM
colnames(DEM.plot) <- make.unique(names(DEM.plot))

## Create a density plot of Age, with a mean line

adens <- ggplot(data = DEM.plot, aes(x=age.unc, color="variable")) +
  geom_density() +
  scale_x_continuous(limits = c(0.00, 105)) +
  geom_vline(xintercept=mean(m),
             color="blue", size=1) +
  scale_color_manual(values = "#E69F00")

adens

## Alternatively, you can just tell R that the dataset contains NA so it can properly calculate the mean
## You can also add lines around the SD

adens.imp <- ggplot(DEM.plot, aes(x=age.unc, color="variable")) +
  geom_density() +
  scale_color_manual(values = "#E69F00") +
  scale_x_continuous(limits = c(0.00, 105)) +
  geom_vline(xintercept = mean(DEM.plot$age.unc, na.rm = T), 
             color = "blue") +  
  geom_vline(xintercept = mean(DEM.plot$age.unc, na.rm = T) + sd(DEM.plot$age.unc, na.rm = T),
             color = "blue",
             linetype = "dashed") +
  geom_vline(xintercept = mean(DEM.plot$age.unc, na.rm = T) - sd(DEM.plot$age.unc, na.rm = T),
             color = "blue",
             linetype = "dashed")

print(adens.imp)
```

```{r checking outliers: Scatterplot}

ggplot(data = subset(DEM.plot, !is.na(age.unc)),
       aes(x = seq_along(age.unc), y = age.unc)) +
       geom_point(color="grey") +
  labs(x = "Index",
       y = "Age",
       title = "Age (self-report, sex-combined, uncleaned)",
       subtitle = paste("Dashed line represents mean and dotted lines represent ± 1 standard deviation\n",
                        "n = ", sum(!is.na(DEM.plot$age.unc)),
                        "; NA = ", sum(is.na(DEM.plot$age.unc)),
                        "; n(total) = ", length(DEM.plot$age.unc), sep = ""),       
       color = "black") +
  theme(panel.grid.major.y = element_line(size = 0.5,
                                        linetype = 'dashed',
                                        colour = "gray"),
        axis.title.y = element_blank(),
        axis.text.x = element_text(colour="black", size = 12),
        axis.text.y = element_text(colour="black", size = 12),
        axis.ticks.x = element_blank(),
        axis.ticks.y = element_blank(),
        panel.background = element_blank()) +
  geom_hline(data = DEM.plot, aes(yintercept = mean(age.unc, na.rm = T)), size = 0.5, linetype = "dashed") +
  geom_hline(data = DEM.plot, aes(yintercept = mean(age.unc, na.rm = T) + sd(age.unc, na.rm = T)), size = 0.5, linetype = "dotted") +
  geom_hline(data = DEM.plot, aes(yintercept = mean(age.unc, na.rm = T) - sd(age.unc, na.rm = T)), size = 0.5, linetype = "dotted")

```

```{r set Age limits}

# Set upper limit for age (no lower limit, as all are >= 16)

age.m_upper = 100

# Check how many participants have outlier values in height

age.n_upper <- which(DEM$age.unc > age.m_upper)

length(age.n_upper)

```

```{r remove Age outliers}

if(length(age.n_upper)>0){
  
# Remove outliers

DEM$age <- with(data = DEM, ifelse(age.unc > age.m_upper, NA, age.unc))

# Overwrite dataset with clean data, make col names unique for plotting
DEM.plot <- DEM
colnames(DEM.plot) <- make.unique(names(DEM.plot))

# Point plot without outliers

ggplot(data = subset(DEM.plot, !is.na(age)),
       aes(x = seq_along(age), y = age)) +
       geom_point(color="grey") +
  labs(x = "Index",
       y = "Age",
       title = "Age (self-report, sex-combined, cleaned)",
       subtitle = paste("Dashed line represents mean and dotted lines represent ± 1 standard deviation\n",
                        "n = ", sum(!is.na(DEM.plot$age)),
                        "; NA = ", sum(is.na(DEM.plot$age)),
                        "; n(total) = ", length(DEM.plot$age),
                        "; n(outlier) removed = ", length(age.n_upper), sep = ""),
       color = "black") +
  theme(panel.grid.major.y = element_line(size = 0.5,
                                        linetype = 'dashed',
                                        colour = "gray"),
        axis.title.y = element_blank(),
        axis.text.x = element_text(colour="black", size = 12),
        axis.text.y = element_text(colour="black", size = 12),
        axis.ticks.x = element_blank(),
        axis.ticks.y = element_blank(),
        panel.background = element_blank()) +
  geom_hline(data = DEM.plot, aes(yintercept = mean(age, na.rm = T)),
             size = 1, linetype = "dashed", colour = "deepskyblue4") +
  geom_hline(data = DEM.plot, aes(yintercept = mean(age, na.rm = T) + sd(age, na.rm = T)),
             size = 1, linetype = "dotted", colour = "deepskyblue3") +
  geom_hline(data = DEM.plot, aes(yintercept = mean(age, na.rm = T) - sd(age, na.rm = T)),
             size = 1, linetype = "dotted", colour = "deepskyblue3") +
  geom_hline(data = DEM.plot, aes(yintercept = mean(age, na.rm = T) + 3.5*sd(age, na.rm = T)),
             size = 1, linetype = "dotted", colour = "firebrick") +
  geom_hline(data = DEM.plot, aes(yintercept = mean(age, na.rm = T) - 3.5*sd(age, na.rm = T)),
             size = 1, linetype = "dotted", colour = "firebrick")
}


```

```{r mean age}
#Get mean of cleaned age variable
mean(DEM$age, na.rm = T)

```

# Sex

Sex variable is pre-cleaned. Rename to remove .unc.
```{r rename sex}
DEM$sex <- DEM$sex.unc
freq(DEM$sex)
```

# Highest education

## Highest Education frequencies

First, define highest education:

Proceed along qualifications fields
If field is not blank, take that as highest qual
If field is blank, check next field
If all fields are blank, NA
Assumes Degree > A level > O level > CSE
NVQ and other professional are disregarded

```{r code education as characters}

#Recode as factors to add text, then change class to character
DEM$College <- as.character(recode_factor(DEM$dem.university_numeric.unc,
                              "1" = "College or university degree",
                              "0" = "No",
                              "-77" = NULL,
                              .missing = NULL))

DEM$A_levels <-as.character(recode_factor(DEM$dem.alevels_numeric.unc,
                              "1" = "A levels/AS levels or equivalent",
                              "0" = "No",
                              "-77" = NULL,
                              .missing = NULL))

DEM$GCSE_edu <- as.character(recode_factor(DEM$dem.gcse_numeric.unc,
                                  "1" = "O levels/GCSEs or equivalent",
                                  "0" = "No",
                                  "-77" = NULL,
                                  .missing = NULL))

DEM$CSE <- as.character(recode_factor(DEM$dem.cse_numeric.unc,
                          "1" = "CSEs or equivalent",
                          "0" = "No",
                          "-77" = NULL,
                          .missing = NULL))

```

```{r define highest education}
DEM$Highest.Education<-NA
DEM$Highest.Education<-ordered(case_when(DEM$College=="College or university degree" ~ DEM$College,
                                          DEM$A_levels=="A levels/AS levels or equivalent" ~ DEM$A_levels,
                                          DEM$GCSE_edu == "O levels/GCSEs or equivalent" ~ DEM$GCSE_edu,
                                          DEM$CSE== "CSEs or equivalent" ~ DEM$CSE,
                                          TRUE ~ as.character(NA)),
                                          c("College or university degree","A levels/AS levels or equivalent","O levels/GCSEs or equivalent", "CSEs or equivalent"))

DEM$Degree<-ifelse(!is.na(DEM$Highest.Education) & DEM$Highest.Education == "College or university degree", "Degree", "No degree")

DEM$GCSE<-ifelse((!is.na(DEM$Highest.Education) & DEM$Highest.Education == "CSEs or equivalent") | is.na(DEM$Highest.Education), "No GCSE equivalent", "At least GCSE equivalent")

head(DEM$Highest.Education)

```


```{r run checks for new variable}
table(DEM$Highest.Education, DEM$College, useNA = "a")
table(DEM$Highest.Education, DEM$A_levels, useNA = "a")
table(DEM$Highest.Education, DEM$GCSE_edu, useNA = "a")
table(DEM$Highest.Education, DEM$CSE, useNA = "a")
#NVD or HND or NHC or equivalent
table(DEM$Highest.Education, DEM$dem.NVQ_numeric.unc, useNA = "a")
#Other professional qualification
table(DEM$Highest.Education, DEM$dem.education_other_numeric.unc, useNA = "a")
```

```{r higher education freq}
#Get frequencies of higher education
freq(DEM$Highest.Education)
```

# Ethnicity

```{r recode ethnicity}
#Recode as factor
DEM$Ethnicity <- recode_factor(DEM$dem.ethnicity_numeric.unc,
                                "1" = "White",
                                "2" = "Mixed",
                                "3" = "Asian or Asian British",
                                "4" = "Black or Black British",
                                "5" = "Arab",
                                "6" = "Other")
#Get frequencies
freq(DEM$Ethnicity)

```

# Employment

```{r recode employment}

DEM <- DEM %>% 
  mutate(Employment = 
           case_when(
             dem.employment_numeric.unc == 1 ~ "In paid employment or self-employed",
             dem.employment_numeric.unc == 2 ~ "Retired",
             dem.employment_numeric.unc == 3 ~ "Looking after home and/or family",
             dem.employment_numeric.unc == 4 ~ "Unable to work because of sickness or disability",
             dem.employment_numeric.unc == 5 ~ "Unemployed",
             dem.employment_numeric.unc == 6 ~ "Doing unpaid or voluntary work",
             dem.employment_numeric.unc == 7 ~ "Full or part-time student",
             dem.employment_numeric.unc == 8 ~ "Other",
             dem.employment_numeric.unc == -99 | is.na(dem.employment_numeric.unc) ~ NA_character_
           ))
         
DEM$Employment <- factor(DEM$Employment, ordered = T,
                               levels = c("In paid employment or self-employed","Retired","Looking after home and/or family", "Unable to work because of sickness or disability", "Unemployed", "Doing unpaid or voluntary work", "Full or part-time student", "Other"))
freq(DEM$dem.employment_numeric.unc)
freq(DEM$Employment)
```

# Clean DEM dataset

```{r clean DEM dataframe}
#Select variables
DEM.clean <- DEM %>%
  select(ID = ID.unc,
        age,
        sex,
        Highest.Education,
        Ethnicity,
        Employment
        )

#Export into a rds file:
saveRDS(object = DEM.clean, file = paste0(cleaned_path, "DEM_cleaned.rds"))

# Saves the R data including the recoding
#save.image(file = paste0(cleaned_path, "GLAD_DEM_clean.RData")
```