---
title: "DIAGCOMP_sensitivity_specificity: Data freeze 1.0"
author: "Molly R. Davies"
date: 18/04/2021
output:  
  html_document:
    df_print: paged
    toc: yes
    toc_depth: 2
    toc_float:
      collapsed: false
    number_sections: false
    highlight: monochrome
    theme: cerulean
code_folding: show

html_notebook:
  theme: cerulean
toc: yes
---

This script runs sensitivity and specificity analyses for single-item and algorithm-based major depression and anxiety disorder diagnoses variables on the GLAD Study and COPING NIHR BioResource (NBR) data. 

Results are reported in the paper "Comparison of algorithm-based versus single-item phenotyping measures of depression and anxiety disorders in the GLAD Study cohort" - Davies et al (in prep).

Script written by M. R. Davies.
Email:  molly.davies@kcl.ac.uk

All scripts for the paper can be accessed at:
https://github.com/mollyrdavies/GLAD-Diagnostic-algorithms.git

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Set up
```{r install packages}

#install.packages("reshape2")
#install.packages("tidyverse")
#install.packages("knitr")
#install.packages("kableExtra")
#install.packages("descr")
#install.packages("caret")
#install.packages("irr")
#install.packages("hablar")
#install.packages("patchwork")
#install.packages("car")
#install.packages("ggpubr")
#install.packages("epiR")
#install.packages("infer")

```

```{r import packages}
library(caret)
library(irr)
library(ggpubr)
library(descr)
library(kableExtra)
library(epiR)
library(infer)
library(tidyverse)
```

```{r source file paths}
source("../../DF1.0_data_path.R")
```

```{r read data}
dat <- read_rds(paste0(cleaned_path, "DIAGCOMP_final_dataset.rds"))
```

# Variables
Create new dataset with only crosstab variables of interest
```{r select variables}
cidi <- dat %>%
  select("ID",
         "sample",
         "age",
         "sex",
         "Ethnicity",
         "highest_education",
         "Employment",
         "mhd.mdd",
         "mhd.gad",
         "mhd.specific_phobia",
         "mhd.social_anxiety",
         "mhd.panic_attacks",
         "mhd.panic_disorder",
         "mhd.agoraphobia",
         "ClinicianAnyAnx.n",
         "cidid.diagnosis_numeric",
         "cidia.diagnosis_numeric",
         "spec.diagnosis_numeric",
         "socp.diagnosis_numeric",
         "pad.diagnosis_numeric",
         "agp.diagnosis_numeric",
         "LifetimeAnyAnx.n"
         )
```

Ensure that all factor levels are the same for the variables, which is required to conduct the sensitivity/specificity analyses.
```{r create new factor version of variables}

cidi <- cidi %>% 
  mutate(ClinicianMDD.f =
           as.factor(case_when(
             mhd.mdd == 0 ~ "No diagnosis",
             mhd.mdd == 1 ~ "Diagnosis"
           )),
         ClinicianGAD.f =
           as.factor(case_when(
             mhd.gad == 0 ~ "No diagnosis",
             mhd.gad == 1 ~ "Diagnosis"
         )),
         ClinicianSpecPhob.f = 
           as.factor(case_when(
             mhd.specific_phobia == 0 ~ "No diagnosis",
             mhd.specific_phobia == 1 ~ "Diagnosis"
           )),
         ClinicianSocialPhob.f = 
           as.factor(case_when(
             mhd.social_anxiety == 0 ~ "No diagnosis",
             mhd.social_anxiety == 1 ~ "Diagnosis"
           )),
         ClinicianPanicDis.f = 
           as.factor(case_when(
             mhd.panic_disorder == 0 ~ "No diagnosis",
             mhd.panic_disorder == 1 ~ "Diagnosis"
           )),
         ClinicianPanicAttacks.f =
           as.factor(case_when(
             mhd.panic_attacks == 0 ~ "No diagnosis",
             mhd.panic_attacks == 1 ~ "Diagnosis"
           )),
         ClinicianAgoraphobia.f = 
           as.factor(case_when(
             mhd.agoraphobia == 0 ~ "No diagnosis",
             mhd.agoraphobia == 1 ~ "Diagnosis"
           )),
         ClinicianAnyAnx.f = 
           as.factor(case_when(
             ClinicianAnyAnx.n == 0 ~ "No diagnosis",
             ClinicianAnyAnx.n == 1 ~ "Diagnosis"
           )),
         LifetimeMDD.f =
           as.factor(case_when(
             cidid.diagnosis_numeric == 0 ~ "No diagnosis",
             cidid.diagnosis_numeric == 1 ~ "Diagnosis"
           )),
         LifetimeGAD.f =
           as.factor(case_when(
             cidia.diagnosis_numeric == 0 ~ "No diagnosis",
             cidia.diagnosis_numeric == 1 ~ "Diagnosis"
         )),
         LifetimeSpecPhob.f = 
           as.factor(case_when(
             spec.diagnosis_numeric == 0 ~ "No diagnosis",
             spec.diagnosis_numeric == 1 ~ "Diagnosis"
           )),
         LifetimeSocialPhob.f = 
           as.factor(case_when(
             socp.diagnosis_numeric == 0 ~ "No diagnosis",
             socp.diagnosis_numeric == 1 ~ "Diagnosis"
           )),
         LifetimePanicDis.f = 
           as.factor(case_when(
             pad.diagnosis_numeric == 0 ~ "No diagnosis",
             pad.diagnosis_numeric == 1 ~ "Diagnosis"
           )),
         LifetimeAgoraphobia.f = 
           as.factor(case_when(
             agp.diagnosis_numeric == 0 ~ "No diagnosis",
             agp.diagnosis_numeric == 1 ~ "Diagnosis"
           )),
         LifetimeAnyAnx.f = 
           as.factor(case_when(
             LifetimeAnyAnx.n == 0 ~ "No diagnosis",
             LifetimeAnyAnx.n == 1 ~ "Diagnosis"
           ))
         )
      
```


Since single-item panic disorder was added midway through data collection, we want to ensure all comparisons with panic attacks are made with the same participants
```{r recode SI panic attacks as NA when panic disorder NA}
#Create variable
cidi <- cidi %>% 
  mutate(ClinicianPanicAttacks.n.cc =
           case_when(is.na(ClinicianPanicDis.f) ~ NA_real_,
                     !is.na(ClinicianPanicDis.f) ~ mhd.panic_attacks)
         )
#Recode as factor
cidi <- cidi %>% 
  mutate(ClinicianPanicAttacks.f.cc = 
           as.factor(case_when(
             ClinicianPanicAttacks.n.cc == 0 ~ "No diagnosis",
             ClinicianPanicAttacks.n.cc == 1 ~ "Diagnosis")
             )
         )
```


# Cross Tabulations and Agreement
Run agreement (accuracy), sensitivity, specificity, Cohen's kappa, and McNemar's Test analyses

```{r set unused agreement statistics}
#These will be removed from the agreements table
unused_agreement <- c("AccuracyNull", "AccuracyPValue", "Balanced Accuracy",
                      "Detection Prevalence", "Detection Rate", "F1",
                      "Neg Pred Value", "Pos Pred Value", "Precision", "Prevalence", "Recall",
                      "Sensitivity", "Specificity")
```


## Full sample

### Algorithm-based diagnosis as reference point

Major depressive disorder
```{r Full sample MDD SI-AB crosstabs and agreement}
si_ab_mdd.cM <- confusionMatrix(cidi$ClinicianMDD.f,
                            cidi$LifetimeMDD.f,
                            positive = "Diagnosis",
                            dnn = c("Single-item", "Algorithm-based"))

#Create dataframe of agreements
si_ab_mdd.classes <- as.matrix(si_ab_mdd.cM, what = "classes")
si_ab_mdd.overall <- as.matrix(si_ab_mdd.cM, what = "overall")
si_ab_mdd.raw <- as.data.frame(rbind(si_ab_mdd.classes,
                                     si_ab_mdd.overall))
colnames(si_ab_mdd.raw) <- "MDD"

#Fromat dataframe
si_ab_mdd.incomplete <- si_ab_mdd.raw %>%  
  rownames_to_column() %>% 
  mutate(rowname = rownames(si_ab_mdd.raw)) %>% 
  gather(Diagnosis, value, -rowname) %>% 
  spread(rowname, value) %>% 
  select(-unused_agreement)

#Calculate sensitivity and specificity with 95% CI
si_ab_mdd.95ci <- summary(epiR::epi.tests(as.table(as.matrix(si_ab_mdd.cM)), conf.level = 0.95)) %>%
  round(., 2) %>% 
  rownames_to_column() %>% 
  filter(rowname == "se" | rowname == "sp") %>% 
  mutate(combined =
           sprintf("%.2f (%.2f, %.2f)", 
                   est,
                   lower,
                   upper),
         Diagnosis = "MDD") %>% 
  select(-c(est, lower, upper)) %>% 
  pivot_wider(names_from = rowname, values_from = combined) %>% 
  rename("Sensitivity" = "se",
         "Specificity" = "sp")

#Combine dataframe with sensitivity/specificity
si_ab_mdd.df <- merge(si_ab_mdd.incomplete,
                      si_ab_mdd.95ci)

#Create dataframe of crosstab
si_ab_mdd.xtabs <- as.data.frame(as.matrix(si_ab_mdd.cM))
si_ab_mdd.xtabs.df <- si_ab_mdd.xtabs %>% 
  rownames_to_column() %>% 
  rename("AB Yes" =
           "Diagnosis",
         "AB No" = "No diagnosis",
        "Crosstab"  = "rowname") %>% 
  mutate(Diagnosis = "MDD",
         Crosstab = recode_factor(Crosstab,
                                 "Diagnosis" = "SI Yes",
                                 "No diagnosis" = "SI No")
         ) 

si_ab_mdd.df
si_ab_mdd.xtabs.df
si_ab_mdd.95ci
```

Generalised anxiety disorder
```{r Full sample GAD SI-AB crosstabs and agreement}
si_ab_gad.cM <- confusionMatrix(cidi$ClinicianGAD.f,
                                cidi$LifetimeGAD.f,
                                positive = "Diagnosis",
                                dnn = c("Single-item", "Algorithm-based"))

#Create dataframe of agreements
si_ab_gad.classes<- as.matrix(si_ab_gad.cM, what = "classes")
si_ab_gad.overall <- as.matrix(si_ab_gad.cM, what = "overall")
si_ab_gad.raw <- as.data.frame(rbind(si_ab_gad.classes,
                                     si_ab_gad.overall))
colnames(si_ab_gad.raw) <- "GAD"

#Fromat dataframe
si_ab_gad.incomplete <- si_ab_gad.raw %>% 
  rownames_to_column() %>% 
  mutate(rowname = rownames(si_ab_gad.raw)) %>% 
  gather(Diagnosis, value, -rowname) %>% 
  spread(rowname, value) %>% 
  select(-unused_agreement)

#Calculate sensitivity and specificity with 95% CI
si_ab_gad.95ci <- summary(epiR::epi.tests(as.table(as.matrix(si_ab_gad.cM)), conf.level = 0.95)) %>%
  round(., 2) %>% 
  rownames_to_column() %>% 
  filter(rowname == "se" | rowname == "sp") %>% 
  mutate(combined =
           sprintf("%.2f (%.2f, %.2f)", 
                   est,
                   lower,
                   upper),
         Diagnosis = "GAD") %>% 
  select(-c(est, lower, upper)) %>% 
  pivot_wider(names_from = rowname, values_from = combined) %>% 
  rename("Sensitivity" = "se",
         "Specificity" = "sp")

#Combine dataframe with sensitivity/specificity
si_ab_gad.df <- merge(si_ab_gad.incomplete,
                      si_ab_gad.95ci)

#Create dataframe of crosstab
si_ab_gad.xtabs <- as.data.frame(as.matrix(si_ab_gad.cM))
si_ab_gad.xtabs.df <- si_ab_gad.xtabs %>% 
  rownames_to_column() %>% 
  rename("AB Yes" =
           "Diagnosis",
         "AB No" = "No diagnosis",
        "Crosstab"  = "rowname") %>% 
  mutate(Diagnosis = "GAD",
         Crosstab = recode_factor(Crosstab,
                                 "Diagnosis" = "SI Yes",
                                 "No diagnosis" = "SI No")
         )

si_ab_gad.df
si_ab_gad.xtabs.df
```

Specific phobia
```{r Full sample Specific phobia SI-AB crosstabs and agreement}
si_ab_spec.cM <- confusionMatrix(cidi$ClinicianSpecPhob.f,
                                 cidi$LifetimeSpecPhob.f,
                                 positive = "Diagnosis",
                                 dnn = c("Single-item", "Algorithm-based"))

#Create dataframe of agreements
si_ab_spec.classes<- as.matrix(si_ab_spec.cM, what = "classes")
si_ab_spec.overall <- as.matrix(si_ab_spec.cM, what = "overall")
si_ab_spec.raw <- as.data.frame(rbind(si_ab_spec.classes,
                                     si_ab_spec.overall))
colnames(si_ab_spec.raw) <- "SPEC"

#Fromat dataframe
si_ab_spec.incomplete <- si_ab_spec.raw %>% 
  rownames_to_column() %>% 
  mutate(rowname = rownames(si_ab_spec.raw)) %>% 
  gather(Diagnosis, value, -rowname) %>% 
  spread(rowname, value) %>% 
  select(-unused_agreement)

#Calculate sensitivity and specificity with 95% CI
si_ab_spec.95ci <- summary(epiR::epi.tests(as.table(as.matrix(si_ab_spec.cM)), conf.level = 0.95)) %>%
  round(., 2) %>% 
  rownames_to_column() %>% 
  filter(rowname == "se" | rowname == "sp") %>% 
  mutate(combined =
           sprintf("%.2f (%.2f, %.2f)", 
                   est,
                   lower,
                   upper),
         Diagnosis = "SPEC") %>% 
  select(-c(est, lower, upper)) %>% 
  pivot_wider(names_from = rowname, values_from = combined) %>% 
  rename("Sensitivity" = "se",
         "Specificity" = "sp")

#Combine dataframe with sensitivity/specificity
si_ab_spec.df <- merge(si_ab_spec.incomplete,
                      si_ab_spec.95ci)

#Create dataframe of crosstab
si_ab_spec.xtabs <- as.data.frame(as.matrix(si_ab_spec.cM))
si_ab_spec.xtabs.df <- si_ab_spec.xtabs %>% 
  rownames_to_column() %>% 
  rename("AB Yes" =
           "Diagnosis",
         "AB No" = "No diagnosis",
        "Crosstab"  = "rowname") %>% 
  mutate(Diagnosis = "SPEC",
         Crosstab = recode_factor(Crosstab,
                                 "Diagnosis" = "SI Yes",
                                 "No diagnosis" = "SI No")
         )

si_ab_spec.df
si_ab_spec.xtabs.df
```

Social anxiety disorder
```{r Full sample Social anxiety disorder SI-AB crosstabs and agreement}
si_ab_socp.cM <- confusionMatrix(cidi$ClinicianSocialPhob.f,
                                  cidi$LifetimeSocialPhob.f,
                                  positive = "Diagnosis",
                                  dnn = c("Single-item", "Algorithm-based"))

#Create dataframe of agreements
si_ab_socp.classes<- as.matrix(si_ab_socp.cM, what = "classes")
si_ab_socp.overall <- as.matrix(si_ab_socp.cM, what = "overall")
si_ab_socp.raw <- as.data.frame(rbind(si_ab_socp.classes,
                                     si_ab_socp.overall))
colnames(si_ab_socp.raw) <- "SOCP"

#Fromat dataframe
si_ab_socp.incomplete <- si_ab_socp.raw %>% 
  rownames_to_column() %>% 
  mutate(rowname = rownames(si_ab_socp.raw)) %>% 
  gather(Diagnosis, value, -rowname) %>% 
  spread(rowname, value) %>% 
  select(-unused_agreement)

#Calculate sensitivity and specificity with 95% CI
si_ab_socp.95ci <- summary(epiR::epi.tests(as.table(as.matrix(si_ab_socp.cM)), conf.level = 0.95)) %>%
  round(., 2) %>% 
  rownames_to_column() %>% 
  filter(rowname == "se" | rowname == "sp") %>% 
  mutate(combined =
           sprintf("%.2f (%.2f, %.2f)", 
                   est,
                   lower,
                   upper),
         Diagnosis = "SOCP") %>% 
  select(-c(est, lower, upper)) %>% 
  pivot_wider(names_from = rowname, values_from = combined) %>% 
  rename("Sensitivity" = "se",
         "Specificity" = "sp")

#Combine dataframe with sensitivity/specificity
si_ab_socp.df <- merge(si_ab_socp.incomplete,
                      si_ab_socp.95ci)

#Create dataframe of crosstab
si_ab_socp.xtabs <- as.data.frame(as.matrix(si_ab_socp.cM))
si_ab_socp.xtabs.df <- si_ab_socp.xtabs %>% 
  rownames_to_column() %>% 
  rename("AB Yes" =
           "Diagnosis",
         "AB No" = "No diagnosis",
        "Crosstab"  = "rowname") %>% 
  mutate(Diagnosis = "SOCP",
         Crosstab = recode_factor(Crosstab,
                                 "Diagnosis" = "SI Yes",
                                 "No diagnosis" = "SI No")
         )

si_ab_socp.df
si_ab_socp.xtabs.df
```

Panic disorder
```{r Full sample Panic disorder SI-AB crosstabs and agreement}
si_ab_pad.cM <- confusionMatrix(cidi$ClinicianPanicDis.f,
                                cidi$LifetimePanicDis.f,
                                positive = "Diagnosis",
                                dnn = c("Single-item", "Algorithm-based"))

#Create dataframe of agreements
si_ab_pad.classes<- as.matrix(si_ab_pad.cM, what = "classes")
si_ab_pad.overall <- as.matrix(si_ab_pad.cM, what = "overall")
si_ab_pad.raw <- as.data.frame(rbind(si_ab_pad.classes,
                                     si_ab_pad.overall))
colnames(si_ab_pad.raw) <- "PAD"

#Fromat dataframe
si_ab_pad.incomplete <- si_ab_pad.raw %>% 
  rownames_to_column() %>% 
  mutate(rowname = rownames(si_ab_pad.raw)) %>% 
  gather(Diagnosis, value, -rowname) %>% 
  spread(rowname, value) %>% 
  select(-unused_agreement)

#Calculate sensitivity and specificity with 95% CI
si_ab_pad.95ci <- summary(epiR::epi.tests(as.table(as.matrix(si_ab_pad.cM)), conf.level = 0.95)) %>%
  round(., 2) %>% 
  rownames_to_column() %>% 
  filter(rowname == "se" | rowname == "sp") %>% 
  mutate(combined =
           sprintf("%.2f (%.2f, %.2f)", 
                   est,
                   lower,
                   upper),
         Diagnosis = "PAD") %>% 
  select(-c(est, lower, upper)) %>% 
  pivot_wider(names_from = rowname, values_from = combined) %>% 
  rename("Sensitivity" = "se",
         "Specificity" = "sp")

#Combine dataframe with sensitivity/specificity
si_ab_pad.df <- merge(si_ab_pad.incomplete,
                      si_ab_pad.95ci)

#Create dataframe of crosstab
si_ab_pad.xtabs <- as.data.frame(as.matrix(si_ab_pad.cM))
si_ab_pad.xtabs.df <- si_ab_pad.xtabs %>% 
  rownames_to_column() %>% 
  rename("AB Yes" =
           "Diagnosis",
         "AB No" = "No diagnosis",
        "Crosstab"  = "rowname") %>% 
  mutate(Diagnosis = "PAD",
         Crosstab = recode_factor(Crosstab,
                                 "Diagnosis" = "SI Yes",
                                 "No diagnosis" = "SI No")
         )

si_ab_pad.df
si_ab_pad.xtabs.df
```

Panic attacks
The single-item panic attack variable here is being compared to lifetime panic disorder.
```{r Full sample Panic Attacks SI-AB crosstabs and agreement for Panic Disorder}
si_ab_pattacks.cM <- confusionMatrix(cidi$ClinicianPanicAttacks.f.cc,
                                cidi$LifetimePanicDis.f, 
                                positive = "Diagnosis",
                                dnn = c("Single-item", "Algorithm-based"))

#Create dataframe of agreements
si_ab_pattacks.classes<- as.matrix(si_ab_pattacks.cM, what = "classes")
si_ab_pattacks.overall <- as.matrix(si_ab_pattacks.cM, what = "overall")
si_ab_pattacks.raw <- as.data.frame(rbind(si_ab_pattacks.classes,
                                     si_ab_pattacks.overall))
colnames(si_ab_pattacks.raw) <- "PanicAttacks"

#Fromat dataframe
si_ab_pattacks.incomplete <- si_ab_pattacks.raw %>% 
  rownames_to_column() %>% 
  mutate(rowname = rownames(si_ab_pattacks.raw)) %>% 
  gather(Diagnosis, value, -rowname) %>% 
  spread(rowname, value) %>% 
  select(-unused_agreement)

#Calculate sensitivity and specificity with 95% CI
si_ab_pattacks.95ci <- summary(epiR::epi.tests(as.table(as.matrix(si_ab_pattacks.cM)), conf.level = 0.95)) %>%
  round(., 2) %>% 
  rownames_to_column() %>% 
  filter(rowname == "se" | rowname == "sp") %>% 
  mutate(combined =
           sprintf("%.2f (%.2f, %.2f)", 
                   est,
                   lower,
                   upper),
         Diagnosis = "PanicAttacks") %>% 
  select(-c(est, lower, upper)) %>% 
  pivot_wider(names_from = rowname, values_from = combined) %>% 
  rename("Sensitivity" = "se",
         "Specificity" = "sp")

#Combine dataframe with sensitivity/specificity
si_ab_pattacks.df <- merge(si_ab_pattacks.incomplete,
                      si_ab_pattacks.95ci)

#Create dataframe of crosstab
si_ab_pattacks.xtabs <- as.data.frame(as.matrix(si_ab_pattacks.cM))
si_ab_pattacks.xtabs.df <- si_ab_pattacks.xtabs %>% 
  rownames_to_column() %>% 
  rename("AB Yes" =
           "Diagnosis",
         "AB No" = "No diagnosis",
        "Crosstab"  = "rowname") %>% 
  mutate(Diagnosis = "PanicAttacks",
         Crosstab = recode_factor(Crosstab,
                                 "Diagnosis" = "SI Yes",
                                 "No diagnosis" = "SI No")
         )

si_ab_pattacks.df
si_ab_pattacks.xtabs.df
```

Agoraphobia
```{r Full sample Agoraphobia SI-AB crosstabs and agreement}
si_ab_agp.cM <- confusionMatrix(cidi$ClinicianAgoraphobia.f,
                                cidi$LifetimeAgoraphobia.f,
                                positive = "Diagnosis",
                                dnn = c("Single-item", "Algorithm-based"))

#Create dataframe of agreements
si_ab_agp.classes<- as.matrix(si_ab_agp.cM, what = "classes")
si_ab_agp.overall <- as.matrix(si_ab_agp.cM, what = "overall")
si_ab_agp.raw <- as.data.frame(rbind(si_ab_agp.classes,
                                     si_ab_agp.overall))
colnames(si_ab_agp.raw) <- "AGP"

#Fromat dataframe
si_ab_agp.incomplete <- si_ab_agp.raw %>% 
  rownames_to_column() %>% 
  mutate(rowname = rownames(si_ab_agp.raw)) %>% 
  gather(Diagnosis, value, -rowname) %>% 
  spread(rowname, value) %>% 
  select(-unused_agreement)

#Calculate sensitivity and specificity with 95% CI
si_ab_agp.95ci <- summary(epiR::epi.tests(as.table(as.matrix(si_ab_agp.cM)), conf.level = 0.95)) %>%
  round(., 2) %>% 
  rownames_to_column() %>% 
  filter(rowname == "se" | rowname == "sp") %>% 
  mutate(combined =
           sprintf("%.2f (%.2f, %.2f)", 
                   est,
                   lower,
                   upper),
         Diagnosis = "AGP") %>% 
  select(-c(est, lower, upper)) %>% 
  pivot_wider(names_from = rowname, values_from = combined) %>% 
  rename("Sensitivity" = "se",
         "Specificity" = "sp")

#Combine dataframe with sensitivity/specificity
si_ab_agp.df <- merge(si_ab_agp.incomplete,
                      si_ab_agp.95ci)

#Create dataframe of crosstab
si_ab_agp.xtabs <- as.data.frame(as.matrix(si_ab_agp.cM))
si_ab_agp.xtabs.df <- si_ab_agp.xtabs %>% 
  rownames_to_column() %>% 
  rename("AB Yes" =
           "Diagnosis",
         "AB No" = "No diagnosis",
        "Crosstab"  = "rowname") %>% 
  mutate(Diagnosis = "AGP",
         Crosstab = recode_factor(Crosstab,
                                 "Diagnosis" = "SI Yes",
                                 "No diagnosis" = "SI No")
         )

si_ab_agp.df
si_ab_agp.xtabs.df
```

Any anxiety
```{r Full sample Any Anxiety SI-AB crosstabs and agreement}
si_ab_anyanx.cM <- confusionMatrix(cidi$ClinicianAnyAnx.f, 
                                cidi$LifetimeAnyAnx.f,
                                positive = "Diagnosis",
                                dnn = c("Single-item", "Algorithm-based"))

#Create dataframe of agreements
si_ab_anyanx.classes<- as.matrix(si_ab_anyanx.cM, what = "classes")
si_ab_anyanx.overall <- as.matrix(si_ab_anyanx.cM, what = "overall")
si_ab_anyanx.raw <- as.data.frame(rbind(si_ab_anyanx.classes,
                                     si_ab_anyanx.overall))
colnames(si_ab_anyanx.raw) <- "AnyAnxiety"

#Fromat dataframe
si_ab_anyanx.incomplete <- si_ab_anyanx.raw %>% 
  rownames_to_column() %>% 
  mutate(rowname = rownames(si_ab_anyanx.raw)) %>% 
  gather(Diagnosis, value, -rowname) %>% 
  spread(rowname, value) %>% 
  select(-unused_agreement)

#Calculate sensitivity and specificity with 95% CI
si_ab_anyanx.95ci <- summary(epiR::epi.tests(as.table(as.matrix(si_ab_anyanx.cM)), conf.level = 0.95)) %>%
  round(., 2) %>% 
  rownames_to_column() %>% 
  filter(rowname == "se" | rowname == "sp") %>% 
  mutate(combined =
           sprintf("%.2f (%.2f, %.2f)", 
                   est,
                   lower,
                   upper),
         Diagnosis = "AnyAnxiety") %>% 
  select(-c(est, lower, upper)) %>% 
  pivot_wider(names_from = rowname, values_from = combined) %>% 
  rename("Sensitivity" = "se",
         "Specificity" = "sp")

#Combine dataframe with sensitivity/specificity
si_ab_anyanx.df <- merge(si_ab_anyanx.incomplete,
                      si_ab_anyanx.95ci)

#Create dataframe of crosstab
si_ab_anyanx.xtabs <- as.data.frame(as.matrix(si_ab_anyanx.cM))
si_ab_anyanx.xtabs.df <- si_ab_anyanx.xtabs %>% 
  rownames_to_column() %>% 
  rename("AB Yes" =
           "Diagnosis",
         "AB No" = "No diagnosis",
        "Crosstab"  = "rowname") %>% 
  mutate(Diagnosis = "AnyAnxiety",
         Crosstab = recode_factor(Crosstab,
                                 "Diagnosis" = "SI Yes",
                                 "No diagnosis" = "SI No")
         )

si_ab_anyanx.df
si_ab_anyanx.xtabs.df
```

```{r Full sample combine SI-AB agreement tables}
si_ab_all.raw <- bind_rows(si_ab_mdd.df,
                           si_ab_anyanx.df,
                           si_ab_gad.df,
                           si_ab_spec.df,
                           si_ab_socp.df,
                           si_ab_pad.df,
                           si_ab_pattacks.df,
                           si_ab_agp.df)

si_ab_all <- si_ab_all.raw %>% 
  rename("Sensitivity SI-AB" = "Sensitivity",
         "Specificity SI-AB" = "Specificity") %>% 
  relocate(Kappa, .after = last_col())

si_ab_all
```

```{r Full sample combine all xtabs tables}
all_xtabs.raw <- bind_rows(si_ab_mdd.xtabs.df,
                           si_ab_anyanx.xtabs.df,
                           si_ab_gad.xtabs.df,
                           si_ab_spec.xtabs.df,
                           si_ab_socp.xtabs.df,
                           si_ab_pad.xtabs.df,
                           si_ab_pattacks.xtabs.df,
                           si_ab_agp.xtabs.df)

all_xtabs <- all_xtabs.raw %>%  
  relocate(Diagnosis)

all_xtabs
```

### Single-item diagnosis as reference point

Major depressive disorder
```{r Full sample MDD AB-SI crosstabs and agreement}
ab_si_mdd.cM <- confusionMatrix(cidi$LifetimeMDD.f,
                                cidi$ClinicianMDD.f, 
                                positive = "Diagnosis",
                                dnn = c("Algorithm-based", "Single-item"))

#Create dataframe of agreements
ab_si_mdd.classes<- as.matrix(ab_si_mdd.cM, what = "classes")
ab_si_mdd.overall <- as.matrix(ab_si_mdd.cM, what = "overall")
ab_si_mdd.raw <- as.data.frame(rbind(ab_si_mdd.classes,
                                     ab_si_mdd.overall))
colnames(ab_si_mdd.raw) <- "MDD"

#Fromat dataframe
ab_si_mdd.incomplete <- ab_si_mdd.raw %>% 
  rownames_to_column() %>% 
  mutate(rowname = rownames(ab_si_mdd.raw)) %>% 
  gather(Diagnosis, value, -rowname) %>% 
  spread(rowname, value) %>% 
  select(-unused_agreement)

#Calculate sensitivity and specificity with 95% CI
ab_si_mdd.95ci <- summary(epiR::epi.tests(as.table(as.matrix(ab_si_mdd.cM)), conf.level = 0.95)) %>%
  round(., 2) %>% 
  rownames_to_column() %>% 
  filter(rowname == "se" | rowname == "sp") %>% 
  mutate(combined =
           sprintf("%.2f (%.2f, %.2f)", 
                   est,
                   lower,
                   upper),
         Diagnosis = "MDD") %>% 
  select(-c(est, lower, upper)) %>% 
  pivot_wider(names_from = rowname, values_from = combined) %>% 
  rename("Sensitivity" = "se",
         "Specificity" = "sp")

#Combine dataframe with sensitivity/specificity
ab_si_mdd.df <- merge(ab_si_mdd.incomplete,
                      ab_si_mdd.95ci)

ab_si_mdd.df
```

Generalised anxiety disorder
```{r Full sample GAD AB-SI crosstabs and agreement}
ab_si_gad.cM <- confusionMatrix(cidi$LifetimeGAD.f,
                                cidi$ClinicianGAD.f, 
                                positive = "Diagnosis",
                                dnn = c("Algorithm-based", "Single-item"))

#Create dataframe of agreements
ab_si_gad.classes<- as.matrix(ab_si_gad.cM, what = "classes")
ab_si_gad.overall <- as.matrix(ab_si_gad.cM, what = "overall")
ab_si_gad.raw <- as.data.frame(rbind(ab_si_gad.classes,
                                     ab_si_gad.overall))
colnames(ab_si_gad.raw) <- "GAD"

#Fromat dataframe
ab_si_gad.incomplete <- ab_si_gad.raw %>% 
  rownames_to_column() %>% 
  mutate(rowname = rownames(ab_si_gad.raw)) %>% 
  gather(Diagnosis, value, -rowname) %>% 
  spread(rowname, value) %>% 
  select(-unused_agreement)

#Calculate sensitivity and specificity with 95% CI
ab_si_gad.95ci <- summary(epiR::epi.tests(as.table(as.matrix(ab_si_gad.cM)), conf.level = 0.95)) %>%
  round(., 2) %>% 
  rownames_to_column() %>% 
  filter(rowname == "se" | rowname == "sp") %>% 
  mutate(combined =
           sprintf("%.2f (%.2f, %.2f)", 
                   est,
                   lower,
                   upper),
         Diagnosis = "GAD") %>% 
  select(-c(est, lower, upper)) %>% 
  pivot_wider(names_from = rowname, values_from = combined) %>% 
  rename("Sensitivity" = "se",
         "Specificity" = "sp")

#Combine dataframe with sensitivity/specificity
ab_si_gad.df <- merge(ab_si_gad.incomplete,
                      ab_si_gad.95ci)

ab_si_gad.df
```

Specific phobia
```{r Full sample Specific phobia AB-SI crosstabs and agreement}
ab_si_spec.cM <- confusionMatrix(cidi$LifetimeSpecPhob.f,
                                 cidi$ClinicianSpecPhob.f, 
                                 positive = "Diagnosis",
                                 dnn = c("Algorithm-based", "Single-item"))

#Create dataframe of agreements
ab_si_spec.classes<- as.matrix(ab_si_spec.cM, what = "classes")
ab_si_spec.overall <- as.matrix(ab_si_spec.cM, what = "overall")
ab_si_spec.raw <- as.data.frame(rbind(ab_si_spec.classes,
                                     ab_si_spec.overall))
colnames(ab_si_spec.raw) <- "SPEC"

#Fromat dataframe
ab_si_spec.incomplete <- ab_si_spec.raw %>% 
  rownames_to_column() %>% 
  mutate(rowname = rownames(ab_si_spec.raw)) %>% 
  gather(Diagnosis, value, -rowname) %>% 
  spread(rowname, value) %>% 
  select(-unused_agreement)

#Calculate sensitivity and specificity with 95% CI
ab_si_spec.95ci <- summary(epiR::epi.tests(as.table(as.matrix(ab_si_spec.cM)), conf.level = 0.95)) %>%
  round(., 2) %>% 
  rownames_to_column() %>% 
  filter(rowname == "se" | rowname == "sp") %>% 
  mutate(combined =
           sprintf("%.2f (%.2f, %.2f)", 
                   est,
                   lower,
                   upper),
         Diagnosis = "SPEC") %>% 
  select(-c(est, lower, upper)) %>% 
  pivot_wider(names_from = rowname, values_from = combined) %>% 
  rename("Sensitivity" = "se",
         "Specificity" = "sp")

#Combine dataframe with sensitivity/specificity
ab_si_spec.df <- merge(ab_si_spec.incomplete,
                      ab_si_spec.95ci)

ab_si_spec.df
```

Social anxiety disorder
```{r Full sample Social anxiety disorder AB-SI crosstabs and agreement}
ab_si_socp.cM <- confusionMatrix(cidi$LifetimeSocialPhob.f,
                                 cidi$ClinicianSocialPhob.f, 
                                 positive = "Diagnosis",
                                 dnn = c("Algorithm-based", "Single-item"))

#Create dataframe of agreements
ab_si_socp.classes<- as.matrix(ab_si_socp.cM, what = "classes")
ab_si_socp.overall <- as.matrix(ab_si_socp.cM, what = "overall")
ab_si_socp.raw <- as.data.frame(rbind(ab_si_socp.classes,
                                     ab_si_socp.overall))
colnames(ab_si_socp.raw) <- "SOCP"

#Fromat dataframe
ab_si_socp.incomplete <- ab_si_socp.raw %>% 
  rownames_to_column() %>% 
  mutate(rowname = rownames(ab_si_socp.raw)) %>% 
  gather(Diagnosis, value, -rowname) %>% 
  spread(rowname, value) %>% 
  select(-unused_agreement)

#Calculate sensitivity and specificity with 95% CI
ab_si_socp.95ci <- summary(epiR::epi.tests(as.table(as.matrix(ab_si_socp.cM)), conf.level = 0.95)) %>%
  round(., 2) %>% 
  rownames_to_column() %>% 
  filter(rowname == "se" | rowname == "sp") %>% 
  mutate(combined =
           sprintf("%.2f (%.2f, %.2f)", 
                   est,
                   lower,
                   upper),
         Diagnosis = "SOCP") %>% 
  select(-c(est, lower, upper)) %>% 
  pivot_wider(names_from = rowname, values_from = combined) %>% 
  rename("Sensitivity" = "se",
         "Specificity" = "sp")

#Combine dataframe with sensitivity/specificity
ab_si_socp.df <- merge(ab_si_socp.incomplete,
                      ab_si_socp.95ci)

ab_si_socp.df
```

Panic disorder
```{r Full sample Panic disorder AB-SI crosstabs and agreement}
ab_si_pad.cM <- confusionMatrix(cidi$LifetimePanicDis.f,
                                cidi$ClinicianPanicDis.f, 
                                positive = "Diagnosis",
                                dnn = c("Algorithm-based", "Single-item"))

#Create dataframe of agreements
ab_si_pad.classes<- as.matrix(ab_si_pad.cM, what = "classes")
ab_si_pad.overall <- as.matrix(ab_si_pad.cM, what = "overall")
ab_si_pad.raw <- as.data.frame(rbind(ab_si_pad.classes,
                                     ab_si_pad.overall))
colnames(ab_si_pad.raw) <- "PAD"

#Fromat dataframe
ab_si_pad.incomplete <- ab_si_pad.raw %>% 
  rownames_to_column() %>% 
  mutate(rowname = rownames(ab_si_pad.raw)) %>% 
  gather(Diagnosis, value, -rowname) %>% 
  spread(rowname, value) %>% 
  select(-unused_agreement)

#Calculate sensitivity and specificity with 95% CI
ab_si_pad.95ci <- summary(epiR::epi.tests(as.table(as.matrix(ab_si_pad.cM)), conf.level = 0.95)) %>%
  round(., 2) %>% 
  rownames_to_column() %>% 
  filter(rowname == "se" | rowname == "sp") %>% 
  mutate(combined =
           sprintf("%.2f (%.2f, %.2f)", 
                   est,
                   lower,
                   upper),
         Diagnosis = "PAD") %>% 
  select(-c(est, lower, upper)) %>% 
  pivot_wider(names_from = rowname, values_from = combined) %>% 
  rename("Sensitivity" = "se",
         "Specificity" = "sp")

#Combine dataframe with sensitivity/specificity
ab_si_pad.df <- merge(ab_si_pad.incomplete,
                      ab_si_pad.95ci)

ab_si_pad.df
```

Panic attacks
Algorithm-based panic disorder is being compared with single-item panic attacks.
```{r Full sample Panic Attacks AB-SI crosstabs and agreement with Panic Disorder, echo=FALSE}
ab_si_pattacks.cM <- confusionMatrix(cidi$LifetimePanicDis.f, 
                                     cidi$ClinicianPanicAttacks.f.cc, 
                                     positive = "Diagnosis",
                                     dnn = c("Algorithm-based", "Single-item"))

#Create dataframe of agreements
ab_si_pattacks.classes<- as.matrix(ab_si_pattacks.cM, what = "classes")
ab_si_pattacks.overall <- as.matrix(ab_si_pattacks.cM, what = "overall")
ab_si_pattacks.raw <- as.data.frame(rbind(ab_si_pattacks.classes,
                                     ab_si_pattacks.overall))
colnames(ab_si_pattacks.raw) <- "PanicAttacks"

#Fromat dataframe
ab_si_pattacks.incomplete <- ab_si_pattacks.raw %>% 
  rownames_to_column() %>% 
  mutate(rowname = rownames(ab_si_pattacks.raw)) %>% 
  gather(Diagnosis, value, -rowname) %>% 
  spread(rowname, value) %>% 
  select(-unused_agreement)

#Calculate sensitivity and specificity with 95% CI
ab_si_pattacks.95ci <- summary(epiR::epi.tests(as.table(as.matrix(ab_si_pattacks.cM)), conf.level = 0.95)) %>%
  round(., 2) %>% 
  rownames_to_column() %>% 
  filter(rowname == "se" | rowname == "sp") %>% 
  mutate(combined =
           sprintf("%.2f (%.2f, %.2f)", 
                   est,
                   lower,
                   upper),
         Diagnosis = "PanicAttacks") %>% 
  select(-c(est, lower, upper)) %>% 
  pivot_wider(names_from = rowname, values_from = combined) %>% 
  rename("Sensitivity" = "se",
         "Specificity" = "sp")

#Combine dataframe with sensitivity/specificity
ab_si_pattacks.df <- merge(ab_si_pattacks.incomplete,
                      ab_si_pattacks.95ci)

ab_si_pattacks.df
```

Agoraphobia
```{r Full sample Agoraphobia AB-SI crosstabs and agreement}
ab_si_agp.cM <- confusionMatrix(cidi$LifetimeAgoraphobia.f, 
                                cidi$ClinicianAgoraphobia.f, 
                                positive = "Diagnosis",
                                dnn = c("Algorithm-based", "Single-item"))

#Create dataframe of agreements
ab_si_agp.classes<- as.matrix(ab_si_agp.cM, what = "classes")
ab_si_agp.overall <- as.matrix(ab_si_agp.cM, what = "overall")
ab_si_agp.raw <- as.data.frame(rbind(ab_si_agp.classes,
                                     ab_si_agp.overall))
colnames(ab_si_agp.raw) <- "AGP"

#Fromat dataframe
ab_si_agp.incomplete <- ab_si_agp.raw %>% 
  rownames_to_column() %>% 
  mutate(rowname = rownames(ab_si_agp.raw)) %>% 
  gather(Diagnosis, value, -rowname) %>% 
  spread(rowname, value) %>% 
  select(-unused_agreement)

#Calculate sensitivity and specificity with 95% CI
ab_si_agp.95ci <- summary(epiR::epi.tests(as.table(as.matrix(ab_si_agp.cM)), conf.level = 0.95)) %>%
  round(., 2) %>% 
  rownames_to_column() %>% 
  filter(rowname == "se" | rowname == "sp") %>% 
  mutate(combined =
           sprintf("%.2f (%.2f, %.2f)", 
                   est,
                   lower,
                   upper),
         Diagnosis = "AGP") %>% 
  select(-c(est, lower, upper)) %>% 
  pivot_wider(names_from = rowname, values_from = combined) %>% 
  rename("Sensitivity" = "se",
         "Specificity" = "sp")

#Combine dataframe with sensitivity/specificity
ab_si_agp.df <- merge(ab_si_agp.incomplete,
                      ab_si_agp.95ci)

ab_si_agp.df
```

Any anxiety
```{r Full sample Any Anxiety AB-SI crosstabs and agreement}
ab_si_anyanx.cM <- confusionMatrix(cidi$LifetimeAnyAnx.f,
                                   cidi$ClinicianAnyAnx.f, 
                                   positive = "Diagnosis",
                                   dnn = c("Algorithm-based", "Single-item"))

#Create dataframe of agreements
ab_si_anyanx.classes<- as.matrix(ab_si_anyanx.cM, what = "classes")
ab_si_anyanx.overall <- as.matrix(ab_si_anyanx.cM, what = "overall")
ab_si_anyanx.raw <- as.data.frame(rbind(ab_si_anyanx.classes,
                                     ab_si_anyanx.overall))
colnames(ab_si_anyanx.raw) <- "AnyAnxiety"

#Fromat dataframe
ab_si_anyanx.incomplete <- ab_si_anyanx.raw %>% 
  rownames_to_column() %>% 
  mutate(rowname = rownames(ab_si_anyanx.raw)) %>% 
  gather(Diagnosis, value, -rowname) %>% 
  spread(rowname, value) %>% 
  select(-unused_agreement)

#Calculate sensitivity and specificity with 95% CI
ab_si_anyanx.95ci <- summary(epiR::epi.tests(as.table(as.matrix(ab_si_anyanx.cM)), conf.level = 0.95)) %>%
  round(., 2) %>% 
  rownames_to_column() %>% 
  filter(rowname == "se" | rowname == "sp") %>% 
  mutate(combined =
           sprintf("%.2f (%.2f, %.2f)", 
                   est,
                   lower,
                   upper),
         Diagnosis = "AnyAnxiety") %>% 
  select(-c(est, lower, upper)) %>% 
  pivot_wider(names_from = rowname, values_from = combined) %>% 
  rename("Sensitivity" = "se",
         "Specificity" = "sp")

#Combine dataframe with sensitivity/specificity
ab_si_anyanx.df <- merge(ab_si_anyanx.incomplete,
                      ab_si_anyanx.95ci)

ab_si_anyanx.df
```

```{r Full sample combine AB-SI agreement tables}
ab_si_all.raw <- bind_rows(ab_si_mdd.df,
                           ab_si_anyanx.df,
                           ab_si_gad.df,
                           ab_si_spec.df,
                           ab_si_socp.df,
                           ab_si_pad.df,
                           ab_si_pattacks.df,
                           ab_si_agp.df)

ab_si_all <- ab_si_all.raw %>% 
  select(Diagnosis,
         "Sensitivity AB-SI" = "Sensitivity",
         "Specificity AB-SI" = "Specificity") 

ab_si_all
```

### Agreement table for all statistics

```{r Full sample combine all agreement tables}
full_sample_all_agreement <- merge(si_ab_all,
                       ab_si_all) %>%
  relocate(Kappa, .after = last_col()) %>% 
  mutate(Diagnosis = 
           factor(Diagnosis,
                  levels = c("MDD", "AnyAnxiety", "GAD", "SPEC", "SOCP", "PanicAttacks", "PAD", "AGP"))
         ) %>% 
  arrange(., Diagnosis)

full_sample_all_agreement
```

```{r Full sample combine agreements and xtabs tables}
full_sample_all_agreement_xtabs <- merge(all_xtabs,
                                         full_sample_all_agreement) %>%
  mutate(Diagnosis = 
           factor(Diagnosis,
                  levels = c("MDD", "AnyAnxiety", "GAD", "SPEC", "SOCP", "PanicAttacks", "PAD", "AGP")),
         Sample = "Full sample"
         ) %>% 
  arrange(., Diagnosis) %>% 
  relocate(Sample)

full_sample_all_agreement_xtabs
```


## By sample

```{r create sample datasets}
cidi.glad <- cidi %>% 
  filter(sample == "GLAD")

cidi.nbr <- cidi %>% 
  filter(sample == "NBR")
```


### GLAD

#### Algorithm-based diagnosis as reference point

Major depressive disorder
```{r GLAD MDD SI-AB crosstabs and agreement}
glad_si_ab_mdd.cM <- confusionMatrix(cidi.glad$ClinicianMDD.f,
                            cidi.glad$LifetimeMDD.f,
                            positive = "Diagnosis",
                            dnn = c("Single-item", "Algorithm-based"))

#Create dataframe of agreements
glad_si_ab_mdd.classes <- as.matrix(glad_si_ab_mdd.cM, what = "classes")
glad_si_ab_mdd.overall <- as.matrix(glad_si_ab_mdd.cM, what = "overall")
glad_si_ab_mdd.raw <- as.data.frame(rbind(glad_si_ab_mdd.classes,
                                     glad_si_ab_mdd.overall))
colnames(glad_si_ab_mdd.raw) <- "MDD"

#Fromat dataframe
glad_si_ab_mdd.incomplete <- glad_si_ab_mdd.raw %>% 
  rownames_to_column() %>% 
  mutate(rowname = rownames(glad_si_ab_mdd.raw)) %>% 
  gather(Diagnosis, value, -rowname) %>% 
  spread(rowname, value) %>% 
  select(-unused_agreement)

#Calculate sensitivity and specificity with 95% CI
glad_si_ab_mdd.95ci <- summary(epiR::epi.tests(as.table(as.matrix(glad_si_ab_mdd.cM)), conf.level = 0.95)) %>%
  round(., 2) %>% 
  rownames_to_column() %>% 
  filter(rowname == "se" | rowname == "sp") %>% 
  mutate(combined =
           sprintf("%.2f (%.2f, %.2f)", 
                   est,
                   lower,
                   upper),
         Diagnosis = "MDD") %>% 
  select(-c(est, lower, upper)) %>% 
  pivot_wider(names_from = rowname, values_from = combined) %>% 
  rename("Sensitivity" = "se",
         "Specificity" = "sp")

#Combine dataframe with sensitivity/specificity
glad_si_ab_mdd.df <- merge(glad_si_ab_mdd.incomplete,
                      glad_si_ab_mdd.95ci)

#Create dataframe of crosstab
glad_si_ab_mdd.xtabs <- as.data.frame(as.matrix(glad_si_ab_mdd.cM))
glad_si_ab_mdd.xtabs.df <- glad_si_ab_mdd.xtabs %>% 
  rownames_to_column() %>% 
  rename("AB Yes" =
           "Diagnosis",
         "AB No" = "No diagnosis",
        "Crosstab"  = "rowname") %>% 
  mutate(Diagnosis = "MDD",
         Crosstab = recode_factor(Crosstab,
                                 "Diagnosis" = "SI Yes",
                                 "No diagnosis" = "SI No")
         )

glad_si_ab_mdd.df
glad_si_ab_mdd.xtabs.df
```

Generalised anxiety disorder
```{r GLAD GAD SI-AB crosstabs and agreement}
glad_si_ab_gad.cM <- confusionMatrix(cidi.glad$ClinicianGAD.f,
                                cidi.glad$LifetimeGAD.f,
                                positive = "Diagnosis",
                                dnn = c("Single-item", "Algorithm-based"))

#Create dataframe of agreements
glad_si_ab_gad.classes<- as.matrix(glad_si_ab_gad.cM, what = "classes")
glad_si_ab_gad.overall <- as.matrix(glad_si_ab_gad.cM, what = "overall")
glad_si_ab_gad.raw <- as.data.frame(rbind(glad_si_ab_gad.classes,
                                     glad_si_ab_gad.overall))
colnames(glad_si_ab_gad.raw) <- "GAD"

#Fromat dataframe
glad_si_ab_gad.incomplete <- glad_si_ab_gad.raw %>% 
  rownames_to_column() %>% 
  mutate(rowname = rownames(glad_si_ab_gad.raw)) %>% 
  gather(Diagnosis, value, -rowname) %>% 
  spread(rowname, value) %>% 
  select(-unused_agreement)

#Calculate sensitivity and specificity with 95% CI
glad_si_ab_gad.95ci <- summary(epiR::epi.tests(as.table(as.matrix(glad_si_ab_gad.cM)), conf.level = 0.95)) %>%
  round(., 2) %>% 
  rownames_to_column() %>% 
  filter(rowname == "se" | rowname == "sp") %>% 
  mutate(combined =
           sprintf("%.2f (%.2f, %.2f)", 
                   est,
                   lower,
                   upper),
         Diagnosis = "GAD") %>% 
  select(-c(est, lower, upper)) %>% 
  pivot_wider(names_from = rowname, values_from = combined) %>% 
  rename("Sensitivity" = "se",
         "Specificity" = "sp")

#Combine dataframe with sensitivity/specificity
glad_si_ab_gad.df <- merge(glad_si_ab_gad.incomplete,
                      glad_si_ab_gad.95ci)

#Create dataframe of crosstab
glad_si_ab_gad.xtabs <- as.data.frame(as.matrix(glad_si_ab_gad.cM))
glad_si_ab_gad.xtabs.df <- glad_si_ab_gad.xtabs %>% 
  rownames_to_column() %>% 
  rename("AB Yes" =
           "Diagnosis",
         "AB No" = "No diagnosis",
        "Crosstab"  = "rowname") %>% 
  mutate(Diagnosis = "GAD",
         Crosstab = recode_factor(Crosstab,
                                 "Diagnosis" = "SI Yes",
                                 "No diagnosis" = "SI No")
         )

glad_si_ab_gad.df
glad_si_ab_gad.xtabs.df
```

Specific phobia
```{r GLAD Specific phobia SI-AB crosstabs and agreement}
glad_si_ab_spec.cM <- confusionMatrix(cidi.glad$ClinicianSpecPhob.f,
                                 cidi.glad$LifetimeSpecPhob.f,
                                 positive = "Diagnosis",
                                 dnn = c("Single-item", "Algorithm-based"))

#Create dataframe of agreements
glad_si_ab_spec.classes<- as.matrix(glad_si_ab_spec.cM, what = "classes")
glad_si_ab_spec.overall <- as.matrix(glad_si_ab_spec.cM, what = "overall")
glad_si_ab_spec.raw <- as.data.frame(rbind(glad_si_ab_spec.classes,
                                     glad_si_ab_spec.overall))
colnames(glad_si_ab_spec.raw) <- "SPEC"

#Fromat dataframe
glad_si_ab_spec.incomplete <- glad_si_ab_spec.raw %>% 
  rownames_to_column() %>% 
  mutate(rowname = rownames(glad_si_ab_spec.raw)) %>% 
  gather(Diagnosis, value, -rowname) %>% 
  spread(rowname, value) %>% 
  select(-unused_agreement)

#Calculate sensitivity and specificity with 95% CI
glad_si_ab_spec.95ci <- summary(epiR::epi.tests(as.table(as.matrix(glad_si_ab_spec.cM)), conf.level = 0.95)) %>%
  round(., 2) %>% 
  rownames_to_column() %>% 
  filter(rowname == "se" | rowname == "sp") %>% 
  mutate(combined =
           sprintf("%.2f (%.2f, %.2f)", 
                   est,
                   lower,
                   upper),
         Diagnosis = "SPEC") %>% 
  select(-c(est, lower, upper)) %>% 
  pivot_wider(names_from = rowname, values_from = combined) %>% 
  rename("Sensitivity" = "se",
         "Specificity" = "sp")

#Combine dataframe with sensitivity/specificity
glad_si_ab_spec.df <- merge(glad_si_ab_spec.incomplete,
                      glad_si_ab_spec.95ci)

#Create dataframe of crosstab
glad_si_ab_spec.xtabs <- as.data.frame(as.matrix(glad_si_ab_spec.cM))
glad_si_ab_spec.xtabs.df <- glad_si_ab_spec.xtabs %>% 
  rownames_to_column() %>% 
  rename("AB Yes" =
           "Diagnosis",
         "AB No" = "No diagnosis",
        "Crosstab"  = "rowname") %>% 
  mutate(Diagnosis = "SPEC",
         Crosstab = recode_factor(Crosstab,
                                 "Diagnosis" = "SI Yes",
                                 "No diagnosis" = "SI No")
         )

glad_si_ab_spec.df
glad_si_ab_spec.xtabs.df
```

Social anxiety disorder
```{r GLAD Social anxiety disorder SI-AB crosstabs and agreement}
glad_si_ab_socp.cM <- confusionMatrix(cidi.glad$ClinicianSocialPhob.f,
                                  cidi.glad$LifetimeSocialPhob.f,
                                  positive = "Diagnosis",
                                  dnn = c("Single-item", "Algorithm-based"))

#Create dataframe of agreements
glad_si_ab_socp.classes<- as.matrix(glad_si_ab_socp.cM, what = "classes")
glad_si_ab_socp.overall <- as.matrix(glad_si_ab_socp.cM, what = "overall")
glad_si_ab_socp.raw <- as.data.frame(rbind(glad_si_ab_socp.classes,
                                     glad_si_ab_socp.overall))
colnames(glad_si_ab_socp.raw) <- "SOCP"

#Fromat dataframe
glad_si_ab_socp.incomplete <- glad_si_ab_socp.raw %>% 
  rownames_to_column() %>% 
  mutate(rowname = rownames(glad_si_ab_socp.raw)) %>% 
  gather(Diagnosis, value, -rowname) %>% 
  spread(rowname, value) %>% 
  select(-unused_agreement)

#Calculate sensitivity and specificity with 95% CI
glad_si_ab_socp.95ci <- summary(epiR::epi.tests(as.table(as.matrix(glad_si_ab_socp.cM)), conf.level = 0.95)) %>%
  round(., 2) %>% 
  rownames_to_column() %>% 
  filter(rowname == "se" | rowname == "sp") %>% 
  mutate(combined =
           sprintf("%.2f (%.2f, %.2f)", 
                   est,
                   lower,
                   upper),
         Diagnosis = "SOCP") %>% 
  select(-c(est, lower, upper)) %>% 
  pivot_wider(names_from = rowname, values_from = combined) %>% 
  rename("Sensitivity" = "se",
         "Specificity" = "sp")

#Combine dataframe with sensitivity/specificity
glad_si_ab_socp.df <- merge(glad_si_ab_socp.incomplete,
                      glad_si_ab_socp.95ci)

#Create dataframe of crosstab
glad_si_ab_socp.xtabs <- as.data.frame(as.matrix(glad_si_ab_socp.cM))
glad_si_ab_socp.xtabs.df <- glad_si_ab_socp.xtabs %>% 
  rownames_to_column() %>% 
  rename("AB Yes" =
           "Diagnosis",
         "AB No" = "No diagnosis",
        "Crosstab"  = "rowname") %>% 
  mutate(Diagnosis = "SOCP",
         Crosstab = recode_factor(Crosstab,
                                 "Diagnosis" = "SI Yes",
                                 "No diagnosis" = "SI No")
         )

glad_si_ab_socp.df
glad_si_ab_socp.xtabs.df
```

Panic disorder
```{r GLAD Panic disorder SI-AB crosstabs and agreement}
glad_si_ab_pad.cM <- confusionMatrix(cidi.glad$ClinicianPanicDis.f,
                                cidi.glad$LifetimePanicDis.f,
                                positive = "Diagnosis",
                                dnn = c("Single-item", "Algorithm-based"))

#Create dataframe of agreements
glad_si_ab_pad.classes<- as.matrix(glad_si_ab_pad.cM, what = "classes")
glad_si_ab_pad.overall <- as.matrix(glad_si_ab_pad.cM, what = "overall")
glad_si_ab_pad.raw <- as.data.frame(rbind(glad_si_ab_pad.classes,
                                     glad_si_ab_pad.overall))
colnames(glad_si_ab_pad.raw) <- "PAD"

#Fromat dataframe
glad_si_ab_pad.incomplete <- glad_si_ab_pad.raw %>% 
  rownames_to_column() %>% 
  mutate(rowname = rownames(glad_si_ab_pad.raw)) %>% 
  gather(Diagnosis, value, -rowname) %>% 
  spread(rowname, value) %>% 
  select(-unused_agreement)

#Calculate sensitivity and specificity with 95% CI
glad_si_ab_pad.95ci <- summary(epiR::epi.tests(as.table(as.matrix(glad_si_ab_pad.cM)), conf.level = 0.95)) %>%
  round(., 2) %>% 
  rownames_to_column() %>% 
  filter(rowname == "se" | rowname == "sp") %>% 
  mutate(combined =
           sprintf("%.2f (%.2f, %.2f)", 
                   est,
                   lower,
                   upper),
         Diagnosis = "PAD") %>% 
  select(-c(est, lower, upper)) %>% 
  pivot_wider(names_from = rowname, values_from = combined) %>% 
  rename("Sensitivity" = "se",
         "Specificity" = "sp")

#Combine dataframe with sensitivity/specificity
glad_si_ab_pad.df <- merge(glad_si_ab_pad.incomplete,
                      glad_si_ab_pad.95ci)

#Create dataframe of crosstab
glad_si_ab_pad.xtabs <- as.data.frame(as.matrix(glad_si_ab_pad.cM))
glad_si_ab_pad.xtabs.df <- glad_si_ab_pad.xtabs %>% 
  rownames_to_column() %>% 
  rename("AB Yes" =
           "Diagnosis",
         "AB No" = "No diagnosis",
        "Crosstab"  = "rowname") %>% 
  mutate(Diagnosis = "PAD",
         Crosstab = recode_factor(Crosstab,
                                 "Diagnosis" = "SI Yes",
                                 "No diagnosis" = "SI No")
         )

glad_si_ab_pad.df
glad_si_ab_pad.xtabs.df
```

Panic attacks
The single-item panic attack variable here is being compared to lifetime panic disorder.
```{r GLAD Panic Attacks SI-AB crosstabs and agreement for Panic Disorder}
glad_si_ab_pattacks.cM <- confusionMatrix(cidi.glad$ClinicianPanicAttacks.f.cc,
                                cidi.glad$LifetimePanicDis.f, 
                                positive = "Diagnosis",
                                dnn = c("Single-item", "Algorithm-based"))

#Create dataframe of agreements
glad_si_ab_pattacks.classes<- as.matrix(glad_si_ab_pattacks.cM, what = "classes")
glad_si_ab_pattacks.overall <- as.matrix(glad_si_ab_pattacks.cM, what = "overall")
glad_si_ab_pattacks.raw <- as.data.frame(rbind(glad_si_ab_pattacks.classes,
                                     glad_si_ab_pattacks.overall))
colnames(glad_si_ab_pattacks.raw) <- "PanicAttacks"

#Fromat dataframe
glad_si_ab_pattacks.incomplete <- glad_si_ab_pattacks.raw %>% 
  rownames_to_column() %>% 
  mutate(rowname = rownames(glad_si_ab_pattacks.raw)) %>% 
  gather(Diagnosis, value, -rowname) %>% 
  spread(rowname, value) %>% 
  select(-unused_agreement)

#Calculate sensitivity and specificity with 95% CI
glad_si_ab_pattacks.95ci <- summary(epiR::epi.tests(as.table(as.matrix(glad_si_ab_pattacks.cM)), conf.level = 0.95)) %>%
  round(., 2) %>% 
  rownames_to_column() %>% 
  filter(rowname == "se" | rowname == "sp") %>% 
  mutate(combined =
           sprintf("%.2f (%.2f, %.2f)", 
                   est,
                   lower,
                   upper),
         Diagnosis = "PanicAttacks") %>% 
  select(-c(est, lower, upper)) %>% 
  pivot_wider(names_from = rowname, values_from = combined) %>% 
  rename("Sensitivity" = "se",
         "Specificity" = "sp")

#Combine dataframe with sensitivity/specificity
glad_si_ab_pattacks.df <- merge(glad_si_ab_pattacks.incomplete,
                      glad_si_ab_pattacks.95ci)

#Create dataframe of crosstab
glad_si_ab_pattacks.xtabs <- as.data.frame(as.matrix(glad_si_ab_pattacks.cM))
glad_si_ab_pattacks.xtabs.df <- glad_si_ab_pattacks.xtabs %>% 
  rownames_to_column() %>% 
  rename("AB Yes" =
           "Diagnosis",
         "AB No" = "No diagnosis",
        "Crosstab"  = "rowname") %>% 
  mutate(Diagnosis = "PanicAttacks",
         Crosstab = recode_factor(Crosstab,
                                 "Diagnosis" = "SI Yes",
                                 "No diagnosis" = "SI No")
         )

glad_si_ab_pattacks.df
glad_si_ab_pattacks.xtabs.df
```

Agoraphobia
```{r GLAD Agoraphobia SI-AB crosstabs and agreement}
glad_si_ab_agp.cM <- confusionMatrix(cidi.glad$ClinicianAgoraphobia.f,
                                cidi.glad$LifetimeAgoraphobia.f,
                                positive = "Diagnosis",
                                dnn = c("Single-item", "Algorithm-based"))

#Create dataframe of agreements
glad_si_ab_agp.classes<- as.matrix(glad_si_ab_agp.cM, what = "classes")
glad_si_ab_agp.overall <- as.matrix(glad_si_ab_agp.cM, what = "overall")
glad_si_ab_agp.raw <- as.data.frame(rbind(glad_si_ab_agp.classes,
                                     glad_si_ab_agp.overall))
colnames(glad_si_ab_agp.raw) <- "AGP"

#Fromat dataframe
glad_si_ab_agp.incomplete <- glad_si_ab_agp.raw %>% 
  rownames_to_column() %>% 
  mutate(rowname = rownames(glad_si_ab_agp.raw)) %>% 
  gather(Diagnosis, value, -rowname) %>% 
  spread(rowname, value) %>% 
  select(-unused_agreement)

#Calculate sensitivity and specificity with 95% CI
glad_si_ab_agp.95ci <- summary(epiR::epi.tests(as.table(as.matrix(glad_si_ab_agp.cM)), conf.level = 0.95)) %>%
  round(., 2) %>% 
  rownames_to_column() %>% 
  filter(rowname == "se" | rowname == "sp") %>% 
  mutate(combined =
           sprintf("%.2f (%.2f, %.2f)", 
                   est,
                   lower,
                   upper),
         Diagnosis = "AGP") %>% 
  select(-c(est, lower, upper)) %>% 
  pivot_wider(names_from = rowname, values_from = combined) %>% 
  rename("Sensitivity" = "se",
         "Specificity" = "sp")

#Combine dataframe with sensitivity/specificity
glad_si_ab_agp.df <- merge(glad_si_ab_agp.incomplete,
                      glad_si_ab_agp.95ci)

#Create dataframe of crosstab
glad_si_ab_agp.xtabs <- as.data.frame(as.matrix(glad_si_ab_agp.cM))
glad_si_ab_agp.xtabs.df <- glad_si_ab_agp.xtabs %>% 
  rownames_to_column() %>% 
  rename("AB Yes" =
           "Diagnosis",
         "AB No" = "No diagnosis",
        "Crosstab"  = "rowname") %>% 
  mutate(Diagnosis = "AGP",
         Crosstab = recode_factor(Crosstab,
                                 "Diagnosis" = "SI Yes",
                                 "No diagnosis" = "SI No")
         )

glad_si_ab_agp.df
glad_si_ab_agp.xtabs.df
```

Any anxiety
```{r GLAD Any Anxiety SI-AB crosstabs and agreement}
glad_si_ab_anyanx.cM <- confusionMatrix(cidi.glad$ClinicianAnyAnx.f, 
                                cidi.glad$LifetimeAnyAnx.f,
                                positive = "Diagnosis",
                                dnn = c("Single-item", "Algorithm-based"))

#Create dataframe of agreements
glad_si_ab_anyanx.classes<- as.matrix(glad_si_ab_anyanx.cM, what = "classes")
glad_si_ab_anyanx.overall <- as.matrix(glad_si_ab_anyanx.cM, what = "overall")
glad_si_ab_anyanx.raw <- as.data.frame(rbind(glad_si_ab_anyanx.classes,
                                     glad_si_ab_anyanx.overall))
colnames(glad_si_ab_anyanx.raw) <- "AnyAnxiety"

#Fromat dataframe
glad_si_ab_anyanx.incomplete <- glad_si_ab_anyanx.raw %>% 
  rownames_to_column() %>% 
  mutate(rowname = rownames(glad_si_ab_anyanx.raw)) %>% 
  gather(Diagnosis, value, -rowname) %>% 
  spread(rowname, value) %>% 
  select(-unused_agreement)

#Calculate sensitivity and specificity with 95% CI
glad_si_ab_anyanx.95ci <- summary(epiR::epi.tests(as.table(as.matrix(glad_si_ab_anyanx.cM)), conf.level = 0.95)) %>%
  round(., 2) %>% 
  rownames_to_column() %>% 
  filter(rowname == "se" | rowname == "sp") %>% 
  mutate(combined =
           sprintf("%.2f (%.2f, %.2f)", 
                   est,
                   lower,
                   upper),
         Diagnosis = "AnyAnxiety") %>% 
  select(-c(est, lower, upper)) %>% 
  pivot_wider(names_from = rowname, values_from = combined) %>% 
  rename("Sensitivity" = "se",
         "Specificity" = "sp")

#Combine dataframe with sensitivity/specificity
glad_si_ab_anyanx.df <- merge(glad_si_ab_anyanx.incomplete,
                      glad_si_ab_anyanx.95ci)

#Create dataframe of crosstab
glad_si_ab_anyanx.xtabs <- as.data.frame(as.matrix(glad_si_ab_anyanx.cM))
glad_si_ab_anyanx.xtabs.df <- glad_si_ab_anyanx.xtabs %>% 
  rownames_to_column() %>% 
  rename("AB Yes" =
           "Diagnosis",
         "AB No" = "No diagnosis",
        "Crosstab"  = "rowname") %>% 
  mutate(Diagnosis = "AnyAnxiety",
         Crosstab = recode_factor(Crosstab,
                                 "Diagnosis" = "SI Yes",
                                 "No diagnosis" = "SI No")
         )

glad_si_ab_anyanx.df
glad_si_ab_anyanx.xtabs.df
```

```{r GLAD combine SI-AB agreement tables}
glad_si_ab_all.raw <- bind_rows(glad_si_ab_mdd.df,
                           glad_si_ab_anyanx.df,
                           glad_si_ab_gad.df,
                           glad_si_ab_spec.df,
                           glad_si_ab_socp.df,
                           glad_si_ab_pad.df,
                           glad_si_ab_pattacks.df,
                           glad_si_ab_agp.df)

glad_si_ab_all <- glad_si_ab_all.raw %>% 
  rename("Sensitivity SI-AB" = "Sensitivity",
         "Specificity SI-AB" = "Specificity") %>% 
  relocate(Kappa, .after = last_col())

glad_si_ab_all
```

```{r GLAD combine all xtabs tables}
glad_all_xtabs.raw <- bind_rows(glad_si_ab_mdd.xtabs.df,
                           glad_si_ab_anyanx.xtabs.df,
                           glad_si_ab_gad.xtabs.df,
                           glad_si_ab_spec.xtabs.df,
                           glad_si_ab_socp.xtabs.df,
                           glad_si_ab_pad.xtabs.df,
                           glad_si_ab_pattacks.xtabs.df,
                           glad_si_ab_agp.xtabs.df)

glad_all_xtabs <- glad_all_xtabs.raw %>%  
  relocate(Diagnosis)

glad_all_xtabs
```

####Single-item diagnosis as reference point

Major depressive disorder
```{r GLAD MDD AB-SI crosstabs and agreement}
glad_ab_si_mdd.cM <- confusionMatrix(cidi.glad$LifetimeMDD.f,
                                cidi.glad$ClinicianMDD.f, 
                                positive = "Diagnosis",
                                dnn = c("Algorithm-based", "Single-item"))

#Create dataframe of agreements
glad_ab_si_mdd.classes<- as.matrix(glad_ab_si_mdd.cM, what = "classes")
glad_ab_si_mdd.overall <- as.matrix(glad_ab_si_mdd.cM, what = "overall")
glad_ab_si_mdd.raw <- as.data.frame(rbind(glad_ab_si_mdd.classes,
                                     glad_ab_si_mdd.overall))
colnames(glad_ab_si_mdd.raw) <- "MDD"

#Fromat dataframe
glad_ab_si_mdd.incomplete <- glad_ab_si_mdd.raw %>% 
  rownames_to_column() %>% 
  mutate(rowname = rownames(glad_ab_si_mdd.raw)) %>% 
  gather(Diagnosis, value, -rowname) %>% 
  spread(rowname, value) %>% 
  select(-unused_agreement)

#Calculate sensitivity and specificity with 95% CI
glad_ab_si_mdd.95ci <- summary(epiR::epi.tests(as.table(as.matrix(glad_ab_si_mdd.cM)), conf.level = 0.95)) %>%
  round(., 2) %>% 
  rownames_to_column() %>% 
  filter(rowname == "se" | rowname == "sp") %>% 
  mutate(combined =
           sprintf("%.2f (%.2f, %.2f)", 
                   est,
                   lower,
                   upper),
         Diagnosis = "MDD") %>% 
  select(-c(est, lower, upper)) %>% 
  pivot_wider(names_from = rowname, values_from = combined) %>% 
  rename("Sensitivity" = "se",
         "Specificity" = "sp")

#Combine dataframe with sensitivity/specificity
glad_ab_si_mdd.df <- merge(glad_ab_si_mdd.incomplete,
                      glad_ab_si_mdd.95ci)

glad_ab_si_mdd.df
```

Generalised anxiety disorder
```{r GLAD GAD AB-SI crosstabs and agreement}
glad_ab_si_gad.cM <- confusionMatrix(cidi.glad$LifetimeGAD.f,
                                cidi.glad$ClinicianGAD.f, 
                                positive = "Diagnosis",
                                dnn = c("Algorithm-based", "Single-item"))

#Create dataframe of agreements
glad_ab_si_gad.classes<- as.matrix(glad_ab_si_gad.cM, what = "classes")
glad_ab_si_gad.overall <- as.matrix(glad_ab_si_gad.cM, what = "overall")
glad_ab_si_gad.raw <- as.data.frame(rbind(glad_ab_si_gad.classes,
                                     glad_ab_si_gad.overall))
colnames(glad_ab_si_gad.raw) <- "GAD"

#Fromat dataframe
glad_ab_si_gad.incomplete <- glad_ab_si_gad.raw %>% 
  rownames_to_column() %>% 
  mutate(rowname = rownames(glad_ab_si_gad.raw)) %>% 
  gather(Diagnosis, value, -rowname) %>% 
  spread(rowname, value) %>% 
  select(-unused_agreement)

#Calculate sensitivity and specificity with 95% CI
glad_ab_si_gad.95ci <- summary(epiR::epi.tests(as.table(as.matrix(glad_ab_si_gad.cM)), conf.level = 0.95)) %>%
  round(., 2) %>% 
  rownames_to_column() %>% 
  filter(rowname == "se" | rowname == "sp") %>% 
  mutate(combined =
           sprintf("%.2f (%.2f, %.2f)", 
                   est,
                   lower,
                   upper),
         Diagnosis = "GAD") %>% 
  select(-c(est, lower, upper)) %>% 
  pivot_wider(names_from = rowname, values_from = combined) %>% 
  rename("Sensitivity" = "se",
         "Specificity" = "sp")

#Combine dataframe with sensitivity/specificity
glad_ab_si_gad.df <- merge(glad_ab_si_gad.incomplete,
                      glad_ab_si_gad.95ci)

glad_ab_si_gad.df
```

Specific phobia
```{r GLAD Specific phobia AB-SI crosstabs and agreement}
glad_ab_si_spec.cM <- confusionMatrix(cidi.glad$LifetimeSpecPhob.f,
                                 cidi.glad$ClinicianSpecPhob.f, 
                                 positive = "Diagnosis",
                                 dnn = c("Algorithm-based", "Single-item"))

#Create dataframe of agreements
glad_ab_si_spec.classes<- as.matrix(glad_ab_si_spec.cM, what = "classes")
glad_ab_si_spec.overall <- as.matrix(glad_ab_si_spec.cM, what = "overall")
glad_ab_si_spec.raw <- as.data.frame(rbind(glad_ab_si_spec.classes,
                                     glad_ab_si_spec.overall))
colnames(glad_ab_si_spec.raw) <- "SPEC"

#Fromat dataframe
glad_ab_si_spec.incomplete <- glad_ab_si_spec.raw %>%  
  rownames_to_column() %>% 
  mutate(rowname = rownames(glad_ab_si_spec.raw)) %>% 
  gather(Diagnosis, value, -rowname) %>% 
  spread(rowname, value) %>% 
  select(-unused_agreement)

#Calculate sensitivity and specificity with 95% CI
glad_ab_si_spec.95ci <- summary(epiR::epi.tests(as.table(as.matrix(glad_ab_si_spec.cM)), conf.level = 0.95)) %>%
  round(., 2) %>% 
  rownames_to_column() %>% 
  filter(rowname == "se" | rowname == "sp") %>% 
  mutate(combined =
           sprintf("%.2f (%.2f, %.2f)", 
                   est,
                   lower,
                   upper),
         Diagnosis = "SPEC") %>% 
  select(-c(est, lower, upper)) %>% 
  pivot_wider(names_from = rowname, values_from = combined) %>% 
  rename("Sensitivity" = "se",
         "Specificity" = "sp")

#Combine dataframe with sensitivity/specificity
glad_ab_si_spec.df <- merge(glad_ab_si_spec.incomplete,
                      glad_ab_si_spec.95ci)

glad_ab_si_spec.df
```

Social anxiety disorder
```{r GLAD Social anxiety disorder AB-SI crosstabs and agreement}
glad_ab_si_socp.cM <- confusionMatrix(cidi.glad$LifetimeSocialPhob.f,
                                 cidi.glad$ClinicianSocialPhob.f, 
                                 positive = "Diagnosis",
                                 dnn = c("Algorithm-based", "Single-item"))

#Create dataframe of agreements
glad_ab_si_socp.classes<- as.matrix(glad_ab_si_socp.cM, what = "classes")
glad_ab_si_socp.overall <- as.matrix(glad_ab_si_socp.cM, what = "overall")
glad_ab_si_socp.raw <- as.data.frame(rbind(glad_ab_si_socp.classes,
                                     glad_ab_si_socp.overall))
colnames(glad_ab_si_socp.raw) <- "SOCP"

#Fromat dataframe
glad_ab_si_socp.incomplete <- glad_ab_si_socp.raw %>% 
  rownames_to_column() %>% 
  mutate(rowname = rownames(glad_ab_si_socp.raw)) %>% 
  gather(Diagnosis, value, -rowname) %>% 
  spread(rowname, value) %>% 
  select(-unused_agreement)

#Calculate sensitivity and specificity with 95% CI
glad_ab_si_socp.95ci <- summary(epiR::epi.tests(as.table(as.matrix(glad_ab_si_socp.cM)), conf.level = 0.95)) %>%
  round(., 2) %>% 
  rownames_to_column() %>% 
  filter(rowname == "se" | rowname == "sp") %>% 
  mutate(combined =
           sprintf("%.2f (%.2f, %.2f)", 
                   est,
                   lower,
                   upper),
         Diagnosis = "SOCP") %>% 
  select(-c(est, lower, upper)) %>% 
  pivot_wider(names_from = rowname, values_from = combined) %>% 
  rename("Sensitivity" = "se",
         "Specificity" = "sp")

#Combine dataframe with sensitivity/specificity
glad_ab_si_socp.df <- merge(glad_ab_si_socp.incomplete,
                      glad_ab_si_socp.95ci)

glad_ab_si_socp.df
```

Panic disorder
```{r GLAD Panic disorder AB-SI crosstabs and agreement}
glad_ab_si_pad.cM <- confusionMatrix(cidi.glad$LifetimePanicDis.f,
                                cidi.glad$ClinicianPanicDis.f, 
                                positive = "Diagnosis",
                                dnn = c("Algorithm-based", "Single-item"))

#Create dataframe of agreements
glad_ab_si_pad.classes<- as.matrix(glad_ab_si_pad.cM, what = "classes")
glad_ab_si_pad.overall <- as.matrix(glad_ab_si_pad.cM, what = "overall")
glad_ab_si_pad.raw <- as.data.frame(rbind(glad_ab_si_pad.classes,
                                     glad_ab_si_pad.overall))
colnames(glad_ab_si_pad.raw) <- "PAD"

#Fromat dataframe
glad_ab_si_pad.incomplete <- glad_ab_si_pad.raw %>% 
  rownames_to_column() %>% 
  mutate(rowname = rownames(glad_ab_si_pad.raw)) %>% 
  gather(Diagnosis, value, -rowname) %>% 
  spread(rowname, value) %>% 
  select(-unused_agreement)

#Calculate sensitivity and specificity with 95% CI
glad_ab_si_pad.95ci <- summary(epiR::epi.tests(as.table(as.matrix(glad_ab_si_pad.cM)), conf.level = 0.95)) %>%
  round(., 2) %>% 
  rownames_to_column() %>% 
  filter(rowname == "se" | rowname == "sp") %>% 
  mutate(combined =
           sprintf("%.2f (%.2f, %.2f)", 
                   est,
                   lower,
                   upper),
         Diagnosis = "PAD") %>% 
  select(-c(est, lower, upper)) %>% 
  pivot_wider(names_from = rowname, values_from = combined) %>% 
  rename("Sensitivity" = "se",
         "Specificity" = "sp")

#Combine dataframe with sensitivity/specificity
glad_ab_si_pad.df <- merge(glad_ab_si_pad.incomplete,
                      glad_ab_si_pad.95ci)

glad_ab_si_pad.df
```

Panic attacks
Algorithm-based panic disorder is being compared with single-item panic attacks.
```{r GLAD Panic Attacks AB-SI crosstabs and agreement with Panic Disorder, echo=FALSE}
glad_ab_si_pattacks.cM <- confusionMatrix(cidi.glad$LifetimePanicDis.f, 
                                     cidi.glad$ClinicianPanicAttacks.f.cc, 
                                     positive = "Diagnosis",
                                     dnn = c("Algorithm-based", "Single-item"))

#Create dataframe of agreements
glad_ab_si_pattacks.classes<- as.matrix(glad_ab_si_pattacks.cM, what = "classes")
glad_ab_si_pattacks.overall <- as.matrix(glad_ab_si_pattacks.cM, what = "overall")
glad_ab_si_pattacks.raw <- as.data.frame(rbind(glad_ab_si_pattacks.classes,
                                     glad_ab_si_pattacks.overall))
colnames(glad_ab_si_pattacks.raw) <- "PanicAttacks"

#Fromat dataframe
glad_ab_si_pattacks.incomplete <- glad_ab_si_pattacks.raw %>% 
  rownames_to_column() %>% 
  mutate(rowname = rownames(glad_ab_si_pattacks.raw)) %>% 
  gather(Diagnosis, value, -rowname) %>% 
  spread(rowname, value) %>% 
  select(-unused_agreement)

#Calculate sensitivity and specificity with 95% CI
glad_ab_si_pattacks.95ci <- summary(epiR::epi.tests(as.table(as.matrix(glad_ab_si_pattacks.cM)), conf.level = 0.95)) %>%
  round(., 2) %>% 
  rownames_to_column() %>% 
  filter(rowname == "se" | rowname == "sp") %>% 
  mutate(combined =
           sprintf("%.2f (%.2f, %.2f)", 
                   est,
                   lower,
                   upper),
         Diagnosis = "PanicAttacks") %>% 
  select(-c(est, lower, upper)) %>% 
  pivot_wider(names_from = rowname, values_from = combined) %>% 
  rename("Sensitivity" = "se",
         "Specificity" = "sp")

#Combine dataframe with sensitivity/specificity
glad_ab_si_pattacks.df <- merge(glad_ab_si_pattacks.incomplete,
                      glad_ab_si_pattacks.95ci)

glad_ab_si_pattacks.df
```

Agoraphobia
```{r GLAD Agoraphobia AB-SI crosstabs and agreement}
glad_ab_si_agp.cM <- confusionMatrix(cidi.glad$LifetimeAgoraphobia.f, 
                                cidi.glad$ClinicianAgoraphobia.f, 
                                positive = "Diagnosis",
                                dnn = c("Algorithm-based", "Single-item"))

#Create dataframe of agreements
glad_ab_si_agp.classes<- as.matrix(glad_ab_si_agp.cM, what = "classes")
glad_ab_si_agp.overall <- as.matrix(glad_ab_si_agp.cM, what = "overall")
glad_ab_si_agp.raw <- as.data.frame(rbind(glad_ab_si_agp.classes,
                                     glad_ab_si_agp.overall))
colnames(glad_ab_si_agp.raw) <- "AGP"

#Fromat dataframe
glad_ab_si_agp.incomplete <- glad_ab_si_agp.raw %>% 
  rownames_to_column() %>% 
  mutate(rowname = rownames(glad_ab_si_agp.raw)) %>% 
  gather(Diagnosis, value, -rowname) %>% 
  spread(rowname, value) %>% 
  select(-unused_agreement)

#Calculate sensitivity and specificity with 95% CI
glad_ab_si_agp.95ci <- summary(epiR::epi.tests(as.table(as.matrix(glad_ab_si_agp.cM)), conf.level = 0.95)) %>%
  round(., 2) %>% 
  rownames_to_column() %>% 
  filter(rowname == "se" | rowname == "sp") %>% 
  mutate(combined =
           sprintf("%.2f (%.2f, %.2f)", 
                   est,
                   lower,
                   upper),
         Diagnosis = "AGP") %>% 
  select(-c(est, lower, upper)) %>% 
  pivot_wider(names_from = rowname, values_from = combined) %>% 
  rename("Sensitivity" = "se",
         "Specificity" = "sp")

#Combine dataframe with sensitivity/specificity
glad_ab_si_agp.df <- merge(glad_ab_si_agp.incomplete,
                      glad_ab_si_agp.95ci)

glad_ab_si_agp.df
```

Any anxiety
```{r GLAD Any Anxiety AB-SI crosstabs and agreement}
glad_ab_si_anyanx.cM <- confusionMatrix(cidi.glad$LifetimeAnyAnx.f,
                                   cidi.glad$ClinicianAnyAnx.f, 
                                   positive = "Diagnosis",
                                   dnn = c("Algorithm-based", "Single-item"))

#Create dataframe of agreements
glad_ab_si_anyanx.classes<- as.matrix(glad_ab_si_anyanx.cM, what = "classes")
glad_ab_si_anyanx.overall <- as.matrix(glad_ab_si_anyanx.cM, what = "overall")
glad_ab_si_anyanx.raw <- as.data.frame(rbind(glad_ab_si_anyanx.classes,
                                     glad_ab_si_anyanx.overall))
colnames(glad_ab_si_anyanx.raw) <- "AnyAnxiety"

#Fromat dataframe
glad_ab_si_anyanx.incomplete <- glad_ab_si_anyanx.raw %>% 
  rownames_to_column() %>% 
  mutate(rowname = rownames(glad_ab_si_anyanx.raw)) %>% 
  gather(Diagnosis, value, -rowname) %>% 
  spread(rowname, value) %>% 
  select(-unused_agreement)

#Calculate sensitivity and specificity with 95% CI
glad_ab_si_anyanx.95ci <- summary(epiR::epi.tests(as.table(as.matrix(glad_ab_si_anyanx.cM)), conf.level = 0.95)) %>%
  round(., 2) %>% 
  rownames_to_column() %>% 
  filter(rowname == "se" | rowname == "sp") %>% 
  mutate(combined =
           sprintf("%.2f (%.2f, %.2f)", 
                   est,
                   lower,
                   upper),
         Diagnosis = "AnyAnxiety") %>% 
  select(-c(est, lower, upper)) %>% 
  pivot_wider(names_from = rowname, values_from = combined) %>% 
  rename("Sensitivity" = "se",
         "Specificity" = "sp")

#Combine dataframe with sensitivity/specificity
glad_ab_si_anyanx.df <- merge(glad_ab_si_anyanx.incomplete,
                      glad_ab_si_anyanx.95ci)

glad_ab_si_anyanx.df
```

```{r GLAD combine AB-SI agreement tables}
glad_ab_si_all.raw <- bind_rows(glad_ab_si_mdd.df,
                           glad_ab_si_anyanx.df,
                           glad_ab_si_gad.df,
                           glad_ab_si_spec.df,
                           glad_ab_si_socp.df,
                           glad_ab_si_pad.df,
                           glad_ab_si_pattacks.df,
                           glad_ab_si_agp.df)

glad_ab_si_all <- glad_ab_si_all.raw %>% 
  select(Diagnosis,
         "Sensitivity AB-SI" = "Sensitivity",
         "Specificity AB-SI" = "Specificity") 

glad_ab_si_all
```

#### Agreement table for all statistics

```{r GLAD combine all agreement tables}
glad_all_agreement <- merge(glad_si_ab_all,
                       glad_ab_si_all) %>%
  relocate(Kappa, .after = last_col()) %>% 
  mutate(Diagnosis = 
           factor(Diagnosis,
                  levels = c("MDD", "AnyAnxiety", "GAD", "SPEC", "SOCP", "PanicAttacks", "PAD", "AGP"))
         ) %>% 
  arrange(., Diagnosis)

glad_all_agreement
```

```{r GLAD combine agreements and xtabs tables}
glad_all_agreement_xtabs <- merge(glad_all_xtabs,
                             glad_all_agreement) %>%
  mutate(Diagnosis = 
           factor(Diagnosis,
                  levels = c("MDD", "AnyAnxiety", "GAD", "SPEC", "SOCP", "PanicAttacks", "PAD", "AGP")),
         Sample = "GLAD"
         ) %>% 
  arrange(., Diagnosis) %>% 
  relocate(Sample)

glad_all_agreement_xtabs
```

### COPING NBR

#### Algorithm-based diagnosis as reference point

Major depressive disorder
```{r COPING NBR MDD SI-AB crosstabs and agreement}
nbr_si_ab_mdd.cM <- confusionMatrix(cidi.nbr$ClinicianMDD.f,
                            cidi.nbr$LifetimeMDD.f,
                            positive = "Diagnosis",
                            dnn = c("Single-item", "Algorithm-based"))

#Create dataframe of agreements
nbr_si_ab_mdd.classes <- as.matrix(nbr_si_ab_mdd.cM, what = "classes")
nbr_si_ab_mdd.overall <- as.matrix(nbr_si_ab_mdd.cM, what = "overall")
nbr_si_ab_mdd.raw <- as.data.frame(rbind(nbr_si_ab_mdd.classes,
                                     nbr_si_ab_mdd.overall))
colnames(nbr_si_ab_mdd.raw) <- "MDD"

#Fromat dataframe
nbr_si_ab_mdd.incomplete <- nbr_si_ab_mdd.raw %>% 
  rownames_to_column() %>% 
  mutate(rowname = rownames(nbr_si_ab_mdd.raw)) %>% 
  gather(Diagnosis, value, -rowname) %>% 
  spread(rowname, value) %>% 
  select(-unused_agreement)

#Calculate sensitivity and specificity with 95% CI
nbr_si_ab_mdd.95ci <- summary(epiR::epi.tests(as.table(as.matrix(nbr_si_ab_mdd.cM)), conf.level = 0.95)) %>%
  round(., 2) %>% 
  rownames_to_column() %>% 
  filter(rowname == "se" | rowname == "sp") %>% 
  mutate(combined =
           sprintf("%.2f (%.2f, %.2f)", 
                   est,
                   lower,
                   upper),
         Diagnosis = "MDD") %>% 
  select(-c(est, lower, upper)) %>% 
  pivot_wider(names_from = rowname, values_from = combined) %>% 
  rename("Sensitivity" = "se",
         "Specificity" = "sp")

#Combine dataframe with sensitivity/specificity
nbr_si_ab_mdd.df <- merge(nbr_si_ab_mdd.incomplete,
                      nbr_si_ab_mdd.95ci)

#Create dataframe of crosstab
nbr_si_ab_mdd.xtabs <- as.data.frame(as.matrix(nbr_si_ab_mdd.cM))
nbr_si_ab_mdd.xtabs.df <- nbr_si_ab_mdd.xtabs %>% 
  rownames_to_column() %>% 
  rename("AB Yes" =
           "Diagnosis",
         "AB No" = "No diagnosis",
        "Crosstab"  = "rowname") %>% 
  mutate(Diagnosis = "MDD",
         Crosstab = recode_factor(Crosstab,
                                 "Diagnosis" = "SI Yes",
                                 "No diagnosis" = "SI No")
         )

nbr_si_ab_mdd.df
nbr_si_ab_mdd.xtabs.df
```

Generalised anxiety disorder
```{r COPING NBR GAD SI-AB crosstabs and agreement}
nbr_si_ab_gad.cM <- confusionMatrix(cidi.nbr$ClinicianGAD.f,
                                cidi.nbr$LifetimeGAD.f,
                                positive = "Diagnosis",
                                dnn = c("Single-item", "Algorithm-based"))

#Create dataframe of agreements
nbr_si_ab_gad.classes<- as.matrix(nbr_si_ab_gad.cM, what = "classes")
nbr_si_ab_gad.overall <- as.matrix(nbr_si_ab_gad.cM, what = "overall")
nbr_si_ab_gad.raw <- as.data.frame(rbind(nbr_si_ab_gad.classes,
                                     nbr_si_ab_gad.overall))
colnames(nbr_si_ab_gad.raw) <- "GAD"

#Fromat dataframe
nbr_si_ab_gad.incomplete <- nbr_si_ab_gad.raw %>% 
  rownames_to_column() %>% 
  mutate(rowname = rownames(nbr_si_ab_gad.raw)) %>% 
  gather(Diagnosis, value, -rowname) %>% 
  spread(rowname, value) %>% 
  select(-unused_agreement)

#Calculate sensitivity and specificity with 95% CI
nbr_si_ab_gad.95ci <- summary(epiR::epi.tests(as.table(as.matrix(nbr_si_ab_gad.cM)), conf.level = 0.95)) %>%
  round(., 2) %>% 
  rownames_to_column() %>% 
  filter(rowname == "se" | rowname == "sp") %>% 
  mutate(combined =
           sprintf("%.2f (%.2f, %.2f)", 
                   est,
                   lower,
                   upper),
         Diagnosis = "GAD") %>% 
  select(-c(est, lower, upper)) %>% 
  pivot_wider(names_from = rowname, values_from = combined) %>% 
  rename("Sensitivity" = "se",
         "Specificity" = "sp")

#Combine dataframe with sensitivity/specificity
nbr_si_ab_gad.df <- merge(nbr_si_ab_gad.incomplete,
                      nbr_si_ab_gad.95ci)

#Create dataframe of crosstab
nbr_si_ab_gad.xtabs <- as.data.frame(as.matrix(nbr_si_ab_gad.cM))
nbr_si_ab_gad.xtabs.df <- nbr_si_ab_gad.xtabs %>% 
  rownames_to_column() %>% 
  rename("AB Yes" =
           "Diagnosis",
         "AB No" = "No diagnosis",
        "Crosstab"  = "rowname") %>% 
  mutate(Diagnosis = "GAD",
         Crosstab = recode_factor(Crosstab,
                                 "Diagnosis" = "SI Yes",
                                 "No diagnosis" = "SI No")
         )

nbr_si_ab_gad.df
nbr_si_ab_gad.xtabs.df
```

Specific phobia
```{r COPING NBR Specific phobia SI-AB crosstabs and agreement}
nbr_si_ab_spec.cM <- confusionMatrix(cidi.nbr$ClinicianSpecPhob.f,
                                 cidi.nbr$LifetimeSpecPhob.f,
                                 positive = "Diagnosis",
                                 dnn = c("Single-item", "Algorithm-based"))

#Create dataframe of agreements
nbr_si_ab_spec.classes<- as.matrix(nbr_si_ab_spec.cM, what = "classes")
nbr_si_ab_spec.overall <- as.matrix(nbr_si_ab_spec.cM, what = "overall")
nbr_si_ab_spec.raw <- as.data.frame(rbind(nbr_si_ab_spec.classes,
                                     nbr_si_ab_spec.overall))
colnames(nbr_si_ab_spec.raw) <- "SPEC"

#Fromat dataframe
nbr_si_ab_spec.incomplete <- nbr_si_ab_spec.raw %>% 
  rownames_to_column() %>% 
  mutate(rowname = rownames(nbr_si_ab_spec.raw)) %>% 
  gather(Diagnosis, value, -rowname) %>% 
  spread(rowname, value) %>% 
  select(-unused_agreement)

#Calculate sensitivity and specificity with 95% CI
nbr_si_ab_spec.95ci <- summary(epiR::epi.tests(as.table(as.matrix(nbr_si_ab_spec.cM)), conf.level = 0.95)) %>%
  round(., 2) %>% 
  rownames_to_column() %>% 
  filter(rowname == "se" | rowname == "sp") %>% 
  mutate(combined =
           sprintf("%.2f (%.2f, %.2f)", 
                   est,
                   lower,
                   upper),
         Diagnosis = "SPEC") %>% 
  select(-c(est, lower, upper)) %>% 
  pivot_wider(names_from = rowname, values_from = combined) %>% 
  rename("Sensitivity" = "se",
         "Specificity" = "sp")

#Combine dataframe with sensitivity/specificity
nbr_si_ab_spec.df <- merge(nbr_si_ab_spec.incomplete,
                      nbr_si_ab_spec.95ci)

#Create dataframe of crosstab
nbr_si_ab_spec.xtabs <- as.data.frame(as.matrix(nbr_si_ab_spec.cM))
nbr_si_ab_spec.xtabs.df <- nbr_si_ab_spec.xtabs %>% 
  rownames_to_column() %>% 
  rename("AB Yes" =
           "Diagnosis",
         "AB No" = "No diagnosis",
        "Crosstab"  = "rowname") %>% 
  mutate(Diagnosis = "SPEC",
         Crosstab = recode_factor(Crosstab,
                                 "Diagnosis" = "SI Yes",
                                 "No diagnosis" = "SI No")
         )

nbr_si_ab_spec.df
nbr_si_ab_spec.xtabs.df
```

Social anxiety disorder
```{r COPING NBR Social anxiety disorder SI-AB crosstabs and agreement}
nbr_si_ab_socp.cM <- confusionMatrix(cidi.nbr$ClinicianSocialPhob.f,
                                  cidi.nbr$LifetimeSocialPhob.f,
                                  positive = "Diagnosis",
                                  dnn = c("Single-item", "Algorithm-based"))

#Create dataframe of agreements
nbr_si_ab_socp.classes<- as.matrix(nbr_si_ab_socp.cM, what = "classes")
nbr_si_ab_socp.overall <- as.matrix(nbr_si_ab_socp.cM, what = "overall")
nbr_si_ab_socp.raw <- as.data.frame(rbind(nbr_si_ab_socp.classes,
                                     nbr_si_ab_socp.overall))
colnames(nbr_si_ab_socp.raw) <- "SOCP"

#Fromat dataframe
nbr_si_ab_socp.incomplete <- nbr_si_ab_socp.raw %>% 
  rownames_to_column() %>% 
  mutate(rowname = rownames(nbr_si_ab_socp.raw)) %>% 
  gather(Diagnosis, value, -rowname) %>% 
  spread(rowname, value) %>% 
  select(-unused_agreement)

#Calculate sensitivity and specificity with 95% CI
nbr_si_ab_socp.95ci <- summary(epiR::epi.tests(as.table(as.matrix(nbr_si_ab_socp.cM)), conf.level = 0.95)) %>%
  round(., 2) %>% 
  rownames_to_column() %>% 
  filter(rowname == "se" | rowname == "sp") %>% 
  mutate(combined =
           sprintf("%.2f (%.2f, %.2f)", 
                   est,
                   lower,
                   upper),
         Diagnosis = "SOCP") %>% 
  select(-c(est, lower, upper)) %>% 
  pivot_wider(names_from = rowname, values_from = combined) %>% 
  rename("Sensitivity" = "se",
         "Specificity" = "sp")

#Combine dataframe with sensitivity/specificity
nbr_si_ab_socp.df <- merge(nbr_si_ab_socp.incomplete,
                      nbr_si_ab_socp.95ci)

#Create dataframe of crosstab
nbr_si_ab_socp.xtabs <- as.data.frame(as.matrix(nbr_si_ab_socp.cM))
nbr_si_ab_socp.xtabs.df <- nbr_si_ab_socp.xtabs %>% 
  rownames_to_column() %>% 
  rename("AB Yes" =
           "Diagnosis",
         "AB No" = "No diagnosis",
        "Crosstab"  = "rowname") %>% 
  mutate(Diagnosis = "SOCP",
         Crosstab = recode_factor(Crosstab,
                                 "Diagnosis" = "SI Yes",
                                 "No diagnosis" = "SI No")
         )

nbr_si_ab_socp.df
nbr_si_ab_socp.xtabs.df
```

Panic disorder
```{r COPING NBR Panic disorder SI-AB crosstabs and agreement}
nbr_si_ab_pad.cM <- confusionMatrix(cidi.nbr$ClinicianPanicDis.f,
                                cidi.nbr$LifetimePanicDis.f,
                                positive = "Diagnosis",
                                dnn = c("Single-item", "Algorithm-based"))

#Create dataframe of agreements
nbr_si_ab_pad.classes<- as.matrix(nbr_si_ab_pad.cM, what = "classes")
nbr_si_ab_pad.overall <- as.matrix(nbr_si_ab_pad.cM, what = "overall")
nbr_si_ab_pad.raw <- as.data.frame(rbind(nbr_si_ab_pad.classes,
                                     nbr_si_ab_pad.overall))
colnames(nbr_si_ab_pad.raw) <- "PAD"

#Fromat dataframe
nbr_si_ab_pad.incomplete <- nbr_si_ab_pad.raw %>% 
  rownames_to_column() %>% 
  mutate(rowname = rownames(nbr_si_ab_pad.raw)) %>% 
  gather(Diagnosis, value, -rowname) %>% 
  spread(rowname, value) %>% 
  select(-unused_agreement)

#Calculate sensitivity and specificity with 95% CI
nbr_si_ab_pad.95ci <- summary(epiR::epi.tests(as.table(as.matrix(nbr_si_ab_pad.cM)), conf.level = 0.95)) %>%
  round(., 2) %>% 
  rownames_to_column() %>% 
  filter(rowname == "se" | rowname == "sp") %>% 
  mutate(combined =
           sprintf("%.2f (%.2f, %.2f)", 
                   est,
                   lower,
                   upper),
         Diagnosis = "PAD") %>% 
  select(-c(est, lower, upper)) %>% 
  pivot_wider(names_from = rowname, values_from = combined) %>% 
  rename("Sensitivity" = "se",
         "Specificity" = "sp")

#Combine dataframe with sensitivity/specificity
nbr_si_ab_pad.df <- merge(nbr_si_ab_pad.incomplete,
                      nbr_si_ab_pad.95ci)

#Create dataframe of crosstab
nbr_si_ab_pad.xtabs <- as.data.frame(as.matrix(nbr_si_ab_pad.cM))
nbr_si_ab_pad.xtabs.df <- nbr_si_ab_pad.xtabs %>% 
  rownames_to_column() %>% 
  rename("AB Yes" =
           "Diagnosis",
         "AB No" = "No diagnosis",
        "Crosstab"  = "rowname") %>% 
  mutate(Diagnosis = "PAD",
         Crosstab = recode_factor(Crosstab,
                                 "Diagnosis" = "SI Yes",
                                 "No diagnosis" = "SI No")
         )

nbr_si_ab_pad.df
nbr_si_ab_pad.xtabs.df
```

Panic attacks
The single-item panic attack variable here is being compared to lifetime panic disorder.
```{r COPING NBR Panic Attacks SI-AB crosstabs and agreement for Panic Disorder}
nbr_si_ab_pattacks.cM <- confusionMatrix(cidi.nbr$ClinicianPanicAttacks.f.cc,
                                cidi.nbr$LifetimePanicDis.f, 
                                positive = "Diagnosis",
                                dnn = c("Single-item", "Algorithm-based"))

#Create dataframe of agreements
nbr_si_ab_pattacks.classes<- as.matrix(nbr_si_ab_pattacks.cM, what = "classes")
nbr_si_ab_pattacks.overall <- as.matrix(nbr_si_ab_pattacks.cM, what = "overall")
nbr_si_ab_pattacks.raw <- as.data.frame(rbind(nbr_si_ab_pattacks.classes,
                                     nbr_si_ab_pattacks.overall))
colnames(nbr_si_ab_pattacks.raw) <- "PanicAttacks"

#Fromat dataframe
nbr_si_ab_pattacks.incomplete <- nbr_si_ab_pattacks.raw %>% 
  rownames_to_column() %>% 
  mutate(rowname = rownames(nbr_si_ab_pattacks.raw)) %>% 
  gather(Diagnosis, value, -rowname) %>% 
  spread(rowname, value) %>% 
  select(-unused_agreement)

#Calculate sensitivity and specificity with 95% CI
nbr_si_ab_pattacks.95ci <- summary(epiR::epi.tests(as.table(as.matrix(nbr_si_ab_pattacks.cM)), conf.level = 0.95)) %>%
  round(., 2) %>% 
  rownames_to_column() %>% 
  filter(rowname == "se" | rowname == "sp") %>% 
  mutate(combined =
           sprintf("%.2f (%.2f, %.2f)", 
                   est,
                   lower,
                   upper),
         Diagnosis = "PanicAttacks") %>% 
  select(-c(est, lower, upper)) %>% 
  pivot_wider(names_from = rowname, values_from = combined) %>% 
  rename("Sensitivity" = "se",
         "Specificity" = "sp")

#Combine dataframe with sensitivity/specificity
nbr_si_ab_pattacks.df <- merge(nbr_si_ab_pattacks.incomplete,
                      nbr_si_ab_pattacks.95ci)

#Create dataframe of crosstab
nbr_si_ab_pattacks.xtabs <- as.data.frame(as.matrix(nbr_si_ab_pattacks.cM))
nbr_si_ab_pattacks.xtabs.df <- nbr_si_ab_pattacks.xtabs %>% 
  rownames_to_column() %>% 
  rename("AB Yes" =
           "Diagnosis",
         "AB No" = "No diagnosis",
        "Crosstab"  = "rowname") %>% 
  mutate(Diagnosis = "PanicAttacks",
         Crosstab = recode_factor(Crosstab,
                                 "Diagnosis" = "SI Yes",
                                 "No diagnosis" = "SI No")
         )

nbr_si_ab_pattacks.df
nbr_si_ab_pattacks.xtabs.df
```

Agoraphobia
```{r COPING NBR Agoraphobia SI-AB crosstabs and agreement}
nbr_si_ab_agp.cM <- confusionMatrix(cidi.nbr$ClinicianAgoraphobia.f,
                                cidi.nbr$LifetimeAgoraphobia.f,
                                positive = "Diagnosis",
                                dnn = c("Single-item", "Algorithm-based"))

#Create dataframe of agreements
nbr_si_ab_agp.classes<- as.matrix(nbr_si_ab_agp.cM, what = "classes")
nbr_si_ab_agp.overall <- as.matrix(nbr_si_ab_agp.cM, what = "overall")
nbr_si_ab_agp.raw <- as.data.frame(rbind(nbr_si_ab_agp.classes,
                                     nbr_si_ab_agp.overall))
colnames(nbr_si_ab_agp.raw) <- "AGP"

#Fromat dataframe
nbr_si_ab_agp.incomplete <- nbr_si_ab_agp.raw %>% 
  rownames_to_column() %>% 
  mutate(rowname = rownames(nbr_si_ab_agp.raw)) %>% 
  gather(Diagnosis, value, -rowname) %>% 
  spread(rowname, value) %>% 
  select(-unused_agreement)

#Calculate sensitivity and specificity with 95% CI
nbr_si_ab_agp.95ci <- summary(epiR::epi.tests(as.table(as.matrix(nbr_si_ab_agp.cM)), conf.level = 0.95)) %>%
  round(., 2) %>% 
  rownames_to_column() %>% 
  filter(rowname == "se" | rowname == "sp") %>% 
  mutate(combined =
           sprintf("%.2f (%.2f, %.2f)", 
                   est,
                   lower,
                   upper),
         Diagnosis = "AGP") %>% 
  select(-c(est, lower, upper)) %>% 
  pivot_wider(names_from = rowname, values_from = combined) %>% 
  rename("Sensitivity" = "se",
         "Specificity" = "sp")

#Combine dataframe with sensitivity/specificity
nbr_si_ab_agp.df <- merge(nbr_si_ab_agp.incomplete,
                      nbr_si_ab_agp.95ci)

#Create dataframe of crosstab
nbr_si_ab_agp.xtabs <- as.data.frame(as.matrix(nbr_si_ab_agp.cM))
nbr_si_ab_agp.xtabs.df <- nbr_si_ab_agp.xtabs %>% 
  rownames_to_column() %>% 
  rename("AB Yes" =
           "Diagnosis",
         "AB No" = "No diagnosis",
        "Crosstab"  = "rowname") %>% 
  mutate(Diagnosis = "AGP",
         Crosstab = recode_factor(Crosstab,
                                 "Diagnosis" = "SI Yes",
                                 "No diagnosis" = "SI No")
         )

nbr_si_ab_agp.df
nbr_si_ab_agp.xtabs.df
```

Any anxiety
```{r COPING NBR Any Anxiety SI-AB crosstabs and agreement}
nbr_si_ab_anyanx.cM <- confusionMatrix(cidi.nbr$ClinicianAnyAnx.f, 
                                cidi.nbr$LifetimeAnyAnx.f,
                                positive = "Diagnosis",
                                dnn = c("Single-item", "Algorithm-based"))

#Create dataframe of agreements
nbr_si_ab_anyanx.classes<- as.matrix(nbr_si_ab_anyanx.cM, what = "classes")
nbr_si_ab_anyanx.overall <- as.matrix(nbr_si_ab_anyanx.cM, what = "overall")
nbr_si_ab_anyanx.raw <- as.data.frame(rbind(nbr_si_ab_anyanx.classes,
                                     nbr_si_ab_anyanx.overall))
colnames(nbr_si_ab_anyanx.raw) <- "AnyAnxiety"

#Fromat dataframe
nbr_si_ab_anyanx.incomplete <- nbr_si_ab_anyanx.raw %>% 
  rownames_to_column() %>% 
  mutate(rowname = rownames(nbr_si_ab_anyanx.raw)) %>% 
  gather(Diagnosis, value, -rowname) %>% 
  spread(rowname, value) %>% 
  select(-unused_agreement)

#Calculate sensitivity and specificity with 95% CI
nbr_si_ab_anyanx.95ci <- summary(epiR::epi.tests(as.table(as.matrix(nbr_si_ab_anyanx.cM)), conf.level = 0.95)) %>%
  round(., 2) %>% 
  rownames_to_column() %>% 
  filter(rowname == "se" | rowname == "sp") %>% 
  mutate(combined =
           sprintf("%.2f (%.2f, %.2f)", 
                   est,
                   lower,
                   upper),
         Diagnosis = "AnyAnxiety") %>% 
  select(-c(est, lower, upper)) %>% 
  pivot_wider(names_from = rowname, values_from = combined) %>% 
  rename("Sensitivity" = "se",
         "Specificity" = "sp")

#Combine dataframe with sensitivity/specificity
nbr_si_ab_anyanx.df <- merge(nbr_si_ab_anyanx.incomplete,
                      nbr_si_ab_anyanx.95ci)

#Create dataframe of crosstab
nbr_si_ab_anyanx.xtabs <- as.data.frame(as.matrix(nbr_si_ab_anyanx.cM))
nbr_si_ab_anyanx.xtabs.df <- nbr_si_ab_anyanx.xtabs %>% 
  rownames_to_column() %>% 
  rename("AB Yes" =
           "Diagnosis",
         "AB No" = "No diagnosis",
        "Crosstab"  = "rowname") %>% 
  mutate(Diagnosis = "AnyAnxiety",
         Crosstab = recode_factor(Crosstab,
                                 "Diagnosis" = "SI Yes",
                                 "No diagnosis" = "SI No")
         )

nbr_si_ab_anyanx.df
nbr_si_ab_anyanx.xtabs.df
```

```{r COPING NBR combine SI-AB agreement tables}
nbr_si_ab_all.raw <- bind_rows(nbr_si_ab_mdd.df,
                           nbr_si_ab_anyanx.df,
                           nbr_si_ab_gad.df,
                           nbr_si_ab_spec.df,
                           nbr_si_ab_socp.df,
                           nbr_si_ab_pad.df,
                           nbr_si_ab_pattacks.df,
                           nbr_si_ab_agp.df)

nbr_si_ab_all <- nbr_si_ab_all.raw %>% 
  rename("Sensitivity SI-AB" = "Sensitivity",
         "Specificity SI-AB" = "Specificity") %>% 
  relocate(Kappa, .after = last_col())

nbr_si_ab_all
```

```{r COPING NBR combine all xtabs tables}
nbr_all_xtabs.raw <- bind_rows(nbr_si_ab_mdd.xtabs.df,
                           nbr_si_ab_anyanx.xtabs.df,
                           nbr_si_ab_gad.xtabs.df,
                           nbr_si_ab_spec.xtabs.df,
                           nbr_si_ab_socp.xtabs.df,
                           nbr_si_ab_pad.xtabs.df,
                           nbr_si_ab_pattacks.xtabs.df,
                           nbr_si_ab_agp.xtabs.df)

nbr_all_xtabs <- nbr_all_xtabs.raw %>%  
  relocate(Diagnosis)

nbr_all_xtabs
```

#### Single-item diagnosis as reference point

Major depressive disorder
```{r COPING NBR MDD AB-SI crosstabs and agreement}
nbr_ab_si_mdd.cM <- confusionMatrix(cidi.nbr$LifetimeMDD.f,
                                cidi.nbr$ClinicianMDD.f, 
                                positive = "Diagnosis",
                                dnn = c("Algorithm-based", "Single-item"))

#Create dataframe of agreements
nbr_ab_si_mdd.classes<- as.matrix(nbr_ab_si_mdd.cM, what = "classes")
nbr_ab_si_mdd.overall <- as.matrix(nbr_ab_si_mdd.cM, what = "overall")
nbr_ab_si_mdd.raw <- as.data.frame(rbind(nbr_ab_si_mdd.classes,
                                     nbr_ab_si_mdd.overall))
colnames(nbr_ab_si_mdd.raw) <- "MDD"

#Fromat dataframe
nbr_ab_si_mdd.incomplete <- nbr_ab_si_mdd.raw %>% 
  rownames_to_column() %>% 
  mutate(rowname = rownames(nbr_ab_si_mdd.raw)) %>% 
  gather(Diagnosis, value, -rowname) %>% 
  spread(rowname, value) %>% 
  select(-unused_agreement)

#Calculate sensitivity and specificity with 95% CI
nbr_ab_si_mdd.95ci <- summary(epiR::epi.tests(as.table(as.matrix(nbr_ab_si_mdd.cM)), conf.level = 0.95)) %>%
  round(., 2) %>% 
  rownames_to_column() %>% 
  filter(rowname == "se" | rowname == "sp") %>% 
  mutate(combined =
           sprintf("%.2f (%.2f, %.2f)", 
                   est,
                   lower,
                   upper),
         Diagnosis = "MDD") %>% 
  select(-c(est, lower, upper)) %>% 
  pivot_wider(names_from = rowname, values_from = combined) %>% 
  rename("Sensitivity" = "se",
         "Specificity" = "sp")

#Combine dataframe with sensitivity/specificity
nbr_ab_si_mdd.df <- merge(nbr_ab_si_mdd.incomplete,
                      nbr_ab_si_mdd.95ci)

nbr_ab_si_mdd.df
```

Generalised anxiety disorder
```{r COPING NBR GAD AB-SI crosstabs and agreement}
nbr_ab_si_gad.cM <- confusionMatrix(cidi.nbr$LifetimeGAD.f,
                                cidi.nbr$ClinicianGAD.f, 
                                positive = "Diagnosis",
                                dnn = c("Algorithm-based", "Single-item"))

#Create dataframe of agreements
nbr_ab_si_gad.classes<- as.matrix(nbr_ab_si_gad.cM, what = "classes")
nbr_ab_si_gad.overall <- as.matrix(nbr_ab_si_gad.cM, what = "overall")
nbr_ab_si_gad.raw <- as.data.frame(rbind(nbr_ab_si_gad.classes,
                                     nbr_ab_si_gad.overall))
colnames(nbr_ab_si_gad.raw) <- "GAD"

#Fromat dataframe
nbr_ab_si_gad.incomplete <- nbr_ab_si_gad.raw %>% 
  rownames_to_column() %>% 
  mutate(rowname = rownames(nbr_ab_si_gad.raw)) %>% 
  gather(Diagnosis, value, -rowname) %>% 
  spread(rowname, value) %>% 
  select(-unused_agreement)

#Calculate sensitivity and specificity with 95% CI
nbr_ab_si_gad.95ci <- summary(epiR::epi.tests(as.table(as.matrix(nbr_ab_si_gad.cM)), conf.level = 0.95)) %>%
  round(., 2) %>% 
  rownames_to_column() %>% 
  filter(rowname == "se" | rowname == "sp") %>% 
  mutate(combined =
           sprintf("%.2f (%.2f, %.2f)", 
                   est,
                   lower,
                   upper),
         Diagnosis = "GAD") %>% 
  select(-c(est, lower, upper)) %>% 
  pivot_wider(names_from = rowname, values_from = combined) %>% 
  rename("Sensitivity" = "se",
         "Specificity" = "sp")

#Combine dataframe with sensitivity/specificity
nbr_ab_si_gad.df <- merge(nbr_ab_si_gad.incomplete,
                      nbr_ab_si_gad.95ci)

nbr_ab_si_gad.df
```

Specific phobia
```{r COPING NBR Specific phobia AB-SI crosstabs and agreement}
nbr_ab_si_spec.cM <- confusionMatrix(cidi.nbr$LifetimeSpecPhob.f,
                                 cidi.nbr$ClinicianSpecPhob.f, 
                                 positive = "Diagnosis",
                                 dnn = c("Algorithm-based", "Single-item"))

#Create dataframe of agreements
nbr_ab_si_spec.classes<- as.matrix(nbr_ab_si_spec.cM, what = "classes")
nbr_ab_si_spec.overall <- as.matrix(nbr_ab_si_spec.cM, what = "overall")
nbr_ab_si_spec.raw <- as.data.frame(rbind(nbr_ab_si_spec.classes,
                                     nbr_ab_si_spec.overall))
colnames(nbr_ab_si_spec.raw) <- "SPEC"

#Fromat dataframe
nbr_ab_si_spec.incomplete <- nbr_ab_si_spec.raw %>% 
  rownames_to_column() %>% 
  mutate(rowname = rownames(nbr_ab_si_spec.raw)) %>% 
  gather(Diagnosis, value, -rowname) %>% 
  spread(rowname, value) %>% 
  select(-unused_agreement)

#Calculate sensitivity and specificity with 95% CI
nbr_ab_si_spec.95ci <- summary(epiR::epi.tests(as.table(as.matrix(nbr_ab_si_spec.cM)), conf.level = 0.95)) %>%
  round(., 2) %>% 
  rownames_to_column() %>% 
  filter(rowname == "se" | rowname == "sp") %>% 
  mutate(combined =
           sprintf("%.2f (%.2f, %.2f)", 
                   est,
                   lower,
                   upper),
         Diagnosis = "SPEC") %>% 
  select(-c(est, lower, upper)) %>% 
  pivot_wider(names_from = rowname, values_from = combined) %>% 
  rename("Sensitivity" = "se",
         "Specificity" = "sp")

#Combine dataframe with sensitivity/specificity
nbr_ab_si_spec.df <- merge(nbr_ab_si_spec.incomplete,
                      nbr_ab_si_spec.95ci)

nbr_ab_si_spec.df
```

Social anxiety disorder
```{r COPING NBR Social anxiety disorder AB-SI crosstabs and agreement}
nbr_ab_si_socp.cM <- confusionMatrix(cidi.nbr$LifetimeSocialPhob.f,
                                 cidi.nbr$ClinicianSocialPhob.f, 
                                 positive = "Diagnosis",
                                 dnn = c("Algorithm-based", "Single-item"))

#Create dataframe of agreements
nbr_ab_si_socp.classes<- as.matrix(nbr_ab_si_socp.cM, what = "classes")
nbr_ab_si_socp.overall <- as.matrix(nbr_ab_si_socp.cM, what = "overall")
nbr_ab_si_socp.raw <- as.data.frame(rbind(nbr_ab_si_socp.classes,
                                     nbr_ab_si_socp.overall))
colnames(nbr_ab_si_socp.raw) <- "SOCP"

#Fromat dataframe
nbr_ab_si_socp.incomplete <- nbr_ab_si_socp.raw %>% 
  rownames_to_column() %>% 
  mutate(rowname = rownames(nbr_ab_si_socp.raw)) %>% 
  gather(Diagnosis, value, -rowname) %>% 
  spread(rowname, value) %>% 
  select(-unused_agreement)

#Calculate sensitivity and specificity with 95% CI
nbr_ab_si_socp.95ci <- summary(epiR::epi.tests(as.table(as.matrix(nbr_ab_si_socp.cM)), conf.level = 0.95)) %>%
  round(., 2) %>% 
  rownames_to_column() %>% 
  filter(rowname == "se" | rowname == "sp") %>% 
  mutate(combined =
           sprintf("%.2f (%.2f, %.2f)", 
                   est,
                   lower,
                   upper),
         Diagnosis = "SOCP") %>% 
  select(-c(est, lower, upper)) %>% 
  pivot_wider(names_from = rowname, values_from = combined) %>% 
  rename("Sensitivity" = "se",
         "Specificity" = "sp")

#Combine dataframe with sensitivity/specificity
nbr_ab_si_socp.df <- merge(nbr_ab_si_socp.incomplete,
                      nbr_ab_si_socp.95ci)

nbr_ab_si_socp.df
```

Panic disorder
```{r COPING NBR Panic disorder AB-SI crosstabs and agreement}
nbr_ab_si_pad.cM <- confusionMatrix(cidi.nbr$LifetimePanicDis.f,
                                cidi.nbr$ClinicianPanicDis.f, 
                                positive = "Diagnosis",
                                dnn = c("Algorithm-based", "Single-item"))

#Create dataframe of agreements
nbr_ab_si_pad.classes<- as.matrix(nbr_ab_si_pad.cM, what = "classes")
nbr_ab_si_pad.overall <- as.matrix(nbr_ab_si_pad.cM, what = "overall")
nbr_ab_si_pad.raw <- as.data.frame(rbind(nbr_ab_si_pad.classes,
                                     nbr_ab_si_pad.overall))
colnames(nbr_ab_si_pad.raw) <- "PAD"

#Fromat dataframe
nbr_ab_si_pad.incomplete <- nbr_ab_si_pad.raw %>% 
  rownames_to_column() %>% 
  mutate(rowname = rownames(nbr_ab_si_pad.raw)) %>% 
  gather(Diagnosis, value, -rowname) %>% 
  spread(rowname, value) %>% 
  select(-unused_agreement)

#Calculate sensitivity and specificity with 95% CI
nbr_ab_si_pad.95ci <- summary(epiR::epi.tests(as.table(as.matrix(nbr_ab_si_pad.cM)), conf.level = 0.95)) %>%
  round(., 2) %>% 
  rownames_to_column() %>% 
  filter(rowname == "se" | rowname == "sp") %>% 
  mutate(combined =
           sprintf("%.2f (%.2f, %.2f)", 
                   est,
                   lower,
                   upper),
         Diagnosis = "PAD") %>% 
  select(-c(est, lower, upper)) %>% 
  pivot_wider(names_from = rowname, values_from = combined) %>% 
  rename("Sensitivity" = "se",
         "Specificity" = "sp")

#Combine dataframe with sensitivity/specificity
nbr_ab_si_pad.df <- merge(nbr_ab_si_pad.incomplete,
                      nbr_ab_si_pad.95ci)

nbr_ab_si_pad.df
```

Panic attacks
Algorithm-based panic disorder is being compared with single-item panic attacks.
```{r COPING NBR Panic Attacks AB-SI crosstabs and agreement with Panic Disorder, echo=FALSE}
nbr_ab_si_pattacks.cM <- confusionMatrix(cidi.nbr$LifetimePanicDis.f, 
                                     cidi.nbr$ClinicianPanicAttacks.f.cc, 
                                     positive = "Diagnosis",
                                     dnn = c("Algorithm-based", "Single-item"))

#Create dataframe of agreements
nbr_ab_si_pattacks.classes<- as.matrix(nbr_ab_si_pattacks.cM, what = "classes")
nbr_ab_si_pattacks.overall <- as.matrix(nbr_ab_si_pattacks.cM, what = "overall")
nbr_ab_si_pattacks.raw <- as.data.frame(rbind(nbr_ab_si_pattacks.classes,
                                     nbr_ab_si_pattacks.overall))
colnames(nbr_ab_si_pattacks.raw) <- "PanicAttacks"

#Fromat dataframe
nbr_ab_si_pattacks.incomplete <- nbr_ab_si_pattacks.raw %>% 
  rownames_to_column() %>% 
  mutate(rowname = rownames(nbr_ab_si_pattacks.raw)) %>% 
  gather(Diagnosis, value, -rowname) %>% 
  spread(rowname, value) %>% 
  select(-unused_agreement)

#Calculate sensitivity and specificity with 95% CI
nbr_ab_si_pattacks.95ci <- summary(epiR::epi.tests(as.table(as.matrix(nbr_ab_si_pattacks.cM)), conf.level = 0.95)) %>%
  round(., 2) %>% 
  rownames_to_column() %>% 
  filter(rowname == "se" | rowname == "sp") %>% 
  mutate(combined =
           sprintf("%.2f (%.2f, %.2f)", 
                   est,
                   lower,
                   upper),
         Diagnosis = "PanicAttacks") %>% 
  select(-c(est, lower, upper)) %>% 
  pivot_wider(names_from = rowname, values_from = combined) %>% 
  rename("Sensitivity" = "se",
         "Specificity" = "sp")

#Combine dataframe with sensitivity/specificity
nbr_ab_si_pattacks.df <- merge(nbr_ab_si_pattacks.incomplete,
                      nbr_ab_si_pattacks.95ci)

nbr_ab_si_pattacks.df
```

Agoraphobia
```{r COPING NBR Agoraphobia AB-SI crosstabs and agreement}
nbr_ab_si_agp.cM <- confusionMatrix(cidi.nbr$LifetimeAgoraphobia.f, 
                                cidi.nbr$ClinicianAgoraphobia.f, 
                                positive = "Diagnosis",
                                dnn = c("Algorithm-based", "Single-item"))

#Create dataframe of agreements
nbr_ab_si_agp.classes<- as.matrix(nbr_ab_si_agp.cM, what = "classes")
nbr_ab_si_agp.overall <- as.matrix(nbr_ab_si_agp.cM, what = "overall")
nbr_ab_si_agp.raw <- as.data.frame(rbind(nbr_ab_si_agp.classes,
                                     nbr_ab_si_agp.overall))
colnames(nbr_ab_si_agp.raw) <- "AGP"

#Fromat dataframe
nbr_ab_si_agp.incomplete <- nbr_ab_si_agp.raw %>% 
  rownames_to_column() %>% 
  mutate(rowname = rownames(nbr_ab_si_agp.raw)) %>% 
  gather(Diagnosis, value, -rowname) %>% 
  spread(rowname, value) %>% 
  select(-unused_agreement)

#Calculate sensitivity and specificity with 95% CI
nbr_ab_si_agp.95ci <- summary(epiR::epi.tests(as.table(as.matrix(nbr_ab_si_agp.cM)), conf.level = 0.95)) %>%
  round(., 2) %>% 
  rownames_to_column() %>% 
  filter(rowname == "se" | rowname == "sp") %>% 
  mutate(combined =
           sprintf("%.2f (%.2f, %.2f)", 
                   est,
                   lower,
                   upper),
         Diagnosis = "AGP") %>% 
  select(-c(est, lower, upper)) %>% 
  pivot_wider(names_from = rowname, values_from = combined) %>% 
  rename("Sensitivity" = "se",
         "Specificity" = "sp")

#Combine dataframe with sensitivity/specificity
nbr_ab_si_agp.df <- merge(nbr_ab_si_agp.incomplete,
                      nbr_ab_si_agp.95ci)

nbr_ab_si_agp.df
```

Any anxiety
```{r COPING NBR Any Anxiety AB-SI crosstabs and agreement}
nbr_ab_si_anyanx.cM <- confusionMatrix(cidi.nbr$LifetimeAnyAnx.f,
                                   cidi.nbr$ClinicianAnyAnx.f, 
                                   positive = "Diagnosis",
                                   dnn = c("Algorithm-based", "Single-item"))

#Create dataframe of agreements
nbr_ab_si_anyanx.classes<- as.matrix(nbr_ab_si_anyanx.cM, what = "classes")
nbr_ab_si_anyanx.overall <- as.matrix(nbr_ab_si_anyanx.cM, what = "overall")
nbr_ab_si_anyanx.raw <- as.data.frame(rbind(nbr_ab_si_anyanx.classes,
                                     nbr_ab_si_anyanx.overall))
colnames(nbr_ab_si_anyanx.raw) <- "AnyAnxiety"

#Fromat dataframe
nbr_ab_si_anyanx.incomplete <- nbr_ab_si_anyanx.raw %>% 
  rownames_to_column() %>% 
  mutate(rowname = rownames(nbr_ab_si_anyanx.raw)) %>% 
  gather(Diagnosis, value, -rowname) %>% 
  spread(rowname, value) %>% 
  select(-unused_agreement)

#Calculate sensitivity and specificity with 95% CI
nbr_ab_si_anyanx.95ci <- summary(epiR::epi.tests(as.table(as.matrix(nbr_ab_si_anyanx.cM)), conf.level = 0.95)) %>%
  round(., 2) %>% 
  rownames_to_column() %>% 
  filter(rowname == "se" | rowname == "sp") %>% 
  mutate(combined =
           sprintf("%.2f (%.2f, %.2f)", 
                   est,
                   lower,
                   upper),
         Diagnosis = "AnyAnxiety") %>% 
  select(-c(est, lower, upper)) %>% 
  pivot_wider(names_from = rowname, values_from = combined) %>% 
  rename("Sensitivity" = "se",
         "Specificity" = "sp")

#Combine dataframe with sensitivity/specificity
nbr_ab_si_anyanx.df <- merge(nbr_ab_si_anyanx.incomplete,
                      nbr_ab_si_anyanx.95ci)

nbr_ab_si_anyanx.df
```

```{r COPING NBR combine AB-SI agreement tables}
nbr_ab_si_all.raw <- bind_rows(nbr_ab_si_mdd.df,
                           nbr_ab_si_anyanx.df,
                           nbr_ab_si_gad.df,
                           nbr_ab_si_spec.df,
                           nbr_ab_si_socp.df,
                           nbr_ab_si_pad.df,
                           nbr_ab_si_pattacks.df,
                           nbr_ab_si_agp.df)

nbr_ab_si_all <- nbr_ab_si_all.raw %>% 
  select(Diagnosis,
         "Sensitivity AB-SI" = "Sensitivity",
         "Specificity AB-SI" = "Specificity") 

nbr_ab_si_all
```

#### Agreement table for all statistics

```{r COPING NBR combine all agreement tables}
nbr_all_agreement <- merge(nbr_si_ab_all,
                       nbr_ab_si_all) %>%
  relocate(Kappa, .after = last_col()) %>% 
  mutate(Diagnosis = 
           factor(Diagnosis,
                  levels = c("MDD", "AnyAnxiety", "GAD", "SPEC", "SOCP", "PanicAttacks", "PAD", "AGP"))
         ) %>% 
  arrange(., Diagnosis)

nbr_all_agreement
```

```{r COPING NBR combine agreements and xtabs tables}
nbr_all_agreement_xtabs <- merge(nbr_all_xtabs,
                             nbr_all_agreement) %>%
  mutate(Diagnosis = 
           factor(Diagnosis,
                  levels = c("MDD", "AnyAnxiety", "GAD", "SPEC", "SOCP", "PanicAttacks", "PAD", "AGP")),
         Sample = "COPING NBR"
         ) %>% 
  arrange(., Diagnosis) %>% 
  relocate(Sample)

nbr_all_agreement_xtabs
```

## Full sample and by sample combined table

```{r combine all agreement tables}
all_agreement_xtabs <- rbind(full_sample_all_agreement_xtabs,
                             glad_all_agreement_xtabs,
                             nbr_all_agreement_xtabs) %>% 
  mutate(Accuracy = 
           sprintf("%.2f (%.2f, %.2f)",
                   Accuracy*100,
                   AccuracyLower*100,
                   AccuracyUpper*100)) %>% 
  select(-c(AccuracyLower, AccuracyUpper)) %>%
  arrange(., Diagnosis) %>% 
  mutate(Diagnosis = 
           case_when(
             Diagnosis == "MDD" ~ "MDD",
             Diagnosis == "GAD" ~ "GAD",
             Diagnosis == "AnyAnxiety" ~ "Any anxiety",
             Diagnosis == "SPEC" ~ "Specific phobia",
             Diagnosis == "SOCP" ~ "Social anxiety disorder",
             Diagnosis == "PAD" ~ "Panic disorder",
             Diagnosis == "PanicAttacks" ~ "Panic attacks",
             Diagnosis == "AGP" ~ "Agoraphobia"
           ),
         Diagnosis = 
           case_when(
             Crosstab == "SI Yes" ~ Diagnosis,
             Crosstab == "SI No" ~ ""
           ),
         Sample = 
           case_when(
             Crosstab == "SI Yes" ~ Sample,
             Crosstab == "SI No" ~ ""
           ),
         SI = 
           case_when(
             Crosstab == "SI Yes" ~ "Single-item (SI)",
             Crosstab == "SI No" ~ ""
           ),
         Accuracy = 
           case_when(
             Crosstab == "SI Yes" ~ Accuracy,
             Crosstab == "SI No" ~ ""
           ),
         `Sensitivity SI-AB` = 
           case_when(
             Crosstab == "SI Yes" ~ `Sensitivity SI-AB`,
             Crosstab == "SI No" ~ ""
           ),
         `Specificity SI-AB` = 
           case_when(
             Crosstab == "SI Yes" ~ `Specificity SI-AB`,
             Crosstab == "SI No" ~ ""
           ),
         `Sensitivity AB-SI` = 
           case_when(
             Crosstab == "SI Yes" ~ `Sensitivity AB-SI`,
             Crosstab == "SI No" ~ ""
           ),
         `Specificity AB-SI` = 
           case_when(
             Crosstab == "SI Yes" ~ `Specificity AB-SI`,
             Crosstab == "SI No" ~ ""
           ),
         Kappa = 
           case_when(
             Crosstab == "SI Yes" ~ as.character(round(Kappa, 2)),
             Crosstab == "SI No" ~ ""
           ),
         McnemarPValue = 
           case_when(
             Crosstab == "SI Yes" & 
               McnemarPValue < 0.001 ~ "p < 0.001",
             Crosstab == "SI Yes" & 
               McnemarPValue > 0.001 & McnemarPValue < 0.01 ~ "p < 0.01",
             Crosstab == "SI Yes" & 
               McnemarPValue > 0.01 & McnemarPValue < 0.05 ~ "p < 0.05",
             Crosstab == "SI Yes" & 
               McnemarPValue > 0.05 ~ paste0("p ~ ", round(McnemarPValue, 2)),
             Crosstab == "SI No" ~ ""
           ),
         Crosstab = 
           case_when(
             Crosstab == "SI Yes" ~ "Yes",
             Crosstab == "SI No" ~ "No"
           )
           ) %>% 
  rename("Accuracy (%)" = "Accuracy",
         "Cohort" = "Sample",
         "Disorder" = "Diagnosis",
         "Mcnemar's test" = "McnemarPValue") %>%
  relocate(c(Disorder, Cohort, SI)) %>% 
  relocate(`Mcnemar's test`, .after = last_col())

kable(all_agreement_xtabs)
```

# Alternate diagnoses for MDD and GAD

## MDD: SI yes, AB no
Create dataset of participants with single-item but no algorithm-based MDD
```{r mdd dataset si yes ab no}
mdd_alt <- cidi %>% 
  filter(cidid.diagnosis_numeric == 0 & mhd.mdd == 1)

nrow(mdd_alt)
```

## GAD: SI yes, AB no
Create dataset of participants with single-item but no algorithm-based GAD
```{r gad dataset si yes ab no}
gad_alt.df <- cidi %>% 
  filter(cidia.diagnosis_numeric == 0 & mhd.gad == 1) %>% 
  select(sample, cidid.diagnosis_numeric, spec.diagnosis_numeric, 
         pad.diagnosis_numeric, socp.diagnosis_numeric, agp.diagnosis_numeric) 

nrow(gad_alt.df)
```

Check N other diagnoses for participants with SI yes/AB no GAD
```{r gad alternate ab diagnoses}

#full sample
gad_alt_totals_full_sample <- gad_alt.df %>%
  mutate(no_diagnosis = 
           case_when(
             cidid.diagnosis_numeric == 0 & 
               spec.diagnosis_numeric == 0 & 
               socp.diagnosis_numeric == 0 &
               pad.diagnosis_numeric == 0 &
               agp.diagnosis_numeric == 0 ~ 1,
             cidid.diagnosis_numeric == 1 | 
               spec.diagnosis_numeric == 1 | 
               socp.diagnosis_numeric == 1 |
               pad.diagnosis_numeric == 1 |
               agp.diagnosis_numeric == 1 ~ 0
           ),
         any_anxiety = case_when( 
               spec.diagnosis_numeric == 0 & 
               socp.diagnosis_numeric == 0 &
               pad.diagnosis_numeric == 0 &
               agp.diagnosis_numeric == 0 ~ 0,
               spec.diagnosis_numeric == 1 | 
               socp.diagnosis_numeric == 1 |
               pad.diagnosis_numeric == 1 |
               agp.diagnosis_numeric == 1 ~ 1)
         ) %>% 
  summarize(MDD = sum(cidid.diagnosis_numeric, na.rm = T),
            MDD_prop = sum(cidid.diagnosis_numeric, na.rm = T)/sum(!is.na(cidid.diagnosis_numeric)),
            AnyAnx = sum(any_anxiety, na.rm = T),
            AnyAnx_prop = sum(any_anxiety, na.rm = T)/sum(!is.na(any_anxiety)),
            SPEC = sum(spec.diagnosis_numeric, na.rm = T),
            SPEC_prop = sum(spec.diagnosis_numeric, na.rm = T)/sum(!is.na(spec.diagnosis_numeric)),
            SOCP = sum(socp.diagnosis_numeric, na.rm = T),
            SOCP_prop = sum(socp.diagnosis_numeric, na.rm = T)/sum(!is.na(socp.diagnosis_numeric)),
            PAD = sum(pad.diagnosis_numeric, na.rm = T),
            PAD_prop = sum(pad.diagnosis_numeric, na.rm = T)/sum(!is.na(pad.diagnosis_numeric)),
            AGP = sum(agp.diagnosis_numeric, na.rm = T),
            AGP_prop = sum(agp.diagnosis_numeric, na.rm = T)/sum(!is.na(agp.diagnosis_numeric)),
            None = sum(no_diagnosis, na.rm = T),
            None_prop = sum(no_diagnosis, na.rm = T)/sum(!is.na(cidid.diagnosis_numeric) & !is.na(any_anxiety)),
            total = n()) %>% 
  mutate(sample = "Full sample")

#by cohort
gad_alt_totals_by_cohort <- gad_alt.df %>% 
  group_by(sample) %>% 
  mutate(no_diagnosis = 
           case_when(
             cidid.diagnosis_numeric == 0 & 
               spec.diagnosis_numeric == 0 & 
               socp.diagnosis_numeric == 0 &
               pad.diagnosis_numeric == 0 &
               agp.diagnosis_numeric == 0 ~ 1,
             cidid.diagnosis_numeric == 1 | 
               spec.diagnosis_numeric == 1 | 
               socp.diagnosis_numeric == 1 |
               pad.diagnosis_numeric == 1 |
               agp.diagnosis_numeric == 1 ~ 0
           ),
         any_anxiety = case_when( 
               spec.diagnosis_numeric == 0 & 
               socp.diagnosis_numeric == 0 &
               pad.diagnosis_numeric == 0 &
               agp.diagnosis_numeric == 0 ~ 0,
               spec.diagnosis_numeric == 1 | 
               socp.diagnosis_numeric == 1 |
               pad.diagnosis_numeric == 1 |
               agp.diagnosis_numeric == 1 ~ 1)
         ) %>% 
  summarize(MDD = sum(cidid.diagnosis_numeric, na.rm = T),
            MDD_prop = sum(cidid.diagnosis_numeric, na.rm = T)/sum(!is.na(cidid.diagnosis_numeric)),
            AnyAnx = sum(any_anxiety, na.rm = T),
            AnyAnx_prop = sum(any_anxiety, na.rm = T)/sum(!is.na(any_anxiety)),
            SPEC = sum(spec.diagnosis_numeric, na.rm = T),
            SPEC_prop = sum(spec.diagnosis_numeric, na.rm = T)/sum(!is.na(spec.diagnosis_numeric)),
            SOCP = sum(socp.diagnosis_numeric, na.rm = T),
            SOCP_prop = sum(socp.diagnosis_numeric, na.rm = T)/sum(!is.na(socp.diagnosis_numeric)),
            PAD = sum(pad.diagnosis_numeric, na.rm = T),
            PAD_prop = sum(pad.diagnosis_numeric, na.rm = T)/sum(!is.na(pad.diagnosis_numeric)),
            AGP = sum(agp.diagnosis_numeric, na.rm = T),
            AGP_prop = sum(agp.diagnosis_numeric, na.rm = T)/sum(!is.na(agp.diagnosis_numeric)),
            None = sum(no_diagnosis, na.rm = T),
            None_prop = sum(no_diagnosis, na.rm = T)/sum(!is.na(cidid.diagnosis_numeric) & !is.na(any_anxiety)),
            total = n()) %>% 
  mutate(sample = 
           case_when(
             sample == "GLAD" ~ "GLAD",
             sample == "NBR" ~ "COPING NBR"
           ))

#merge full sample and by cohort
gad_alt_totals <- rbind(gad_alt_totals_full_sample,
                        gad_alt_totals_by_cohort)

gad_alt_totals

gad_alt_totals.long <- gad_alt_totals %>%
  select(-c(MDD, AnyAnx, SPEC, SOCP, PAD, AGP, None, total)) %>% 
  pivot_longer(cols = c(MDD_prop, AnyAnx_prop, SPEC_prop, SOCP_prop, PAD_prop, AGP_prop, None_prop)) %>% 
  #pivot_wider(names_from = sample, values_from = value) %>% 
  mutate(name = 
           as.factor(case_when(
             name == "MDD_prop" ~ "MDD",
             name == "AnyAnx_prop" ~ "Any anxiety",
             name == "SPEC_prop" ~ "Specific phobia",
             name == "SOCP_prop" ~ "Social anxiety disorder",
             name == "PAD_prop" ~ "Panic disorder",
             name == "AGP_prop" ~ "Agoraphobia",
             name == "None_prop" ~ "No diagnosis"
           ))
  )

gad_alt_totals.long$name <- fct_relevel(gad_alt_totals.long$name, "MDD", "Any anxiety", "Specific phobia", "Social anxiety disorder", "Panic disorder", "Agoraphobia", "No diagnosis")

gad_alt_totals.long$sample <- fct_relevel(gad_alt_totals.long$sample, "Full sample", "GLAD", "COPING NBR")

gad_alt_totals.long
```

```{r gad graph alternate diagnoses}

## Graph of alternate algorithm-based diagnoses for participants with single-item but no algorithm-based GAD

gad_alt_ab_diagnoses_barchart <- ggplot(gad_alt_totals.long, aes(x = name, y = value, fill = sample, label = paste(round(value*100, 2), "%", sep = " "))) + 
  labs(x = "Algorithm-based diagnosis", 
       y = element_blank(), 
       fill = "Cohort",
       color="black",
       subtitle = paste0("N = ", nrow(gad_alt.df), 
                         " (GLAD: ", sum(gad_alt.df$sample == "GLAD"),
                         "; COPING NBR: ", sum(gad_alt.df$sample == "NBR"), ")")) +
  theme(plot.subtitle = element_text(face = "italic"),
        axis.text.x = element_text(color="black",
                                   #angle = 25, 
                                   size = 10), 
                                   #hjust = 1),
        axis.title.x = element_text(color = "black",
                                    size = 10,
                                    vjust = -2),
        axis.title.y = element_text(color = "black",
                                    size = 10),
        axis.ticks = element_blank(),
        axis.text.y = element_text(colour="black", 
                                   size = 10),
        panel.grid.major.y = element_line(size = 0.5,
                                        linetype = 'dashed',
                                        colour = "light blue"),
        panel.background = element_rect(color = "light blue", fill = "white"),
        plot.margin = margin(10, 10, 10, 10)) +   
  scale_color_manual(values = GLADpalette) +
  scale_fill_manual(values = GLADpalette) +
  geom_bar(stat = 'identity', position = 'dodge') +
  geom_text(aes(label = paste0(round(value*100, 2), "%")), 
            position = position_dodge(width = 0.95),
            vjust = -0.5,
            size = 3
            ) +
  scale_y_continuous(limits = c(0, 1), #Y-axis goes from 0-1
                     breaks=seq(0,1, 0.1), #Y-axis goes from 0 - 1, with tick marks every 0.1
                     labels = scales::percent_format(accuracy = 5L), #Makes y-axis % and removes decimals
                     expand = c(0,0))

gad_alt_ab_diagnoses_barchart
```

```{r save GAD alternate diagnosis barchart}
grDevices::dev.set(1)
#Save jpeg of diagnosis barchart
ggsave(paste0("gad_alt_ab_diagnoses_barchart_", Sys.Date(), ".jpeg"),
       path = "/Users/mollydavies/OneDrive - King's College London/PhD/GLAD Diagnosis paper/Figures/2021-04 SECOND SUBMISSION",
       plot = gad_alt_ab_diagnoses_barchart,
       width = 12,
       height = 6.5,
       dpi = 150,
       units = "in")

#Save tiff of diagnosis barchart
ggsave(paste0("gad_alt_ab_diagnoses_barchart_", Sys.Date(), ".tiff"),
       path = "/Users/mollydavies/OneDrive - King's College London/PhD/GLAD Diagnosis paper/Figures/2021-04 SECOND SUBMISSION",
       plot = gad_alt_ab_diagnoses_barchart,
       width = 12,
       height = 6.5,
       dpi = 150,
       units = "in")
```

## Alternate SI diagnoses for AB anxiety disorders
The purpose is to explore whether participants with an algorithm-based diagnosis of one of the anxiety disorders (excluding GAD) reported a different single-item diagnosis.

### SPEC

```{r spec dataset ab yes si no}
spec_alt.df <- cidi %>% 
  filter(spec.diagnosis_numeric == 1 & mhd.specific_phobia == 0)
```

```{r spec alternate si diagnoses}

#full sample
spec_alt_totals_full_sample <- spec_alt.df %>%
  mutate(no_diagnosis = 
           case_when(
             mhd.mdd == 0 & 
               mhd.gad == 0 & 
               mhd.social_anxiety == 0 &
               mhd.panic_disorder == 0 &
               mhd.agoraphobia == 0 ~ 1,
             mhd.mdd == 1 | 
               mhd.gad == 1 | 
               mhd.social_anxiety == 1 |
               mhd.panic_disorder == 1 |
               mhd.agoraphobia == 1 ~ 0
           ),
         any_anxiety = case_when( 
               mhd.gad == 0 & 
               mhd.social_anxiety == 0 &
               mhd.panic_disorder == 0 &
               mhd.agoraphobia == 0 ~ 0,
               mhd.gad == 1 | 
               mhd.social_anxiety == 1 |
               mhd.panic_disorder == 1 |
               mhd.agoraphobia == 1 ~ 1)
         ) %>% 
  summarize(MDD = sum(mhd.mdd, na.rm = T),
            MDD_prop = sum(mhd.mdd, na.rm = T)/sum(!is.na(mhd.mdd)),
            AnyAnx = sum(any_anxiety, na.rm = T),
            AnyAnx_prop = sum(any_anxiety, na.rm = T)/sum(!is.na(any_anxiety)),
            GAD = sum(mhd.gad, na.rm = T),
            GAD_prop = sum(mhd.gad, na.rm = T)/sum(!is.na(mhd.gad)),
            SOCP = sum(mhd.social_anxiety, na.rm = T),
            SOCP_prop = sum(mhd.social_anxiety, na.rm = T)/sum(!is.na(mhd.social_anxiety)),
            PAD = sum(mhd.panic_disorder, na.rm = T),
            PAD_prop = sum(mhd.panic_disorder, na.rm = T)/sum(!is.na(mhd.panic_disorder)),
            AGP = sum(mhd.agoraphobia, na.rm = T),
            AGP_prop = sum(mhd.agoraphobia, na.rm = T)/sum(!is.na(mhd.agoraphobia)),
            None = sum(no_diagnosis, na.rm = T),
            None_prop = sum(no_diagnosis, na.rm = T)/sum(!is.na(mhd.mdd) & !is.na(any_anxiety)),
            total = n()) %>% 
  mutate(sample = "Full sample")

#by cohort
spec_alt_totals_by_cohort <- spec_alt.df %>% 
  group_by(sample) %>% 
  mutate(no_diagnosis = 
           case_when(
             mhd.mdd == 0 & 
               mhd.gad == 0 & 
               mhd.social_anxiety == 0 &
               mhd.panic_disorder == 0 &
               mhd.agoraphobia == 0 ~ 1,
             mhd.mdd == 1 | 
               mhd.gad == 1 | 
               mhd.social_anxiety == 1 |
               mhd.panic_disorder == 1 |
               mhd.agoraphobia == 1 ~ 0
           ),
         any_anxiety = case_when( 
               mhd.gad == 0 & 
               mhd.social_anxiety == 0 &
               mhd.panic_disorder == 0 &
               mhd.agoraphobia == 0 ~ 0,
               mhd.gad == 1 | 
               mhd.social_anxiety == 1 |
               mhd.panic_disorder == 1 |
               mhd.agoraphobia == 1 ~ 1)
         ) %>% 
  summarize(MDD = sum(mhd.mdd, na.rm = T),
            MDD_prop = sum(mhd.mdd, na.rm = T)/sum(!is.na(mhd.mdd)),
            AnyAnx = sum(any_anxiety, na.rm = T),
            AnyAnx_prop = sum(any_anxiety, na.rm = T)/sum(!is.na(any_anxiety)),
            GAD = sum(mhd.gad, na.rm = T),
            GAD_prop = sum(mhd.gad, na.rm = T)/sum(!is.na(mhd.gad)),
            SOCP = sum(mhd.social_anxiety, na.rm = T),
            SOCP_prop = sum(mhd.social_anxiety, na.rm = T)/sum(!is.na(mhd.social_anxiety)),
            PAD = sum(mhd.panic_disorder, na.rm = T),
            PAD_prop = sum(mhd.panic_disorder, na.rm = T)/sum(!is.na(mhd.panic_disorder)),
            AGP = sum(mhd.agoraphobia, na.rm = T),
            AGP_prop = sum(mhd.agoraphobia, na.rm = T)/sum(!is.na(mhd.agoraphobia)),
            None = sum(no_diagnosis, na.rm = T),
            None_prop = sum(no_diagnosis, na.rm = T)/sum(!is.na(mhd.mdd) & !is.na(any_anxiety)),
            total = n()) %>% 
  mutate(sample = 
           case_when(
             sample == "GLAD" ~ "GLAD",
             sample == "NBR" ~ "COPING NBR"
           ))

#merge full sample and by cohort
spec_alt_totals <- rbind(spec_alt_totals_full_sample,
                        spec_alt_totals_by_cohort)

spec_alt_totals

spec_alt_totals.long <- spec_alt_totals %>%
  select(-c(MDD, AnyAnx, GAD, SOCP, PAD, AGP, None, total)) %>% 
  pivot_longer(cols = c(MDD_prop, AnyAnx_prop, GAD_prop, SOCP_prop, PAD_prop, AGP_prop, None_prop)) %>% 
  #pivot_wider(names_from = sample, values_from = value) %>% 
  mutate(name = 
           as.factor(case_when(
             name == "MDD_prop" ~ "MDD",
             name == "AnyAnx_prop" ~ "Any anxiety",
             name == "GAD_prop" ~ "GAD",
             name == "SOCP_prop" ~ "Social anxiety disorder",
             name == "PAD_prop" ~ "Panic disorder",
             name == "AGP_prop" ~ "Agoraphobia",
             name == "None_prop" ~ "No diagnosis"
           ))
  )

spec_alt_totals.long$name <- fct_relevel(spec_alt_totals.long$name, "MDD", "Any anxiety", "GAD", "Social anxiety disorder", "Panic disorder", "Agoraphobia", "No diagnosis")

spec_alt_totals.long$sample <- fct_relevel(spec_alt_totals.long$sample, "Full sample", "GLAD", "COPING NBR")

spec_alt_totals.long
```

```{r spec graph alternate diagnoses}

## Graph of alternate algorithm-based diagnoses for participants with single-item but no algorithm-based GAD

spec_alt_si_diagnoses_barchart <- ggplot(spec_alt_totals.long, aes(x = name, y = value, fill = sample, label = paste(round(value*100, 2), "%", sep = " "))) + 
  labs(x = "Single-item diagnosis", 
       y = element_blank(), 
       fill = "Cohort",
       color="black",
       title = "Specific phobia",
       subtitle = paste0("N = ", nrow(spec_alt.df), 
                         " (GLAD: ", sum(spec_alt.df$sample == "GLAD"),
                         "; COPING NBR: ", sum(spec_alt.df$sample == "NBR"), ")")) +
  theme(plot.subtitle = element_text(face = "italic"),
        axis.text.x = element_text(color="black",
                                   #angle = 25, 
                                   size = 8), 
                                   #hjust = 1),
        axis.title.x = element_text(color = "black",
                                    size = 8,
                                    vjust = -2),
        axis.title.y = element_text(color = "black",
                                    size = 8),
        axis.ticks = element_blank(),
        axis.text.y = element_text(colour="black", 
                                   size = 8),
        panel.grid.major.y = element_line(size = 0.5,
                                        linetype = 'dashed',
                                        colour = "light blue"),
        panel.background = element_rect(color = "light blue", fill = "white"),
        plot.margin = margin(10, 10, 10, 10)) +   
  scale_color_manual(values = GLADpalette) +
  scale_fill_manual(values = GLADpalette) +
  geom_bar(stat = 'identity', position = 'dodge') +
  geom_text(aes(label = paste0(round(value*100, 2), "%")), 
            position = position_dodge(width = 0.95),
            vjust = -0.5,
            size = 3
            ) +
  scale_y_continuous(limits = c(0, 1), #Y-axis goes from 0-1
                     breaks=seq(0,1, 0.1), #Y-axis goes from 0 - 1, with tick marks every 0.1
                     labels = scales::percent_format(accuracy = 5L), #Makes y-axis % and removes decimals
                     expand = c(0,0))

spec_alt_si_diagnoses_barchart
```

### SOCP

```{r socp dataset ab yes si no}
socp_alt.df <- cidi %>% 
  filter(socp.diagnosis_numeric == 1 & mhd.social_anxiety == 0)
```

```{r socp alternate si diagnoses}

#full sample
socp_alt_totals_full_sample <- socp_alt.df %>%
  mutate(no_diagnosis = 
           case_when(
             mhd.mdd == 0 & 
               mhd.gad == 0 & 
               mhd.specific_phobia == 0 &
               mhd.panic_disorder == 0 &
               mhd.agoraphobia == 0 ~ 1,
             mhd.mdd == 1 | 
               mhd.gad == 1 | 
               mhd.specific_phobia == 1 |
               mhd.panic_disorder == 1 |
               mhd.agoraphobia == 1 ~ 0
           ),
         any_anxiety = case_when( 
               mhd.gad == 0 & 
               mhd.specific_phobia == 0 &
               mhd.panic_disorder == 0 &
               mhd.agoraphobia == 0 ~ 0,
               mhd.gad == 1 | 
               mhd.specific_phobia == 1 |
               mhd.panic_disorder == 1 |
               mhd.agoraphobia == 1 ~ 1)
         ) %>% 
  summarize(MDD = sum(mhd.mdd, na.rm = T),
            MDD_prop = sum(mhd.mdd, na.rm = T)/sum(!is.na(mhd.mdd)),
            AnyAnx = sum(any_anxiety, na.rm = T),
            AnyAnx_prop = sum(any_anxiety, na.rm = T)/sum(!is.na(any_anxiety)),
            GAD = sum(mhd.gad, na.rm = T),
            GAD_prop = sum(mhd.gad, na.rm = T)/sum(!is.na(mhd.gad)),
            SPEC = sum(mhd.specific_phobia, na.rm = T),
            SPEC_prop = sum(mhd.specific_phobia, na.rm = T)/sum(!is.na(mhd.specific_phobia)),
            PAD = sum(mhd.panic_disorder, na.rm = T),
            PAD_prop = sum(mhd.panic_disorder, na.rm = T)/sum(!is.na(mhd.panic_disorder)),
            AGP = sum(mhd.agoraphobia, na.rm = T),
            AGP_prop = sum(mhd.agoraphobia, na.rm = T)/sum(!is.na(mhd.agoraphobia)),
            None = sum(no_diagnosis, na.rm = T),
            None_prop = sum(no_diagnosis, na.rm = T)/sum(!is.na(mhd.mdd) & !is.na(any_anxiety)),
            total = n()) %>% 
  mutate(sample = "Full sample")

#by cohort
socp_alt_totals_by_cohort <- socp_alt.df %>% 
  group_by(sample) %>% 
  mutate(no_diagnosis = 
           case_when(
             mhd.mdd == 0 & 
               mhd.gad == 0 & 
               mhd.specific_phobia == 0 &
               mhd.panic_disorder == 0 &
               mhd.agoraphobia == 0 ~ 1,
             mhd.mdd == 1 | 
               mhd.gad == 1 | 
               mhd.specific_phobia == 1 |
               mhd.panic_disorder == 1 |
               mhd.agoraphobia == 1 ~ 0
           ),
         any_anxiety = case_when( 
               mhd.gad == 0 & 
               mhd.specific_phobia == 0 &
               mhd.panic_disorder == 0 &
               mhd.agoraphobia == 0 ~ 0,
               mhd.gad == 1 | 
               mhd.specific_phobia == 1 |
               mhd.panic_disorder == 1 |
               mhd.agoraphobia == 1 ~ 1)
         ) %>% 
  summarize(MDD = sum(mhd.mdd, na.rm = T),
            MDD_prop = sum(mhd.mdd, na.rm = T)/sum(!is.na(mhd.mdd)),
            AnyAnx = sum(any_anxiety, na.rm = T),
            AnyAnx_prop = sum(any_anxiety, na.rm = T)/sum(!is.na(any_anxiety)),
            GAD = sum(mhd.gad, na.rm = T),
            GAD_prop = sum(mhd.gad, na.rm = T)/sum(!is.na(mhd.gad)),
            SPEC = sum(mhd.specific_phobia, na.rm = T),
            SPEC_prop = sum(mhd.specific_phobia, na.rm = T)/sum(!is.na(mhd.specific_phobia)),
            PAD = sum(mhd.panic_disorder, na.rm = T),
            PAD_prop = sum(mhd.panic_disorder, na.rm = T)/sum(!is.na(mhd.panic_disorder)),
            AGP = sum(mhd.agoraphobia, na.rm = T),
            AGP_prop = sum(mhd.agoraphobia, na.rm = T)/sum(!is.na(mhd.agoraphobia)),
            None = sum(no_diagnosis, na.rm = T),
            None_prop = sum(no_diagnosis, na.rm = T)/sum(!is.na(mhd.mdd) & !is.na(any_anxiety)),
            total = n()) %>% 
  mutate(sample = 
           case_when(
             sample == "GLAD" ~ "GLAD",
             sample == "NBR" ~ "COPING NBR"
           ))

#merge full sample and by cohort
socp_alt_totals <- rbind(socp_alt_totals_full_sample,
                        socp_alt_totals_by_cohort)

socp_alt_totals

socp_alt_totals.long <- socp_alt_totals %>%
  select(-c(MDD, AnyAnx, GAD, SPEC, PAD, AGP, None, total)) %>% 
  pivot_longer(cols = c(MDD_prop, AnyAnx_prop, GAD_prop, SPEC_prop, PAD_prop, AGP_prop, None_prop)) %>% 
  #pivot_wider(names_from = sample, values_from = value) %>% 
  mutate(name = 
           as.factor(case_when(
             name == "MDD_prop" ~ "MDD",
             name == "AnyAnx_prop" ~ "Any anxiety",
             name == "GAD_prop" ~ "GAD",
             name == "SPEC_prop" ~ "Specific phobia",
             name == "PAD_prop" ~ "Panic disorder",
             name == "AGP_prop" ~ "Agoraphobia",
             name == "None_prop" ~ "No diagnosis"
           ))
  )

socp_alt_totals.long$name <- fct_relevel(socp_alt_totals.long$name, "MDD", "Any anxiety", "GAD", "Specific phobia", "Panic disorder", "Agoraphobia", "No diagnosis")

socp_alt_totals.long$sample <- fct_relevel(socp_alt_totals.long$sample, "Full sample", "GLAD", "COPING NBR")

socp_alt_totals.long
```

```{r socp graph alternate diagnoses}

## Graph of alternate algorithm-based diagnoses for participants with single-item but no algorithm-based GAD

socp_alt_si_diagnoses_barchart <- ggplot(socp_alt_totals.long, aes(x = name, y = value, fill = sample, label = paste(round(value*100, 2), "%", sep = " "))) + 
  labs(x = "Single-item diagnosis", 
       y = element_blank(), 
       fill = "Cohort",
       color="black",
       title = "Social anxiety disorder",
       subtitle = paste0("N = ", nrow(socp_alt.df), 
                         " (GLAD: ", sum(socp_alt.df$sample == "GLAD"),
                         "; COPING NBR: ", sum(socp_alt.df$sample == "NBR"), ")")) +
  theme(plot.subtitle = element_text(face = "italic"),
        axis.text.x = element_text(color="black",
                                   #angle = 25, 
                                   size = 8), 
                                   #hjust = 1),
        axis.title.x = element_text(color = "black",
                                    size = 8,
                                    vjust = -2),
        axis.title.y = element_text(color = "black",
                                    size = 8),
        axis.ticks = element_blank(),
        axis.text.y = element_text(colour="black", 
                                   size = 8),
        panel.grid.major.y = element_line(size = 0.5,
                                        linetype = 'dashed',
                                        colour = "light blue"),
        panel.background = element_rect(color = "light blue", fill = "white"),
        plot.margin = margin(10, 10, 10, 10)) +   
  scale_color_manual(values = GLADpalette) +
  scale_fill_manual(values = GLADpalette) +
  geom_bar(stat = 'identity', position = 'dodge') +
  geom_text(aes(label = paste0(round(value*100, 2), "%")), 
            position = position_dodge(width = 0.95),
            vjust = -0.5,
            size = 3
            ) +
  scale_y_continuous(limits = c(0, 1), #Y-axis goes from 0-1
                     breaks=seq(0,1, 0.1), #Y-axis goes from 0 - 1, with tick marks every 0.1
                     labels = scales::percent_format(accuracy = 5L), #Makes y-axis % and removes decimals
                     expand = c(0,0))

socp_alt_si_diagnoses_barchart
```

### PAD

```{r pad dataset ab yes si no}
pad_alt.df <- cidi %>% 
  filter(pad.diagnosis_numeric == 1 & mhd.panic_disorder == 0)
```

```{r pad alternate si diagnoses}

#full sample
pad_alt_totals_full_sample <- pad_alt.df %>%
  mutate(no_diagnosis = 
           case_when(
             mhd.mdd == 0 & 
               mhd.gad == 0 & 
               mhd.specific_phobia == 0 &
               mhd.social_anxiety == 0 &
               mhd.agoraphobia == 0 ~ 1,
             mhd.mdd == 1 | 
               mhd.gad == 1 | 
               mhd.specific_phobia == 1 |
               mhd.social_anxiety == 1 |
               mhd.agoraphobia == 1 ~ 0
           ),
         any_anxiety = case_when( 
               mhd.gad == 0 & 
               mhd.specific_phobia == 0 &
               mhd.social_anxiety == 0 &
               mhd.agoraphobia == 0 ~ 0,
               mhd.gad == 1 | 
               mhd.specific_phobia == 1 |
               mhd.social_anxiety == 1 |
               mhd.agoraphobia == 1 ~ 1)
         ) %>% 
  summarize(MDD = sum(mhd.mdd, na.rm = T),
            MDD_prop = sum(mhd.mdd, na.rm = T)/sum(!is.na(mhd.mdd)),
            AnyAnx = sum(any_anxiety, na.rm = T),
            AnyAnx_prop = sum(any_anxiety, na.rm = T)/sum(!is.na(any_anxiety)),
            GAD = sum(mhd.gad, na.rm = T),
            GAD_prop = sum(mhd.gad, na.rm = T)/sum(!is.na(mhd.gad)),
            SPEC = sum(mhd.specific_phobia, na.rm = T),
            SPEC_prop = sum(mhd.specific_phobia, na.rm = T)/sum(!is.na(mhd.specific_phobia)),
            SOCP = sum(mhd.social_anxiety, na.rm = T),
            SOCP_prop = sum(mhd.social_anxiety, na.rm = T)/sum(!is.na(mhd.social_anxiety)),
            AGP = sum(mhd.agoraphobia, na.rm = T),
            AGP_prop = sum(mhd.agoraphobia, na.rm = T)/sum(!is.na(mhd.agoraphobia)),
            None = sum(no_diagnosis, na.rm = T),
            None_prop = sum(no_diagnosis, na.rm = T)/sum(!is.na(mhd.mdd) & !is.na(any_anxiety)),
            total = n()) %>% 
  mutate(sample = "Full sample")

#by cohort
pad_alt_totals_by_cohort <- pad_alt.df %>% 
  group_by(sample) %>% 
  mutate(no_diagnosis = 
           case_when(
             mhd.mdd == 0 & 
               mhd.gad == 0 & 
               mhd.specific_phobia == 0 &
               mhd.social_anxiety == 0 &
               mhd.agoraphobia == 0 ~ 1,
             mhd.mdd == 1 | 
               mhd.gad == 1 | 
               mhd.specific_phobia == 1 |
               mhd.social_anxiety == 1 |
               mhd.agoraphobia == 1 ~ 0
           ),
         any_anxiety = case_when( 
               mhd.gad == 0 & 
               mhd.specific_phobia == 0 &
               mhd.social_anxiety == 0 &
               mhd.agoraphobia == 0 ~ 0,
               mhd.gad == 1 | 
               mhd.specific_phobia == 1 |
               mhd.social_anxiety == 1 |
               mhd.agoraphobia == 1 ~ 1)
         ) %>% 
  summarize(MDD = sum(mhd.mdd, na.rm = T),
            MDD_prop = sum(mhd.mdd, na.rm = T)/sum(!is.na(mhd.mdd)),
            AnyAnx = sum(any_anxiety, na.rm = T),
            AnyAnx_prop = sum(any_anxiety, na.rm = T)/sum(!is.na(any_anxiety)),
            GAD = sum(mhd.gad, na.rm = T),
            GAD_prop = sum(mhd.gad, na.rm = T)/sum(!is.na(mhd.gad)),
            SPEC = sum(mhd.specific_phobia, na.rm = T),
            SPEC_prop = sum(mhd.specific_phobia, na.rm = T)/sum(!is.na(mhd.specific_phobia)),
            SOCP = sum(mhd.social_anxiety, na.rm = T),
            SOCP_prop = sum(mhd.social_anxiety, na.rm = T)/sum(!is.na(mhd.social_anxiety)),
            AGP = sum(mhd.agoraphobia, na.rm = T),
            AGP_prop = sum(mhd.agoraphobia, na.rm = T)/sum(!is.na(mhd.agoraphobia)),
            None = sum(no_diagnosis, na.rm = T),
            None_prop = sum(no_diagnosis, na.rm = T)/sum(!is.na(mhd.mdd) & !is.na(any_anxiety)),
            total = n()) %>% 
  mutate(sample = 
           case_when(
             sample == "GLAD" ~ "GLAD",
             sample == "NBR" ~ "COPING NBR"
           ))

#merge full sample and by cohort
pad_alt_totals <- rbind(pad_alt_totals_full_sample,
                        pad_alt_totals_by_cohort)

pad_alt_totals

pad_alt_totals.long <- pad_alt_totals %>%
  select(-c(MDD, AnyAnx, GAD, SPEC, SOCP, AGP, None, total)) %>% 
  pivot_longer(cols = c(MDD_prop, AnyAnx_prop, GAD_prop, SPEC_prop, SOCP_prop, AGP_prop, None_prop)) %>% 
  #pivot_wider(names_from = sample, values_from = value) %>% 
  mutate(name = 
           as.factor(case_when(
             name == "MDD_prop" ~ "MDD",
             name == "AnyAnx_prop" ~ "Any anxiety",
             name == "GAD_prop" ~ "GAD",
             name == "SPEC_prop" ~ "Specific phobia",
             name == "SOCP_prop" ~ "Social anxiety disorder",
             name == "AGP_prop" ~ "Agoraphobia",
             name == "None_prop" ~ "No diagnosis"
           ))
  )

pad_alt_totals.long$name <- fct_relevel(pad_alt_totals.long$name, "MDD", "Any anxiety", "GAD", "Specific phobia", "Social anxiety disorder", "Agoraphobia", "No diagnosis")

pad_alt_totals.long$sample <- fct_relevel(pad_alt_totals.long$sample, "Full sample", "GLAD", "COPING NBR")

pad_alt_totals.long
```

```{r pad graph alternate diagnoses}

## Graph of alternate algorithm-based diagnoses for participants with single-item but no algorithm-based GAD

pad_alt_si_diagnoses_barchart <- ggplot(pad_alt_totals.long, aes(x = name, y = value, fill = sample, label = paste(round(value*100, 2), "%", sep = " "))) + 
  labs(x = "Single-item diagnosis", 
       y = element_blank(), 
       fill = "Cohort",
       color="black",
       title = "Panic disorder",
       subtitle = paste0("N = ", nrow(pad_alt.df), 
                         " (GLAD: ", sum(pad_alt.df$sample == "GLAD"),
                         "; COPING NBR: ", sum(pad_alt.df$sample == "NBR"), ")")) +
  theme(plot.subtitle = element_text(face = "italic"),
        axis.text.x = element_text(color="black",
                                   #angle = 25, 
                                   size = 8), 
                                   #hjust = 1),
        axis.title.x = element_text(color = "black",
                                    size = 8,
                                    vjust = -2),
        axis.title.y = element_text(color = "black",
                                    size = 8),
        axis.ticks = element_blank(),
        axis.text.y = element_text(colour="black", 
                                   size = 8),
        panel.grid.major.y = element_line(size = 0.5,
                                        linetype = 'dashed',
                                        colour = "light blue"),
        panel.background = element_rect(color = "light blue", fill = "white"),
        plot.margin = margin(10, 10, 10, 10)) +   
  scale_color_manual(values = GLADpalette) +
  scale_fill_manual(values = GLADpalette) +
  geom_bar(stat = 'identity', position = 'dodge') +
  geom_text(aes(label = paste0(round(value*100, 2), "%")), 
            position = position_dodge(width = 0.95),
            vjust = -0.5,
            size = 3
            ) +
  scale_y_continuous(limits = c(0, 1), #Y-axis goes from 0-1
                     breaks=seq(0,1, 0.1), #Y-axis goes from 0 - 1, with tick marks every 0.1
                     labels = scales::percent_format(accuracy = 5L), #Makes y-axis % and removes decimals
                     expand = c(0,0))

pad_alt_si_diagnoses_barchart
```

### AGP

```{r agp dataset ab yes si no}
agp_alt.df <- cidi %>% 
  filter(agp.diagnosis_numeric == 1 & mhd.agoraphobia == 0)
```

```{r agp alternate si diagnoses}

#full sample
agp_alt_totals_full_sample <- agp_alt.df %>%
  mutate(no_diagnosis = 
           case_when(
             mhd.mdd == 0 & 
               mhd.gad == 0 & 
               mhd.specific_phobia == 0 &
               mhd.social_anxiety == 0 &
               mhd.panic_disorder == 0 ~ 1,
             mhd.mdd == 1 | 
               mhd.gad == 1 | 
               mhd.specific_phobia == 1 |
               mhd.social_anxiety == 1 |
               mhd.panic_disorder == 1 ~ 0
           ),
         any_anxiety = case_when( 
               mhd.gad == 0 & 
               mhd.specific_phobia == 0 &
               mhd.social_anxiety == 0 &
               mhd.panic_disorder == 0 ~ 0,
               mhd.gad == 1 | 
               mhd.specific_phobia == 1 |
               mhd.social_anxiety == 1 |
               mhd.panic_disorder == 1 ~ 1)
         ) %>% 
  summarize(MDD = sum(mhd.mdd, na.rm = T),
            MDD_prop = sum(mhd.mdd, na.rm = T)/sum(!is.na(mhd.mdd)),
            AnyAnx = sum(any_anxiety, na.rm = T),
            AnyAnx_prop = sum(any_anxiety, na.rm = T)/sum(!is.na(any_anxiety)),
            GAD = sum(mhd.gad, na.rm = T),
            GAD_prop = sum(mhd.gad, na.rm = T)/sum(!is.na(mhd.gad)),
            SPEC = sum(mhd.specific_phobia, na.rm = T),
            SPEC_prop = sum(mhd.specific_phobia, na.rm = T)/sum(!is.na(mhd.specific_phobia)),
            SOCP = sum(mhd.social_anxiety, na.rm = T),
            SOCP_prop = sum(mhd.social_anxiety, na.rm = T)/sum(!is.na(mhd.social_anxiety)),
            PAD = sum(mhd.panic_disorder, na.rm = T),
            PAD_prop = sum(mhd.panic_disorder, na.rm = T)/sum(!is.na(mhd.panic_disorder)),
            None = sum(no_diagnosis, na.rm = T),
            None_prop = sum(no_diagnosis, na.rm = T)/sum(!is.na(mhd.mdd) & !is.na(any_anxiety)),
            total = n()) %>% 
  mutate(sample = "Full sample")

#by cohort
agp_alt_totals_by_cohort <- agp_alt.df %>% 
  group_by(sample) %>% 
  mutate(no_diagnosis = 
           case_when(
             mhd.mdd == 0 & 
               mhd.gad == 0 & 
               mhd.specific_phobia == 0 &
               mhd.social_anxiety == 0 &
               mhd.panic_disorder == 0 ~ 1,
             mhd.mdd == 1 | 
               mhd.gad == 1 | 
               mhd.specific_phobia == 1 |
               mhd.social_anxiety == 1 |
               mhd.panic_disorder == 1 ~ 0
           ),
         any_anxiety = case_when( 
               mhd.gad == 0 & 
               mhd.specific_phobia == 0 &
               mhd.social_anxiety == 0 &
               mhd.panic_disorder == 0 ~ 0,
               mhd.gad == 1 | 
               mhd.specific_phobia == 1 |
               mhd.social_anxiety == 1 |
               mhd.panic_disorder == 1 ~ 1)
         ) %>% 
  summarize(MDD = sum(mhd.mdd, na.rm = T),
            MDD_prop = sum(mhd.mdd, na.rm = T)/sum(!is.na(mhd.mdd)),
            AnyAnx = sum(any_anxiety, na.rm = T),
            AnyAnx_prop = sum(any_anxiety, na.rm = T)/sum(!is.na(any_anxiety)),
            GAD = sum(mhd.gad, na.rm = T),
            GAD_prop = sum(mhd.gad, na.rm = T)/sum(!is.na(mhd.gad)),
            SPEC = sum(mhd.specific_phobia, na.rm = T),
            SPEC_prop = sum(mhd.specific_phobia, na.rm = T)/sum(!is.na(mhd.specific_phobia)),
            SOCP = sum(mhd.social_anxiety, na.rm = T),
            SOCP_prop = sum(mhd.social_anxiety, na.rm = T)/sum(!is.na(mhd.social_anxiety)),
            PAD = sum(mhd.panic_disorder, na.rm = T),
            PAD_prop = sum(mhd.panic_disorder, na.rm = T)/sum(!is.na(mhd.panic_disorder)),
            None = sum(no_diagnosis, na.rm = T),
            None_prop = sum(no_diagnosis, na.rm = T)/sum(!is.na(mhd.mdd) & !is.na(any_anxiety)),
            total = n()) %>% 
  mutate(sample = 
           case_when(
             sample == "GLAD" ~ "GLAD",
             sample == "NBR" ~ "COPING NBR"
           ))

#merge full sample and by cohort
agp_alt_totals <- rbind(agp_alt_totals_full_sample,
                        agp_alt_totals_by_cohort)

agp_alt_totals

agp_alt_totals.long <- agp_alt_totals %>%
  select(-c(MDD, AnyAnx, GAD, SPEC, SOCP, PAD, None, total)) %>% 
  pivot_longer(cols = c(MDD_prop, AnyAnx_prop, GAD_prop, SPEC_prop, SOCP_prop, PAD_prop, None_prop)) %>% 
  #pivot_wider(names_from = sample, values_from = value) %>% 
  mutate(name = 
           as.factor(case_when(
             name == "MDD_prop" ~ "MDD",
             name == "AnyAnx_prop" ~ "Any anxiety",
             name == "GAD_prop" ~ "GAD",
             name == "SPEC_prop" ~ "Specific phobia",
             name == "SOCP_prop" ~ "Social anxiety disorder",
             name == "PAD_prop" ~ "Panic disorder",
             name == "None_prop" ~ "No diagnosis"
           ))
  )

agp_alt_totals.long$name <- fct_relevel(agp_alt_totals.long$name, "MDD", "Any anxiety", "GAD", "Specific phobia", "Social anxiety disorder", "Panic disorder", "No diagnosis")

agp_alt_totals.long$sample <- fct_relevel(agp_alt_totals.long$sample, "Full sample", "GLAD", "COPING NBR")

agp_alt_totals.long
```

```{r agp graph alternate diagnoses}

## Graph of alternate algorithm-based diagnoses for participants with algorithm-based but no single-item agoraphobia

agp_alt_si_diagnoses_barchart <- ggplot(agp_alt_totals.long, aes(x = name, y = value, fill = sample, label = paste(round(value*100, 2), "%", sep = " "))) + 
  labs(x = "Single-item diagnosis", 
       y = element_blank(), 
       fill = "Cohort",
       color="black",
       title = "Agoraphobia",
       subtitle = paste0("N = ", nrow(agp_alt.df), 
                         " (GLAD: ", sum(agp_alt.df$sample == "GLAD"),
                         "; COPING NBR: ", sum(agp_alt.df$sample == "NBR"), ")")) +
  theme(plot.subtitle = element_text(face = "italic"),
        axis.text.x = element_text(color="black",
                                   #angle = 25, 
                                   size = 8), 
                                   #hjust = 1),
        axis.title.x = element_text(color = "black",
                                    size = 8,
                                    vjust = -2),
        axis.title.y = element_text(color = "black",
                                    size = 8),
        axis.ticks = element_blank(),
        axis.text.y = element_text(colour="black", 
                                   size = 8),
        panel.grid.major.y = element_line(size = 0.5,
                                        linetype = 'dashed',
                                        colour = "light blue"),
        panel.background = element_rect(color = "light blue", fill = "white"),
        plot.margin = margin(10, 10, 10, 10)) +   
  scale_color_manual(values = GLADpalette) +
  scale_fill_manual(values = GLADpalette) +
  geom_bar(stat = 'identity', position = 'dodge') +
  geom_text(aes(label = paste0(round(value*100, 2), "%")), 
            position = position_dodge(width = 0.95),
            vjust = -0.5,
            size = 3
            ) +
  scale_y_continuous(limits = c(0, 1), #Y-axis goes from 0-1
                     breaks=seq(0,1, 0.1), #Y-axis goes from 0 - 1, with tick marks every 0.1
                     labels = scales::percent_format(accuracy = 5L), #Makes y-axis % and removes decimals
                     expand = c(0,0))

agp_alt_si_diagnoses_barchart
```

## Combine alternate SI diagnoses graphs

```{r combine alternate si diagnosis graphs}
#install.packages("patchwork")
#library(patchwork)

all_alt_si_diagnoses_barchart <- ((spec_alt_si_diagnoses_barchart + 
    theme(legend.position = "none", 
          axis.title.x = element_blank(),
          title = element_text(size = 10),
          axis.text = element_text(size = 10)) +
    labs(title = "Specific phobia")
  ) |
  (socp_alt_si_diagnoses_barchart + 
     theme(legend.position = "none", 
           axis.title.x = element_blank(),
           title = element_text(size = 10)) +
     labs(title = "Social anxiety disorder"))) / 
  ((pad_alt_si_diagnoses_barchart + 
      theme(legend.position = "none",
           title = element_text(size = 10)) +
     labs(title = "Panic disorder")) |
  (agp_alt_si_diagnoses_barchart + 
     theme(title = element_text(size = 10)) +
     labs(title = "Agoraphobia"))) +
  plot_layout(guides = "collect", heights = c(10,10), widths = c(20,20))

all_alt_si_diagnoses_barchart

```

```{r save all alternate si diagnosis barchart}
grDevices::dev.set(1)
#Save jpeg of diagnosis barchart
ggsave(paste0("all_alt_si_diagnoses_barchart_subtitle_", Sys.Date(), ".jpeg"),
       path = "/Users/mollydavies/OneDrive - King's College London/PhD/GLAD Diagnosis paper/Figures/2021-04 SECOND SUBMISSION",
       plot = all_alt_si_diagnoses_barchart,
       width = 20,
       height = 10,
       dpi = 150,
       units = "in")

#Save tiff of diagnosis barchart
ggsave(paste0("all_alt_si_diagnoses_barchart_", Sys.Date(), ".tiff"),
       path = "/Users/mollydavies/OneDrive - King's College London/PhD/GLAD Diagnosis paper/Figures/2021-04 SECOND SUBMISSION",
       plot = all_alt_si_diagnoses_barchart,
       width = 10,
       height = 20,
       dpi = 150,
       units = "in")
```

**Supplementary materials**

# Analyses of difference

## GLAD vs COPING sample characteristics
    Cohort as grouping variable with the different characteristics
    Chi-square if dichotomous; independent t-test for continuous variables

Indendent samples t-test to assess differences in age between GLAD vs COPING cohorts
```{r t-test age}
t_test_age_by_cohort <- cidi %>%
  t_test(
    age ~ sample,
    order = c("GLAD", "NBR"),
    alternative = "two.sided"
) %>% 
  select(c(statistic, p_value)) %>% 
  mutate(characteristic = "age",
         test = "t-test")

t_test_age_by_cohort
```


Chi-square tests to assess differences between GLAD vs COPING cohorts in:
- Sex
- Ethnicity
- Highest education

```{r chi-square sex}
chisq_sex_by_cohort <- cidi %>% 
  mutate(sex = as.factor(sex)) %>% 
  chisq_test(sex ~ sample) %>% 
  select(c(statistic, p_value)) %>% 
  mutate(characteristic = "sex",
         test = "chi-squared")

chisq_sex_by_cohort
```

```{r chi-square ethnicity}
chisq_ethnicity_by_cohort <- cidi %>% 
  chisq_test(Ethnicity ~ sample) %>%  
  select(c(statistic, p_value)) %>% 
  mutate(characteristic = "ethnicity",
         test = "chi-squared")

chisq_ethnicity_by_cohort
```

```{r chi-square highest education}
chisq_education_by_cohort <- cidi %>% 
  chisq_test(highest_education ~ sample) %>%  
  select(c(statistic, p_value)) %>% 
  mutate(characteristic = "education",
         test = "chi-squared")

chisq_education_by_cohort
```

```{r table of all variance analyses by cohort}
comparisons_by_cohort <- rbind(
  t_test_age_by_cohort,
  chisq_sex_by_cohort,
  chisq_ethnicity_by_cohort,
  chisq_education_by_cohort
) %>% 
  relocate(c(test, characteristic))

kable(comparisons_by_cohort)
```


## Male vs female diagnostic agreements
    Chi-square test (Female: Yes/No)

```{r recode agreements as factors}
dat.sex <- cidi %>% 
  mutate(mdd_agreement_binary_numeric = as.factor(
    case_when(
      cidid.diagnosis_numeric == 1 & mhd.mdd == 1 ~ 0,
      cidid.diagnosis_numeric == 0 & mhd.mdd == 0 ~ 0,
      cidid.diagnosis_numeric == 0 & mhd.mdd == 1 ~ 1,
      cidid.diagnosis_numeric == 1 & mhd.mdd == 0 ~ 0
    )),
    anyanx_agreement_binary_numeric = as.factor(
    case_when(
      LifetimeAnyAnx.n == 1 & ClinicianAnyAnx.n == 1 ~ 0,
      LifetimeAnyAnx.n == 0 & ClinicianAnyAnx.n == 0 ~ 0,
      LifetimeAnyAnx.n == 0 & ClinicianAnyAnx.n == 1 ~ 1,
      LifetimeAnyAnx.n == 1 & ClinicianAnyAnx.n == 0 ~ 0,
    )),
    gad_agreement_binary_numeric = as.factor(
    case_when(
      cidia.diagnosis_numeric == 1 & mhd.gad == 1 ~ 0,
      cidia.diagnosis_numeric == 0 & mhd.gad == 0 ~ 0,
      cidia.diagnosis_numeric == 0 & mhd.gad == 1 ~ 1,
      cidia.diagnosis_numeric == 1 & mhd.gad == 0 ~ 0
    )),
    spec_agreement_binary_numeric = as.factor(
    case_when(
      spec.diagnosis_numeric == 1 & mhd.specific_phobia == 1 ~ 0,
      spec.diagnosis_numeric == 0 & mhd.specific_phobia == 0 ~ 0,
      spec.diagnosis_numeric == 0 & mhd.specific_phobia == 1 ~ 1,
      spec.diagnosis_numeric == 1 & mhd.specific_phobia == 0 ~ 0
    )),
    socp_agreement_binary_numeric = as.factor(
    case_when(
      socp.diagnosis_numeric == 1 & mhd.social_anxiety == 1 ~ 0,
      socp.diagnosis_numeric == 0 & mhd.social_anxiety == 0 ~ 0,
      socp.diagnosis_numeric == 0 & mhd.social_anxiety == 1 ~ 1,
      socp.diagnosis_numeric == 1 & mhd.social_anxiety == 0 ~ 0
    )),
    pattacks_agreement_binary_numeric = as.factor(
    case_when(
      pad.diagnosis_numeric == 1 & mhd.panic_attacks == 1 & !is.na(mhd.panic_disorder) ~ 0,
      pad.diagnosis_numeric == 0 & mhd.panic_attacks == 0 & !is.na(mhd.panic_disorder) ~ 0,
      pad.diagnosis_numeric == 0 & mhd.panic_attacks == 1 & !is.na(mhd.panic_disorder) ~ 1,
      pad.diagnosis_numeric == 1 & mhd.panic_attacks == 0 & !is.na(mhd.panic_disorder) ~ 0
    )),
    pad_agreement_binary_numeric = as.factor(
    case_when(
      pad.diagnosis_numeric == 1 & mhd.panic_disorder == 1 ~ 0,
      pad.diagnosis_numeric == 0 & mhd.panic_disorder == 0 ~ 0,
      pad.diagnosis_numeric == 0 & mhd.panic_disorder == 1 ~ 1,
      pad.diagnosis_numeric == 1 & mhd.panic_disorder == 0 ~ 0
    )),
    agp_agreement_binary_numeric = as.factor(
    case_when(
      agp.diagnosis_numeric == 1 & mhd.agoraphobia == 1 ~ 0,
      agp.diagnosis_numeric == 0 & mhd.agoraphobia == 0 ~ 0,
      agp.diagnosis_numeric == 0 & mhd.agoraphobia == 1 ~ 1,
      agp.diagnosis_numeric == 1 & mhd.agoraphobia == 0 ~ 0
    )),
    mdd_agreement_numeric = as.factor(
    case_when(
      cidid.diagnosis_numeric == 1 & mhd.mdd == 1 ~ 0,
      cidid.diagnosis_numeric == 0 & mhd.mdd == 0 ~ 1,
      cidid.diagnosis_numeric == 0 & mhd.mdd == 1 ~ 2,
      cidid.diagnosis_numeric == 1 & mhd.mdd == 0 ~ 3
    )),
    anyanx_agreement_numeric = as.factor(
    case_when(
      LifetimeAnyAnx.n == 1 & ClinicianAnyAnx.n == 1 ~ 0,
      LifetimeAnyAnx.n == 0 & ClinicianAnyAnx.n == 0 ~ 1,
      LifetimeAnyAnx.n == 0 & ClinicianAnyAnx.n == 1 ~ 2,
      LifetimeAnyAnx.n == 1 & ClinicianAnyAnx.n == 0 ~ 3,
    )),
    gad_agreement_numeric = as.factor(
    case_when(
      cidia.diagnosis_numeric == 1 & mhd.gad == 1 ~ 0,
      cidia.diagnosis_numeric == 0 & mhd.gad == 0 ~ 1,
      cidia.diagnosis_numeric == 0 & mhd.gad == 1 ~ 2,
      cidia.diagnosis_numeric == 1 & mhd.gad == 0 ~ 3
    )),
    spec_agreement_numeric = as.factor(
    case_when(
      spec.diagnosis_numeric == 1 & mhd.specific_phobia == 1 ~ 0,
      spec.diagnosis_numeric == 0 & mhd.specific_phobia == 0 ~ 1,
      spec.diagnosis_numeric == 0 & mhd.specific_phobia == 1 ~ 2,
      spec.diagnosis_numeric == 1 & mhd.specific_phobia == 0 ~ 3
    )),
    socp_agreement_numeric = as.factor(
    case_when(
      socp.diagnosis_numeric == 1 & mhd.social_anxiety == 1 ~ 0,
      socp.diagnosis_numeric == 0 & mhd.social_anxiety == 0 ~ 1,
      socp.diagnosis_numeric == 0 & mhd.social_anxiety == 1 ~ 2,
      socp.diagnosis_numeric == 1 & mhd.social_anxiety == 0 ~ 3
    )),
    pattacks_agreement_numeric = as.factor(
    case_when(
      pad.diagnosis_numeric == 1 & mhd.panic_attacks == 1 & !is.na(mhd.panic_disorder) ~ 0,
      pad.diagnosis_numeric == 0 & mhd.panic_attacks == 0 & !is.na(mhd.panic_disorder) ~ 1,
      pad.diagnosis_numeric == 0 & mhd.panic_attacks == 1 & !is.na(mhd.panic_disorder) ~ 2,
      pad.diagnosis_numeric == 1 & mhd.panic_attacks == 0 & !is.na(mhd.panic_disorder) ~ 3
    )),
    pad_agreement_numeric = as.factor(
    case_when(
      pad.diagnosis_numeric == 1 & mhd.panic_disorder == 1 ~ 0,
      pad.diagnosis_numeric == 0 & mhd.panic_disorder == 0 ~ 1,
      pad.diagnosis_numeric == 0 & mhd.panic_disorder == 1 ~ 2,
      pad.diagnosis_numeric == 1 & mhd.panic_disorder == 0 ~ 3
    )),
    agp_agreement_numeric = as.factor(
    case_when(
      agp.diagnosis_numeric == 1 & mhd.agoraphobia == 1 ~ 0,
      agp.diagnosis_numeric == 0 & mhd.agoraphobia == 0 ~ 1,
      agp.diagnosis_numeric == 0 & mhd.agoraphobia == 1 ~ 2,
      agp.diagnosis_numeric == 1 & mhd.agoraphobia == 0 ~ 3
    ))
  ) %>% 
  select(c(sex, mdd_agreement_binary_numeric, anyanx_agreement_binary_numeric, 
           gad_agreement_binary_numeric, spec_agreement_binary_numeric, socp_agreement_binary_numeric,
           pattacks_agreement_binary_numeric, pad_agreement_binary_numeric, agp_agreement_binary_numeric,
           mdd_agreement_numeric, anyanx_agreement_numeric, 
           gad_agreement_numeric, spec_agreement_numeric, socp_agreement_numeric,
           pattacks_agreement_numeric, pad_agreement_numeric, agp_agreement_numeric))
  
```

## Fine-grained agreement

```{r chi-square test MDD agreement by sex}
chisq_mdd_agreement_by_sex <- dat.sex %>%
  mutate(sex = as.factor(sex)) %>% 
  chisq_test(mdd_agreement_numeric ~ sex) %>% 
  mutate(disorder = "MDD")

chisq_mdd_agreement_by_sex
```

```{r chi-square test AnyAnx agreement by sex}
chisq_anyanx_agreement_by_sex <- dat.sex %>%
  mutate(sex = as.factor(sex)) %>% 
  chisq_test(anyanx_agreement_numeric ~ sex) %>% 
  mutate(disorder = "Any anxiety")

chisq_anyanx_agreement_by_sex
```

```{r chi-square test GAD agreement by sex}
chisq_gad_agreement_by_sex <- dat.sex %>%
  mutate(sex = as.factor(sex)) %>% 
  chisq_test(gad_agreement_numeric ~ sex) %>% 
  mutate(disorder = "GAD")

chisq_gad_agreement_by_sex
```


```{r chi-square test SPEC agreement by sex}
chisq_spec_agreement_by_sex <- dat.sex %>%
  mutate(sex = as.factor(sex)) %>% 
  chisq_test(spec_agreement_numeric ~ sex) %>% 
  mutate(disorder = "Specific phobia")

chisq_spec_agreement_by_sex
```

```{r chi-square test SOCP agreement by sex}
chisq_socp_agreement_by_sex <- dat.sex %>%
  mutate(sex = as.factor(sex)) %>% 
  chisq_test(socp_agreement_numeric ~ sex) %>% 
  mutate(disorder = "Social phobia")

chisq_socp_agreement_by_sex
```

```{r chi-square test PanicAttacks agreement by sex}
chisq_pattacks_agreement_by_sex <- dat.sex %>%
  mutate(sex = as.factor(sex)) %>% 
  chisq_test(pattacks_agreement_numeric ~ sex) %>% 
  mutate(disorder = "Panic attacks")

chisq_pattacks_agreement_by_sex
```

```{r chi-square test PAD agreement by sex}
chisq_pad_agreement_by_sex <- dat.sex %>%
  mutate(sex = as.factor(sex)) %>% 
  chisq_test(pad_agreement_numeric ~ sex) %>% 
  mutate(disorder = "Panic disorder")

chisq_pad_agreement_by_sex
```

```{r chi-square test AGP agreement by sex}
chisq_agp_agreement_by_sex <- dat.sex %>%
  mutate(sex = as.factor(sex)) %>% 
  chisq_test(agp_agreement_numeric ~ sex) %>% 
  mutate(disorder = "Agoraphobia")

chisq_agp_agreement_by_sex
```

```{r combine all fine-grained chi-squared agreement tables}

chisq_all_agreement_by_sex <- rbind(chisq_mdd_agreement_by_sex,
                                    chisq_anyanx_agreement_by_sex,
                                    chisq_gad_agreement_by_sex,
                                    chisq_spec_agreement_by_sex,
                                    chisq_socp_agreement_by_sex,
                                    chisq_pattacks_agreement_by_sex,
                                    chisq_pad_agreement_by_sex,
                                    chisq_agp_agreement_by_sex) %>% 
  relocate(disorder)

kable(chisq_all_agreement_by_sex)

```


## Binary agreement
```{r chi-square test MDD binary agreement by sex}
chisq_mdd_agreement_binary_by_sex <- dat.sex %>%
  mutate(sex = as.factor(sex)) %>% 
  chisq_test(mdd_agreement_binary_numeric ~ sex) %>% 
  mutate(disorder = "MDD")

chisq_mdd_agreement_binary_by_sex
```

```{r chi-square test AnyAnx binary agreement by sex}
chisq_anyanx_agreement_binary_by_sex <- dat.sex %>%
  mutate(sex = as.factor(sex)) %>% 
  chisq_test(anyanx_agreement_binary_numeric ~ sex) %>% 
  mutate(disorder = "Any anxiety")

chisq_anyanx_agreement_binary_by_sex
```

```{r chi-square test GAD binary agreement by sex}
chisq_gad_agreement_binary_by_sex <- dat.sex %>%
  mutate(sex = as.factor(sex)) %>% 
  chisq_test(gad_agreement_binary_numeric ~ sex) %>% 
  mutate(disorder = "GAD")

chisq_gad_agreement_binary_by_sex
```

```{r chi-square test SPEC binary agreement by sex}
chisq_spec_agreement_binary_by_sex <- dat.sex %>%
  mutate(sex = as.factor(sex)) %>% 
  chisq_test(spec_agreement_binary_numeric ~ sex) %>% 
  mutate(disorder = "Specific phobia")

chisq_spec_agreement_binary_by_sex
```

```{r chi-square test SOCP binary agreement by sex}
chisq_socp_agreement_binary_by_sex <- dat.sex %>%
  mutate(sex = as.factor(sex)) %>% 
  chisq_test(socp_agreement_binary_numeric ~ sex) %>% 
  mutate(disorder = "Social anxiety disorder")

chisq_socp_agreement_binary_by_sex
```

```{r chi-square test PanicAttacks binary agreement by sex}
chisq_pattacks_agreement_binary_by_sex <- dat.sex %>%
  mutate(sex = as.factor(sex)) %>% 
  chisq_test(pattacks_agreement_binary_numeric ~ sex) %>% 
  mutate(disorder = "Panic attacks")

chisq_pattacks_agreement_binary_by_sex
```

```{r chi-square test PAD binary agreement by sex}
chisq_pad_agreement_binary_by_sex <- dat.sex %>%
  mutate(sex = as.factor(sex)) %>% 
  chisq_test(pad_agreement_binary_numeric ~ sex) %>% 
  mutate(disorder = "Panic disorder")

chisq_pad_agreement_binary_by_sex
```

```{r chi-square test AGP binary agreement by sex}
chisq_agp_agreement_binary_by_sex <- dat.sex %>%
  mutate(sex = as.factor(sex)) %>% 
  chisq_test(agp_agreement_binary_numeric ~ sex) %>% 
  mutate(disorder = "Agoraphobia")

chisq_agp_agreement_binary_by_sex
```

```{r combine all binary chi-squared agreement tables}

chisq_all_agreement_binary_by_sex <- rbind(chisq_mdd_agreement_binary_by_sex,
                                           chisq_anyanx_agreement_binary_by_sex,
                                           chisq_gad_agreement_binary_by_sex,
                                           chisq_spec_agreement_binary_by_sex,
                                           chisq_socp_agreement_binary_by_sex,
                                           chisq_pattacks_agreement_binary_by_sex,
                                           chisq_pad_agreement_binary_by_sex,
                                           chisq_agp_agreement_binary_by_sex) %>% 
  relocate(disorder)

kable(chisq_all_agreement_binary_by_sex)

```

# Missing data 

## Table of missing data for each variable

```{r table of missing data}
na_count <- as.data.frame(colSums(is.na(cidi))) %>% 
  rownames_to_column() %>% 
  rename("variable" = "rowname",
         "NA Count" = "colSums(is.na(cidi))") %>% 
  filter(variable == "Ethnicity" | 
                       variable == "highest_education" | 
                       variable == "Employment" |
                       variable == "mhd.mdd" |
                       variable == "mhd.gad" |
                       variable == "mhd.specific_phobia" |
                       variable == "mhd.social_anxiety" |
                       variable == "mhd.panic_attacks" |
                       variable == "mhd.panic_disorder" |
                       variable == "mhd.agoraphobia" |
                       variable == "ClinicianAnyAnx.n" |
                       variable == "cidid.diagnosis_numeric" |
                       variable == "cidia.diagnosis_numeric" |
                       variable == "spec.diagnosis_numeric" |
                       variable == "socp.diagnosis_numeric" |
                       variable == "pad.diagnosis_numeric" |
                       variable == "agp.diagnosis_numeric" |
                       variable == "LifetimeAnyAnx.n") %>% 
  mutate(variable = 
           case_when(
             variable == "Ethnicity" ~ "Ethnicity", 
             variable == "highest_education" ~ "Highest education", 
             variable == "Employment" ~ "Employment",
             variable == "mhd.mdd" ~ "Single-item MDD",
             variable == "mhd.gad" ~ "Single-item GAD",
             variable == "mhd.specific_phobia" ~ "Single-item specific phobia",
             variable == "mhd.social_anxiety" ~ "Single-item social anxiety disorder",
             variable == "mhd.panic_attacks" ~ "Single-item panic attacks",
             variable == "mhd.panic_disorder" ~ "Single-item panic disorder",
             variable == "mhd.agoraphobia" ~ "Single-item agoraphobia",
             variable == "ClinicianAnyAnx.n" ~ "Single-item any anxiety",
             variable == "cidid.diagnosis_numeric" ~ "Algorithm-based MDD",
             variable == "cidia.diagnosis_numeric" ~ "Algorithm-based GAD",
             variable == "spec.diagnosis_numeric" ~ "Algorithm-based specific phobia",
             variable == "socp.diagnosis_numeric" ~ "Algorithm-based social anxiety disorder",
             variable == "pad.diagnosis_numeric" ~ "Algorithm-based panic disorder",
             variable == "agp.diagnosis_numeric" ~ "Algorithm-based agoraphobia",
             variable == "LifetimeAnyAnx.n" ~ "Algorithm-based any anxiety"
           ))

kable(na_count)
```

## Associations with missing data

```{r set-up for missing data associations}
#install.packages("finalfit")
library(finalfit)

#Set explanatory variables
explanatory = c("age", "sex", 
  "highest_education",  
  "Ethnicity")

```

```{r associations with AB MDD}
#Algorithm-based
missing_cidid <- dat %>% 
  missing_compare("cidid.diagnosis", explanatory) %>% 
  mutate(diagnosis = "MDD",
         method = "Algorithm-based")

kable(missing_cidid)
```

```{r associations with SI MDD}
#Single-item
missing_mhd.mdd <- dat %>% 
  missing_compare("mhd.mdd", explanatory) %>% 
  mutate(diagnosis = "MDD",
         method = "Single-item")

kable(missing_mhd.mdd)
```

```{r associations with AB GAD}
#Algorithm-based
missing_cidia <- dat %>% 
  missing_compare("cidia.diagnosis", explanatory) %>% 
  mutate(diagnosis = "GAD",
         method = "Algorithm-based")

kable(missing_cidia)
```

```{r associations with SI GAD}
#Single-item
missing_mhd.gad <- dat %>% 
  missing_compare("mhd.gad", explanatory) %>% 
  mutate(diagnosis = "GAD",
         method = "Single-item")

kable(missing_mhd.gad)
```

```{r associations with AB SPEC}
#Algorithm-based
missing_spec <- dat %>% 
  missing_compare("spec.diagnosis", explanatory) %>% 
  mutate(diagnosis = "Specific phobia",
         method = "Algorithm-based")

kable(missing_spec)
```

```{r associations with SI SPEC}
#Single-item
missing_mhd.specific_phobia <- dat %>% 
  missing_compare("mhd.specific_phobia", explanatory) %>% 
  mutate(diagnosis = "Specific phobia",
         method = "Single-item")

kable(missing_mhd.specific_phobia)
```

```{r associations with AB SOCP}
#Algorithm-based
missing_socp <- dat %>% 
  missing_compare("socp.diagnosis", explanatory) %>% 
  mutate(diagnosis = "Social anxiety disorder",
         method = "Algorithm-based")

kable(missing_socp)
```

```{r associations with SI SOCP}
#Single-item
missing_mhd.social_anxiety <- dat %>% 
  missing_compare("mhd.social_anxiety", explanatory)%>% 
  mutate(diagnosis = "Social anxiety disorder",
         method = "Single-item")

kable(missing_mhd.social_anxiety)
```

```{r associations with AB PAD}
#Algorithm-based
missing_pad <- dat %>% 
  missing_compare("pad.diagnosis", explanatory) %>% 
  mutate(diagnosis = "Panic disorder",
         method = "Algorithm-based")

kable(missing_pad)
```

```{r associations with SI PAD}
#Single-item
missing_mhd.panic_disorder <- dat %>% 
  missing_compare("mhd.panic_disorder", explanatory) %>% 
  mutate(diagnosis = "Panic disorder",
         method = "Single-item")

kable(missing_mhd.panic_disorder)
```

```{r associations with SI Panic Attacks}
#Single-item
missing_mhd.panic_attacks <- dat %>% 
  missing_compare("mhd.panic_attacks", explanatory) %>% 
  mutate(diagnosis = "Panic attacks",
         method = "Single-item")

kable(missing_mhd.panic_attacks)
```

```{r associations with AB AGP}
#Algorithm-based
missing_agp <- dat %>% 
  missing_compare("agp.diagnosis", explanatory) %>% 
  mutate(diagnosis = "Agoraphobia",
         method = "Algorithm-based")

kable(missing_agp)
```

```{r associations with SI AGP}
#Single-item
missing_mhd.agoraphobia <- dat %>% 
  missing_compare("mhd.agoraphobia", explanatory) %>% 
  mutate(diagnosis = "Agoraphobia",
         method = "Single-item")

kable(missing_mhd.agoraphobia)
```

```{r combine all missing data association tables}
#missing_all_associations <- rbind(missing_cidid,
#                                  missing_mhd.mdd,
#                                  missing_cidia,
#                                  missing_mhd.gad,
#                                  missing_spec,
#                                  missing_mhd.specific_phobia,
#                                  missing_socp,
#                                  missing_mhd.social_anxiety,
#                                  missing_pad,
#                                  missing_mhd.panic_attacks,
#                                  missing_mhd.panic_disorder,
#                                  missing_agp,
#                                  missing_mhd.agoraphobia)
#
#missing_all_associations
```

## Associations with NA counts

```{r NA algorithm-based diagnosis count}

cidi$algorithm_based_na_count<-0

cidi$algorithm_based_na_count<-with(cidi, 
                                    ifelse(is.na(cidid.diagnosis_numeric), 
                                           algorithm_based_na_count + 1, algorithm_based_na_count))

cidi$algorithm_based_na_count<-with(cidi,
                                    ifelse(is.na(cidia.diagnosis_numeric),
                                           algorithm_based_na_count + 1, algorithm_based_na_count))

cidi$algorithm_based_na_count<-with(cidi,
                                    ifelse(is.na(spec.diagnosis_numeric),
                                           algorithm_based_na_count + 1, algorithm_based_na_count))

cidi$algorithm_based_na_count<-with(cidi, 
                                    ifelse(is.na(socp.diagnosis_numeric), 
                                           algorithm_based_na_count + 1, algorithm_based_na_count))

cidi$algorithm_based_na_count<-with(cidi, 
                                    ifelse(is.na(pad.diagnosis_numeric), 
                                           algorithm_based_na_count + 1, algorithm_based_na_count))

cidi$algorithm_based_na_count<-with(cidi, 
                                    ifelse(is.na(agp.diagnosis_numeric), 
                                           algorithm_based_na_count + 1, algorithm_based_na_count))

kable(freq(cidi$algorithm_based_na_count))
```

Note that due to the formatting of the single-item diagnoses in the survey, participants are either missing all or none of the single-item disorder data. Therefore, the single-item NA count variable is created using only one single-item diagnosis to reflect the missingness as a binary variable (0 = no missing data, 1 = all missing data).

The exception is panic disorder, which was added partway through data collection. As a result, panic disorder is not considered here.
```{r NA single-item diagnosis count}

cidi$single_item_na_count<-0

cidi$single_item_na_count<-with(cidi, 
                                    ifelse(is.na(mhd.mdd), 
                                           single_item_na_count + 1, single_item_na_count))

freq(cidi$single_item_na_count)
```

```{r get package for regression summary tables}
#install.packages("gtsummary")
library(gtsummary)
```


```{r calculating associations with AB missingness}
algorithm_missingness_associations <- lm(algorithm_based_na_count ~ age + sex + Ethnicity + highest_education, data = cidi)

summary(algorithm_missingness_associations)
tbl_regression(algorithm_missingness_associations)
```

```{r calculating associations with SI missingness}
single_item_missingness_associations <- lm(single_item_na_count ~ age + sex + Ethnicity + highest_education, data = cidi)

summary(single_item_missingness_associations)
tbl_regression(single_item_missingness_associations)
```