---
title: "DIAGCOMP_DEM_cleaning"
author: "Molly R. Davies"
date: "30/10/2020"
output: html_document
---

This is the cleaning script for the demographic (DEM) variables of the GLAD Study sample for the paper titled "Comparison of algorithm-based versus single-item phenotyping measures of depression and anxiety disorders in the GLAD Study cohort" - Davies et al (in prep).

Script written by M. R. Davies.
Email:  molly.davies@kcl.ac.uk

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Set up

Clear workspace
```{r clear workspace}
rm(list = ls())
```

```{r load packages}
library(tidyverse)
library(psych)
library(summarytools)
```

```{r source path for reading/saving data}
#Source raw data directory (raw_path) & clean data export directory (cleaned_path)
source("../GLAD_data_path.R")
```

```{r read in cleaned SOCP data}
DEM_file <- paste(raw_path, "DEM.rds", sep = "")

DEM.cc <- read_rds(DEM_file)
```

```{r select variables}
DEM.items <- DEM.cc %>% 
  select(ID,
         age,
         sex,
         dem.university_numeric,
         dem.alevels_numeric,
         dem.gcse_numeric,
         dem.cse_numeric,
         dem.NVQ_numeric,
         dem.education_other_numeric,
         dem.NVQ,
         dem.education_other,
         dem.ethnicity_numeric,
         dem.employment,
         dem.employment_numeric
         )
```

```{r recode as NAs}
#Change all prefer not to answers and don't knows to NA
DEM.items[DEM.items == -77] <- NA
DEM.items[DEM.items == -88] <- NA
DEM.items[DEM.items == -99] <- NA
DEM.items[DEM.items == "Don't know"] <- NA
DEM.items[DEM.items == "Prefer not to answer"] <- NA
DEM.items[DEM.items == "Seen but not answered"] <- NA
```

```{r add unc to column names}
colnames(DEM.items) <- paste(colnames(DEM.items), "unc", sep = ".")
```

```{r visualise demographics data}
head(DEM.items)
```

# Age

## Average age (in text, Sample Descriptors section)

```{r checking outliers: density plot Age}
##Get summary to see range
summary(DEM.items$age.unc)

## Create a variable for the mean to add the mean line in the graph
age.clean <- DEM.items$age.unc
m <- mean(age.clean, na.rm = TRUE)

## Create version of dataset with only unique column names (to fix an error with ggplot)
DEM.items.plot <- DEM.items
colnames(DEM.items.plot) <- make.unique(names(DEM.items.plot))

## Create a density plot of Age, with a mean line

adens <- ggplot(data = DEM.items.plot, aes(x=age.unc, color="variable")) +
  geom_density() +
  scale_x_continuous(limits = c(0.00, 105)) +
  geom_vline(xintercept=mean(m),
             color="blue", size=1) +
  scale_color_manual(values = "#E69F00")

adens

## Alternatively, you can just tell R that the dataset contains NA so it can properly calculate the mean
## You can also add lines around the SD

adens.imp <- ggplot(DEM.items.plot, aes(x=age.unc, color="variable")) +
  geom_density() +
  scale_color_manual(values = "#E69F00") +
  scale_x_continuous(limits = c(0.00, 105)) +
  geom_vline(xintercept = mean(DEM.items.plot$age.unc, na.rm = T), 
             color = "blue") +  
  geom_vline(xintercept = mean(DEM.items.plot$age.unc, na.rm = T) + sd(DEM.items.plot$age.unc, na.rm = T),
             color = "blue",
             linetype = "dashed") +
  geom_vline(xintercept = mean(DEM.items.plot$age.unc, na.rm = T) - sd(DEM.items.plot$age.unc, na.rm = T),
             color = "blue",
             linetype = "dashed")

print(adens.imp)
```

```{r checking outliers: Scatterplot}

ggplot(data = subset(DEM.items.plot, !is.na(age.unc)),
       aes(x = seq_along(age.unc), y = age.unc)) +
       geom_point(color="grey") +
  labs(x = "Index",
       y = "Age",
       title = "Age (self-report, sex-combined, uncleaned)",
       subtitle = paste("Dashed line represents mean and dotted lines represent ± 1 standard deviation\n",
                        "n = ", sum(!is.na(DEM.items.plot$age.unc)),
                        "; NA = ", sum(is.na(DEM.items.plot$age.unc)),
                        "; n(total) = ", length(DEM.items.plot$age.unc), sep = ""),       
       color = "black") +
  theme(panel.grid.major.y = element_line(size = 0.5,
                                        linetype = 'dashed',
                                        colour = "gray"),
        axis.title.y = element_blank(),
        axis.text.x = element_text(colour="black", size = 12),
        axis.text.y = element_text(colour="black", size = 12),
        axis.ticks.x = element_blank(),
        axis.ticks.y = element_blank(),
        panel.background = element_blank()) +
  geom_hline(data = DEM.items.plot, aes(yintercept = mean(age.unc, na.rm = T)), size = 0.5, linetype = "dashed") +
  geom_hline(data = DEM.items.plot, aes(yintercept = mean(age.unc, na.rm = T) + sd(age.unc, na.rm = T)), size = 0.5, linetype = "dotted") +
  geom_hline(data = DEM.items.plot, aes(yintercept = mean(age.unc, na.rm = T) - sd(age.unc, na.rm = T)), size = 0.5, linetype = "dotted")

```

```{r set Age limits}

# Set upper limit for age (no lower limit, as all are >= 16)

age.m_upper = 100

# Check how many participants have outlier values in height

age.n_upper <- which(DEM.items$age.unc > age.m_upper)

length(age.n_upper)

```

```{r remove Age outliers}

if(length(age.n_upper)>0){
  
# Remove outliers

DEM.items$age <- with(data = DEM.items, ifelse(age.unc > age.m_upper, NA, age.unc))

# Overwrite dataset with clean data, make col names unique for plotting
DEM.items.plot <- DEM.items
colnames(DEM.items.plot) <- make.unique(names(DEM.items.plot))

# Point plot without outliers

ggplot(data = subset(DEM.items.plot, !is.na(age)),
       aes(x = seq_along(age), y = age)) +
       geom_point(color="grey") +
  labs(x = "Index",
       y = "Age",
       title = "Age (self-report, sex-combined, cleaned)",
       subtitle = paste("Dashed line represents mean and dotted lines represent ± 1 standard deviation\n",
                        "n = ", sum(!is.na(DEM.items.plot$age)),
                        "; NA = ", sum(is.na(DEM.items.plot$age)),
                        "; n(total) = ", length(DEM.items.plot$age),
                        "; n(outlier) removed = ", length(age.n_upper), sep = ""),
       color = "black") +
  theme(panel.grid.major.y = element_line(size = 0.5,
                                        linetype = 'dashed',
                                        colour = "gray"),
        axis.title.y = element_blank(),
        axis.text.x = element_text(colour="black", size = 12),
        axis.text.y = element_text(colour="black", size = 12),
        axis.ticks.x = element_blank(),
        axis.ticks.y = element_blank(),
        panel.background = element_blank()) +
  geom_hline(data = DEM.items.plot, aes(yintercept = mean(age, na.rm = T)),
             size = 1, linetype = "dashed", colour = "deepskyblue4") +
  geom_hline(data = DEM.items.plot, aes(yintercept = mean(age, na.rm = T) + sd(age, na.rm = T)),
             size = 1, linetype = "dotted", colour = "deepskyblue3") +
  geom_hline(data = DEM.items.plot, aes(yintercept = mean(age, na.rm = T) - sd(age, na.rm = T)),
             size = 1, linetype = "dotted", colour = "deepskyblue3") +
  geom_hline(data = DEM.items.plot, aes(yintercept = mean(age, na.rm = T) + 3.5*sd(age, na.rm = T)),
             size = 1, linetype = "dotted", colour = "firebrick") +
  geom_hline(data = DEM.items.plot, aes(yintercept = mean(age, na.rm = T) - 3.5*sd(age, na.rm = T)),
             size = 1, linetype = "dotted", colour = "firebrick")
}


```

```{r mean age}
#Get mean of cleaned age variable
mean(DEM.items$age, na.rm = T)

```

# Sex

Sex variable is pre-cleaned. Rename to remove .unc.
```{r rename sex}
DEM.items$sex <- DEM.items$sex.unc
freq(DEM.items$sex)
```

# Highest education

## Highest Education frequencies

First, define highest education:

Proceed along qualifications fields
If field is not blank, take that as highest qual
If field is blank, check next field
If all fields are blank, NA
Assumes Degree > A level > O level > CSE
NVQ and other professional are disregarded

```{r code education as characters}

#Recode as factors to add text, then change class to character
DEM.items$College <- as.character(recode_factor(DEM.items$dem.university_numeric.unc,
                              "1" = "College or university degree",
                              "0" = "No",
                              "-77" = NULL,
                              .missing = NULL))

DEM.items$A_levels <-as.character(recode_factor(DEM.items$dem.alevels_numeric.unc,
                              "1" = "A levels/AS levels or equivalent",
                              "0" = "No",
                              "-77" = NULL,
                              .missing = NULL))

DEM.items$GCSE_edu <- as.character(recode_factor(DEM.items$dem.gcse_numeric.unc,
                                  "1" = "O levels/GCSEs or equivalent",
                                  "0" = "No",
                                  "-77" = NULL,
                                  .missing = NULL))

DEM.items$CSE <- as.character(recode_factor(DEM.items$dem.cse_numeric.unc,
                          "1" = "CSEs or equivalent",
                          "0" = "No",
                          "-77" = NULL,
                          .missing = NULL))

```

```{r define highest education}
DEM.items$Highest.Education<-NA
DEM.items$Highest.Education<-ordered(case_when(DEM.items$College=="College or university degree" ~ DEM.items$College,
                                          DEM.items$A_levels=="A levels/AS levels or equivalent" ~ DEM.items$A_levels,
                                          DEM.items$GCSE_edu == "O levels/GCSEs or equivalent" ~ DEM.items$GCSE_edu,
                                          DEM.items$CSE== "CSEs or equivalent" ~ DEM.items$CSE,
                                          TRUE ~ as.character(NA)),
                                          c("College or university degree","A levels/AS levels or equivalent","O levels/GCSEs or equivalent", "CSEs or equivalent"))

DEM.items$Degree<-ifelse(!is.na(DEM.items$Highest.Education) & DEM.items$Highest.Education == "College or university degree", "Degree", "No degree")

DEM.items$GCSE<-ifelse((!is.na(DEM.items$Highest.Education) & DEM.items$Highest.Education == "CSEs or equivalent") | is.na(DEM.items$Highest.Education), "No GCSE equivalent", "At least GCSE equivalent")

head(DEM.items$Highest.Education)

```


```{r run checks for new variable}
table(DEM.items$Highest.Education, DEM.items$College, useNA = "a")
table(DEM.items$Highest.Education, DEM.items$A_levels, useNA = "a")
table(DEM.items$Highest.Education, DEM.items$GCSE_edu, useNA = "a")
table(DEM.items$Highest.Education, DEM.items$CSE, useNA = "a")
#NVD or HND or NHC or equivalent
table(DEM.items$Highest.Education, DEM.items$dem.NVQ.unc, useNA = "a")
#Other professional qualification
table(DEM.items$Highest.Education, DEM.items$dem.education_other.unc, useNA = "a")
```

```{r higher education freq}
#Get frequencies of higher education
freq(DEM.items$Highest.Education)
```

# Ethnicity

```{r recode ethnicity}
#Recode as factor
DEM.items$Ethnicity <- recode_factor(DEM.items$dem.ethnicity_numeric.unc,
                                "1" = "White",
                                "2" = "Mixed",
                                "3" = "Asian or Asian British",
                                "4" = "Black or Black British",
                                "5" = "Arab",
                                "6" = "Other")
#Get frequencies
freq(DEM.items$Ethnicity)

```

# Employment

```{r recode employment}

DEM.items <- DEM.items %>% 
  mutate(Employment = 
           case_when(
             dem.employment_numeric.unc == 1 ~ "In paid employment or self-employed",
             dem.employment_numeric.unc == 2 ~ "Retired",
             dem.employment_numeric.unc == 3 ~ "Looking after home and/or family",
             dem.employment_numeric.unc == 4 ~ "Unable to work because of sickness or disability",
             dem.employment_numeric.unc == 5 ~ "Unemployed",
             dem.employment_numeric.unc == 6 ~ "Doing unpaid or voluntary work",
             dem.employment_numeric.unc == 7 ~ "Full or part-time student",
             dem.employment_numeric.unc == 8 ~ "Other",
             dem.employment_numeric.unc == -99 | is.na(dem.employment_numeric.unc) ~ NA_character_
           ))
         
DEM.items$Employment <- factor(DEM.items$Employment, ordered = T,
                               levels = c("In paid employment or self-employed","Retired","Looking after home and/or family", "Unable to work because of sickness or disability", "Unemployed", "Doing unpaid or voluntary work", "Full or part-time student", "Other"))
freq(DEM.items$dem.employment.unc)
freq(DEM.items$Employment)
```

# Clean DEM dataset

```{r clean DEM dataframe}
#Rename ID column
DEM.items$ID <- DEM.items$ID.unc

#Select variables
DEM.clean <- DEM.items %>%
  select(ID,
        age,
        sex,
        Highest.Education,
        Ethnicity,
        Employment
        )

#Export into a rds file:
saveRDS(object = DEM.clean, file = paste0(cleaned_path, "DEM_cleaned.rds"))

# Saves the R data including the recoding
#save.image(file = paste0(cleaned_path, "GLAD_DEM_clean.RData")
```