---
title: "DIAGCOMP_sensitivity_specificity"
author: "Molly R. Davies"
date: "30/10/2020"
output: html_document
---

This script runs sensitivity and specificity analyses for single-item and algorithm-based major depression and anxiety disorder diagnoses variables on the GLAD Study data. 

Results are reported in the paper "Comparison of algorithm-based versus single-item phenotyping measures of depression and anxiety disorders in the GLAD Study cohort" - Davies et al (in prep).

Script written by M. R. Davies.
Email:  molly.davies@kcl.ac.uk

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Set up
```{r install packages}

#install.packages("reshape2")
#install.packages("tidyverse")
#install.packages("knitr")
#install.packages("kableExtra")
#install.packages("descr")
#install.packages("caret")
#install.packages("irr")
#install.packages("hablar")
#install.packages("patchwork")
#install.packages("car")
#install.packages("ggpubr")

```

```{r import packages}
library(caret)
library(irr)
library(ggpubr)
library(descr)
library(tidyverse)
```

```{r source file paths}
source("../GLAD_data_path.R")
```

```{r read data}
dat.cc <- read_rds(paste0(cleaned_path, "combined_cleaned.rds"))
```

# Variables
Create new dataset with only crosstab variables of interest
```{r select variables}
cidi <- dat.cc %>%
  select("ID",
         "mhd.MDD_numeric",
         "mhd.GAD_numeric",
         "mhd.specific_phobia_numeric",
         "mhd.social_anxiety_numeric",
         "mhd.panic_attacks_numeric",
         "mhd.panic_disorder_numeric",
         "mhd.agoraphobia_numeric",
         "ClinicianAnyAnx.n",
         "cidid.diagnosis_numeric",
         "cidia.diagnosis_numeric",
         "spec.diagnosis_numeric",
         "socp.diagnosis_numeric",
         "pad.diagnosis_numeric",
         "agp.diagnosis_numeric",
         "LifetimeAnyAnx.n"
         )
```

Ensure that all factor levels are the same for the variables, which is required to conduct the sensitivity/specificity analyses.
```{r create new factor version of variables}

cidi <- cidi %>% 
  mutate(ClinicianMDD.f =
           as.factor(case_when(
             mhd.MDD_numeric == 0 ~ "No diagnosis",
             mhd.MDD_numeric == 1 ~ "Diagnosis"
           )),
         ClinicianGAD.f =
           as.factor(case_when(
             mhd.GAD_numeric == 0 ~ "No diagnosis",
             mhd.GAD_numeric == 1 ~ "Diagnosis"
         )),
         ClinicianSpecPhob.f = 
           as.factor(case_when(
             mhd.specific_phobia_numeric == 0 ~ "No diagnosis",
             mhd.specific_phobia_numeric == 1 ~ "Diagnosis"
           )),
         ClinicianSocialPhob.f = 
           as.factor(case_when(
             mhd.social_anxiety_numeric == 0 ~ "No diagnosis",
             mhd.social_anxiety_numeric == 1 ~ "Diagnosis"
           )),
         ClinicianPanicDis.f = 
           as.factor(case_when(
             mhd.panic_disorder_numeric == 0 ~ "No diagnosis",
             mhd.panic_disorder_numeric == 1 ~ "Diagnosis"
           )),
         ClinicianPanicAttacks.f =
           as.factor(case_when(
             mhd.panic_attacks_numeric == 0 ~ "No diagnosis",
             mhd.panic_attacks_numeric == 1 ~ "Diagnosis"
           )),
         ClinicianAgoraphobia.f = 
           as.factor(case_when(
             mhd.agoraphobia_numeric == 0 ~ "No diagnosis",
             mhd.agoraphobia_numeric == 1 ~ "Diagnosis"
           )),
         ClinicianAnyAnx.f = 
           as.factor(case_when(
             ClinicianAnyAnx.n == 0 ~ "No diagnosis",
             ClinicianAnyAnx.n == 1 ~ "Diagnosis"
           )),
         LifetimeMDD.f =
           as.factor(case_when(
             cidid.diagnosis_numeric == 0 ~ "No diagnosis",
             cidid.diagnosis_numeric == 1 ~ "Diagnosis"
           )),
         LifetimeGAD.f =
           as.factor(case_when(
             cidia.diagnosis_numeric == 0 ~ "No diagnosis",
             cidia.diagnosis_numeric == 1 ~ "Diagnosis"
         )),
         LifetimeSpecPhob.f = 
           as.factor(case_when(
             spec.diagnosis_numeric == 0 ~ "No diagnosis",
             spec.diagnosis_numeric == 1 ~ "Diagnosis"
           )),
         LifetimeSocialPhob.f = 
           as.factor(case_when(
             socp.diagnosis_numeric == 0 ~ "No diagnosis",
             socp.diagnosis_numeric == 1 ~ "Diagnosis"
           )),
         LifetimePanicDis.f = 
           as.factor(case_when(
             pad.diagnosis_numeric == 0 ~ "No diagnosis",
             pad.diagnosis_numeric == 1 ~ "Diagnosis"
           )),
         LifetimeAgoraphobia.f = 
           as.factor(case_when(
             agp.diagnosis_numeric == 0 ~ "No diagnosis",
             agp.diagnosis_numeric == 1 ~ "Diagnosis"
           )),
         LifetimeAnyAnx.f = 
           as.factor(case_when(
             LifetimeAnyAnx.n == 0 ~ "No diagnosis",
             LifetimeAnyAnx.n == 1 ~ "Diagnosis"
           ))
         )
      
```

# Cross Tabulations and Agreement
Run agreement (accuracy), sensitivity, specificity, and Cohen's kappa analyses

## Algorithm-based diagnosis as reference point

Major depressive disorder
```{r MDD SI-AB crosstabs and agreement}
confusionMatrix(cidi$ClinicianMDD.f, 
                cidi$LifetimeMDD.f, 
                positive = "Diagnosis",
                dnn = c("Single-item", "Algorithm-based"))

```

Generalised anxiety disorder
```{r GAD SI-AB crosstabs and agreement}
confusionMatrix(cidi$ClinicianGAD.f, 
                cidi$LifetimeGAD.f, 
                positive = "Diagnosis",
                dnn = c("Single-item", "Algorithm-based"))
```

Specific phobia
```{r Specific phobia SI-AB crosstabs and agreement}
confusionMatrix(cidi$ClinicianSpecPhob.f, 
                cidi$LifetimeSpecPhob.f, 
                positive = "Diagnosis",
                dnn = c("Single-item", "Algorithm-based"))

```

Social anxiety disorder
```{r Social anxiety disorder SI-AB crosstabs and agreement}
confusionMatrix(cidi$ClinicianSocialPhob.f, 
                cidi$LifetimeSocialPhob.f, 
                positive = "Diagnosis",
                dnn = c("Single-item", "Algorithm-based"))

```

Panic attacks
```{r Panic disorder SI-AB crosstabs and agreement}
confusionMatrix(cidi$ClinicianPanicDis.f, 
                cidi$LifetimePanicDis.f, 
                positive = "Diagnosis",
                dnn = c("Single-item", "Algorithm-based"))

```

Panic attacks
The single-item panic attack variable here is being compared to lifetime panic disorder.
```{r Panic Attacks SI-AB crosstabs and agreement for Panic Disorder}
confusionMatrix(cidi$ClinicianPanicAttacks.f, 
                cidi$LifetimePanicDis.f, 
                positive = "Diagnosis",
                dnn = c("Single-item", "Algorithm-based"))

```

Agoraphobia
```{r Agoraphobia SI-AB crosstabs and agreement}
confusionMatrix(cidi$ClinicianAgoraphobia.f, 
                cidi$LifetimeAgoraphobia.f, 
                positive = "Diagnosis",
                dnn = c("Single-item", "Algorithm-based"))

```

Any anxiety
```{r Any Anxiety SI-AB crosstabs and agreement}
confusionMatrix(cidi$ClinicianAnyAnx.f, 
                cidi$LifetimeAnyAnx.f, 
                positive = "Diagnosis",
                dnn = c("Single-item", "Algorithm-based"))

```


##Single-item diagnosis as reference point

Major depressive disorder
```{r MDD AB-SI crosstabs and agreement}
confusionMatrix(cidi$LifetimeMDD.f,
                cidi$ClinicianMDD.f, 
                positive = "Diagnosis",
                dnn = c("Algorithm-based", "Single-item"))
```

Generalised anxiety disorder
```{r GAD AB-SI crosstabs and agreement}
confusionMatrix(cidi$LifetimeGAD.f,
                cidi$ClinicianGAD.f, 
                positive = "Diagnosis",
                dnn = c("Algorithm-based", "Single-item"))

```

Specific phobia
```{r Specific phobia AB-SI crosstabs and agreement}
confusionMatrix(cidi$LifetimeSpecPhob.f,
                cidi$ClinicianSpecPhob.f, 
                positive = "Diagnosis",
                dnn = c("Algorithm-based", "Single-item"))

```

Social anxiety disorder
```{r Social anxiety disorder AB-SI crosstabs and agreement}
confusionMatrix(cidi$LifetimeSocialPhob.f,
                cidi$ClinicianSocialPhob.f, 
                positive = "Diagnosis",
                dnn = c("Algorithm-based", "Single-item"))

```

Panic disorder
```{r Panic disorder AB-SI crosstabs and agreement}
confusionMatrix(cidi$LifetimePanicDis.f,
                cidi$ClinicianPanicDis.f, 
                positive = "Diagnosis",
                dnn = c("Algorithm-based", "Single-item"))
```

Panic attacks
Algorithm-based panic disorder is being compared with single-item panic attacks.
```{r Panic Attacks AB-SI crosstabs and agreement with Panic Disorder, echo=FALSE}
confusionMatrix(cidi$LifetimePanicDis.f, 
                cidi$ClinicianPanicAttacks.f, 
                positive = "Diagnosis",
                dnn = c("Algorithm-based", "Single-item"))


```

Agoraphobia
```{r Agoraphobia AB-SI crosstabs and agreement}
confusionMatrix(cidi$LifetimeAgoraphobia.f, 
                cidi$ClinicianAgoraphobia.f, 
                positive = "Diagnosis",
                dnn = c("Algorithm-based", "Single-item"))

```

Any anxiety
```{r Any Anxiety AB-SI crosstabs and agreement}
confusionMatrix(cidi$LifetimeAnyAnx.f,
                cidi$ClinicianAnyAnx.f, 
                positive = "Diagnosis",
                dnn = c("Algorithm-based", "Single-item"))

```

