---
title: "DIAGCOMP_merging_script: Data freeze 1.0"
author: "Molly R. Davies"
date: "18/10/2020"
output: html_document
---

This script merges cleaned datasets for the purpose of analyses included in the paper titled "Comparison of algorithm-based versus single-item phenotyping measures of depression and anxiety disorders in the GLAD Study cohort" - Davies et al (in prep).

Script written by M. R. Davies.
Email:  molly.davies@kcl.ac.uk

All scripts for the paper can be accessed at:
https://github.com/mollyrdavies/GLAD-Diagnostic-algorithms.git

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#Set up
```{r Setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      comment=NA,
                      prompt=FALSE,
                      cache=FALSE)


options(bitmapType = 'quartz') # to render fonts better
```

Clear global environment
```{r Clear global environment}
remove(list = ls())
```

Retrieve the current date to use it for file endings to not overwrite files when one exports files
```{r Recent date}
date = Sys.Date()
```


Load packages
```{r load packages}
library(tidyverse)
library(skimr)
```

# Read data

```{r source path for reading/saving data}
#Source raw data directory (raw_path) & clean data export directory (cleaned_path)
source("../../DF1.0_data_path.R")
```

```{r set paths}
#Names
dem_name <- "DEM_cleaned.rds"
mhd_name <- "MHD_cleaned.rds"
CIDID_name <- "CIDID_cleaned.rds"
CIDIA_name <- "CIDIA_cleaned.rds"
SPEC_name <- "SPEC_cleaned.rds"
SOCP_name <- "SOCP_cleaned.rds"
PAD_name <- "PAD_cleaned.rds"
AGP_name <- "AGP_cleaned.rds"

#Files
dem_filename <- paste(cleaned_path, dem_name, sep = "")
mhd_filename <- paste(cleaned_path, mhd_name, sep = "")
CIDID_filename <- paste(cleaned_path, CIDID_name, sep = "")
CIDIA_filename <- paste(cleaned_path, CIDIA_name, sep = "")
SPEC_filename <- paste(cleaned_path, SPEC_name, sep = "")
SOCP_filename <- paste(cleaned_path, SOCP_name, sep = "")
PAD_filename <- paste(cleaned_path, PAD_name, sep = "")
AGP_filename <- paste(cleaned_path, AGP_name, sep = "")

```

# Import data
```{r import data}
dem <- read_rds(dem_filename)
dim(dem)

mhd <- read_rds(mhd_filename)
dim(mhd)

CIDID <- read_rds(CIDID_filename)
dim(CIDID)

CIDIA <- read_rds(CIDIA_filename)
dim(CIDIA)

SPEC <- read_rds(SPEC_filename)
dim(SPEC)

SOCP <- read_rds(SOCP_filename)
dim(SOCP)

PAD <- read_rds(PAD_filename)
dim(PAD)

AGP <- read_rds(AGP_filename)
dim(AGP)
```

```{r check IDs match across datasets}
#COPING NBR sample have 2 surveys being merged: 
#DEM, CIDID, and CIDIA are part of COPING baseline; SPEC, SOCP, PAD, and AGP are optional questionnaires
DEM_NBR <- dem %>% 
  filter(sample == "NBR")
SPEC_NBR <- SPEC %>% 
  filter(sample == "NBR")
x <- DEM_NBR[DEM_NBR$ID %in% SPEC_NBR$ID,]

length(DEM_NBR$ID)
length(SPEC_NBR$ID)
length(x$ID)
head(DEM_NBR$ID)
head(SPEC_NBR)
```

```{r drop startDate and endDate columns from all datasets except DEM}
MHD_nodate <- subset(mhd, select = -c(startDate, endDate, externalDataReference))
CIDID_nodate <- subset(CIDID, select = -c(startDate, endDate))
CIDIA_nodate <- subset(CIDIA, select = -c(startDate, endDate))
SPEC_nodate <- subset(SPEC, select = -c(startDate, endDate, COPING_ID))
SOCP_nodate <- subset(SOCP, select = -c(startDate, endDate, COPING_ID))
PAD_nodate <- subset(PAD, select = -c(startDate, endDate, COPING_ID))
AGP_nodate <- subset(AGP, select = -c(startDate, endDate, COPING_ID))
```

Merge the datasets by ID.
```{r merge datasets}
dat <- list(
            dem,
            MHD_nodate,
            CIDID_nodate,
            CIDIA_nodate,
            SPEC_nodate, 
            SOCP_nodate,
            PAD_nodate,
            AGP_nodate
            ) %>% 
  reduce(left_join, by = c("ID", "sample"))
```

```{r check merge worked as expected}
#Check that the NAs for a diagnosis remain the same in the combined datasets (there will be more NAs for NBR SPEC because the questionnaire was optional)
sum(ifelse(SPEC$sample == "NBR" & is.na(SPEC$spec.diagnosis), 1, 0))
sum(ifelse(dat$sample == "NBR" & is.na(dat$spec.diagnosis), 1, 0))
sum(ifelse(SPEC$sample == "GLAD" & is.na(SPEC$spec.diagnosis), 1, 0))
sum(ifelse(dat$sample == "GLAD" & is.na(dat$spec.diagnosis), 1, 0))

#Check for PAD (waiting for updated SPEC dataset)
sum(ifelse(PAD$sample == "NBR" & is.na(PAD$pad.diagnosis), 1, 0))
sum(ifelse(dat$sample == "NBR" & is.na(dat$pad.diagnosis), 1, 0))
sum(ifelse(PAD$sample == "GLAD" & is.na(PAD$pad.diagnosis), 1, 0))
sum(ifelse(dat$sample == "GLAD" & is.na(dat$pad.diagnosis), 1, 0))

#Check that the NAs for one of the demographics variables remain the same in the combined datasets
sum(ifelse(dem$sample == "NBR" & is.na(dem$Highest.Education), 1, 0))
sum(ifelse(dat$sample == "NBR" & is.na(dat$Highest.Education), 1, 0))
sum(ifelse(dem$sample == "GLAD" & is.na(dem$Highest.Education), 1, 0))
sum(ifelse(dat$sample == "GLAD" & is.na(dat$Highest.Education), 1, 0))

sum(ifelse(dem$sample == "NBR" & is.na(dem$age), 1, 0))
sum(ifelse(dat$sample == "NBR" & is.na(dat$age), 1, 0))
sum(ifelse(dem$sample == "GLAD" & is.na(dem$age), 1, 0))
sum(ifelse(dat$sample == "GLAD" & is.na(dat$age), 1, 0))
```


```{r Skim data}
#look at the data
skimr::skim(dat)
```

```{r Save combined dataset as rds file}
saveRDS(object = dat, file = paste0(cleaned_path, "combined_cleaned.rds"))
```

