---
title: "DIAGCOMP_MHD_cleaning"
author: "Molly R. Davies"
date: "30/10/2020"
output: html_document
---

This is the script to clean the mental health diagnoses (MHD) variables of the GLAD Study data for the paper "Comparison of algorithm-based versus single-item phenotyping measures of depression and anxiety disorders in the GLAD Study cohort" - Davies et al (in prep).

The MHD dataset includes all single-item diagnoses.

Script written by M. R. Davies.
Email:  molly.davies@kcl.ac.uk

All scripts for the paper can be accessed at:
https://github.com/mollyrdavies/GLAD-Diagnostic-algorithms.git

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Set up

Clear workspace
```{r clear workspace}
rm(list = ls())
```

```{r load packages}
library(tidyverse)
library(psych)
library(summarytools)
```

# Load data

```{r source path for reading/saving data}
#Source raw data directory (raw_path) & clean data export directory (cleaned_path)
source("../GLAD_data_path.R")
```

```{r read in MHD data}
MHD_file <- paste(raw_path, "MHD.rds", sep = "")

MHD.cc <- read_rds(MHD_file)

#Visualise
head(MHD.cc)
```

# Clean data

```{r select MHD variables}
#Select variables
MHD.items <- MHD.cc %>%
  select(ID,
        mhd.MDD,
        mhd.PMDD,
        mhd.bipolar,
        mhd.GAD,
        mhd.specific_phobia,
        mhd.social_anxiety,
        mhd.panic_attacks,
        mhd.panic_disorder,
        mhd.agoraphobia,
        mhd.MDD_numeric,
        mhd.PMDD_numeric,
        mhd.bipolar_numeric,
        mhd.GAD_numeric,
        mhd.specific_phobia_numeric,
        mhd.social_anxiety_numeric,
        mhd.panic_attacks_numeric,
        mhd.panic_disorder_numeric,
        mhd.agoraphobia_numeric
        )
```

```{r recode as NAs}
#Change all prefer not to answers and don't knows to NA
MHD.items[MHD.items == -77] <- NA
MHD.items[MHD.items == -88] <- NA
MHD.items[MHD.items == -99] <- NA
MHD.items[MHD.items == "Don't know"] <- NA
MHD.items[MHD.items == "Prefer not to answer"] <- NA
MHD.items[MHD.items == "Seen but not answered"] <- NA
```

# Export clean dataset

```{r select MHD variables}
#Select variables
MHD.clean <- MHD.items %>%
  select(ID,
        mhd.MDD,
        mhd.PMDD,
        mhd.bipolar,
        mhd.GAD,
        mhd.specific_phobia,
        mhd.social_anxiety,
        mhd.panic_attacks,
        mhd.panic_disorder,
        mhd.agoraphobia,
        mhd.MDD_numeric,
        mhd.PMDD_numeric,
        mhd.bipolar_numeric,
        mhd.GAD_numeric,
        mhd.specific_phobia_numeric,
        mhd.social_anxiety_numeric,
        mhd.panic_attacks_numeric,
        mhd.panic_disorder_numeric,
        mhd.agoraphobia_numeric
        )

#Export into a rds file:
saveRDS(object = MHD.clean, file = paste0(cleaned_path, "MHD_cleaned.rds"))

# Saves the R data including the recoding
#save.image(file = paste0(cleaned_path, "GLAD_MHD_clean.RData")
```